### 2021-01-18 abstract.tex
initial commit

\begin{abstract}
Due to the popularization of Android and the full range of applications (apps) targeting this platform, many security issues have emerged, attracting researchers and practitioners' attention. As such, many techniques for addressing security Android issues appeared, including approaches for mining sandboxes. Previous research studies have compared Android test case generation tools for this specific goal. Our research aims to explore new techniques for mining sandboxes, especially we are interested in understanding the limits of both static and dynamic analysis in this process. Although the use of test generation tools for mining sandboxes has been explored before, the potential to combine static analysis and dynamic analysis has not been sufficiently investigated yet. That is, in this paper, we will investigate the hypothesis that combining static and dynamic analysis techniques increases the process of mining Android sandboxes. To understand the bound of this combination, we conducted a non-exact replication of a previous study to detect what is the role of each of these analyses in malware detection using mining sandboxes. Like the original studies, we used DroidFax, a tool that instruments Android apps and collects relevant information about their execution (using the test case generation tools). DroidFax also executes static analysis that collects code coverage information and a set of sensitive APIs used by a given app during test execution. Our results demonstrate that analysis static has an important contribution to the mining sandboxes process, and his combination with dynamic analysis has the potential to improve malware detection techniques.

\end{abstract}

\begin{IEEEkeywords}
Malware Detection,
Mining Sandboxes,
Software Security,
Android Platform,
Empirical Studies,
Static Analysis and Dynamic Analysis
\end{IEEEkeywords}

### 2021-01-18 benchmark.tex
initial commit

\section{The Benchmark - droidXP}

\begin{figure*}[ht]
  \includegraphics[width=1\textwidth]{images/benchmark3.png}
  \label{benchArq}
  \caption{Benchmark architecture}
  \label{fig:benchArq}
\end{figure*}

To systematically assess and compare test generation tools for mining android sandboxes, we use a benchmark solution, called DroidXP. It relies on a simple \emph{Command Line Interface} (CLI) that favors the execution and configuration of the benchmark. It also
relies on DroidFax \cite{cai2016understanding}, a tools that instruments Android apps and collects relevant information about their execution, like the set of sensitive APIs a given
app calls during a test execution. DroidFax also collects inter-component communication (ICC)  intent  tracing  using  static  program analysis.

The droidXP CLI provides two commands: a command that lists all test case
generation tools (executing the project with the option ``list-tools'') that had been
integrated into the benchmark; and a command that performs the execution of the benchmark,
which can be configured using the following parameters:

\begin{itemize}
    \item \texttt{-tools}: Specifies the test tools used in the experiment
    \item \texttt{-t}: Specifies the threshold (in seconds) for the execution time in the experiment
    \item \texttt{-r}: Specifies the number of repetitions used in the experiment
    \item \texttt{-output-format}: Specifies the output format
    \item \texttt{--debug}: Specifies to run in DEBUG mode (default: false)    
\end{itemize}

The droidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
and includes three main components; where each component is responsible for a specific phase of the
benchmark (instrumentation, execution, and result analysis).

\subsection{Phase 1: Instrumentation}

In the first phase, a researcher must define the corpus of APK files droidXP
should consider during a benchmark execution. After that, droidXP starts the DroidFax service that instruments each APK file, so that droidXP would be able to collect data about each execution. To improve the performance of the benchmark, the instrumentation phase runs only once for each APK. In this phase, the DroidFax tool also runs some static analysis procedures, to collect the number of methods and classes of each app, which is a necessary information to estimate code coverage.

\subsection{Phase 2: Execution}

In this phase, droidXP installs an (already instrumented) APK file into
an Android emulator, and then executes a test case generation tool
during a period of time. This process repeats for every test case generation
tool and APK files. To provide repeatability of the experiment,
droidXP removes all data stored in the emulator before starting
a new execution. That is, every execution uses a \emph{fresh} emulator,
without any information that might have been kept during
previous executions.

The benchmark is relatively easy to add new test
case generation tools. To achieve this goal, it leverage the
Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into droidXP. Listing \ref{lst:toolspec} shows the contract a developer must override to integrate a new tool. According to this contract, one have to: (a) implement a class that inherits from \texttt{ToolSpec}, define constructors that calls the \texttt{super} constructor, passing the name, the description, and the process id as arguments, and (c) implement the \texttt{execute} method, which receives as argument the path of an APK file and a timeout.

%\begin{lstlisting}[caption=ToolSpec Sample, language=Python, label={lst:toolspec}, basicstyle=\tiny]
\begin{lstlisting}[caption=ToolSpec Sample,label={lst:toolspec}]
class ToolSpec(AbstractTool):
  def __init__(self):
    super(ToolSpec, self).__init__(
      "Test Generator Name", 
      "Test Generator Description", 
      "process_id"
    )

  def execute(self, path, timeout):
    # Execute test generator ...
\end{lstlisting}

The benchmark uses the last parameter to kill the execution process
on the emulator after a \emph{timeout event} throws.
This step is necessary to provide a fresh environment
for the next test execution. The actual logic for executing a
specific tool resides in the  \texttt{execute} method,
so it is the responsibility of a developer to
set up all configuration necessary to run a specific
test case generation tool. To performance our study replication we integrated successfully 
the following tools into droidXP.

\begin{enumerate}[(a)]
  \item {\bf Monkey} is a Google testing utility that generates
    pseudo-random streams of user events. 
    \item {\bf DroidBot}  is a test input generator for
       Android, which sends random or scripted input events~\cite{li2017droidbot}. 
    \item {\bf DroidMate} is an automated execution generator /
      dynamic analysis engine for Android apps\cite{jamrozik2016droidmate}. 
      generation for Android~\cite{mao2016sapienz}. 
    \item {\bf Humanoid} is a tool that uses deep learning techniques to explore Android apps, mimicking the human behavior\cite{li2019deep}; 
    \item {\bf Joke} is a make-believe tool that perform no analysis dynamic, and execute just the static analysis from droifax. More detail about this fake tool will be discussed in the next section; 
\end{enumerate}

\subsection{Phase 3: Result Analysis}

During the execution, all the data that is required to compute the results are provided by Logcat \cite{Logcat}, one of the Android SDK's native tools and is a command-line tool that dumps a log from the Android emulator. Thus, the only part of the log that is analyzed in this phase is the messages sent by the methods inside the Android app that were instrumented on the first phase using the DroidFax tool.

Droidfax computes the coverage each test achieved and which sensitive API was accessed during the execution of that test. That last information is required to compute the test generator performance in identifying malicious apps by spotting differences between the sensitive API accessed by each version of an app. This information is vital to the measurement of the test generator performance and qualification. After this phase, the benchmark outputs the results of the experiment, which is informing the performance of one or more testing generator tools in mining sandboxes.

### 2021-01-18 introduction.tex
initial commit

\section{Introduction}

The use of mobile devices such as smartphones and tablets continues increasing its importance in our daily lives. It is estimated that two-thirds of people on the planet use mobile technologies \cite{Comscore}, and in this context, Android Operating System has dominated this marketplace of smartphones, tablets, and others electronic devices. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}. Security issues in application consumption (commonly known as "apps") have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}. Currently, researchers have explored the use of dynamic analysis tools and test case generators to mine sandboxes, whose goal is to protect Android users from malicious behaviors \cite{jamrozik2016mining}.

The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using automated tools for testing. These tools, explore apps behaviors based on their sensitive APIs. A sandbox builds upon the calls to sensitive Android APIs, during the execution of test cases (exploratory phase). The sandbox could then block future calls to other sensitive resources, which diverge from those found in the exploratory phase. Using this approach, the sandbox accuracy depends on the exploratory power of each testing tool used to compose the sandbox rules.

Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes. For instance, Bao et al. \cite{bao2018mining} present the results of an empirical study comparing 5 automated testing tools: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. The study measured the efficiency of each tool, as well as if the combination of one or more of them could lead to performance improvements. That research work consisted of performing experiments in pairs of apps, one benign and one malign that piggybacks the corresponding benign app, leading to malicious behavior. The dataset used comprised of 102 pairs of benign and malign apps (B/M). This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in this dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior. Nonetheless, the field of automatic test generation of mobile apps is everything but listless---many promising automatic test generation tools have been recently proposed
~\cite{cai2020longitudinal,li2019deep}, which might outperform previous tools that have been used to mine sandboxes.

Jamrozik et al. \cite{jamrozik2016mining} discuss that dynamic analysis exceeds static analysis on mining Android sandboxes domain, although your point of view has not been validated empirically, and there was no effective discussion about the possibility of combination of both proposals, even though in some preliminary results, we found that some analysis static algorithms can complements analysis dynamic performance in mining sandbox task.

In this paper, we further dig into the role of static analysis order for malware detecting. Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes. To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called DroidXP \cite{dadroidxp}, whose main objective is  assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes. Our study differs from the original in the following aspects. First, we refined the dataset used, analyzing 96 pairs of apps (B/M). Second, we introduced in our study, two recent tools that were not considered in the previous work. Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.

Thus, this paper contributes to comprehend the role of each of the analyzes in the malware detection task by:

\begin{enumerate}[(1)]
 \item presenting a non-exact replication of the study of the efficiency of test generation tools for mining android sandboxes, using a benchmark solution developed for this specific purpose.

 \item discovering which are the contribution installments of types of analysis for malware detection task.

 \item presenting which are malware characteristics, that was not detected by any tool in our analysis dynamic and static experiment.

 \item presenting data that indicate that static analysis can improve the mining sandboxes process for malware detection.
 \end{enumerate}

We organize the remainder of this paper as follows. Section 2 describes all the apps malware used in our experiment, presenting their characterization. Section 3 introduces the benchmark solution used to replicate the study presented in this paper. Section 4 describes the original experiment, its replication, and its results as well. Section 5 highlights some motivation malware example, discovered in our research, and its attack strategy. In section 6 we present the use of a promising static analysis tool, in our motivation example. Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

%% Our objective is to assist researchers and practitioners in reproducing research studies in this field. Altogether, the main contribution of \droidxp  is to facilitate the reproduction of empirical studies, and allowing
%% researchers to integrate test case generation tools ratify.}

### 2021-01-18 setup.tex
initial commit

\section{Experimental Setup}
\begin{figure*}[h!]
  \includegraphics[width=0.5\textwidth]{images/setup.png}
  \label{Experiment setup}
  \caption{Experiment setup}
  \label{fig:setup}
\end{figure*}

To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox. Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app. (Figure  \ref{fig:setup}) show all the experimental setup.

\subsection{Experiment motivation}

As described

### 2021-01-20 introduction.tex
integrating Handrick updates

@@
 The study measured the efficiency of each tool, as well as if the combination of one or more of them could lead to performance improvements.
-That research work consisted of performing experiments in pairs of apps, one benign and one malign that piggybacks the corresponding benign app, leading to malicious behavior.
-The dataset used comprised of 102 pairs of benign and malign apps (B/M).
-This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in this dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior.
+That research work consisted of performing experiments in pairs of apps, one benign and one malign (B/M), that piggybacks the corresponding benign app, leading to malicious behavior.
+This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior.
 Nonetheless, the field of automatic test generation of mobile apps is everything but listless---many promising automatic test generation tools have been recently proposed
@@
 Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes.
-To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called DroidXP \cite{dadroidxp}, whose main objective is  assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes.
+To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called droidXP \cite{dadroidxp}, whose main objective is  assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes.
 Our study differs from the original in the following aspects.
-First, we refined the dataset used, analyzing 96 pairs of apps (B/M).
-Second, we introduced in our study, two recent tools that were not considered in the previous work.
+First, we refined the dataset used, and executed the analysis of each apps, for a time biggest than the original experiment.
+Second, we introduced in our study, two tools that were not considered in the previous work.
 Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.
@@
 Section 2 describes all the apps malware used in our experiment, presenting their characterization.
-Section 3 introduces the benchmark solution used to replicate the study presented in this paper.
-Section 4 describes the original experiment, its replication, and its results as well.
-Section 5 highlights some motivation malware example, discovered in our research, and its attack strategy.
-In section 6 we present the use of a promising static analysis tool, in our motivation example.
+Section 3 introduces the study setting of our research.
+Section 4 describes the benchmark solution used in our experiment.
+Section 5 presented some results, highlighting some motivation malware example, which will be described at Section 6.
+Section 7 we present the use of a promising static analysis tool, in our motivation example.
 Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-01-20 setup.tex
Just a review of the study settings organization.
integrating Handrick updates

@@
-\section{Experimental Setup}
+\section{Study Settings}
+
+Before the conception of droidXP, there were studies that provided valuable information about the comparison between test generation tools \cite{bao2018mining}\cite{hao2014puma}.
+This data was required to measure the benchmark droidXP's performance and precision.
+Particularly, L Bao et al.
+\cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques, and that inspired our study settings.
+His first experiment used a small set of apps (10 pairs B/M) to be run for different periods of time to compare how much time the tools needed to achieve the maximum coverage possible and to identify the sensitive APIs accessed.
+This study showed that the coverage and accuracy of the testing tool have a negative correlation.
+That is, improving the performance of code coverage might not directly contribute to the performance of detecting malware.
+The second experiment used a set of 102 pairs of apps that were executed for just one minute.
+The goal of this experiment was to compare a bigger number of apps and the number of sensitive APIs accessed by each tool in a small time.
+However, this study did not focus on the possible interference of the DroidFax \cite{cai2017droidfax} tool on the benchmark results.
+The benchmark uses DroidFax to analyze Android apps during execution, but this tool also performs a static analysis of the apps.
+
+The first empirical study had shown useful aspects of the tools while being executed by the benchmark droidXP.
+To replicate the previous studies, we choice a subset of pairs (B/M), based on the set of pairs presented by L Bao et al.
+The addition of Humanoid and the fake tools, "Joke", in the comparison brought newer techniques that explored Android apps better.
+
+Hence, the main goal of this research work is
+to understand the influence of the static analysis, which is performed by DroidFax, in the benchmark execution. To achieve this general goal, we answer the following research questions.
+
+\begin{enumerate}[(RQ1)]
+\item What is the effective performance of each tool in terms of the number of detected malware ?
+\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
+\item What is the impact of DroidFax’s static analysis on benchmark results ?
+\end{enumerate}
+
+In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes.
+At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax.
+So, we used this experiment to answer the first research questions (RQ1).
+In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence.
+With these results, we can answer the last two research question (RQ2 and RQ3).
+
+\subsection{Settings for RQ1}
+
+To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
+Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
+(Figure  \ref{fig:setup}) show all this experimental setup.
+
+\subsection{Settings for RQ2 and RQ3}
+
 \begin{figure*}[h!]
@@
 
-To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
-Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
-(Figure  \ref{fig:setup}) show all the experimental setup.
-
 \subsection{Experiment motivation}

### 2021-01-25 background.tex
add background section , revised introduction, begin of restructuring

\section{Background and related works}

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device. It also guarantee an on-biased testing environment, ensuring the same pre-configured beginning status of the environment.

In this sandbox context, the Android Mining Sandbox concept emerges as a technique that consists of extract rules from android app, and use these rules to ensure system security. The technique performs two steps. First, rules are mined and will compose the sandbox, through test generator tools. These tools explore program behavior and monitor access to sensitive APIs. In a second stage, it is taken into account that resources not accessed, or accessed differently, at first stage, must be denied access. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

The idea of mine automatically software resources or components, to inferring behavior is not new, and has been discussed before. For instance, Whaley et al. \cite{whaley2002automatic} combine dynamic and static analysis to API mining and so extract interface from software components. Ammons et al \cite{ammons2002mining} propose a machine learning
approach, called specification mining, to discovering some temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.

Regarding test generating tools used to mining Sandboxes, Jamrozik et al \cite{jamrozik2016droidmate} proposed DroidMate, a test generation tools that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps. Li e tal. proposed in \cite{li2017droidbot}, DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy. In this paper, the authors presented comparison between DroidBot and Monkey \cite{Monkey} in a proof of concept example of using DroidBot in malware analysis. From the same authors, another test generator tool for Android, described as Humanoid \cite{humanoid-paper}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.

Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes. For instance. For example, L Bao et al. \cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. His first experiment used a small set of apps (10 pairs B/M) to be run for different periods to compare how much time the tools needed to achieve the maximum coverage possible and to identify the sensitive APIs accessed. This study showed that the coverage and accuracy of the testing tool have a negative correlation. That is, improving the performance of code coverage might not directly contribute to the performance of detecting malware. The second experiment used a set of 102 pairs of apps that were executed for just one minute. The goal of this experiment was to compare a bigger number of apps and the number of sensitive APIs accessed by each tool in a small time.

### 2021-01-25 introduction.tex
add background section , revised introduction, begin of restructuring

@@
 
-Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes.
-For instance, Bao et al.
-\cite{bao2018mining} present the results of an empirical study comparing 5 automated testing tools: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}.
-The study measured the efficiency of each tool, as well as if the combination of one or more of them could lead to performance improvements.
-That research work consisted of performing experiments in pairs of apps, one benign and one malign (B/M), that piggybacks the corresponding benign app, leading to malicious behavior.
-This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior.
-Nonetheless, the field of automatic test generation of mobile apps is everything but listless---many promising automatic test generation tools have been recently proposed
-~\cite{cai2020longitudinal,li2019deep}, which might outperform previous tools that have been used to mine sandboxes.
+Previous research studies \cite{bao2018mining} have investigated the effectiveness of mining sandboxes, using automated testing tools, comparing the performance of each tool to mine sandboxes, as well as if the combination of one or more of them could lead to performance improvements.
+This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.
 
@@
 
-In this paper, we further dig into the role of static analysis order for malware detecting.
+Hence, in this paper we further dig into the role of static analysis order for malware detecting.
 Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes.
@@
 
-Thus, this paper contributes to comprehend the role of each of the analyzes in the malware detection task by:
+Altogether, this paper contributes to comprehend the role of each of the analyzes in the malware detection task by:
 
@@
 We organize the remainder of this paper as follows.
-Section 2 describes all the apps malware used in our experiment, presenting their characterization.
-Section 3 introduces the study setting of our research.
-Section 4 describes the benchmark solution used in our experiment.
-Section 5 presented some results, highlighting some motivation malware example, which will be described at Section 6.
-Section 7 we present the use of a promising static analysis tool, in our motivation example.
+Section 2 we present a background and some related works.
+Section 3 describes all the apps malware used in our experiment, presenting their characterization.
+Section 4 introduces the study setting of our research.
+Section 5 presented some results, highlighting some motivation malware example.
+Section 6 we present the use of a promising static analysis tool, in our motivation example.
 Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-01-25 results.tex
add background section , revised introduction, begin of restructuring

\section{Results and discussion}

%%Here we can write about MOTIVATION EXAMPLES.

### 2021-01-25 setup.tex
add background section , revised introduction, begin of restructuring

--- 2021-01-18 setup.tex
@@
-\section{Experimental Setup}
+\section{Study Settings}
+
+The main goal of this research work is to replicate Bao et al.
+study to understand the implications of static analysis algorithms in his results.
+We also investigate how static analysis can improve the performance of testing tools in the task of identifying malicious behaviors.
+
+To achieve this general goal, we answer the following research questions.
+
+\begin{enumerate}[(RQ1)]
+\item What is the effective performance of each tool in terms of the number of detected malware ?
+\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
+\item What is the impact of static analysis on benchmark results ?
+\end{enumerate}
+
+In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes.
+At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax.
+So, we used this experiment to answer the first research questions (RQ1).
+In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence.
+With these results, we can answer the last two research question (RQ2 and RQ3).
+
+To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
+Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
+(Figure  \ref{fig:setup}) show all this experimental setup.
+
+\subsection{Settings for RQ1}
+
+\subsection{Settings for RQ2 and RQ3}
+
 \begin{figure*}[h!]
@@
 
-To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
-Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
-(Figure  \ref{fig:setup}) show all the experimental setup.
-
-\subsection{Experiment motivation}
-
-As described
+\begin{figure*}[ht]
+  \includegraphics[width=1\textwidth]{images/benchmark3.png}
+  \label{benchArq}
+  \caption{Benchmark architecture}
+  \label{fig:benchArq}
+\end{figure*}

### 2021-01-25 background.tex
first introduction fit

@@
 
-Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes.
-For instance.
-For example, L Bao et al.
+L Bao et al.
 \cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}.
-His first experiment used a small set of apps (10 pairs B/M) to be run for different periods to compare how much time the tools needed to achieve the maximum coverage possible and to identify the sensitive APIs accessed.
-This study showed that the coverage and accuracy of the testing tool have a negative correlation.
-That is, improving the performance of code coverage might not directly contribute to the performance of detecting malware.
-The second experiment used a set of 102 pairs of apps that were executed for just one minute.
-The goal of this experiment was to compare a bigger number of apps and the number of sensitive APIs accessed by each tool in a small time.
+This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.

### 2021-01-25 introduction.tex
first introduction fit

@@
 
-The use of mobile devices such as smartphones and tablets continues increasing its importance in our daily lives.
-It is estimated that two-thirds of people on the planet use mobile technologies \cite{Comscore}, and in this context, Android Operating System has dominated this marketplace of smartphones, tablets, and others electronic devices.
+Almost two-thirds of the world population use mobile technologies \cite{Comscore}, and Android Operating System has dominated this marketplace of smartphones, tablets, and others electronic devices.
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}.
-Security issues in application consumption (commonly known as "apps") have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}.
-Currently, researchers have explored the use of dynamic analysis tools and test case generators to mine sandboxes, whose goal is to protect Android users from malicious behaviors \cite{jamrozik2016mining}.
+Security issues in (commonly known as "apps") have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}.
+For instance, researchers have explored the use of dynamic analysis tools and test case generators to mine sandboxes, whose goal is to protect Android users from malicious behaviors \cite{jamrozik2016mining}.
 
@@
 The sandbox could then block future calls to other sensitive resources, which diverge from those found in the exploratory phase.
-Using this approach, the sandbox accuracy depends on the exploratory power of each testing tool used to compose the sandbox rules.
+Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.
 
-Previous research studies \cite{bao2018mining} have investigated the effectiveness of mining sandboxes, using automated testing tools, comparing the performance of each tool to mine sandboxes, as well as if the combination of one or more of them could lead to performance improvements.
-This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
-However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.
-
-Jamrozik et al.
-\cite{jamrozik2016mining} discuss that dynamic analysis exceeds static analysis on mining Android sandboxes domain, although your point of view has not been validated empirically, and there was no effective discussion about the possibility of combination of both proposals, even though in some preliminary results, we found that some analysis static algorithms can complements analysis dynamic performance in mining sandbox task.
+A previous work has argued in favor of dynamic analysis for mining sandboxes, instead of using static analysis \cite{jamrozik2016mining}.
+The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain.
+However, they do not provide any empirical validation about this claim, and there was no effective discussion about the possibility of combination of both proposals.
+Moreover, Bao et al.
+\cite{bao2018mining} present an empirical study comparing different dynamic analysis tools for mining sandboxes, that leverage DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comparing a benign and a malign version of an App), and collect information needed to mine sandboxes.
+Although the authors report an efficient in identifying 70\% of the malware in this specific dataset, part of this result is due to an internal static analysis algorithm of DroidFax, which might improve the performance of the dynamic analysis tools for mining sandboxes, introducing a possible threat to the work.
 
@@
 Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.
-
-%% Our objective is to assist researchers and practitioners in reproducing research studies in this field.
-Altogether, the main contribution of \droidxp  is to facilitate the reproduction of empirical studies, and allowing
-%% researchers to integrate test case generation tools ratify.}

### 2021-01-25 introduction.tex
first introduction fit

@@
 A previous work has argued in favor of dynamic analysis for mining sandboxes, instead of using static analysis \cite{jamrozik2016mining}.
-The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain.
+The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain because the analysis must often assume that more behaviors are possible than actually would be, and if static analysis determine that some behavior is impossible, this behavior no longer needs to be checked at runtime.
+Thereby, code that is interpreted, decrypted, or downloaded at run time is challenging for static analysis.
 However, they do not provide any empirical validation about this claim, and there was no effective discussion about the possibility of combination of both proposals.

### 2021-01-26 introduction.tex
additional review of the Introduction section

--- 2021-01-25 introduction.tex
@@
 
-Almost two-thirds of the world population use mobile technologies \cite{Comscore}, and Android Operating System has dominated this marketplace of smartphones, tablets, and others electronic devices.
+Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices.
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}.
-Security issues in (commonly known as "apps") have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}.
-For instance, researchers have explored the use of dynamic analysis tools and test case generators to mine sandboxes, whose goal is to protect Android users from malicious behaviors \cite{jamrozik2016mining}.
+Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}, {\color{blue}including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{arzt-pldi-2014} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}}.
+{\color{blue}Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{jamrozik2016mining}.
 
-The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using automated tools for testing.
-These tools, explore apps behaviors based on their sensitive APIs.
-A sandbox builds upon the calls to sensitive Android APIs, during the execution of test cases (exploratory phase).
-The sandbox could then block future calls to other sensitive resources, which diverge from those found in the exploratory phase.
+The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using different approaches for automatically testing Android apps.
+These tools, explore apps behavior and record all calls to sensitive APIs.
+A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase).
+The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase.
 Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.
 
-A previous work has argued in favor of dynamic analysis for mining sandboxes, instead of using static analysis \cite{jamrozik2016mining}.
-The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes domain.
-However, they do not provide any empirical validation about this claim, and there was no effective discussion about the possibility of combination of both proposals.
-Moreover, Bao et al.
-\cite{bao2018mining} present an empirical study comparing different dynamic analysis tools for mining sandboxes, that leverage DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comparing a benign and a malign version of an App), and collect information needed to mine sandboxes.
-Although the authors report an efficient in identifying 70\% of the malware in this specific dataset, part of this result is due to an internal static analysis algorithm of DroidFax, which might improve the performance of the dynamic analysis tools for mining sandboxes, introducing a possible threat to the work.
+Jamrozik et al.~\cite{jamrozik2016mining} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
+The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be.
+Otherwise, static analysis might determine that some behavior is impossible, this behavior no longer needs to be checked at runtime.
+Thereby, code that is interpreted, decrypted, or downloaded at run time is challenging for static analysis---even though these more \emph{dynamic} strategies are often used to introduce malicious behavior.
+Nonetheless, the authors do not give any empirical validation about the limitations of static analysis to mine sandboxes.
+In addition, it is not clear how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
 
-Hence, in this paper we further dig into the role of static analysis order for malware detecting.
-Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes.
-To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called droidXP \cite{dadroidxp}, whose main objective is assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes.
-Our study differs from the original in the following aspects.
-First, we refined the dataset used, and executed the analysis of each apps, for a time biggest than the original experiment.
-Second, we introduced in our study, two tools that were not considered in the previous work.
-Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.
+The same lack of understanding about the role of static analysis also appears in the work of Bao et al.
+\cite{bao2018mining}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
+Their study leverages DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
+Although the authors report a performance of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
 
-Altogether, this paper contributes to comprehend the role of each of the analyzes in the malware detection task by:
+Our goal is to understand how static analysis
+algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
+first, we conduct a non-exact replication of the work of Bao et al.~\cite{bao2018mining}. Our study differs from the original work in two aspects: (a)
+by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
+and (c) by evaluating the performance of DroidMate~\cite{jamrozik2016mining} in its original settings. Considering the other dynamic analysis approaches, which are
+general purpose test case tools for Android, DroidMate has been designed with the goal of mining Android sandboxes---eventhough it has not been tested adequatly
+in the work of Bao et al~\cite{bao2018mining}. In the second study, we explore to what extent we can complement the dynamic analysis approach using
+tainted analysis algorithms.
 
-\begin{enumerate}[(1)]
- \item presenting a non-exact replication of the study of the efficiency of test generation tools for mining android sandboxes, using a benchmark solution developed for this specific purpose.
+Altogether, this paper brings the following contributions:
 
- \item discovering which are the contribution installments of types of analysis for malware detection task.
+\todo[inline]{RB.: Later we can enumerate the paper contributions}
 
- \item presenting which are malware characteristics, that was not detected by any tool in our analysis dynamic and static experiment.
+%% \begin{enumerate}[(1)]
+%%  \item presenting a non-exact replication of the study of the efficiency of test generation tools for mining android sandboxes, using a benchmark solution developed for this specific purpose.
 
- \item presenting data that indicate that static analysis can improve the mining sandboxes process for malware detection.
- \end{enumerate}
+%%  \item discovering which are the contribution installments of types of analysis for malware detection task.
 
-We organize the remainder of this paper as follows.
+%%  \item presenting which are malware characteristics, that was not detected by any tool in our analysis dynamic and static experiment.
+
+%%  \item presenting data that indicate that static analysis can improve the mining sandboxes process for malware detection.
+%%  \end{enumerate}
+
+%% We organize the remainder of this paper as follows.
 Section 2 we present a background and some related works.

### 2021-01-26 introduction.tex
minor

@@
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}.
-Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}, {\color{blue}including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{arzt-pldi-2014} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}}.
-{\color{blue}Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{jamrozik2016mining}.
+Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{arzt-pldi-2014} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}.
+Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes, whose goal is to protect Android users from malicious behavior~\cite{jamrozik2016mining}.
 
@@
 
-\todo[inline]{RB.: Later we can enumerate the paper contributions}
+\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
 

### 2021-01-26 background.tex
update reference and study setting begin

@@
 For instance, Whaley et al.
-\cite{whaley2002automatic} combine dynamic and static analysis to API mining and so extract interface from software components.
-Ammons et al \cite{ammons2002mining} propose a machine learning
+\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis to API mining and so extract interface from software components.
+Ammons et al \cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
 approach, called specification mining, to discovering some temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
 
-Regarding test generating tools used to mining Sandboxes, Jamrozik et al \cite{jamrozik2016droidmate} proposed DroidMate, a test generation tools that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+Regarding test generating tools used to mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tools that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
 Li e tal.
-proposed in \cite{li2017droidbot}, DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
+proposed in \cite{DBLP:conf/icse/LiYGC17}, DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
 In this paper, the authors presented comparison between DroidBot and Monkey \cite{Monkey} in a proof of concept example of using DroidBot in malware analysis.
-From the same authors, another test generator tool for Android, described as Humanoid \cite{humanoid-paper}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
+From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
 
 L Bao et al.
-\cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}.
+\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
 This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
-However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps.

### 2021-01-26 introduction.tex
update reference and study setting begin

@@
 Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices.
-Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}.
-Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{arzt-pldi-2014} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}.
-Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes, whose goal is to protect Android users from malicious behavior~\cite{jamrozik2016mining}.
+Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
+Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}.
+Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
 
@@
 
-Jamrozik et al.~\cite{jamrozik2016mining} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
+Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
 The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be.
@@
 The same lack of understanding about the role of static analysis also appears in the work of Bao et al.
-\cite{bao2018mining}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
-Their study leverages DroidFax \cite{cai2017droidfax} to instrument 102 pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
+\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
+Their study leverages DroidFax \cite{DBLP:conf/icsm/CaiR17a} to instrument 102 pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
 Although the authors report a performance of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
@@
 algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
-first, we conduct a non-exact replication of the work of Bao et al.~\cite{bao2018mining}. Our study differs from the original work in two aspects: (a)
+first, we conduct a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}. Our study differs from the original work in two aspects: (a)
 by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
-and (c) by evaluating the performance of DroidMate~\cite{jamrozik2016mining} in its original settings. Considering the other dynamic analysis approaches, which are
+and (c) by evaluating the performance of DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} in its original settings. Considering the other dynamic analysis approaches, which are
 general purpose test case tools for Android, DroidMate has been designed with the goal of mining Android sandboxes---eventhough it has not been tested adequatly
-in the work of Bao et al~\cite{bao2018mining}. In the second study, we explore to what extent we can complement the dynamic analysis approach using
+in the work of Bao et al~\cite{DBLP:conf/wcre/BaoLL18}. In the second study, we explore to what extent we can complement the dynamic analysis approach using
 tainted analysis algorithms.

### 2021-01-26 setup.tex
update reference and study setting begin

@@
 
-The main goal of this research work is to replicate Bao et al.
-study to understand the implications of static analysis algorithms in his results.
+\begin{figure*}[ht]
+  \includegraphics[width=1\textwidth]{images/benchmark3.png}
+  \label{benchArq}
+  \caption{Benchmark architecture}
+  \label{fig:benchArq}
+\end{figure*}
+
+In this section, we present the setting of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.
+and understand the implications of static analysis algorithms in his results.
 We also investigate how static analysis can improve the performance of testing tools in the task of identifying malicious behaviors.
@@
 
-In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes.
-At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax.
+To assess the effectiveness of mining sandboxes created by each test case generation tools, we used a benchmark solution for test case generation called droidXP \cite{DBLP:conf/scam/CostaMCMVBC20}, that aims us to reproduce previous research work on mining sandboxes.
+(Figure \ref{fig:benchArq}) show all details of the benchmark architecture used at our experiments.
+The benchmark run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
+
+Thereby, to answer the research questions above, we perform two experiments.
+At both we employed the same dataset, 98 pair of real-world apps (B/M), shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} group.
+This time we executed each app in one of the five test generator tool, selected for our experiments, for 3 minutes, and for just one time.
+The droidXP benchmark also relies on DroidFax, the same tool used by Bao et al.
+in your study, that instruments Android apps and collects relevant information about their execution (using the test case generation tools).
+DroidFax collects the set of sensitive APIs during a test execution, and during a static analysis at each code apps.
+Based on this sensitive APIs, that will compose our sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app by the tool under analysis, together with the static analysis of the DroidFax.
+(Figure \ref{fig:setup}) show this experimental setup.
+
+\subsection{First Study: hybrid proposal}
+
+In the first experiment, we executed the benchmark considering the droidXP default configuration, that is, using a hybrid proposal.
+To generate inputs to apps, we investigate five popular test case generation tools, one from industry (Monkey \cite{Monkey}) and four from academia (Droidbot \cite{DBLP:conf/icse/LiYGC17}, Humanoid \cite{DBLP:conf/kbse/LiY0C19}, DroidMate \cite{DBLP:conf/icse/JamrozikZ16} and ``Joke" tool).
+This last is a fake tool that we implemented, which does not do anything during the benchmark execution, and through it we can compute results without the dynamic analysis influence.
 So, we used this experiment to answer the first research questions (RQ1).
-In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence.
-With these results, we can answer the last two research question (RQ2 and RQ3).
 
-To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
-Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
-(Figure  \ref{fig:setup}) show all this experimental setup.
+\subsection{Second Study: Dynamic analysis proposal}
 
-\subsection{Settings for RQ1}
+In this second experiment we used a option of the benchmark that disables the static analysis performed by DroidFax, and with this new configuration, we performed our second study in the same set of apps from the first, at the same execution time, and at the same test case generation tools, including our ``Joke" tool.
+With the results, it was possible to compute what was the aid portion of the static analysis in the malware detection, since the Joke results, was computed without the dynamic analysis influence.
+We used this experiment to answer the research questions (RQ2) and (RQ3).
 
-\subsection{Settings for RQ2 and RQ3}
-
-\begin{figure*}[h!]
+\begin{figure*}[ht]
   \includegraphics[width=0.5\textwidth]{images/setup.png}
@@
 \end{figure*}
-
-\begin{figure*}[ht]
-  \includegraphics[width=1\textwidth]{images/benchmark3.png}
-  \label{benchArq}
-  \caption{Benchmark architecture}
-  \label{fig:benchArq}
-\end{figure*}

### 2021-01-27 setup.tex
study setting first version

--- 2021-01-25 setup.tex
@@
 \section{Study Settings}
-
-The main goal of this research work is to replicate Bao et al.
-study to understand the implications of static analysis algorithms in his results.
-We also investigate how static analysis can improve the performance of testing tools in the task of identifying malicious behaviors.
-
-To achieve this general goal, we answer the following research questions.
-
-\begin{enumerate}[(RQ1)]
-\item What is the effective performance of each tool in terms of the number of detected malware ?
-\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
-\item What is the impact of static analysis on benchmark results ?
-\end{enumerate}
-
-In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes.
-At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax.
-So, we used this experiment to answer the first research questions (RQ1).
-In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence.
-With these results, we can answer the last two research question (RQ2 and RQ3).
-
-To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
-Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
-(Figure  \ref{fig:setup}) show all this experimental setup.
-
-\subsection{Settings for RQ1}
-
-\subsection{Settings for RQ2 and RQ3}
-
-\begin{figure*}[h!]
-  \includegraphics[width=0.5\textwidth]{images/setup.png}
-  \label{Experiment setup}
-  \caption{Experiment setup}
-  \label{fig:setup}
-\end{figure*}
 
@@
 \end{figure*}
+
+In this section, we present the setting of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.
+and understand the implications of static analysis algorithms in his results.
+We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behaviors.
+
+To achieve this general goal, we answer the following research questions.
+
+\begin{enumerate}[(RQ1)]
+\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
+\item What is the effective performance of each tool in terms of the number of detected malware ?
+\item What is the impact of static analysis on benchmark results ?
+\end{enumerate}
+
+To answer the research questions above, we conduct two experiments using a benchmark solution called droidXP \cite{DBLP:conf/scam/CostaMCMVBC20}.
+This benchmark help us to reproduce Bao et al.
+work on mining sandboxes, allowing integrate different test case tools, define your execution time, and the number of experiment repetitions.
+The (Figure \ref{fig:benchArq}) show all details of the benchmark architecture used in our experiments.
+The benchmark runs these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
+
+At both experiments, we employed the same dataset, 98 pair of real-world apps (B/M), shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} group.
+We executed each app in each one of the five test generator tool, selected for our study, for three minutes, and for just one time.
+The droidXP benchmark relies on DroidFax, the same tool used by Bao et al.
+in your study.
+Droidfax instrumented Android apps and collected relevant information about their execution (using the test case generation tools).
+It collects the set of sensitive APIs accessed during test execution, and during a static analysis at each code apps.
+Based on these sensitive APIs, that will compose the sandbox, we investigate the capacity to detect malicious behaviors in the corresponding malign app by the tool under analysis, together with the DroidFax static analysis.
+(Figure \ref{fig:setup}) show this experiment setup.
+We detail the procedures of each study in what follows.
+
+\begin{figure}[h]
+  \includegraphics[width=0.45\textwidth]{images/setup.png}
+  \label{Experiment setup}
+  \caption{Experiment setup}
+  \label{fig:setup}
+\end{figure}
+
+\subsection{First Study: hybrid proposal}
+
+In the first experiment, we executed the benchmark using the droidXP default configuration, that is, combining static and dynamic analysis while collecting the accessed sensitive APIs, a hybrid approach.
+To generate inputs to apps, we investigate five popular test case generation tools, one from industry (Monkey \cite{Monkey}) and four from academia (Droidbot \cite{DBLP:conf/icse/LiYGC17}, Humanoid \cite{DBLP:conf/kbse/LiY0C19}, DroidMate \cite{DBLP:conf/icse/JamrozikZ16} and ``Joke" tool).
+This last is a fake tool that simulates a tool that does nothing during the benchmark execution.
+Using this tool, the results of the dynamic analysis are not considered and we can compute the results with only the static analysis, performed by the benchmark droidXP.
+So, we used this experiment to answer the research questions (RQ1) and (RQ3), since the ``Joke" tool result presented the real impact of static analysis on benchmark, assuming that our fake tools, do not performs dynamic analysis.
+
+\subsection{Second Study: Dynamic analysis proposal}
+
+In this second experiment, we used an option of the benchmark that disables the static analysis performed by DroidFax.
+With this new configuration, we conduct our second study, with the same dataset apps from the first, the same execution time, and the same test case generation tools, including our ``Joke" tool.
+With the results, it was possible to compute the real aid portion of the dynamic analysis in the malware detection of each test generation tool, since the results, was computed without the static analysis DroidFax influence.
+We used this experiment to answer the research questions (RQ2) and also complements (RQ3), since it is expected that our fake tool will not be able to detect malware with this benchmark configuration, considering that it depends solely the DroidFax static analysis for this task.

### 2021-02-01 setup.tex
study setting second version

--- 2021-01-25 setup.tex
@@
 
-The main goal of this research work is to replicate Bao et al.
-study to understand the implications of static analysis algorithms in his results.
-We also investigate how static analysis can improve the performance of testing tools in the task of identifying malicious behaviors.
+In this section, we present the setting of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.
+and understand the implications of static analysis algorithms in his results.
+We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behaviors.
 
-To achieve this general goal, we answer the following research questions.
+To achieve these general goals, we intend to answer the following research questions.
 
 \begin{enumerate}[(RQ1)]
-\item What is the effective performance of each tool in terms of the number of detected malware ?
-\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
-\item What is the impact of static analysis on benchmark results ?
+\item What is the impact of static analysis DroidFax at the Bao et al. study ?
+\item What is the effective performance of each test generation tool, in terms of the number of detected malware, at Bao et al work, disregarding static analysis DroidFax ?
+\item What benefits of using tainted analysis algorithms to complement the dynamic analysis provided by test generation tools, for mining sandboxes ?
 \end{enumerate}
 
-In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes.
-At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax.
-So, we used this experiment to answer the first research questions (RQ1).
-In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence.
-With these results, we can answer the last two research question (RQ2 and RQ3).
+Answering these research questions has several implications.
+The questions (RQ1) and (RQ2) for instance, can disclose an overestimation of the performance of test generation tools for mining sandboxes, explored at Bao et al work, and introduce a possible threat to the final work conclusions.
+Lastly, the third research question allows us to open up the possibility of finding new strategies for improving the technique of mining sandboxes, strengthening the static analysis, through the use of tainted analysis algorithms.
 
-To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
-Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app.
-(Figure  \ref{fig:setup}) show all this experimental setup.
+We conducted two studies to answer the research questions above.
+First we performed a non-exact replication of Bao et al work.
+For that purpose, we initially selected four test generation tools, three from the original study, and other recently proposed.
+The original test generation tools used were: Droidbot (academic) \cite{DBLP:conf/icse/LiYGC17}, DroidMate  (academic) \cite{DBLP:conf/icse/JamrozikZ16} and Monkey (industry) \cite{Monkey}.
+Droidbot and DroiMate were selected because, at original study, they achieved the best performance on detecting malicious behavior at their respective sandboxes.
+We also select Monkey because it is the main and the most popular test generation tool used by Android developers, coming up with Android SDK installation.
+The other test generation tool selected was Humanoid (academic) \cite{DBLP:conf/kbse/LiY0C19}, a recent test generation tool, that generates human-like test inputs using deep learning techniques, promising to achieve higher and faster code coverage than state-of-the-art test generation tool.
 
-\subsection{Settings for RQ1}
+For this non-exact replication, we also used a benchmark called droidXP \cite{DBLP:conf/scam/CostaMCMVBC20}.
+The benchmark helps us to reproduce the original work, allowing integrate test generation tools, define execution time for each tool, and the number of study repetitions.
+The droidXP benchmark relies on DroidFax, the same tool used by Bao et al.
+in your study.
+Droidfax instrumented Android apps and collected relevant information about their execution (using the test case generation tools).
+It collects the set of sensitive APIs accessed during test execution, and during static analysis at instrumentation stage of each app.
+Based on these sensitive APIs access, the sandbox of each tool will be compose.
+For this study we considered two metrics: The number of malware that each test generation tool detected, and the code coverage of each tool at the analysis time.
 
-\subsection{Settings for RQ2 and RQ3}
+The second study, we used a static taint analysis approaches through Flowdroid \cite{DBLP:conf/pldi/ArztRFBBKTOM14} tool, that execute this kind of analysis at Android apps.
+Our aim is to investigate the performance on detecting malicious behavior using static taint analysis at Android apps.
+The metrics computed at this study was the number of source-sink flows at pairs apps (B/M), and analysis time at each apps.
 
-\begin{figure*}[h!]
-  \includegraphics[width=0.5\textwidth]{images/setup.png}
+At both studies, we employed the same dataset, 98 pair of real-world apps (B/M), shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} group. We detail the procedures of each study in what follows.
+
+\subsection{First Study: A non-exact replication}
+
+In this first study, we executed droidXP benchmark with your default configuration, that is, using static analysis Droidfax and test generation tools while collecting the accessed sensitive APIs.
+We investigate the four test case generation tools described earlier and added a fifth tool described as Joke tool.
+Joke is a ``fake" tool that simulates a test tool that does nothing during the benchmark execution.
+Using this tool, the results of the dynamic analysis are not considered and we can compute the results with only the static analysis, performed by Droidfax.
+Our study executed each pairs app (B/M) in each one of the five test generator tool, including Joke, for three minutes, and for just one time.
+We investigate the capacity to detect malicious behaviors in the corresponding malign app by the sandbox, modeled by test generation tool under analysis.
+(Figure \ref{fig:setup}) show this experimental setup.
+
+\begin{figure}[ht]
+  \includegraphics[width=0.45\textwidth]{images/setup.png}
   \label{Experiment setup}
@@
   \label{fig:setup}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[ht]
-  \includegraphics[width=1\textwidth]{images/benchmark3.png}
-  \label{benchArq}
-  \caption{Benchmark architecture}
-  \label{fig:benchArq}
-\end{figure*}
+In a second moment, we used an benchmark option that disables the static analysis performed by DroidFax.
+With this new configuration, we executed the benchmark again, with the same dataset apps, the same execution time, and the same test case generation tools.
+With the results, it was possible to compute the real aid portion of the dynamic analysis in the malware detection of each test generation tool, since the results, was computed without the static analysis Droidfax influence.
+
+We used this study to answer the research questions (RQ1) and (RQ2), since the ``fake" tool result, presented the real impact of static analysis on benchmark, assuming that Joke tool, do not performs dynamic analysis, depending solely Droidfax static analysis to detect malicious behaviors.
+
+\subsection{Second Study: Tainted analysis algorithms.}
+
+To complement our initial study, we performed the tainted analysis at the same data set from the first study.
+For this second study, we used a static flow analysis tool for Android apps, called Flowdroid \cite{10.1145/2666356.2594299}.
+The goal is to test accuracy of static analysis, through tainted analysis algorithms, at finding malicious behavior, and compare the results with previous study at the same data set.
+At this second study, a behavior is considered malicious, every time the algorithms detected a flow suspicious, between source and sink, that can characterize a privacy leaks.
+
+Initially, Flowdroid mine all sources and sinks of each benign apps, and enumerates all possible data flows between them.
+Next, it performs the same process for the malicious app correspondent.
+In the final step, we compared the set of source-sink track between the benign app and its corresponding malicious app, in order to discovery some taint tracer different between the apps under analysis.
+
+This study was useful to answer the research question (RQ3), because it disclosed some pairs of applications with malicious behavior, that could not be detected at first study at none of the scenarios presented, evidencing that there is a benefit of new static analysis techniques, to complement the dynamic analysis provided by test generation tools, at mining sandboxes solutions.
+Details of studies results are at next section.

### 2021-02-02 setup.tex
first pass in the setup section

--- 2021-01-26 setup.tex
@@
 
-\begin{figure*}[ht]
-  \includegraphics[width=1\textwidth]{images/benchmark3.png}
-  \label{benchArq}
-  \caption{Benchmark architecture}
-  \label{fig:benchArq}
-\end{figure*}
+In this section, we present the settings of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} and thus build
+a general understanding of the implications of static analysis algorithms in their results. We also investigate how static analysis can improve
+the performance of mining sandboxes, in the task of identifying malicious behavior.
 
-In this section, we present the setting of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.
-and understand the implications of static analysis algorithms in his results.
-We also investigate how static analysis can improve the performance of testing tools in the task of identifying malicious behaviors.
-
-To achieve this general goal, we answer the following research questions.
+To achieve these general goals, we intend to answer the following research questions.
 
 \begin{enumerate}[(RQ1)]
-\item What is the effective performance of each tool in terms of the number of detected malware ?
-\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
-\item What is the impact of static analysis on benchmark results ?
+ \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?
+
+ \item What is the effective performance of each test generation tool, in terms of the number of detected malware, in the Bao et al. study, disregarding the DroidFax
+  static analysis algorithms?
+
+ \item What are the benefits of using tainted analysis algorithms to complement the dynamic analysis provided by test generation tools for mining sandboxes?
 \end{enumerate}
 
-To assess the effectiveness of mining sandboxes created by each test case generation tools, we used a benchmark solution for test case generation called droidXP \cite{DBLP:conf/scam/CostaMCMVBC20}, that aims us to reproduce previous research work on mining sandboxes.
-(Figure \ref{fig:benchArq}) show all details of the benchmark architecture used at our experiments.
-The benchmark run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox.
+Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation of the performance of test generation tools for mining sandboxes,
+as reported by Bao et all.~\cite{DBLP:conf/wcre/BaoLL18}, which might introduce a possible threat to their conclusions. Answering the third research question
+allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
+dynamic analysis through the use of static analysis algorithms.
 
-Thereby, to answer the research questions above, we perform two experiments.
-At both we employed the same dataset, 98 pair of real-world apps (B/M), shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} group.
-This time we executed each app in one of the five test generator tool, selected for our experiments, for 3 minutes, and for just one time.
-The droidXP benchmark also relies on DroidFax, the same tool used by Bao et al.
-in your study, that instruments Android apps and collects relevant information about their execution (using the test case generation tools).
-DroidFax collects the set of sensitive APIs during a test execution, and during a static analysis at each code apps.
-Based on this sensitive APIs, that will compose our sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app by the tool under analysis, together with the static analysis of the DroidFax.
-(Figure \ref{fig:setup}) show this experimental setup.
+We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work.
+For that purpose, we initially selected four test generation tools: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
+DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, Monkey~\cite{Monkey}, and Humanoid~\cite{DBLP:conf/kbse/LiY0C19}. The first three have
+been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
+the best performance on detecting malicious behavior in the original work. We also selected Monkey because it is the most popular test
+generation tool for Android, coming up with the Android SDK installation. Finally, we selected Humanoid  because it is a recent test generation tool,
+which generates human-like test inputs using deep learning techniques and promises to achieve higher code coverage
+than state-of-the-art test generation tool. 
+For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
+which helped us to reproduce the original work.
 
-\subsection{First Study: hybrid proposal}
+In the second study we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to execute
+tainted analysis algorithms in Android apps, in order to identify pairs of \emph{sources and sinks}. In this case,
+our goal is to investigate the performance on detecting malicious
+behavior using static taint analysis of Android apps. We use two metrics in this second study: the number
+of source-sink flows that FlowDroid identifies when considering the pairs of Android apps (B/M) and the
+execution time of the analysis for each app.
+For both studies, we employed the same dataset 98 pairs of Android apps (B/M),
+shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail the procedures of each study in what follows.
 
-In the first experiment, we executed the benchmark considering the droidXP default configuration, that is, using a hybrid proposal.
-To generate inputs to apps, we investigate five popular test case generation tools, one from industry (Monkey \cite{Monkey}) and four from academia (Droidbot \cite{DBLP:conf/icse/LiYGC17}, Humanoid \cite{DBLP:conf/kbse/LiY0C19}, DroidMate \cite{DBLP:conf/icse/JamrozikZ16} and ``Joke" tool).
-This last is a fake tool that we implemented, which does not do anything during the benchmark execution, and through it we can compute results without the dynamic analysis influence.
-So, we used this experiment to answer the first research questions (RQ1).
+\subsection{First Study: A non-exact replication}
 
-\subsection{Second Study: Dynamic analysis proposal}
+In the first study we executed the DroidXP benchmark with its
+default configuration, that is, enabling the DroidFax
+static analysis algorithms and the test generation tools.
 
-In this second experiment we used a option of the benchmark that disables the static analysis performed by DroidFax, and with this new configuration, we performed our second study in the same set of apps from the first, at the same execution time, and at the same test case generation tools, including our ``Joke" tool.
-With the results, it was possible to compute what was the aid portion of the static analysis in the malware detection, since the Joke results, was computed without the dynamic analysis influence.
-We used this experiment to answer the research questions (RQ2) and (RQ3).
+We investigate the four test case generation tools described earlier and added a fake test
+case generation tool (named Joke) that simulates a test tool that does not execute
+the Android apps during a benchmark execution. Using this tool, the results
+of the dynamic analysis are not considered and we can compute the results with
+only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
+Android app (B/M) in each one of the five test generation tools, including Joke,
+for three minutes. We then investigate the performance of each tool to detect
+malicious behaviors in the sandbox modeled by the test generation tool
+under analysis.
 
-\begin{figure*}[ht]
-  \includegraphics[width=0.5\textwidth]{images/setup.png}
-  \label{Experiment setup}
-  \caption{Experiment setup}
-  \label{fig:setup}
-\end{figure*}
+%% Figure \ref{fig:setup} shows this experimental setup.
+
+%% \begin{figure}[ht]
+%%   \includegraphics[width=0.45\textwidth]{images/setup.png}
+%%   \label{Experiment setup}
+%%   \caption{}
+%%   \label{fig:setup}
+%% \end{figure}
+
+After that, we replicated the study using a configuration of DroidXP that
+disables the DroidFax static analysis algorithm. With this new configuration,
+we executed the benchmark one more time, using the same dataset of Android
+apps, the same execution time, and the same test case generation tools.
+The results of this replication allow us to compute the effective performance
+of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
+DroidFax static analysis algorithms.
+
+\subsection{Second Study: Tainted analysis algorithms.}
+
+To complement our initial study, we performed the tainted analysis at the same
+data set from the first study. For this second study, we used
+FlowDroid~\cite{10.1145/2666356.2594299}, a static flow analysis tool for Android apps.
+The goal is to test accuracy of static analysis, through tainted analysis algorithms, at finding malicious behavior, and compare the results with previous study at the same data set.
+In this second study, a behavior is considered malicious whenever the algorithms
+detected a different set of source-sink pairs, coming from the benign and malign
+versions of an Android app.
+
+Initially, Flowdroid mine all sources and sinks of each benign apps, and enumerates all possible data flows between them. Next, it performs the same process for the malicious version
+of the correspondent app.
+In the final step, we compare the set of source-sink track between the benign app and its corresponding malicious app, in order to discovery some taint tracer different between the apps under analysis.
+
+This study was useful to answer the third research question (RQ3), because it disclosed some pairs of applications with malicious behavior, that could not be detected at first study at none of the scenarios presented, evidencing that there is a benefit of new static analysis techniques, to complement the dynamic analysis provided by test generation tools, at mining sandboxes solutions.
+Details of studies results are at next section.

### 2021-02-05 introduction.tex
Missing

@@
 
-Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices.
-Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
-Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}.
-Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
+Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices\kn{citation for android being the most popular?}.
+Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
+Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} \kn{source and sink arrives out of nowhere in introduction.
+Either rephrase into a simpler term please or define those in a sentenc before.} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}.
+Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes~ \kn{A small sentence defining sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
 
-The main idea of mining sandboxes is to explore the set of calls to sensitive API methods, using different approaches for automatically testing Android apps.
-These tools, explore apps behavior and record all calls to sensitive APIs.
+The main idea of mining sandboxes is to explore the set of calls to sensitive API methods \kn{in an Android app?}, using different approaches for automatically testing Android apps.
+These tools \kn{these analysis?
+because tools was not a word used before}, explore apps behavior and record all calls to sensitive APIs.
 A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase).
@@
 Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.
+\kn{This paragraph attempts to explain what a sandbox does and what it is dependent on, but the overall picture is still not clear.
+Consider defining sandbox in one sentence in previous paragraph, and in this paragraph use more concise terms like "Given an App A, with sensitive calls Set\_s, a Sanxbox Y does .....}
 
 Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
-The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be.
-Otherwise, static analysis might determine that some behavior is impossible, this behavior no longer needs to be checked at runtime.
-Thereby, code that is interpreted, decrypted, or downloaded at run time is challenging for static analysis---even though these more \emph{dynamic} strategies are often used to introduce malicious behavior.
+The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be \kn{Ok.
+In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes.
+The overall flow of definitions needs some thought}.
+Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime.
+Thereby, code that is interpreted, decrypted, or downloaded at run time is out of scope for static analysis---even though these more \emph{dynamic} strategies are often used to introduce malicious behavior.
 Nonetheless, the authors do not give any empirical validation about the limitations of static analysis to mine sandboxes.
-In addition, it is not clear how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
+As a consequence, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
 
-The same lack of understanding about the role of static analysis also appears in the work of Bao et al.
-\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
-Their study leverages DroidFax \cite{DBLP:conf/icsm/CaiR17a} to instrument 102 pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
-Although the authors report a performance of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
+The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
+Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
+Although the authors report a performance kn{performance or accuracy/ precision?} of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
 
@@
 \todo[inline]{RB.: Later we can enumerate the paper contributions here.}
+\kn{The rest of the paper is organized as follows...}
 

### 2021-02-06 results.tex
results - initial version

@@
 
-%%Here we can write about MOTIVATION EXAMPLES.
+In this section, we present the finding of our study.
+We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study.
+
+\subsection{Result of the first study: A non-exact replication}
+
+Our first study performed a non-exact replication of Bao et al work.
+Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandboxes.
+We could not use all 102 pairs apps (B/M) from the original study, because bechmark tool could not instrument six pair apps from Bao et al work.
+We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
+The purpose of this time expansion is checking if the test generation tool code coverage results are consistent with Bao et al.
+results.
+
+Initially, we present the result of 96 pairs apps analyses, performing DroidXP benchmark with its default configuration.
+Except for the Joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tool.
+Even though Joke tool does not execute the Android apps during benchmark execution, it was responsible to detect 43.75\% of malwares, only aided by static analysis Droidfax.
+Table \ref{tab:malware} presents the number of malwares detected by the sandboxes designed for each test case generation tool.
+The result of the first step of this study, shows that the sandbox constructed by Droidbot, Droidmate, Humanoid, Joke and Monkey identified, 68, 64, 49, 42 and 71 malwares apps among the 96 pairs apps analysed, respectively.
+Sandboxes build by running Monkey detects more apps with malicious behavior than the other tools analysed.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lcc}\toprule
+ Test Generation Tool & Malwares & \\
+ & Detected & \% \\ \midrule
+ Monkey & 71 & 73.95 \\
+ Droidmate & 64 &  66.66  \\
+ Humanoid & 49 & 51.04  \\
+ Joke & 42 & 43.75  \\
+ Droidbot & 68 & 70.83  \\\midrule
+
+\end{tabular} 
+\caption{Malwares detected in 96 pair (B/M)}
+\label{tab:malware}
+\end{table}
+
+In the original study, the test case generation tool that detected the largest number of malicious apps was Droidbot, 68 among 102 (66,66\%), the same number of apps find in our experiment, followed by Droimate, that in original study, detected 54 among 102 (52.94\%).
+This minor variation may be caused due the original work used the oldest version of Droidmate, and our study used Droidmate 2 \cite{DBLP:conf/kbse/BorgesHZ18}, an improved version of the original DroidMate project, that we believe has a better mine strategy than his previous version and may have generated a more efficient sandbox.
+About Monkey tool, due to his random exploration strategy, his results may vary between studies.
+Although it had the best performance at our study, at original study it got the third best performance, detecting 48 among 102 pairs investigated (47.05\%).
+The sandboxes built by running the only test generation tool, not present at Bao et al.
+work, Humanoid, had the worse performance, identifying a little more than half of the pairs analyzed, 49.
+
+This first setup of our first study also shows that all the constructed sandboxes did not identify the malwares in 19 pairs among 96 (19.79\%).
+These 19 malicious apps, according to Euphony tool \cite{hurier2017euphony}, that infer a single label per malicious application based on VirusTotal, were: 13 adwares, 3 trojans, 2 PUP (Potentially Unwanted Program) and 1 exploit.
+
+Next, we replicated the study, disabling the Droidfax static analysis algorithm, to investigate the number of malwares detected by the sandbox, generated by the effective performance of the dynamic analysis tools, ignoring the influence of static analysis.
+Since Joke tool depends exclusively static analysis Droidfax for build it sandbox, we suppose that it sandbox was unable to detect malwares at our data set, result confirmed in our study, where Joke was unable to detect any malware, reducting its sandbox accuracy in 100\%.
+The sandboxes constructed by the other test generation tool detected 56.25\%-15.62\% of malicious pair apps investigated, reporting an average reduction at the accuracy of each sandbox in 27.78\%.
+This study setup shows that sandbox conceived by Droidbot, Droidmate, Humanoid, Joke, and Monkey identified: 54, 48, 15, 0 and  54 malwares among 96 pairs apps investigated, respectively, evidencing an average total reduction of 47.78\% of sandboxes efficiency constructed by the test generation tools under analysis.
+Supporting the results of second step of the first study, Table \ref{tab:malwareWithout} displays the results of the number of malwares detected by the sandboxes, designed by each tool, without static analysis Droidfax aid.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}\toprule
+ Test Generation & Malwares & & Reduction\\
+ Tool & Detected & \% & Without s.a. (\%)\\ \midrule
+ Monkey & 54 & 56.25 & 23.94\\
+ Droidmate & 48 &  50.00 & 25 \\
+ Humanoid & 15 & 15.62 & 69.38  \\
+ Joke & 0 & 0 & 100 \\
+ Droidbot & 54 & 56.25 & 20.58  \\\midrule
+
+\end{tabular} 
+\caption{Malwares detected in 96 pair (B/M) without static analysis aid}
+\label{tab:malwareWithout}
+\end{table}
+
+This time, Monkey and Droidbot detected the same and the largest number (54) of malicious apps, and Joke tool, as described, can not detect malwares without static analysis aid.
+Table \ref{tab:malwareWithout} also show the efficiency loss with the static analysis withdrawal.
+Humanoid was the most affected by the absence of static analysis, losing 69.38\% of its effectiveness with this benchmark setting.
+Droidbot was the least affected by this new situation.
+
+When analyzing the number of pairs apps, that none of the sandboxes could not identify malwares, the results are the same of the first step of this study, evidencing that static analysis provided by Droidfax, could not be useful in the task of detecting malware at this specific set of pairs.
+
+Based on these results, we provide evidence that, although static analysis Droidfax, do not affect detection malwares at 19 specific pair apps, its absence impact on sandboxes performance, impairing the accuracy of all of them.
+
+\subsection{Result of the second study: Tainted analysis algorithms.}
+
+To complement our initial survey, we performed ...
+
+%Here we can write about MOTIVATION EXAMPLES.

### 2021-02-09 background.tex
Background

@@
 
-A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries.
-It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device.
-It also guarantee an on-biased testing environment, ensuring the same pre-configured beginning status of the environment.
+A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network or other device data.
+It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application.
+It also guarantees an unbiased testing environment, ensuring the same pre-configured beginning status of the environment \kn{I dont understand what a pre-configured beginning status is}.
 
-In this sandbox context, the Android Mining Sandbox concept emerges as a technique that consists of extract rules from android app, and use these rules to ensure system security.
-The technique performs two steps.
-First, rules are mined and will compose the sandbox, through test generator tools.
+The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security.
+The technique comprises of two steps.
+First, rules are mined and will compose the sandbox \kn{I thought sandbox was an environment, now it is comprised of rules?}, through test generator tools.
 These tools explore program behavior and monitor access to sensitive APIs.
-In a second stage, it is taken into account that resources not accessed, or accessed differently, at first stage, must be denied access.
+The second stage ensures that resources not accessed, or accessed differently, at first stage, are denied access.
 So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.
 
-The idea of mine automatically software resources or components, to inferring behavior is not new, and has been discussed before.
+Automatically mining software resources or components, to infer behavior is not new, and has been discussed before.
 For instance, Whaley et al.
-\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis to API mining and so extract interface from software components.
+\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so extract interface from software components.
 Ammons et al \cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
-approach, called specification mining, to discovering some temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
+approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
 
-Regarding test generating tools used to mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tools that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
-Li e tal.
-proposed in \cite{DBLP:conf/icse/LiYGC17}, DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
-In this paper, the authors presented comparison between DroidBot and Monkey \cite{Monkey} in a proof of concept example of using DroidBot in malware analysis.
+Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
+In this~\kn{This meaning our paper or the droidbot paper, then use "their work"} paper, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} as a proof of concept example of using DroidBot in malware analysis~\kn{What is being compared with what.
+Is droidbot compared with monkey.
+If yes, then what is the proof  of concept example of using Droidbot?
+Something we have built.
+Or is the comparison between Droidbot and Monkey as an example of using droidbot?}.
 From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
 
-L Bao et al.
-\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
-This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
-However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps.
+L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
+This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, and after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps \kn{The last bit requires further extrapolation.
+The way it was explained to me is not evident here.
+Especially the "interference of static analysis" requires expansion something in the lines of "The papers did not explore what happens when an existing static analysis in the background is removed, and how much of the analysis results actually come from existing static analysis"}.

### 2021-02-10 results.tex
results - first update

--- 2021-01-25 results.tex
@@
 
-%%Here we can write about MOTIVATION EXAMPLES.
+In this section, we present the finding of our study.
+We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study.
+
+\subsection{Result of the first study: A non-exact replication}
+
+Our first study performed a non-exact replication of Bao et al work.
+Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandbox.
+We could use all 102 pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93.
+We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
+The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al.
+results.
+
+We present the results of 96 pairs apps analyses, performing DroidXP benchmark with its default configuration, and then we performing DroidXP disabling the Droidfax static analysis algorithm, to investigate the number of malware detected by the sandbox, generated by the effective performance of the dynamic analysis tools, ignoring static analysis influence.
+Next, we report the detection capability of each tool in terms of malware detected.
+
+\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among 96 pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed 102 pairs, the percent is close.
+At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among 102 (66,66\%).
+However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect 54 malware.
+Despite this reduction, it had the largest number of malicious apps detected in this new situation.
+
+\textbf{Monkey} at the first step, created a sandbox that could detect more apps with malicious behavior than the other tools analyzed, 71 among 96 pairs.
+Although the original study, it got the third-best performance, detecting 48 among 102 pairs investigated (47.05\%), the result between studies could vary due to its random exploration strategy.
+When disabling static analysis, its accuracy reduced to 23.94\%, totaling 54 malware detected, matching the detect capacity of Droidbot at this configuration.
+
+\textbf{Droimate} with default configuration was able to detect 64 apps with malicious behaviors (66,66\%), and at the original study, it detected 54 among 102 (52.94\%).
+This minor variation may be caused due the original work used the oldest version of Droidmate, and our study used Droidmate 2 \cite{DBLP:conf/kbse/BorgesHZ18}, an improved version of the original DroidMate project, that we believe has a better mine strategy than his previous version and may have generated a more efficient sandbox.
+Disabling static analysis, Droidmate has its accuracy reduced at 25\%, being able to detect 48 among 96 pairs analyzed.
+
+\textbf{Humanoid} at the first step of our study had the worse performance, identifying a little more than half of the pairs analyzed, 49 (51.04\%).
+It is the only tool not present at Bao et al work, so we could not compare our results with its work.
+Regarding the second part of the study, without static analysis, Humanoid was the most affected by this new situation, losing 69.38\% of its effectiveness, being able to detect just 15 pair apps malicious.
+
+\textbf{Joke}, as described, is a fake tool, that simulates a test tool that does not execute Android apps during a benchmark execution, considering just static analysis results.
+Even though Joke tool does not execute the Android apps, it was responsible to detect 43.75\% of malware, only aided by static analysis Droidfax, at the default configuration.
+Ignoring the influence of static analysis, since Joke tool depends exclusively on static analysis Droidfax, we suppose that it sandbox was unable to detect malware at our data set, result confirmed in our study, where Joke was unable to detect any malware, reducing its sandbox accuracy in 100\%.
+
+Except for the Joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tools, with de DroidXP default configuration.
+This first setup of our first study also shows that all the constructed sandboxes did not identify the malware in 19 pairs among 96 (19.79\%).
+These 19 malicious apps, according to Euphony tool \cite{hurier2017euphony}, that infer a single label per malicious application based on VirusTotal, were: 13 adwares, 3 trojans, 2 PUP (Potentially Unwanted Program) and 1 exploit.
+Table \ref{tab:malware} presents the number of malware detected by the sandboxes designed for each test case generation tool, with DroidXP default configuration, with static analysis Droidfax aid.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lcc}\toprule
+ Test Generation Tool & Malwares & \\
+ & Detected & \% \\ \midrule
+ Monkey & 71 & 73.95 \\
+ Droidmate & 64 &  66.66  \\
+ Humanoid & 49 & 51.04  \\
+ Joke & 42 & 43.75  \\
+ Droidbot & 68 & 70.83  \\\midrule
+
+\end{tabular} 
+\caption{Malwares detected in 96 pair (B/M)}
+\label{tab:malware}
+\end{table}
+
+Disabling the Droidfax static analysis algorithm, to investigate the number of malware detected by the sandbox, ignoring the influence of static analysis, the sandboxes constructed, except for Joke tool, detected 56.25\%-15.62\% of malicious pair apps investigated, evidencing an average total reduction of 47.78\% of sandboxes efficiency constructed without the static analysis aid.
+Table \ref{tab:malwareWithout} displays the results of the number of malware detected by the sandboxes, without static analysis Droidfax aid.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}\toprule
+ Test Generation & Malwares & & Reduction (\%)\\
+ Tool & Detected & \% & Without s.a.\\ \midrule
+ Monkey & 54 & 56.25 & 23.94\\
+ Droidmate & 48 &  50.00 & 25 \\
+ Humanoid & 15 & 15.62 & 69.38  \\
+ Joke & 0 & 0 & 100 \\
+ Droidbot & 54 & 56.25 & 20.58  \\\midrule
+
+\end{tabular} 
+\caption{Malwares detected in 96 pair (B/M) without static analysis aid}
+\label{tab:malwareWithout}
+\end{table}
+
+When analyzing the number of pairs apps, which none of the sandboxes could identify malware, the results are the same as the first step of this study, evidencing that static analysis provided by Droidfax, could not be useful in the task of detecting malware at this specific set of pairs.
+
+Based on these results, we provide evidence that, although static analysis Droidfax, do not affect detection malware at 19 specific pair apps, its absence impact on sandboxes performance, impairing the accuracy of all of them.
+
+\subsection{Result of the second study: Tainted analysis algorithms.}
+
+To complement our initial survey, we performed our second study focusing just on static analysis, but this time, using an algorithm different from the first study, performed by Droidfax.
+This time, we used tainted analysis algorithms, using FlowDroid tool, that tracking how private information flows through the apps, and if it is leaked in an unwanted way.
+The results presents were obtained through the analysis of the same data set of the previous study, that is, on the same 96 pairs apps (B/M).
+
+The first results show that with tainted analysis, we had an analysis processing cost of 32.08 seconds per app pair on average, totaling a processing time of 52 minutes to analyze all the pairs.
+The processing time depends on the size of the app, and the pair that took the fastest time analyzed in 3 seconds and the longest 437 seconds.
+Regarding the accuracy of tainted analysis algorithms our study also shows that it was responsible to detect 58 among 96 pair apps (60,42\%), a quantity higher than presented by static analysis algorithms Droidfax, suggested by Joke, our fake test case generation tool, that detected 43.75\% of malware as showed at our first study.
+
+Considering the static analysis provided by Droidfax, and Flowdroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%).
+We also realized that just 9 pairs were detected by Droidfax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by Droidfax, evincing a better accuracy of tainted analysis algorithm.
+Table \ref{tab:recursos} compile the results of this comparison.
+
+\begin{table}[htb]
+\centering
+\begin{tabular}{lcc}\toprule
+
+Detected by  & Malwares detected & \%   \\ 
+(Droidfax/Flowdroid) & (Among 96 pair) & \\ \midrule
+Both tools & 33 & 34.37\%  \\
+Just Droidfax & 9 &  \\
+Just Flowdroid & 25 &  \\
+None & 29 & 30.20\% \\\midrule
+
+\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
+\end{tabular} 
+\caption{Comparison between Droidfax and Flowdroid algorithms}
+\label{tab:recursos}
+\end{table}
+
+Furthermore, we can highlight that among 19 pair apps that at our first study, were not detected by the sandboxes constructed by test generation tool and static analysis Droidfax miner, 4 could be detected by Flowdroid; P35, P38, P56, and P94, therefore exposing, better accuracy of the static analysis algorithms.
+Among these 4 pairs detected, 2 were trojans, 1 was the exploit, the only no detected, and 1 was adware.
+
+%%here we also have to write about the intersection between droidfax and tainted analysis now, and about what 1 reveled and other dont, and otherwise.
+
+%Here we can write about MOTIVATION EXAMPLES.

### 2021-02-11 abstract.tex
update abstract and introduction

@@
 \begin{abstract}
-Due to the popularization of Android and the full range of applications (apps) targeting this platform, many security issues have emerged, attracting researchers and practitioners' attention.
-As such, many techniques for addressing security Android issues appeared, including approaches for mining sandboxes.
-Previous research studies have compared Android test case generation tools for this specific goal.
-Our research aims to explore new techniques for mining sandboxes, especially we are interested in understanding the limits of both static and dynamic analysis in this process.
-Although the use of test generation tools for mining sandboxes has been explored before, the potential to combine static analysis and dynamic analysis has not been sufficiently investigated yet.
-That is, in this paper, we will investigate the hypothesis that combining static and dynamic analysis techniques increases the process of mining Android sandboxes.
-To understand the bound of this combination, we conducted a non-exact replication of a previous study to detect what is the role of each of these analyses in malware detection using mining sandboxes.
-Like the original studies, we used DroidFax, a tool that instruments Android apps and collects relevant information about their execution (using the test case generation tools).
-DroidFax also executes static analysis that collects code coverage information and a set of sensitive APIs used by a given app during test execution.
+The popularization of Android platform and the growth number of Android apps that manage sensitive data, brought several security threats.
+During the last years researchers and practitioners have investigated techniques addressing security Android issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
+Mining sandboxes through test generation tool is not new, and has been investigated before, however a potential combination with static analysis has not been sufficiently explored.
+
+In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
+To this end, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compare the results of test case generation for mining sandboxes, isolating all possible effects of the static analysis on the results, that could leverage the original results.
+We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.
+
 Our results demonstrate that analysis static has an important contribution to the mining sandboxes process, and his combination with dynamic analysis has the potential to improve malware detection techniques.

### 2021-02-11 introduction.tex
update abstract and introduction

@@
 
-Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices\kn{citation for android being the most popular?}.
+Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}.
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
-Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} \kn{source and sink arrives out of nowhere in introduction.
-Either rephrase into a simpler term please or define those in a sentenc before.} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}.
-Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes~ \kn{A small sentence defining sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
+Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
+Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes.
+Given an app A, a sandbox S identifies sensitive resources access by app A, during dynamic analysis, and then block calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
 
-The main idea of mining sandboxes is to explore the set of calls to sensitive API methods \kn{in an Android app?}, using different approaches for automatically testing Android apps.
-These tools \kn{these analysis?
-because tools was not a word used before}, explore apps behavior and record all calls to sensitive APIs.
+The main idea of mining sandboxes is to explore the set of calls to sensitive API methods in a Android app, using different approaches for automatically testing Android apps.
+These analysis explore apps behavior and record all calls to sensitive APIs.
 A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase).
@@
 Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.
-\kn{This paragraph attempts to explain what a sandbox does and what it is dependent on, but the overall picture is still not clear.
-Consider defining sandbox in one sentence in previous paragraph, and in this paragraph use more concise terms like "Given an App A, with sensitive calls Set\_s, a Sanxbox Y does .....}
 
@@
 \todo[inline]{RB.: Later we can enumerate the paper contributions here.}
-\kn{The rest of the paper is organized as follows...}
+The rest of the paper is organized as follows.
+Section 2 we present a background and some related works.
+Section 3 describes all the apps malware used in our experiment, presenting their characterization.
+Section 4 introduces the study setting of our research.
+Section 5 presented some results, highlighting some motivation malware examples and the use of a promising static analysis tool, on these examples.
+Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.
 

### 2021-02-11 abstract.tex
update abstract for submission

@@
 \begin{abstract}
-The popularization of Android platform and the growth number of Android apps that manage sensitive data, brought several security threats.
-During the last years researchers and practitioners have investigated techniques addressing security Android issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
-Mining sandboxes through test generation tool is not new, and has been investigated before, however a potential combination with static analysis has not been sufficiently explored.
+The popularization of Android platform and the growing number of Android apps that manage sensitive data, brought several security threats.
+Over the past years, researchers and practitioners have investigated techniques addressing Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
+Mining sandboxes through test generation tools is not a new strategy, and has been investigated before, however a potential combination with static analysis has not been sufficiently explored yet.
 
 In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
-To this end, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compare the results of test case generation for mining sandboxes, isolating all possible effects of the static analysis on the results, that could leverage the original results.
+Therefore, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compares dynamic test case generation tools for mining sandboxes, isolating all possible effects of the static analysis, that could leverage the results.
 We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.
 
-Our results demonstrate that analysis static has an important contribution to the mining sandboxes process, and his combination with dynamic analysis has the potential to improve malware detection techniques.
+Our results demonstrate that static analysis has an important contribution to the sandbox mining process, and its combination with dynamic analysis has the potential to improve malware detection techniques.
 

### 2021-02-11 abstract.tex
update abstract for submission

@@
 In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
-Therefore, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compares dynamic test case generation tools for mining sandboxes, isolating all possible effects of the static analysis, that could leverage the results.
+Therefore, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compares dynamic test case generation tools for mining sandboxes, isolating all possible effects on the results of the static analysis tools the original work leverage to instrument the Android apps.
 We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.

### 2021-02-12 abstract.tex
abstract submited

--- 2021-02-11 abstract.tex
@@
 \begin{abstract}
-The popularization of Android platform and the growing number of Android apps that manage sensitive data, brought several security threats.
-Over the past years, researchers and practitioners have investigated techniques addressing Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
-Mining sandboxes through test generation tools is not a new strategy, and has been investigated before, however a potential combination with static analysis has not been sufficiently explored yet.
 
-In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
-Therefore, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compares dynamic test case generation tools for mining sandboxes, isolating all possible effects of the static analysis, that could leverage the results.
-We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.
+The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
 
-Our results demonstrate that static analysis has an important contribution to the sandbox mining process, and its combination with dynamic analysis has the potential to improve malware detection techniques.
+Although the use of dynamic analysis for mining Android sandboxes has been investigated before, the potential benefits of using static and dynamic analysis for mining sandboxes are still unclear.
+
+In this paper, we investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
+
+We first conducted a non-exact replication of the Bao et al.
+work \cite{DBLP:conf/wcre/BaoLL18}, which compares the performance of test case generation tools for mining Android sandboxes.
+Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) the authors of the original work used to instrument the Android apps in their experiments.
+Our motivation for this decision is that the use of DroidFax could have improved the dynamic analysis tools' performance through specific static analysis algorithms.
+In our second study, we conduct a new experiment to investigate the performance of tainted analysis algorithms for mining Android sandboxes.
+To this end, we executed the FlowDroid tool to mine and compared the source-sink flows of benign/malign pairs of Android apps in the Bao et al.
+dataset.
+Results.
+The first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
+work, increasing the dynamic analysis tools' performance substantially.
+The second study results show that (static) tainted analysis is also practical for mining sandboxes, with a performance similar to dynamic analysis tools.
 

### 2021-02-12 abstract.tex
minor

@@
 \begin{abstract}
-
-The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+\emph{Context.} The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
 For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
-
-Although the use of dynamic analysis for mining Android sandboxes has been investigated before, the potential benefits of using static and dynamic analysis for mining sandboxes are still unclear.
-
-In this paper, we investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
-
+\emph{Problem.} Although the use of dynamic analysis for mining Android sandboxes has been investigated before, the potential benefits of using static and dynamic analysis for mining sandboxes are still unclear.
+In this paper, we investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. \emph{Method.}
 We first conducted a non-exact replication of the Bao et al.
-work \cite{DBLP:conf/wcre/BaoLL18}, which compares the performance of test case generation tools for mining Android sandboxes.
-Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) the authors of the original work used to instrument the Android apps in their experiments.
-Our motivation for this decision is that the use of DroidFax could have improved the dynamic analysis tools' performance through specific static analysis algorithms.
-In our second study, we conduct a new experiment to investigate the performance of tainted analysis algorithms for mining Android sandboxes.
-To this end, we executed the FlowDroid tool to mine and compared the source-sink flows of benign/malign pairs of Android apps in the Bao et al.
-dataset.
-Results.
-The first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
-work, increasing the dynamic analysis tools' performance substantially.
-The second study results show that (static) tainted analysis is also practical for mining sandboxes, with a performance similar to dynamic analysis tools.
-
+work, which compares the performance of test case generation tools for mining Android sandboxes.
+Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) used in the original work to instrument the Android apps in their experiments.
+This decision was motivated by the fact that DroidFax could have influenced the performance of the dynamic analysis positively---through the execution of specific static analysis algorithms.
+In our second study, we carried out a new experiment to investigate the performance of tainted analysis algorithms for mining Android sandboxes.
+To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al.
+study.
+\emph{Results.} The first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
+work, increasing the performance of the dynamic analysis tools substantially.
+The results of the second study show that (static) tainted analysis is also practical for mining sandboxes, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}

### 2021-02-12 abstract.tex
shrinking the abstract's context

@@
 \begin{abstract}
-\emph{Context.} The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+%  \emph{Context.}
+%  The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
 For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
-\emph{Problem.} Although the use of dynamic analysis for mining Android sandboxes has been investigated before, the potential benefits of using static and dynamic analysis for mining sandboxes are still unclear.
-In this paper, we investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. \emph{Method.}
-We first conducted a non-exact replication of the Bao et al.
-work, which compares the performance of test case generation tools for mining Android sandboxes.
-Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) used in the original work to instrument the Android apps in their experiments.
-This decision was motivated by the fact that DroidFax could have influenced the performance of the dynamic analysis positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the performance of tainted analysis algorithms for mining Android sandboxes.
+%  \emph{Problem.}
+  The use of sandboxes is an effective technique for malware analysis.
+However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for mining Android sandboxes.
+Accordingly, in this paper we present the results of two studies that investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
+%\emph{Method.}
+In the first study we conduct a non-exact replication of the Bao et al.
+work, a previous study that compares the performance of test case generation tools for mining Android sandboxes.
+Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) they used to instrument the Android apps in their experiments.
+This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analysis positively---through the execution of specific static analysis algorithms.
+In our second study, we carried out a new experiment to investigate the efficacy of tainted analysis algorithms for mining Android sandboxes.
 To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al.
 study.
-\emph{Results.} The first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
+%\emph{Results.}
+The first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
 work, increasing the performance of the dynamic analysis tools substantially.

### 2021-02-12 setup.tex
Setup temporary

@@
 
+\kn{This paragraph requires a motivation.
+The details of Boa's study must be described upfront.
+Something like "Boa et al.'s study performs .....
+Since their study also involved a static analysis component whose impact was not measured, we perform a non-exact replication to understand the impact static analysis may have had in the results...}
 In this section, we present the settings of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} and thus build
@@
 \begin{enumerate}[(RQ1)]
+ \kn{Droidfax comes out of nowhere.
+We should introduce this or if already introduced earlier, remind the readers of where it stands with the Bao study in the first line of this section when describing boas study}
  \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?
@@
 
-Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation of the performance of test generation tools for mining sandboxes,
+Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation \kn{of what} of the performance of test generation tools for mining sandboxes,
 as reported by Bao et all.~\cite{DBLP:conf/wcre/BaoLL18}, which might introduce a possible threat to their conclusions. Answering the third research question
@@
 been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
-the best performance on detecting malicious behavior in the original work. We also selected Monkey because it is the most popular test
-generation tool for Android, coming up with the Android SDK installation. Finally, we selected Humanoid  because it is a recent test generation tool,
+the best performance on detecting malicious behavior in the original work \kn{Whats the original work. Best in comparison to what? }. We also selected Monkey because it is the most popular test
+generation tool for Android \kn{cite}, coming up with the Android SDK installation.
+Finally, we selected Humanoid  because it is a recent\kn{There are many recent, why this?
+Is it  the most recent?
+} test generation tool,
 which generates human-like test inputs using deep learning techniques and promises to achieve higher code coverage

### 2021-02-12 abstract.tex

@@
 Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) they used to instrument the Android apps in their experiments.
-This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analysis positively---through the execution of specific static analysis algorithms.
+This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
 In our second study, we carried out a new experiment to investigate the efficacy of tainted analysis algorithms for mining Android sandboxes.
@@
 %\emph{Results.}
-The first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
-work, increasing the performance of the dynamic analysis tools substantially.
-The results of the second study show that (static) tainted analysis is also practical for mining sandboxes, with a performance similar to that reached by dynamic analysis tools.
+Our study brings several findings.
+For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
+work, leading to an overestimation of the performance of the dynamic analysis tools.
+The results of the second study show that (static) tainted analysis is also practical for mining Android sandboxes, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}

### 2021-02-13 background.tex
fisrt revision introduction,backgroud,set. result first version

@@
 It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application.
-It also guarantees an unbiased testing environment, ensuring the same pre-configured beginning status of the environment \kn{I dont understand what a pre-configured beginning status is}.
+
+%It also guarantees an unbiased testing environment, ensuring the same pre-configured beginning status of the environment \kn{I dont understand what a pre-configured beginning status is}.
 
 The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security.
-The technique comprises of two steps.
-First, rules are mined and will compose the sandbox \kn{I thought sandbox was an environment, now it is comprised of rules?}, through test generator tools.
+The sandboxing technique comprises of two steps.
+First, rules are miner and will compose the sandbox,
+%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
+through test generator tools.
 These tools explore program behavior and monitor access to sensitive APIs.
@@
 Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
-In this~\kn{This meaning our paper or the droidbot paper, then use "their work"} paper, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} as a proof of concept example of using DroidBot in malware analysis~\kn{What is being compared with what.
+In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} at a malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey.
+From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
+
+%~\kn{What is being compared with what.
 Is droidbot compared with monkey.
@@
 Or is the comparison between Droidbot and Monkey as an example of using droidbot?}.
-From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
 
 L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
-This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, and after combining all test generator tools, it was possible to detect 80\% of malicious behavior.
+This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect 75.49\% of malicious behavior explored ($77$ among $102$).
 However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps \kn{The last bit requires further extrapolation.

### 2021-02-13 introduction.tex
fisrt revision introduction,backgroud,set. result first version

@@
 Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes.
-Given an app A, a sandbox S identifies sensitive resources access by app A, during dynamic analysis, and then block calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
+In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic analysis, and then block future calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
 
@@
 The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
-Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
-Although the authors report a performance kn{performance or accuracy/ precision?} of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
+Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
+Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
 
@@
 Section 2 we present a background and some related works.
-Section 3 describes all the apps malware used in our experiment, presenting their characterization.
-Section 4 introduces the study setting of our research.
-Section 5 presented some results, highlighting some motivation malware examples and the use of a promising static analysis tool, on these examples.
+Section 3 describes all malware apps used in our experiment, presenting their characterization.
+Section 4 introduces the study setting of our research and Section 5 complements presenting some results, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples.
 Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-02-13 results.tex
fisrt revision introduction,backgroud,set. result first version

@@
 In this section, we present the finding of our study.
-We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study.
+We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study (Section V-C).
 
@@
 Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandbox.
-We could use all 102 pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93.
+We could use all $102$ pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93.
 We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
@@
 
-\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among 96 pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed 102 pairs, the percent is close.
-At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among 102 (66,66\%).
-However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect 54 malware.
+\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among $96$ pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed $102$ pairs, the percent is close.
+At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among $102$ (66,66\%).
+However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect $54$ malware.
 Despite this reduction, it had the largest number of malicious apps detected in this new situation.
@@
 We also realized that just 9 pairs were detected by Droidfax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by Droidfax, evincing a better accuracy of tainted analysis algorithm.
-Table \ref{tab:recursos} compile the results of this comparison.
+Table \ref{tab:comparison} compile the results of this comparison.
 
@@
 \caption{Comparison between Droidfax and Flowdroid algorithms}
-\label{tab:recursos}
+\label{tab:comparison}
 \end{table}
 
-Furthermore, we can highlight that among 19 pair apps that at our first study, were not detected by the sandboxes constructed by test generation tool and static analysis Droidfax miner, 4 could be detected by Flowdroid; P35, P38, P56, and P94, therefore exposing, better accuracy of the static analysis algorithms.
-Among these 4 pairs detected, 2 were trojans, 1 was the exploit, the only no detected, and 1 was adware.
+Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis Droidfax miner, 4 were detected by Flowdroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms.
+Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.
+
+\subsection{Result Summary}
+
+First we find that static analysis summaries had impact in the Bao et al.
+study.
+It was responsible for improving the results of the tools by 47.78\% than its executions alone, answering our first research question (RQ1).
+Second, Table \ref{tab:malwareWithout} summarizes our findings addressing the second research question (RQ2).
+We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was Droidbot, proving be the tool with better effective performance, in terms of the number of detected malware.
+Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms.
+Our experiment highlight that 69.79\%-81.25\% of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that
+sandboxes can be further boosted when coupled with new static analysis techniques.
+We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, 81.25\% with Monkey, a better performance than all five tools explored at Bao et al., even when they combined all the tools together at theirs work 75.49\%.
+Table \ref{tab:tanted} display the increase of all tools explored at our research.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}\toprule
+ Test Generation & FlowDroid & Total & \%\\
+ Tool & Increase  &  & \\ \midrule
+ Monkey & 7 & 78 & 81.25\\
+ Droidmate & 10 &  74 & 77.08 \\
+ Humanoid & 20 & 69 & 71.87  \\
+ Joke & 25 & 67 & 69.79 \\
+ Droidbot & 9 & 77 & 80.20  \\\midrule
+
+\end{tabular} 
+\caption{Malwares detected in 96 pair (B/M) increased by Tainted analysis Algorithms}
+\label{tab:tanted}
+\end{table}
 

### 2021-02-13 setup.tex
fisrt revision introduction,backgroud,set. result first version

--- 2021-02-02 setup.tex
@@
 
-In this section, we present the settings of our study, whose main goal is to perform a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} and thus build
-a general understanding of the implications of static analysis algorithms in their results. We also investigate how static analysis can improve
-the performance of mining sandboxes, in the task of identifying malicious behavior.
+%\kn{This paragraph requires a motivation.
+The details of Boa's study must be described upfront.
+Something like "Boa et al.'s study performs .....
+Since their study also involved a static analysis component whose impact was not measured, we perform a non-exact replication to understand the impact static analysis may have had in the results...}
+
+Bao et al.'s ~\cite{DBLP:conf/wcre/BaoLL18} study explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis.
+Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we perform a non-exact replication to understand the static analysis impact may have had in the results.
+Thus, this section present the settings of our study, whose goal is to perform this non-exact replication, and thus build a general understanding of the implications of static analysis algorithms in their results.
+We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.
 
@@
 \begin{enumerate}[(RQ1)]
+
  \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?
@@
 
-Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation of the performance of test generation tools for mining sandboxes,
-as reported by Bao et all.~\cite{DBLP:conf/wcre/BaoLL18}, which might introduce a possible threat to their conclusions. Answering the third research question
+%\kn{Droidfax comes out of nowhere.
+We should introduce this or if already introduced earlier, remind the readers of where it stands with the Bao study in the first line of this section when describing boas study}
+
+Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation performance of test generation tools for mining sandboxes,
+as reported by Bao et al., which might introduce a possible threat to their conclusions. Answering the third research question
 allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
@@
 been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
-the best performance on detecting malicious behavior in the original work. We also selected Monkey because it is the most popular test
-generation tool for Android, coming up with the Android SDK installation. Finally, we selected Humanoid  because it is a recent test generation tool,
-which generates human-like test inputs using deep learning techniques and promises to achieve higher code coverage
-than state-of-the-art test generation tool. 
+the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work.
+We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation.
+Monkey was developed for stress testing and can not perform text input.
+Therefore, we also selected Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
 For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
@@
 execution time of the analysis for each app.
-For both studies, we employed the same dataset 98 pairs of Android apps (B/M),
+For both studies, we employed the same dataset $96$ pairs of Android apps (B/M),
 shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail the procedures of each study in what follows.

### 2021-02-13 results.tex
first pass in the results section

@@
 
-In this section, we present the finding of our study.
-We first present the results of each study at sub-section (Section V-A and Section V-B), and finish this result session, consolidating our findings and present the main implications of our study (Section V-C).
+In this section we detail the findings of our study. We first present the results of each study
+in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}. In Section~\ref{sec:discussion} we summarize the
+implications of our study.
 
-\subsection{Result of the first study: A non-exact replication}
+\subsection{Result of the first study: A non-exact replication}\label{sec:res-fs}
 
 Our first study performed a non-exact replication of Bao et al work.
-Our study differs from the original because in your study we isolated the effect of static analysis at our results of malicious apps detected by each mined sandbox.
-We could use all $102$ pairs apps (B/M) from the original study, because the benchmark tool could instrument six pair apps from Bao et al work, i.e., P25, P32, P36, P41, P88, and P93.
-We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
+Our study differs from the original because here we isolated the effect
+of the DroidFax static analysis algorithms in the performance to
+identify malicious apps using the test case generation tools for
+mining sandboxes. In addition, we discarded six pairs of
+Android apps we were not able to instrument---out of the $102$ pairs used in the \original work.
+\rb{All of this following information should be detailed in
+the study settings, and not repeated here if it is already there.} {\color{red}We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
 The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al.
-results.
+results.}
 
-We present the results of 96 pairs apps analyses, performing DroidXP benchmark with its default configuration, and then we performing DroidXP disabling the Droidfax static analysis algorithm, to investigate the number of malware detected by the sandbox, generated by the effective performance of the dynamic analysis tools, ignoring static analysis influence.
-Next, we report the detection capability of each tool in terms of malware detected.
+As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration.
+After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
+Table~\ref{tab:fs} summarizes the results of th execution.
+The columns Exec.
+(I) and Exec.
+(II)
+show the number of malwares identified when executing each tool (I) with the
+support of the DroidFax static analysis algorithms and (II) withouth the support
+of DroidFax static analysis algorithms. The Improvement column shows the impact
+(in percentage) of DroidFax static analysis algorithms in the results.
+In the previous work~\cite{}, the authors do not present a
+discussion about the influence of DroidFax in the results, even
+though here we report that this difference is in the
+range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
+\joke tool for wich DroidFax improves its performance in 100\% (as expected).
+Next we discuss the result of each individual test generation tool.
 
-\textbf{Droidbot} with DroidXP default configuration detects a total of 68 malware among $96$ pairs analyzed (70.83\%), the same number of apps find at original study, although the original study analyzed $102$ pairs, the percent is close.
-At the original study, Droidbot was the test case generation tool that detected the largest number of malicious apps, 68 among $102$ (66,66\%).
-However, when we disabling the static analysis, Droidbot has an efficiency reduction of 20.58 \%, and was able to detect $54$ malware.
-Despite this reduction, it had the largest number of malicious apps detected in this new situation.
+\begin{table}[ht]
+  \caption{Summary of the results of the first study. }
+  \centering
+  \begin{small}
+ \begin{tabular}{lrrr}
+   \toprule
+   Tool & Exec. (I) & Exec. (II) & Improvement (\%) \\   \midrule
+  Monkey &  71 &  54 & 23.94 \\ 
+  Droidmate &  64 &  48 & 25.00 \\ 
+  Droidbot &  68 &  54 & 20.59 \\ 
+  Humanoid &  49 &  15 & 69.39 \\ 
+  \joke &  42 &   0 & 100.00 \\ 
+ \bottomrule
+ \end{tabular}
+ \end{small}
+ \label{tab:fs}
+\end{table}
 
-\textbf{Monkey} at the first step, created a sandbox that could detect more apps with malicious behavior than the other tools analyzed, 71 among 96 pairs.
-Although the original study, it got the third-best performance, detecting 48 among 102 pairs investigated (47.05\%), the result between studies could vary due to its random exploration strategy.
-When disabling static analysis, its accuracy reduced to 23.94\%, totaling 54 malware detected, matching the detect capacity of Droidbot at this configuration.
+\subsubsection*{Monkey} sandbox for the first execution (Exec.
+(I)) detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps).
+Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%).
+This difference might be due to the Monkey randomic strategy for test case generation.
+\rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec.
+(II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of Droidbot for Exec.
+(II).
+\rb{Considering only one run for each configuration, that is Exec.
+(I) and Exec.
+(II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}
 
-\textbf{Droimate} with default configuration was able to detect 64 apps with malicious behaviors (66,66\%), and at the original study, it detected 54 among 102 (52.94\%).
-This minor variation may be caused due the original work used the oldest version of Droidmate, and our study used Droidmate 2 \cite{DBLP:conf/kbse/BorgesHZ18}, an improved version of the original DroidMate project, that we believe has a better mine strategy than his previous version and may have generated a more efficient sandbox.
-Disabling static analysis, Droidmate has its accuracy reduced at 25\%, being able to detect 48 among 96 pairs analyzed.
+\subsubsection*{Droidbot} in the first execution (Exec.
+(I)) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%).
+Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps.
+Also, in the original study, Droidbot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
+However, in our second execution (Exec.
+(II)), its performance decreased in 20.58 \%.
+\rb{Not sure if the following sentence is right.} Despite this reduction, it achieved the largest number of malicious apps detected in the second execution.
 
-\textbf{Humanoid} at the first step of our study had the worse performance, identifying a little more than half of the pairs analyzed, 49 (51.04\%).
+\subsubsection*{Droimate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%).
+Contrasting, in the original study Droidmate detected 54 among 102 (52.94\%).
+A possible explanation for this difference is that here we use the more recent version of Droidmate.
+In the second execution, without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect 48 out of the 96 pairs of Android apps.
+
+\rb{I have read the paper until this point.}
+
+\subsubsection*{Humanoid} at the first step of our study had the worse performance, identifying a little more than half of the pairs analyzed, 49 (51.04\%).
 It is the only tool not present at Bao et al work, so we could not compare our results with its work.
@@
 
-\textbf{Joke}, as described, is a fake tool, that simulates a test tool that does not execute Android apps during a benchmark execution, considering just static analysis results.
+\subsubsection*{\joke}, as described, is a fake tool, that simulates a test tool that does not execute Android apps during a benchmark execution, considering just static analysis results.
 Even though Joke tool does not execute the Android apps, it was responsible to detect 43.75\% of malware, only aided by static analysis Droidfax, at the default configuration.
@@
 
-Except for the Joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tools, with de DroidXP default configuration.
+Except for the \joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tools, with de DroidXP default configuration.
 This first setup of our first study also shows that all the constructed sandboxes did not identify the malware in 19 pairs among 96 (19.79\%).
@@
 
-\subsection{Result of the second study: Tainted analysis algorithms.}
+\subsection{Result of the second study: Tainted analysis algorithms.}\label{sec:res-ss}
 
@@
 
-\subsection{Result Summary}
+\subsection{Discussion}\label{sec:discussion}
 

### 2021-02-13 results.tex
review untill section V-A

@@
 
-\rb{I have read the paper until this point.}
+\subsubsection*{Humanoid} presented the worse performance, even though a previous
+work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate.
+In the first execution (Exec.
+(I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%).
+Since Bao et al.
+did not explored Humanoid in their study, we do not hava a baseline for comparison.
+Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.
 
-\subsubsection*{Humanoid} at the first step of our study had the worse performance, identifying a little more than half of the pairs analyzed, 49 (51.04\%).
-It is the only tool not present at Bao et al work, so we could not compare our results with its work.
-Regarding the second part of the study, without static analysis, Humanoid was the most affected by this new situation, losing 69.38\% of its effectiveness, being able to detect just 15 pair apps malicious.
+\subsubsection*{\joke} is our fake test case generation tool that we use to help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes.
+We integrated \joke into the DroidXP benchmark as an additional test generation tool that does not run the Android apps during the benchmark execution.
+As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms only.
+For the first execution, with the DroidFax static algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares.
+For the second execution, that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was unable to detect any malware.
+This result was expected, since \joke does not analyse the Android apps during the benchmark execution.
 
-\subsubsection*{\joke}, as described, is a fake tool, that simulates a test tool that does not execute Android apps during a benchmark execution, considering just static analysis results.
-Even though Joke tool does not execute the Android apps, it was responsible to detect 43.75\% of malware, only aided by static analysis Droidfax, at the default configuration.
-Ignoring the influence of static analysis, since Joke tool depends exclusively on static analysis Droidfax, we suppose that it sandbox was unable to detect malware at our data set, result confirmed in our study, where Joke was unable to detect any malware, reducing its sandbox accuracy in 100\%.
+Ignoring the \joke tool, our study show that 51.04\%-73.95\% of the malicious apps investigatedin our study can be detected using the sandboxes constructed running the test case generation tools with the support of DroidFax static analysis algorithms.
+Besides that, in the first execution none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%).
+According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are adwares, three are trojans, two are PUP (Potentially Unwanted Program), and one is an exploit.
 
-Except for the \joke dummy tool, our studies show that 73.95\%-51.04\% of malicious pairs apps investigated, can be detected by the sandboxes constructed by others selected test generation tools, with de DroidXP default configuration.
-This first setup of our first study also shows that all the constructed sandboxes did not identify the malware in 19 pairs among 96 (19.79\%).
-These 19 malicious apps, according to Euphony tool \cite{hurier2017euphony}, that infer a single label per malicious application based on VirusTotal, were: 13 adwares, 3 trojans, 2 PUP (Potentially Unwanted Program) and 1 exploit.
-Table \ref{tab:malware} presents the number of malware detected by the sandboxes designed for each test case generation tool, with DroidXP default configuration, with static analysis Droidfax aid.
+\rb{This is an interesting point to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.}
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{lcc}\toprule
- Test Generation Tool & Malwares & \\
- & Detected & \% \\ \midrule
- Monkey & 71 & 73.95 \\
- Droidmate & 64 &  66.66  \\
- Humanoid & 49 & 51.04  \\
- Joke & 42 & 43.75  \\
- Droidbot & 68 & 70.83  \\\midrule
-
-\end{tabular} 
-\caption{Malwares detected in 96 pair (B/M)}
-\label{tab:malware}
-\end{table}
-
-Disabling the Droidfax static analysis algorithm, to investigate the number of malware detected by the sandbox, ignoring the influence of static analysis, the sandboxes constructed, except for Joke tool, detected 56.25\%-15.62\% of malicious pair apps investigated, evidencing an average total reduction of 47.78\% of sandboxes efficiency constructed without the static analysis aid.
-Table \ref{tab:malwareWithout} displays the results of the number of malware detected by the sandboxes, without static analysis Droidfax aid.
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{lccc}\toprule
- Test Generation & Malwares & & Reduction (\%)\\
- Tool & Detected  & \% & Without s.a.\\ \midrule
- Monkey & 54 & 56.25 & 23.94\\
- Droidmate & 48 &  50.00 & 25 \\
- Humanoid & 15 & 15.62 & 69.38  \\
- Joke & 0 & 0 & 100 \\
- Droidbot & 54 & 56.25 & 20.58  \\\midrule
-
-\end{tabular} 
-\caption{Malwares detected in 96 pair (B/M) without static analysis aid}
-\label{tab:malwareWithout}
-\end{table}
-
-When analyzing the number of pairs apps, which none of the sandboxes could identify malware, the results are the same as the first step of this study, evidencing that static analysis provided by Droidfax, could not be useful in the task of detecting malware at this specific set of pairs.
-
+\begin{finding}
 Based on these results, we provide evidence that, although static analysis Droidfax, do not affect detection malware at 19 specific pair apps, its absence impact on sandboxes performance, impairing the accuracy of all of them.
+\end{finding}
 

### 2021-02-14 results.tex
add a venn-diagram for the first study

@@
 After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
-Table~\ref{tab:fs} summarizes the results of th execution.
+Table~\ref{tab:fs} summarizes the results of the execution.
 The columns Exec.
@@
 show the number of malwares identified when executing each tool (I) with the
-support of the DroidFax static analysis algorithms and (II) withouth the support
+support of the DroidFax static analysis algorithms and (II) without the support
 of DroidFax static analysis algorithms. The Improvement column shows the impact
@@
 range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
-\joke tool for wich DroidFax improves its performance in 100\% (as expected).
+\joke tool for which DroidFax improves its performance in 100\% (as expected).
 Next we discuss the result of each individual test generation tool.
@@
   Monkey &  71 &  54 & 23.94 \\ 
-  Droidmate &  64 &  48 & 25.00 \\ 
-  Droidbot &  68 &  54 & 20.59 \\ 
+  DroidMate &  64 &  48 & 25.00 \\ 
+  DroidBot &  68 &  54 & 20.59 \\ 
   Humanoid &  49 &  15 & 69.39 \\ 
@@
 Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%).
-This difference might be due to the Monkey randomic strategy for test case generation.
+This difference might be due to the Monkey randomly strategy for test case generation.
 \rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec.
-(II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of Droidbot for Exec.
+(II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec.
 (II).
@@
 
-\subsubsection*{Droidbot} in the first execution (Exec.
+\subsubsection*{DroidBot} in the first execution (Exec.
 (I)) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%).
 Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps.
-Also, in the original study, Droidbot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
+Also, in the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
 However, in our second execution (Exec.
@@
 
-\subsubsection*{Droimate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%).
-Contrasting, in the original study Droidmate detected 54 among 102 (52.94\%).
-A possible explanation for this difference is that here we use the more recent version of Droidmate.
+\subsubsection*{DroidMate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%).
+Contrasting, in the original study DroidMate detected 54 among 102 (52.94\%).
+A possible explanation for this difference is that here we use the more recent version of DroidMate.
 In the second execution, without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect 48 out of the 96 pairs of Android apps.
@@
 Since Bao et al.
-did not explored Humanoid in their study, we do not hava a baseline for comparison.
+did not explored Humanoid in their study, we do not have a baseline for comparison.
 Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.
@@
 For the second execution, that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was unable to detect any malware.
-This result was expected, since \joke does not analyse the Android apps during the benchmark execution.
-
-Ignoring the \joke tool, our study show that 51.04\%-73.95\% of the malicious apps investigatedin our study can be detected using the sandboxes constructed running the test case generation tools with the support of DroidFax static analysis algorithms.
-Besides that, in the first execution none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%).
-According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are adwares, three are trojans, two are PUP (Potentially Unwanted Program), and one is an exploit.
-
-\rb{This is an interesting point to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.}
+This result was expected, since \joke does not analyze the Android apps during the benchmark execution.
 
 \begin{finding}
-Based on these results, we provide evidence that, although static analysis Droidfax, do not affect detection malware at 19 specific pair apps, its absence impact on sandboxes performance, impairing the accuracy of all of them.
+  Integrating the dynamic analysis tools
+  with the DroidFax static analysis algorithms
+  improves substantially the performance
+  of the resulting Android sandboxes for
+  detecting malicious behavior. 
 \end{finding}
+
+The Venn-diagram of Figure~\ref{fig:venn-plot1}
+summarizes how the tools can complement each other.
+Note in the diagram that 47 malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 77 identified by at least one sandbox.
+In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools.
+Differently, the Monkey's sandbox detected five malwares that had not been detected by any other sandbox, DroidBot sandbox detected four malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox.
+Contrasting with the Bao et al.
+work~\cite{DBLP:conf/wcre/BaoLL18},
+our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
+Android sandboxes.
+
+\begin{finding}
+  Our results suggest that one might benefit from using  an integrated
+  environment that combines Monkey, DroidMate, and Humanoid to
+  mine Android sandboxes. Introducing the DroidBot 
+  tool does not improve the results.
+\end{finding}
+
+\begin{figure}[htb]
+  \centering{
+  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-1.pdf}}
+  \caption{Venn Diagram highlighting how the sandboxes from the tools can
+    complement each other.}
+  \label{fig:venn-plot1}
+\end{figure}
+
+Altogether, ignoring the \joke tool, our study reveals that from 51.04\% (Humanoid)
+to 73.95\% (Monkey) of the malicious apps investigated in our study can be
+detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms.
+Besides that, in the first execution, none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%).
+According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are \emph{adwares}, three are \emph{trojans}, two are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
+\rb{In what follows we present some characteristics of malwares that had not been detected by the sandboxes.}
+
+\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.
+I think Thales could work on this, since he has helped Handrick to dissect the malwares.}
 
@@
 
-To complement our initial survey, we performed our second study focusing just on static analysis, but this time, using an algorithm different from the first study, performed by Droidfax.
-This time, we used tainted analysis algorithms, using FlowDroid tool, that tracking how private information flows through the apps, and if it is leaked in an unwanted way.
-The results presents were obtained through the analysis of the same data set of the previous study, that is, on the same 96 pairs apps (B/M).
+In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset.
+To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
+Regarding accuracy, the tainted analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
+
+\begin{finding}
+  The performance of FlowDroid to identify malicious behavior
+  using our approach is superior than the performance of the
+  mining sandbox approach supported by dynamic analysis only---without
+  the DroidFax static analysis algorithms.
+\end{finding}
+
+Additionally, we investigate if we could benefit from combining
+the results from FlowDroid and DroidFax. Figure~\ref{}
+shows the results.
+Considering the static analysis provided by DroidFax and FlowDroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%).
+We also realized that just 9 pairs were detected by DroidFax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by DroidFax, evincing a better accuracy of tainted analysis algorithm.
 
@@
 The processing time depends on the size of the app, and the pair that took the fastest time analyzed in 3 seconds and the longest 437 seconds.
-Regarding the accuracy of tainted analysis algorithms our study also shows that it was responsible to detect 58 among 96 pair apps (60,42\%), a quantity higher than presented by static analysis algorithms Droidfax, suggested by Joke, our fake test case generation tool, that detected 43.75\% of malware as showed at our first study.
 
-Considering the static analysis provided by Droidfax, and Flowdroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%).
-We also realized that just 9 pairs were detected by Droidfax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by Droidfax, evincing a better accuracy of tainted analysis algorithm.
 Table \ref{tab:comparison} compile the results of this comparison.
@@
 Detected by  & Malwares detected & \%   \\ 
-(Droidfax/Flowdroid) & (Among 96 pair) & \\ \midrule
+(DroidFax/FlowDroid) & (Among 96 pair) & \\ \midrule
 Both tools & 33 & 34.37\%  \\
-Just Droidfax & 9 &  \\
-Just Flowdroid & 25 &  \\
+Just DroidFax & 9 &  \\
+Just FlowDroid & 25 &  \\
 None & 29 & 30.20\% \\\midrule
@@
 \end{tabular} 
-\caption{Comparison between Droidfax and Flowdroid algorithms}
+\caption{Comparison between DroidFax and FlowDroid algorithms}
 \label{tab:comparison}
@@
 
-Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis Droidfax miner, 4 were detected by Flowdroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms.
+Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis DroidFax miner, 4 were detected by FlowDroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms.
 Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.
@@
 Second, Table \ref{tab:malwareWithout} summarizes our findings addressing the second research question (RQ2).
-We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was Droidbot, proving be the tool with better effective performance, in terms of the number of detected malware.
+We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was DroidBot, proving be the tool with better effective performance, in terms of the number of detected malware.
 Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms.
@@
  Monkey & 7 & 78 & 81.25\\
- Droidmate & 10 &  74 & 77.08 \\
+ DroidMate & 10 &  74 & 77.08 \\
  Humanoid & 20 & 69 & 71.87  \\
  Joke & 25 & 67 & 69.79 \\
- Droidbot & 9 & 77 & 80.20  \\\midrule
+ DroidBot & 9 & 77 & 80.20  \\\midrule
 

### 2021-02-14 results.tex
additional review to the results section

@@
   \centering{
-  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-1.pdf}}
+  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-s1-1.pdf}}
   \caption{Venn Diagram highlighting how the sandboxes from the tools can
@@
 Additionally, we investigate if we could benefit from combining
-the results from FlowDroid and DroidFax. Figure~\ref{}
-shows the results.
-Considering the static analysis provided by DroidFax and FlowDroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%).
-We also realized that just 9 pairs were detected by DroidFax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by DroidFax, evincing a better accuracy of tainted analysis algorithm.
+the results from FlowDroid and DroidFax. Figure~\ref{fig:venn-plot2} shows a
+Venn-diagram summarizing the results. So, when combining
+the results from FlowDroid and DroidFax, we were able to detect
+67 of the malicious apps (69.79\%), a performance compatible
+to that we found as response to the first execution of the
+test case generation tools---which also considers the DroidFax
+static analysis algorithms. More interesting, from those 67
+malicious apps identified, 33 pairs had been found by
+both tools (FlowDroid and DroidFax), even though they follow
+a completely different static analysis approach. Furthermore,
+FlowDroid shows to bem more effective than DroidFax, detecting 25 malicious
+apps that had not been detected by DroidFax (while DroidFax detected nine
+malicious apps that had not been detected by FlowDroid).
 
-The first results show that with tainted analysis, we had an analysis processing cost of 32.08 seconds per app pair on average, totaling a processing time of 52 minutes to analyze all the pairs.
-The processing time depends on the size of the app, and the pair that took the fastest time analyzed in 3 seconds and the longest 437 seconds.
+\begin{finding}
+  Integrating the results of static analysis tools
+  (such as FlowDroid and DroidFax) seems promising,
+  leading to a performance similar to that achievend
+  when combining test case generation tools with the
+  DroidFax tool. 
+\end{finding}
 
-Table \ref{tab:comparison} compile the results of this comparison.
+\begin{figure}
+  \centering{
+  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-s2-1.pdf}}
+  \caption{Venn Diagram highlighting the possible benefits of
+    integrating FlowDroid and DroidFax.}
+  \label{fig:venn-plot2}
 
-\begin{table}[htb]
-\centering
-\begin{tabular}{lcc}\toprule
+\end{figure}
 
-Detected by  & Malwares detected & \%   \\ 
-(DroidFax/FlowDroid) & (Among 96 pair) & \\ \midrule
-Both tools & 33 & 34.37\%  \\
-Just DroidFax & 9 &  \\
-Just FlowDroid & 25 &  \\
-None & 29 & 30.20\% \\\midrule
+The execution of FlowDroid is also feasible: the analysis takes only
+32.08 seconds per app on average, totaling a processing time of 52
+minutes to analyze all 96 pairs of Android apps.
+Even though the time to execute the FlowDroid analysis depends on the size
+of the app, the longest run took only 437 seconds.
 
-\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
-\end{tabular} 
-\caption{Comparison between DroidFax and FlowDroid algorithms}
-\label{tab:comparison}
-\end{table}
+Finally, we can highlight that FlowDroid was able to detect four malwares among the 19 malicious Android apps that had not
+been detected by the sandboxes constructed in the first study. Among these
+four malwares, two are \emph{trojans}, 1 is an \emph{exploit}, and 1
+is an \emph{adware}.
 
-Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis DroidFax miner, 4 were detected by FlowDroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms.
-Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.
+\begin{finding}
+  Although FlowDroid presents a performance similar
+  to that of using the dynamic analysis approach for mining sandboxes,
+  it was able to detect only four additional malwares (out of the
+  19) that had not been detected in the first study. 
+\end{finding}
+
+\rb{This is a nice place to present some details about the malwares
+  that FlowDroid had detected, showin the additional source-sink pairs
+  that emmerged. A discussion about these aforementioned four pairs would
+  also be relevant.}
+
+\rb{I finished my first review until this place. Tomorrow I will continue
+from here.}
 

### 2021-02-14 results/script.Rmd
additional review to the results section

---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.path='../images/', dev=c('png', 'pdf'))

require(sqldf)
require(ggplot2)
require(xtable)
require(VennDiagram)
require(ggvenn)
```

## Load the Summary Dataset for Study 1

```{r}
ds <- read.csv("./execution01.csv", head=T, sep=",")
ds["Improvement"] = (ds$WithDroidFax - ds$WithoutDroidFax) * 100 / ds$WithDroidFax
xtable(ds)
```

## Load the Complete Dataset for Study 1

```{r venn-plot-s1}
ds <- read.csv("./report_withStatic.csv", head=T, sep=",")

sets <- sqldf("select tool, app from ds where malware = 'True'")
monkey = sets[sets$tool=="monkey", c("app")]
humanoid = sets[sets$tool=="humanoid", c("app")]
droidmate = sets[sets$tool=="droidmate", c("app")]
droidbot = sets[sets$tool=="droidbot", c("app")]
joker = sets[sets$tool=="joke", c("app")]

venn.diagram(
  x = list(monkey, humanoid, droidmate, droidbot, joker),
  category.names = c("Monkey" , "Humanoid" , "DroidMate", "DroidBot", "Joker"),
  filename = './venn.png',
  output=TRUE
)

x <- list(
  Monkey = monkey,
  Humanoid = humanoid, 
  DroidMate = droidmate,
  DroidBot = droidbot
)

ggvenn(
 x,
 fill_color = c("#0073C2FF", "#EFC000FF", "#868686FF", "#CD534CFF","#CD534CAA"),
   stroke_size = 0.5, set_name_size = 4, text_size=2
)
```

## Total of malwares detected by at least one tool

```{r}
sqldf("select count(distinct app) from ds where malware = 'True'")
```

## Load the Complete Dataset for Study 2

```{r venn-plot-s2}
 ds <- read.csv("allreportResults.csv", head=T, sep=",")
sets <- sqldf("select tool, app 
                  from ds 
                  where malware = 1 
                    and (tool='flowdroid' or tool = 'joke')")

notDetected <- sqldf("select distinct app from ds where 
                      app not in (select app from sets)")

# subsets
notDetected

flowdroid = sets[sets$tool=="flowdroid", c("app")]
droidfax = sets[sets$tool=="joke", c("app")]
notDetected = sets[, c("app")]

x <- list(
  FlowDroid = flowdroid,
  DroidFax = droidfax
)

ggvenn(
 x,
 fill_color = c("#0073C2FF", "#EFC000FF"),
   stroke_size = 0.5, set_name_size = 4, text_size=2.5
)

```

### 2021-02-15 background.tex
Taint analysis in background

@@
 This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect 75.49\% of malicious behavior explored ($77$ among $102$).
-However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps \kn{The last bit requires further extrapolation.
-The way it was explained to me is not evident here.
-Especially the "interference of static analysis" requires expansion something in the lines of "The papers did not explore what happens when an existing static analysis in the background is removed, and how much of the analysis results actually come from existing static analysis"}.
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps
+
+Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet.
+Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}.
+Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system.
+Flowdroid~\cite{arzt:pldi-2014} improves on precision of traditional approaches by including context and flow sensitivity.
+A significant issue with taint analysis is the cost of the tool itself hampering the performance.
+FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.
+Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.

### 2021-02-15 results.tex
Minor

@@
 Our first study performed a non-exact replication of Bao et al work.
+\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }
 Our study differs from the original because here we isolated the effect

### 2021-02-15 results.tex
second revision result,backgroud,setup. threats first version

--- 2021-02-14 results.tex
@@
 Our first study performed a non-exact replication of Bao et al work.
-Our study differs from the original because here we isolated the effect
-of the DroidFax static analysis algorithms in the performance to
-identify malicious apps using the test case generation tools for
-mining sandboxes. In addition, we discarded six pairs of
-Android apps we were not able to instrument---out of the $102$ pairs used in the \original work.
-\rb{All of this following information should be detailed in
-the study settings, and not repeated here if it is already there.} {\color{red}We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
-The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al.
-results.}
-
+%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
 As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration.

### 2021-02-15 setup.tex
second revision result,backgroud,setup. threats first version

@@
 
-We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work.
-For that purpose, we initially selected four test generation tools: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
-DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, Monkey~\cite{Monkey}, and Humanoid~\cite{DBLP:conf/kbse/LiY0C19}. The first three have
-been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
+We conducted two studies to answer the research questions above.
+First we performed a non-exact replication of Bao et al work.
+Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
+mining sandboxes. In addition, we discarded six pairs of
+Android apps we were not able to instrument---out of the $102$ pairs used in the original work.
+We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
+
+The other $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
+DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}.
+We selected Droidbot and DroiMate because they achieved
 the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work.
 We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation.
-Monkey was developed for stress testing and can not perform text input.
-Therefore, we also selected Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
+Since Monkey was developed for stress testing, and can not perform text input, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
 For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
@@
 We investigate the four test case generation tools described earlier and added a fake test
-case generation tool (named Joke) that simulates a test tool that does not execute
+case generation tool (named Joker) that simulates a test tool that does not execute
 the Android apps during a benchmark execution. Using this tool, the results
@@
 only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
-Android app (B/M) in each one of the five test generation tools, including Joke,
-for three minutes. We then investigate the performance of each tool to detect
+Android app (B/M) in each one of the five test generation tools, including Joker,
+for $3$ minutes. We then investigate the performance of each tool to detect
 malicious behaviors in the sandbox modeled by the test generation tool

### 2021-02-15 threatsfutureworks.tex
second revision result,backgroud,setup. threats first version

\section{Threats and future works}

Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution. To mitigate this, we have used a configuration of the benchmark DroidXP tool that runs multiple times each test and computes the average result from those executions. So, the comparison between the results of this experiment and the experiment presented by Bao et al. could be more precise.
Beyond that, we tested only 96 of the original 102 pairs of apps in this experiment because the benchmark could not execute those six pairs of apps due to crashes in the Android emulator. This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.
As future work, we plan to investigate other promising tools to enhance our data from previous executions. We will use the benchmark to test tools like Sapienz (a search-based test generation tool) \cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}. And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
Also, we will execute each of the tools used in this experiment without the benchmark. And, we will compare these results with this experiment's results. This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.

### 2021-02-16 results.tex
Minot

@@
 As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration.
-After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
+After that, we executed the analysis again by disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
 Table~\ref{tab:fs} summarizes the results of the execution.
 The columns Exec.
-(I) and Exec.
-(II)
-show the number of malwares identified when executing each tool (I) with the
-support of the DroidFax static analysis algorithms and (II) without the support
-of DroidFax static analysis algorithms. The Improvement column shows the impact
+(WS) and Exec.
+(WOS)
+show the number of malwares identified when executing each tool with the
+support of the DroidFax static analysis algorithms(WS) and without the support
+of DroidFax static analysis algorithms(WOS).
+\kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done.
+}The Improvement column shows the impact
 (in percentage) of DroidFax static analysis algorithms in the results.
+\kn{Is this really improvement?
+Is this not "contribution" of droidfax.
+Improvement happens when an earlier approach detected malware without support of droidfax.
+Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
 In the previous work~\cite{}, the authors do not present a
 discussion about the influence of DroidFax in the results, even
-though here we report that this difference is in the
+though here we report that the impact of DroidFax to the results is significant in the
 range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
-\joke tool for which DroidFax improves its performance in 100\% (as expected).
+\joke tool for which DroidFax improves its performance by 100\% (as expected).
 Next we discuss the result of each individual test generation tool.
@@
    \toprule
-   Tool & Exec. (I) & Exec. (II) & Improvement (\%) \\   \midrule
+   Tool & Exec. (WS) & Exec. (WOS) & Improvement (\%) \\   \midrule
   Monkey &  71 &  54 & 23.94 \\ 
@@
 
-\subsubsection*{Monkey} sandbox for the first execution (Exec.
-(I)) detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps).
+\subsubsection*{Monkey} sandbox for the execution WS detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps).
 Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%).
-This difference might be due to the Monkey randomly strategy for test case generation.
-\rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec.
-(II)), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec.
+This difference might be due to the Monkey using strategy that incorporates randomness for test case generation.
+\rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec WOS), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec.
 (II).
@@
 \subsubsection*{DroidBot} in the first execution (Exec.
-(I)) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%).
+WS) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%).
 Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps.
 Also, in the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
-However, in our second execution (Exec.
-(II)), its performance decreased in 20.58 \%.
-\rb{Not sure if the following sentence is right.} Despite this reduction, it achieved the largest number of malicious apps detected in the second execution.
+However, in our second execution (Exec WOS), its performance decreased to 20.58 \%.
+\rb{Not sure if the following sentence is right.} Despite this reduction, it detected the largest number of malicious apps in the Exec.
+WOS.
 
-\subsubsection*{DroidMate} in the first execution led to a sandbox that detected 64 apps with malicious behavior (66.66\%).
+\subsubsection*{DroidMate} in the first execution(WS) led to a sandbox that detected 64 apps with malicious behavior (66.66\%).
 Contrasting, in the original study DroidMate detected 54 among 102 (52.94\%).
 A possible explanation for this difference is that here we use the more recent version of DroidMate.
-In the second execution, without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect 48 out of the 96 pairs of Android apps.
+In the second execution(WOS), without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect only 48 out of the 96 pairs of Android apps.
 

### 2021-02-16 introduction.tex
add a new command that refers to the Bao et al. study

@@
 
-The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}, which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
+The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
 Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).

### 2021-02-16 setup.tex
add a new command that refers to the Bao et al. study

@@
 
- \item What is the impact of the DroidFax static analysis algorithms in the Bao et al. study?
+ \item What is the impact of the DroidFax static analysis algorithms in the \blls?
 
- \item What is the effective performance of each test generation tool, in terms of the number of detected malware, in the Bao et al. study, disregarding the DroidFax
+ \item What is the effective performance of each test generation tool, in terms of the number of detected malware, in \blls, disregarding the DroidFax
   static analysis algorithms?
@@
 Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation performance of test generation tools for mining sandboxes,
-as reported by Bao et al., which might introduce a possible threat to their conclusions. Answering the third research question
+as reported in \blls, which might introduce a possible threat to their conclusions. Answering the third research question
 allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
@@
 We conducted two studies to answer the research questions above.
-First we performed a non-exact replication of Bao et al work.
+First we performed a non-exact replication of the \blls.
 Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
@@
 We selected Droidbot and DroiMate because they achieved
-the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work.
+the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls.
 We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation.

### 2021-02-16 conclusionfutureworks.tex
first version of conclusion and update of thread session

\section{conclusion and future work}

Static analysis is becoming increasingly important for complement dynamic analysis approaches in the process of mining Android sandboxes. New static analysis techniques, like tainted analysis algorithms can also supports test generator tools for construct sandboxes more  sophisticated. However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it. To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.

In this paper, we performed two studies. In the first we conducted a non-exact replication of Bao et al. work, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and a second moment we disables the Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. At the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that ignoring the Joker tool, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax staTic analysis, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

As future work, we plan to investigate other promising tools to enhance our data from previous executions. We will use the benchmark to test tools like Sapienz (a search-based test generation tool) \cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}. And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
Also, we will execute each of the tools used in this experiment without the benchmark. And, we will compare these results with this experiment's results. This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.

### 2021-02-16 threats.tex
first version of conclusion and update of thread session

--- 2021-02-15 threatsfutureworks.tex
@@
-\section{Threats and future works}
+\section{Threats}
 
@@
 This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.
-As future work, we plan to investigate other promising tools to enhance our data from previous executions.
-We will use the benchmark to test tools like Sapienz (a search-based test generation tool) \cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}.
-And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
-Also, we will execute each of the tools used in this experiment without the benchmark.
-And, we will compare these results with this experiment's results.
-This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.

### 2021-02-17 conclusionfutureworks.tex
More comments and editis

@@
 
-Static analysis is becoming increasingly important for complement dynamic analysis approaches in the process of mining Android sandboxes.
-New static analysis techniques, like tainted analysis algorithms can also supports test generator tools for construct sandboxes more  sophisticated.
-However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it.
+Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities.
+Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including Boa et al.
+But the impact of static analysis on these mining approaches is unexplored currently.
+New static analysis techniques, like taint analysis algorithms can also support test generator tools to construct sandboxes.
+\kn{The following sentence is completely not understandable.
+Consider splitting it.
+}However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it.
 To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.
@@
 work, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times.
-Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and a second moment we disables the Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis.
-At the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
-The results of the first experiment reveals that ignoring the Joker tool, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
+Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis.
+For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
+The results of the first experiment reveals that ignoring the Joker tool \kn{Briefly mention what is joker tool prior to using the word}, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
 Enabling the Droidfax staTic analysis, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid).
@@
 As future work, we plan to investigate other promising tools to enhance our data from previous executions.
-We will use the benchmark to test tools like Sapienz (a search-based test generation tool) \cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}.
+We will use the benchmark to test tools like Sapienz (a search-based test generation tool)~\cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}.
 And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.

### 2021-02-17 results.tex
add a new command that refers to the Bao et al. study
More comments and editis

@@
 
-Our first study performed a non-exact replication of Bao et al work.
+Our first study performed a non-exact replication of the \blls.
 %\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
@@
 In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset.
-To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
-Regarding accuracy, the tainted analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
+To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using taint analysis.
+Regarding accuracy, the taint analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the execution of the dynamic analysis tools without DroidFax support (WOS).
 
@@
 \end{finding}
+
+\kn{What does "our" approach mean in the finding box. I thought we simply study the malware detection under various settings With/without Droidfax and now with flowdroid}
 

### 2021-02-17 background.tex
second revision result,backgroud,setup. threats first version
first general review

@@
 Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
-In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} at a malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey.
+In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey.
 From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
@@
 Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system.
-Flowdroid~\cite{arzt:pldi-2014} improves on precision of traditional approaches by including context and flow sensitivity.
+Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity.
 A significant issue with taint analysis is the cost of the tool itself hampering the performance.
 FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.
-Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.
+
+%Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.

### 2021-02-17 conclusionfutureworks.tex
first general review

@@
 Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities.
-Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including Boa et al.
+Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including \blls.
 But the impact of static analysis on these mining approaches is unexplored currently.
-New static analysis techniques, like taint analysis algorithms can also support test generator tools to construct sandboxes.
-\kn{The following sentence is completely not understandable.
-Consider splitting it.
-}However, state-of-the-art of mining Android sandboxes explore set of sensitive API methods in a Android app, using test generation tools, and highlight limitations at static analysis to mine sandboxes, neglecting the complement that could be obtained with it.
+The use of static analysis techniques, like taint analysis algorithms, to detect malicious behaviours, seems promising and can leverage sandboxes accuracy.
+However, many authors argue in favor of dynamic analysis for  mining sandboxes, highlight limitations at static analysis at this task, neglecting the complement that could be obtained with it.
 To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.
@@
 In this paper, we performed two studies.
-In the first we conducted a non-exact replication of Bao et al.
-work, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times.
+In the first we conducted a non-exact replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times.
 Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis.
 For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
-The results of the first experiment reveals that ignoring the Joker tool \kn{Briefly mention what is joker tool prior to using the word}, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
-Enabling the Droidfax staTic analysis, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid).
+The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
+Enabling the Droidfax, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid).
 We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated.

### 2021-02-17 introduction.tex
first general review

@@
 algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
-first, we conduct a non-exact replication of the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18}. Our study differs from the original work in two aspects: (a)
+first, we conduct a non-exact replication of the work of \blls. Our study differs from the original work in three aspects: (a)
 by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
-and (c) by evaluating the performance of DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} in its original settings. Considering the other dynamic analysis approaches, which are
-general purpose test case tools for Android, DroidMate has been designed with the goal of mining Android sandboxes---eventhough it has not been tested adequatly
-in the work of Bao et al~\cite{DBLP:conf/wcre/BaoLL18}. In the second study, we explore to what extent we can complement the dynamic analysis approach using
-tainted analysis algorithms.
+and (c) we considering more execution time for each apps analysed at our replication.
+In the second study, we explore to what extent we can complement the dynamic analysis approach using tainted analysis algorithms, through Flowdroid \cite{DBLP:conf/pldi/ArztRFBBKTOM14} tool.
 
@@
 Section 2 we present a background and some related works.
-Section 3 describes all malware apps used in our experiment, presenting their characterization.
-Section 4 introduces the study setting of our research and Section 5 complements presenting some results, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples.
-Finally, Sections 6 and 7, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.
+Section 3 introduces the study setting of our research and Section 4 complements presenting some results and discussion, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples.
+Finally, Sections 5 and 6, summarizes the paper, presenting some threats, presenting the final conclusions, and discussing our ideas for future works.
 

### 2021-02-17 results.tex
first general review

--- 2021-02-16 results.tex
@@
 of DroidFax static analysis algorithms(WOS). 
-\kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done.
-}The Improvement column shows the impact
+%\kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done. }
+The Impact column shows the impact
 (in percentage) of DroidFax static analysis algorithms in the results.
-\kn{Is this really improvement?
+%\kn{Is this really improvement?
 Is this not "contribution" of droidfax.
@@
 Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
-In the previous work~\cite{}, the authors do not present a
+In the \blls, the authors do not present a
 discussion about the influence of DroidFax in the results, even
@@
    \toprule
-   Tool & Exec. (WS) & Exec. (WOS) & Improvement (\%) \\   \midrule
+   Tool & Exec. (WS) & Exec. (WOS) & Impact (\%) \\   \midrule
   Monkey &  71 &  54 & 23.94 \\ 
@@
 This difference might be due to the Monkey using strategy that incorporates randomness for test case generation.
-\rb{I am not convinced that the other tools do not employ any randomness.} For our second execution (Exec WOS), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec.
+%\rb{I am not convinced that the other tools do not employ any randomness.}
+For our second execution (Exec WOS), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec.
 (II).
-\rb{Considering only one run for each configuration, that is Exec.
+%\rb{Considering only one run for each configuration, that is Exec.
 (I) and Exec.
@@
 However, in our second execution (Exec WOS), its performance decreased to 20.58 \%.
-\rb{Not sure if the following sentence is right.} Despite this reduction, it detected the largest number of malicious apps in the Exec.
-WOS.
+%\rb{Not sure if the following sentence is right.}
+Despite this reduction, it detected the largest number of malicious apps in the Exec. WOS.
 
@@
 (I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%).
-Since Bao et al.
-did not explored Humanoid in their study, we do not have a baseline for comparison.
+Since \blls did not explored Humanoid in their study, we do not have a baseline for comparison.
 Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.
@@
 Differently, the Monkey's sandbox detected five malwares that had not been detected by any other sandbox, DroidBot sandbox detected four malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox.
-Contrasting with the Bao et al.
-work~\cite{DBLP:conf/wcre/BaoLL18},
+Contrasting with the \blls,
 our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
@@
 According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are \emph{adwares}, three are \emph{trojans}, two are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
-\rb{In what follows we present some characteristics of malwares that had not been detected by the sandboxes.}
+In what follows we present some characteristics of malware that had not been detected by the sandboxes (app 81 and app 65).
 
-\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.
+The first listing refers to app 81, which has a less dangerous malicious strategies, and just translate the app from English language to Chinese language.
+That modification, does not threaten the user's device, however it is a unwanted private app change, and can characterize as misappropriation app.
+
+\begin{lstlisting}[caption= smali/mobi/infolife/cachepro/h.smali - App81,language=Java, basicstyle=\tiny,label={lst:app81}]
+
+1:B <     const-string v3, "Swith To "
+---
+1:M >     const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
+\end{lstlisting}
+
+\begin{lstlisting}[caption=AndroidManifest.xml - App 65, language=Java, basicstyle=\tiny,label={lst:app65}]
+
+1:B <         <meta-data android:name="ADMOB_PUBLISHER_ID"
+                     android:value="a14cf7346295891"/>
+---
+1:M >         <meta-data android:name="ADMOB_PUBLISHER_ID"
+                     android:value="a14f099bfbf3c61"/>
+\end{lstlisting}
+
+The second listing refers to app 65.
+Your malicious version change the Android Manifest file, modifying the identification of meta-data ADMOB\_PUBLISHER\_ID.
+AdMob \cite{admob} is a mobile app monetization service, provided by Google.
+The Publisher ID \cite{publisherID} is the unique identifier for the AdMob account, and may be used to authenticate communication with Google.
+With that change, the malware is changing the ad revenue destination.
+
+Now we present an malicious app that was detected by 2 sandboxes.
+The app 47 belongs to ours dataset, and is a troubling example.
+First it modify the Android Manifest file, adding permissions to receive and send SMS (Listing 3).
+Then, the malicious app use those permissions to performs MainService.java file, that get user's sensitive information, like International Mobile Equipment Identity (IMEI), and sink by SMS message (Listing 4).
+This malicious behaviours was detected by Droidbot and Humanoid tools.
+
+\begin{lstlisting}[caption= AndroidManifest.xml - App 47, language=Java, basicstyle=\tiny,label={lst:app47:androidmanifest}]
+
+67:M >    <uses-permission android:name="android.permission.RECEIVE_SMS"/>
+68:M >    <uses-permission android:name="android.permission.SEND_SMS"/>
+\end{lstlisting}
+
+\begin{lstlisting}[caption= com/android/main/MainService.java - App 47, language=Java, basicstyle=\tiny,label={lst:app47:mainservice}]
+
+492:M > localObject2 = (TelephonyManager)getSystemService("phone");
+493:M > if (localObject2 != null)
+494:M > {
+495:M >  this.imei = ((TelephonyManager)localObject2).getDeviceId();
+496:M >  this.imsi = ((TelephonyManager)localObject2).getSubscriberId();
+497:M >  this.iccid = ((TelephonyManager)localObject2).getSimSerialNumber();
+498:M > }
+// [...]
+519:M > if ("".equals(this.destMobile)) {
+520:M >  getDestMobile();
+521:M > }
+522:M > sendSMS(this.destMobile, "imei:" + this.imei)
+\end{lstlisting}
+
+%\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.
 I think Thales could work on this, since he has helped Handrick to dissect the malwares.}
@@
   The performance of FlowDroid to identify malicious behavior
-  using our approach is superior than the performance of the
+  is superior than the performance of the
   mining sandbox approach supported by dynamic analysis only---without
@@
 a completely different static analysis approach. Furthermore,
-FlowDroid shows to bem more effective than DroidFax, detecting 25 malicious
+FlowDroid shows to be more effective than DroidFax, detecting 25 malicious
 apps that had not been detected by DroidFax (while DroidFax detected nine

### 2021-02-17 setup.tex
first general review

@@
 
-Bao et al.'s ~\cite{DBLP:conf/wcre/BaoLL18} study explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis.
+\blls explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis.
 Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we perform a non-exact replication to understand the static analysis impact may have had in the results.
@@
 Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
-mining sandboxes. In addition, we discarded six pairs of
+mining sandboxes. In addition, we discarded $6$ pairs of
 Android apps we were not able to instrument---out of the $102$ pairs used in the original work.
@@
 
-The other $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
-DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}.
-We selected Droidbot and DroiMate because they achieved
+The others $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
+DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at \blls. We selected Droidbot and DroiMate because they achieved
 the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls.
-We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation.
-Since Monkey was developed for stress testing, and can not perform text input, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
+We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}.
+It is part of the Android SDK, and does not require any additional installation effort.
+Since Monkey was developed for stress testing, and can not perform text input, only generating
+UI events, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
 For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
@@
 malicious behaviors in the sandbox modeled by the test generation tool
-under analysis.
+under analysis. Figure \ref{fig:setup} shows this experimental setup.
 
-%% Figure \ref{fig:setup} shows this experimental setup.
-
-%% \begin{figure}[ht]
-%%   \includegraphics[width=0.45\textwidth]{images/setup.png}
-%%   \label{Experiment setup}
-%%   \caption{}
-%%   \label{fig:setup}
-%% \end{figure}
+\begin{figure}[ht]
+   \includegraphics[width=0.45\textwidth]{images/setup2.png}
+   \label{Experiment setup}
+   \caption{Experiment setup}
+   \label{fig:setup}
+ \end{figure}
 

### 2021-02-17 threats.tex
first general review

@@
 
-Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution.
+As any empirical work, this work also has limitations and threats to its validity.
+
+\textbf{Internal Validity.} Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution.
 To mitigate this, we have used a configuration of the benchmark DroidXP tool that runs multiple times each test and computes the average result from those executions.
@@
 This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.
+
+\textbf{External Validity.} As this is a replication study, it brings some of the same threats \blls had presented.
+This study used the same set of apps, which were from a piggy-backed app dataset released by Li et al.~\cite{li2017understanding} So, using this dataset, we could not cover all categories of Android malware.
+Besides that, we only used a small number of test case generation tools in this study.
+To mitigate these threats and enrich our research data, we plan to test more apps and use other test case generation tools.
+
+In this study, we used a single tool for Tainted Analysis.
+With such a small number of tools, we could not have a sample of what a static analysis tool could help in Tainted Analysis.
+So, we plan to use more tools to mitigate this threat.

### 2021-02-22 results.tex
add new results version

@@
 
-\rb{This is a nice place to present some details about the malwares
-  that FlowDroid had detected, showin the additional source-sink pairs
-  that emmerged. A discussion about these aforementioned four pairs would
-  also be relevant.}
+Here we present details about one of the malwares that Flowdroid had detected.
+At this example, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours.
+The pictures \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.
 
-\rb{I finished my first review until this place. Tomorrow I will continue
-from here.}
+\begin{figure}[h]%
+    \centering
+    \subfloat[\centering Path source/sink from benign app]{{\includegraphics[width=5cm]{images/pathbenign.png} }}%
+    \qquad
+    \subfloat[\centering Path source/sink from malicious app]{{\includegraphics[width=5cm]{images/pathmalicious.png} }}%
+    \caption{Pairs source/sink different (B/M)}%
+    \label{fig:sourcesink}%
+\end{figure}
 

### 2021-02-25 results.tex
update the script to report the results of the three executions

@@
    Tool & Exec. (WS) & Exec. (WOS) & Impact (\%) \\   \midrule
-  Monkey &  71 &  54 & 23.94 \\ 
-  DroidMate &  64 &  48 & 25.00 \\ 
-  DroidBot &  68 &  54 & 20.59 \\ 
-  Humanoid &  49 &  15 & 69.39 \\ 
-  \joke &  42 &   0 & 100.00 \\ 
+   DroidBot &  73 & 61.00 & 16.44 \\ 
+   Monkey &  71 & 56.00 & 21.13 \\ 
+   DroidMate &  68 & 52.00 & 23.53 \\ 
+   Humanoid &  56 & 27.00 & 51.79 \\ 
+\joke &  42 & 0.00 & 100.00 \\ 
  \bottomrule

### 2021-02-25 results/script.Rmd
update the script to report the results of the three executions

@@
 title: "Analysis"
-output: html_document
+output:
+  html_document: default
+  pdf_document: default
 ---
@@
 
-## Load the Summary Dataset for Study 1
+## Load the Complete Dataset for Study 1
 
 ```{r}
-ds <- read.csv("./execution01.csv", head=T, sep=",")
-ds["Improvement"] = (ds$WithDroidFax - ds$WithoutDroidFax) * 100 / ds$WithDroidFax
-xtable(ds)
+ds <- read.csv("allreportResults.csv", head=T, sep=",")
+
+staticAnalysis <- sqldf("select tool, count(distinct app) totalWith
+                        from ds 
+                        where malware = 1 and static = 1 and tool != 'flowdroid'
+                        group by tool")
+
+withoutStaticAnalysis <-  sqldf("select tool, count(distinct app) totalWithout
+                                  from ds 
+                                  where malware = 1 and static = 0
+                                  group by tool")
+
+res <- merge(staticAnalysis, withoutStaticAnalysis, all.x=T)
+
+res[is.na(res)] <- 0
+res["Improvement"] = (res$totalWith  - res$totalWithout) * 100 / res$totalWith 
+xtable(res[order(-res$totalWith),])
 ```
 
-## Load the Complete Dataset for Study 1
+## Compare the performance of the different tools (with DroidFax)
 
-```{r venn-plot-s1}
-ds <- read.csv("./report_withStatic.csv", head=T, sep=",")
+```{r, venn-plot-s1}
 
-sets <- sqldf("select tool, app from ds where malware = 'True'")
+colnames(ds)
+sets <- sqldf("select tool, app, count(*) total 
+                  from ds 
+                  where malware = 1 and static = 1
+                  group by tool, app")
+
 monkey = sets[sets$tool=="monkey", c("app")]
@@
 joker = sets[sets$tool=="joke", c("app")]
-
-venn.diagram(
-  x = list(monkey, humanoid, droidmate, droidbot, joker),
-  category.names = c("Monkey" , "Humanoid" , "DroidMate", "DroidBot", "Joker"),
-  filename = './venn.png',
-  output=TRUE
-)
 
@@
 ```{r}
-sqldf("select count(distinct app) from ds where malware = 'True'")
+sqldf("select count(distinct app) from ds where malware = 1")
 ```
@@
 
-```{r venn-plot-s2}
+```{r}
 ds <- read.csv("allreportResults.csv", head=T, sep=",")
+```
+
+## Compare the performance of FlowDroid and DroidFax (Joker tool)
+
+```{r, venn-plot-s2}
 sets <- sqldf("select tool, app 
@@
                       app not in (select app from sets)")
-
-# subsets
-notDetected
 

### 2021-02-25 abstract-jss.tex
elsevier template

--- 2021-02-12 abstract.tex
@@
 \begin{abstract}
-%  \emph{Context.}
-%  The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
-For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
-%  \emph{Problem.}
   The use of sandboxes is an effective technique for malware analysis.
@@
 
-\begin{IEEEkeywords}
-Malware Detection,
-Mining Sandboxes,
-Software Security,
-Android Platform,
-Empirical Studies,
-Static Analysis and Dynamic Analysis
-\end{IEEEkeywords}
+\begin{keyword}
+Malware Detection \sep Mining Sandboxes \sep Android Platform \sep Static Analysis and Dynamic Analysis 
+\end{keyword}

### 2021-02-25 abstract.tex
revision for jounal - abstract/introduction/background/study settings

@@
 %  \emph{Context.}
-%  The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
-For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to mine Android Sandboxes.
+The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}.
 %  \emph{Problem.}

### 2021-02-25 background.tex
revision for jounal - abstract/introduction/background/study settings

@@
 L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
-This study indicates that these tools was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect 75.49\% of malicious behavior explored ($77$ among $102$).
+This study indicates that these tools was efficient in identifying at most $70$\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect $75.49$\% of malicious behavior explored ($77$ among $102$).
 However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps

### 2021-02-25 introduction.tex
revision for jounal - abstract/introduction/background/study settings

@@
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
-Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
+Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
 Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes.
-In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic analysis, and then block future calls to sensitive resources unidentified during testing, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
+In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic and static analysis, and then block future calls to sensitive resources unidentified during this exploratory phase, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
 
@@
 The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase.
-Using this approach, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox rules.
+Using this approach, based on just test case generation tools, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox security rules.
 
 Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
-The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be \kn{Ok.
+The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be.
+%\kn{Ok.
 In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes.
-The overall flow of definitions needs some thought}.
+The overall flow of definitions needs some thought}
 Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime.
@@
 algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
-first, we conduct a non-exact replication of the work of \blls. Our study differs from the original work in three aspects: (a)
+first, we conduct a replication of the work of \blls. Our study differs from the original work in three aspects: (a)
 by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
-and (c) we considering more execution time for each apps analysed at our replication.
+and (c) we considering more execution time, and more repetitions, for each apps analysed at our replication.
 In the second study, we explore to what extent we can complement the dynamic analysis approach using tainted analysis algorithms, through Flowdroid \cite{DBLP:conf/pldi/ArztRFBBKTOM14} tool.
 
-Altogether, this paper brings the following contributions:
+\textit{Extended Version.} This journal paper extends a previous conference publication~\cite{DBLP:conf/scam/CostaMCMVBC20} by expanding the empirical evaluation of sandboxes solutions using DroidXP benchmark tool with:
+ \begin{enumerate}[(1)]
+  \item presenting a replication of the accuracy study of test generation tools for mining android sandboxes, using an extension and update of our benchmark solution, that aided us disables the static analysis performed by DroidFax.
 
-\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
+  \item discovering which are the contribution installments of types of analysis for malware detection task.
+
+  \item presenting what malware and its characteristics, that was not detected by any tool in our analysis dynamic and static experiment.
+
+  \item presenting data that indicate that static analysis can improve the mining sandboxes process for malware detection.
+  \end{enumerate}
+
+%Altogether, this paper brings the following contributions:
+%\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
 The rest of the paper is organized as follows.

### 2021-02-25 setup.tex
revision for jounal - abstract/introduction/background/study settings

@@
 \blls explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis.
-Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we perform a non-exact replication to understand the static analysis impact may have had in the results.
-Thus, this section present the settings of our study, whose goal is to perform this non-exact replication, and thus build a general understanding of the implications of static analysis algorithms in their results.
+Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we replicated its work to understand the static analysis impact may have had in their results.
+Thus, this section present the settings of our study, whose goal is to perform this replication, and thus build a general understanding of the implications of static analysis algorithms in the results.
 We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.
@@
 We conducted two studies to answer the research questions above.
-First we performed a non-exact replication of the \blls.
-Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
-mining sandboxes. In addition, we discarded $6$ pairs of
+First we replicated the \blls.
+However, our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms, in the task to identify malicious apps.
+In addition, we discarded $6$ pairs of
 Android apps we were not able to instrument---out of the $102$ pairs used in the original work.
-We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.
+We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, and repeated all the execution more 2 times, therefore totaling three executions.
+The original study executed each app at each tool, for just one minute, and just one time.
 
@@
 UI events, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
-For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
+For the replication, we also used our benchmark tool, DroidXP ~\cite{DBLP:conf/scam/CostaMCMVBC20},
 which helped us to reproduce the original work.
@@
 behavior using static taint analysis of Android apps. We use two metrics in this second study: the number
-of source-sink flows that FlowDroid identifies when considering the pairs of Android apps (B/M) and the
+of source-sink flows that FlowDroid identifies when considering the pairs of Android apps (B/M), and the
 execution time of the analysis for each app.
@@
 
-\subsection{First Study: A non-exact replication}
+\subsection{First Study: A replication \blls}
 
@@
 Android app (B/M) in each one of the five test generation tools, including Joker,
-for $3$ minutes. We then investigate the performance of each tool to detect
-malicious behaviors in the sandbox modeled by the test generation tool
+for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox modeled by the test generation tool
 under analysis. Figure \ref{fig:setup} shows this experimental setup.
@@
 
-After that, we replicated the study using a configuration of DroidXP that
-disables the DroidFax static analysis algorithm. With this new configuration,
-we executed the benchmark one more time, using the same dataset of Android
-apps, the same execution time, and the same test case generation tools.
+After that, we replicated the study using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
+With this new configuration, we executed the benchmark again, using the same dataset of Android pairs apps, the same execution time, and the same test case generation tools.
 The results of this replication allow us to compute the effective performance

### 2021-02-26 results.tex
revision for jounal - results

--- 2021-02-22 results.tex
@@
 
-Our first study performed a non-exact replication of the \blls.
+Our first study performed a replication of \blls.
 %\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
@@
 though here we report that the impact of DroidFax to the results is significant in the
-range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
+range from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
 \joke tool for which DroidFax improves its performance by 100\% (as expected).
@@
    Tool & Exec. (WS) & Exec. (WOS) & Impact (\%) \\   \midrule
-  Monkey &  71 &  54 & 23.94 \\ 
-  DroidMate &  64 &  48 & 25.00 \\ 
-  DroidBot &  68 &  54 & 20.59 \\ 
-  Humanoid &  49 &  15 & 69.39 \\ 
+   DroidBot &  73 & 61 & 16.44 \\ 
+   Monkey &  71 & 56 & 21.13 \\ 
+   DroidMate &  68 & 52 & 23.53 \\ 
+   Humanoid &  56 & 27 & 51.79 \\ 
 \joke &  42 & 0 & 100.00 \\ 
@@
 
-\subsubsection*{Monkey} sandbox for the execution WS detected more apps with malicious behavior than any other tool considered in our study (71 out of the 96 pairs of Android apps).
-Contrasting, in the original study, Monkey got the third-best performance, detecting 48 malwares within the 102 pairs (47.05\%).
+\subsubsection*{Monkey} sandbox for the execution WS detected in our study ($71$ out of the $96$ pairs of Android apps).
+Contrasting, in the original study, where Monkey got the third-best performance, detecting $48$ malwares within the 102 pairs ($47.05$\%).
 This difference might be due to the Monkey using strategy that incorporates randomness for test case generation.
 %\rb{I am not convinced that the other tools do not employ any randomness.}
-For our second execution (Exec WOS), there is a reduction of 23.94\% in the Monkey's performance, totaling 54 malware detected---which matches the performance of DroidBot for Exec.
-(II).
+For our second execution (Exec WOS), there is a reduction of $21.13$\% in the Monkey's performance, totaling $56$ malware detected.
 %\rb{Considering only one run for each configuration, that is Exec.
@@
 \subsubsection*{DroidBot} in the first execution (Exec.
-WS) its resulting sandbox detected a total of 68 malware among $96$ pairs analyzed (70.83\%).
-Interesting, this is the same performance of the original study---although the original study analyzed $102$ pairs of Android apps.
-Also, in the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
-However, in our second execution (Exec WOS), its performance decreased to 20.58 \%.
+WS) its resulting sandbox detected a total of $73$ malware among $96$ pairs analyzed ($76.04$\%), more apps with malicious behavior than any other tool.
+Like the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
+However, in our second execution (Exec WOS), its performance decreased to ($16.44$\%).
 %\rb{Not sure if the following sentence is right.}
@@
 
-\subsubsection*{DroidMate} in the first execution(WS) led to a sandbox that detected 64 apps with malicious behavior (66.66\%).
-Contrasting, in the original study DroidMate detected 54 among 102 (52.94\%).
+\subsubsection*{DroidMate} in the first execution(WS) led to a sandbox that detected 68 apps with malicious behavior ($70.83$\%).
+Contrasting, in the original study DroidMate detected $54$ among $102$ ($52.94$\%).
 A possible explanation for this difference is that here we use the more recent version of DroidMate.
-In the second execution(WOS), without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by 25\%, being able to detect only 48 out of the 96 pairs of Android apps.
+In the second execution(WOS), without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by ($23.53$\%), being able to detect only 52 out of the 96 pairs of Android apps.
 
@@
 work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate.
-In the first execution (Exec.
-(I)), the resulting Humanoid sandbox identified 49 malwares in our dataset (51.04\%).
+In the first execution (WS), the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%).
 Since \blls did not explored Humanoid in their study, we do not have a baseline for comparison.
-Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing 69.38\% of its effectiveness, and being able to detect just 15 malwares.
+Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing ($51.79$\%) of its effectiveness, and being able to detect just $27$ malwares.
 
@@
 summarizes how the tools can complement each other.
-Note in the diagram that 47 malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 77 identified by at least one sandbox.
+Note in the diagram that $53$ malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 78 identified by at least one sandbox.
 In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools.
-Differently, the Monkey's sandbox detected five malwares that had not been detected by any other sandbox, DroidBot sandbox detected four malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox.
+Differently, the Monkey's sandbox detected three malwares that had not been detected by any other sandbox, DroidBot sandbox detected two malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox.
 Contrasting with the \blls,
@@
 
-Altogether, ignoring the \joke tool, our study reveals that from 51.04\% (Humanoid)
-to 73.95\% (Monkey) of the malicious apps investigated in our study can be
+Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
+to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
 detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms.
-Besides that, in the first execution, none of the resulting sandboxes could detect 19 malwares in our dataset (19.79\%).
-According to the Euphony tool~\cite{hurier2017euphony}, 13 of these 19 malwares are \emph{adwares}, three are \emph{trojans}, two are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
-In what follows we present some characteristics of malware that had not been detected by the sandboxes (app 81 and app 65).
+Besides that, in the first execution, none of the resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%).
+According to the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
+In what follows we present some characteristics of two malware that had not been detected by the sandboxes (mobi.infolife.cachepro) and (com.andoop.flyracing), both downloaded from alternative android market, anzhi~\cite{anzhi}.
 
-The first listing refers to app 81, which has a less dangerous malicious strategies, and just translate the app from English language to Chinese language.
+The first listing refers to package (mobi.infolife.cachepro), which has a less dangerous malicious strategies, and just translate the app from English language to Chinese language.
 That modification, does not threaten the user's device, however it is a unwanted private app change, and can characterize as misappropriation app.
 
-\begin{lstlisting}[caption= smali/mobi/infolife/cachepro/h.smali - App81,language=Java, basicstyle=\tiny,label={lst:app81}]
+\begin{lstlisting}[caption= smali/mobi/infolife/cachepro/h.smali - (mobi.infolife.cachepro),language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:mobi.infolife.cachepro}]
 
@@
 
-\begin{lstlisting}[caption=AndroidManifest.xml - App 65, language=Java, basicstyle=\tiny,label={lst:app65}]
+\begin{lstlisting}[caption=AndroidManifest.xml - (com.andoop.flyracing), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65}]
 
@@
 
-The second listing refers to app 65.
+The second listing refers to package (com.andoop.flyracing).
 Your malicious version change the Android Manifest file, modifying the identification of meta-data ADMOB\_PUBLISHER\_ID.
@@
 Now we present an malicious app that was detected by 2 sandboxes.
-The app 47 belongs to ours dataset, and is a troubling example.
+The package (com.gau.screenguru.finger) belongs to ours dataset, and is a troubling example.
 First it modify the Android Manifest file, adding permissions to receive and send SMS (Listing 3).
 Then, the malicious app use those permissions to performs MainService.java file, that get user's sensitive information, like International Mobile Equipment Identity (IMEI), and sink by SMS message (Listing 4).
-This malicious behaviours was detected by Droidbot and Humanoid tools.
+This malicious behaviours was detected by sandboxes builded by Droidbot and Humanoid tools.
 
-\begin{lstlisting}[caption= AndroidManifest.xml - App 47, language=Java, basicstyle=\tiny,label={lst:app47:androidmanifest}]
+\begin{lstlisting}[caption= AndroidManifest.xml - (com.gau.screenguru.finger), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:com.gau.screenguru.finger:androidmanifest}]
 
@@
 
-\begin{lstlisting}[caption= com/android/main/MainService.java - App 47, language=Java, basicstyle=\tiny,label={lst:app47:mainservice}]
+\begin{lstlisting}[caption= com/android/main/MainService.java - (com.gau.screenguru.finger), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:(com.gau.screenguru.finger):mainservice}]
 
@@
 To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
-Regarding accuracy, the tainted analysis approach detected 58 out of the 96 pairs in our dataset (60,42\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
+Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
 
@@
 the results from FlowDroid and DroidFax, we were able to detect
-67 of the malicious apps (69.79\%), a performance compatible
+$67$ of the malicious apps ($69.79$\%), a performance compatible
 to that we found as response to the first execution of the
 test case generation tools---which also considers the DroidFax
-static analysis algorithms. More interesting, from those 67
-malicious apps identified, 33 pairs had been found by
+static analysis algorithms. More interesting, from those $67$
+malicious apps identified, $33$ pairs had been found by
 both tools (FlowDroid and DroidFax), even though they follow
 a completely different static analysis approach. Furthermore,
-FlowDroid shows to be more effective than DroidFax, detecting 25 malicious
-apps that had not been detected by DroidFax (while DroidFax detected nine
+FlowDroid shows to be more effective than DroidFax, detecting $25$ malicious
+apps that had not been detected by DroidFax (while DroidFax detected $9$
 malicious apps that had not been detected by FlowDroid).
@@
 
-Finally, we can highlight that FlowDroid was able to detect four malwares among the 19 malicious Android apps that had not
+Finally, we can highlight that FlowDroid was able to detect $4$ malwares among the $18$ malicious Android apps that had not
 been detected by the sandboxes constructed in the first study. Among these
-four malwares, two are \emph{trojans}, 1 is an \emph{exploit}, and 1
-is an \emph{adware}.
+four malwares, $2$ are \emph{trojans}, $1$ is an \emph{exploit}, and 1 is an \emph{adware}.
 
@@
   it was able to detect only four additional malwares (out of the
-  19) that had not been detected in the first study. 
+  18) that had not been detected in the first study. 
 \end{finding}
 
-Here we present details about one of the malwares that Flowdroid had detected.
-At this example, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours.
-The pictures \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.
+Here we present details about one of the malware that Flowdroid had detected.
+At this package (com.yy.fontmaster), from another alternative android market, angeeks~\cite{angeeks}, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours.
+The Figure \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.
 
-\begin{figure}[h]%
+\begin{figure}[ht]%
     \centering

### 2021-03-01 results.tex
review of the first part of the Results section

@@
 
-In this section we detail the findings of our study. We first present the results of each study
-in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}. In Section~\ref{sec:discussion} we summarize the
+In this section we detail the findings of our study. We present the results of the first and
+second studies in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}. In Section~\ref{sec:discussion} we summarize the
 implications of our study.
@@
 
-Our first study performed a replication of \blls.
-%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
-As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration.
-After that, we executed the analysis again by disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
-Table~\ref{tab:fs} summarizes the results of the execution.
-The columns Exec.
-(WS) and Exec.
-(WOS)
+Our first study is a replication of the \blls.
+As discussed in the previous section, to this end, we first executed the analysis using the DroidXP benchmark with its default
+configuration. After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm.
+In this way, we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
+Table~\ref{tab:fs} summarizes the results of the executions. The columns Exec. (WS) and Exec. (WOS) 
 show the number of malwares identified when executing each tool with the
-support of the DroidFax static analysis algorithms(WS) and without the support
-of DroidFax static analysis algorithms(WOS). 
-%\kn{I have changed the I and II to Ws and WOS because I and II makes it sound like we ran the experiments two times which we have not yet done. }
+support of the DroidFax static analysis algorithms (WS) and without the support
+of DroidFax static analysis algorithms (WOS). 
 The Impact column shows the impact
 (in percentage) of DroidFax static analysis algorithms in the results.
-%\kn{Is this really improvement?
-Is this not "contribution" of droidfax.
-Improvement happens when an earlier approach detected malware without support of droidfax.
-Here 23\% of malwares are simply detected by the presence of droidfax (so IMO it should be impact or contribution) not improvement}
-In the \blls, the authors do not present a
+
+Note taht, in the \blls, the authors do not present a
 discussion about the influence of DroidFax in the results, even
-though here we report that the impact of DroidFax to the results is significant in the
-range from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
-\joke tool for which DroidFax improves its performance by 100\% (as expected).
+though here we report that the impact of DroidFax in the results is significant, ranging
+from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
+\joke tool for which DroidFax improves its performance by 100\%. This result is
+expected, since the \joke tool does not execute any dynamic analysis.
 Next we discuss the result of each individual test generation tool.
@@
 
-\subsubsection*{Monkey} sandbox for the execution WS detected in our study ($71$ out of the $96$ pairs of Android apps).
-Contrasting, in the original study, where Monkey got the third-best performance, detecting $48$ malwares within the 102 pairs ($47.05$\%).
-This difference might be due to the Monkey using strategy that incorporates randomness for test case generation.
-%\rb{I am not convinced that the other tools do not employ any randomness.}
-For our second execution (Exec WOS), there is a reduction of $21.13$\% in the Monkey's performance, totaling $56$ malware detected.
-%\rb{Considering only one run for each configuration, that is Exec.
-(I) and Exec.
-(II), we cannot assure that the difference is due to disabling the DroidFax static analysis algorithms.}
+\begin{description}
+\item[DroidBot] in the first execution (Exec. WS) led to a sandbox that detected a total of $73$ malware among $96$ pairs present in our dataset ($76.04$\%),
+  detecting more apps with malicious behavior than any other tool. Similar to the \blls, DroidBot is the test case generation tool
+  whose resulting sandbox detected the largest number of malicious apps. Moreover, in our second execution (Exec WOS), removing the DroidFax
+  static analysis support reduced the DroidBot performance in 16.44\%, the smaller impact we observed among the tools.
 
-\subsubsection*{DroidBot} in the first execution (Exec.
-WS) its resulting sandbox detected a total of $73$ malware among $96$ pairs analyzed ($76.04$\%), more apps with malicious behavior than any other tool.
-Like the original study, DroidBot was the test case generation tool whose resulting sandbox detected the largest number of malicious apps.
-However, in our second execution (Exec WOS), its performance decreased to ($16.44$\%).
-%\rb{Not sure if the following sentence is right.}
-Despite this reduction, it detected the largest number of malicious apps in the Exec. WOS.
+  \item [Monkey] in the first execution (Exec. WS) produced a sandbox that detected $71$ out of the $96$ pairs of Android apps.
+    Contrasting, in the original study, the Monkey's sandbox detected $48$ malwares within the 102 pairs ($47.05$\%). This difference
+    might be due to the fact that Monkey uses a random strategy for test case generation and here we considered the outcomes
+    of three executions---while in the \blls, the authors consider the outcomes of one execution. 
+    Considering our second execution (Exec WOS), there is a reduction of $21.13$\% in the Monkey's performance, leading to
+    a sandobox that was able to detect $56$ malwares.
 
-\subsubsection*{DroidMate} in the first execution(WS) led to a sandbox that detected 68 apps with malicious behavior ($70.83$\%).
-Contrasting, in the original study DroidMate detected $54$ among $102$ ($52.94$\%).
-A possible explanation for this difference is that here we use the more recent version of DroidMate.
-In the second execution(WOS), without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by ($23.53$\%), being able to detect only 52 out of the 96 pairs of Android apps.
+  \item[DroidMate] in the first execution (Exec. WS) led to a sandbox that detected 68 apps with malicious behavior ($70.83$\%).
+    In the \blls study, DroidMate also detected $68$ malwares, though considering the $102$ pairs of apps used in the
+    original study. In the second execution(WOS),
+    without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by $23.53$\%, being able to detect
+    52 out of the 96 pairs of Android apps.
 
-\subsubsection*{Humanoid} presented the worse performance, even though a previous
-work~\cite{DBLP:conf/kbse/LiY0C19} shows that it presents the highest lines coverage in comparison to Monkey, DroidBot, and DroidMate.
-In the first execution (WS), the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%).
-Since \blls did not explored Humanoid in their study, we do not have a baseline for comparison.
-Regarding the second execution, without static analysis, Humanoid was the most affected by disabling the DroidFax static analysis algorithm, losing ($51.79$\%) of its effectiveness, and being able to detect just $27$ malwares.
+  \item[Humanoid] showed the worse performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
+    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. WS),
+    the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%). Humanoid was the most affected in the second
+    execution (Exec. WOS), whose resulting sandbox presents a redunction of $51.79$\%  in the number of detected malwares.
+    Since the \blls did not explore Humanoid,
+    we do not have a baseline for comparison with the previous work.
 
-\subsubsection*{\joke} is our fake test case generation tool that we use to help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes.
-We integrated \joke into the DroidXP benchmark as an additional test generation tool that does not run the Android apps during the benchmark execution.
-As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms only.
-For the first execution, with the DroidFax static algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares.
-For the second execution, that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was unable to detect any malware.
-This result was expected, since \joke does not analyze the Android apps during the benchmark execution.
+  \item[\joke] is our fake test case generation tool that help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes.
+    We integrated \joke into the DroidXP benchmark as an additional test case generation tool that does not run the Android apps during the benchmark execution.
+    As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms alone. For the first execution, with the DroidFax static
+    algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares. For the second execution,
+    that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was not able to detect any malware. This result
+    was expected, since \joke does not analyze the Android apps during the benchmark execution.
+
+\end{description}
 

### 2021-03-01 results.tex
additional review related to the malware examples

@@
 summarizes how the tools can complement each other.
-Note in the diagram that $53$ malwares have been detected by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms), out of the 78 identified by at least one sandbox.
-In addition, the DroidBot sandbox did not detect any malware that had not been detected by the other tools.
-Differently, the Monkey's sandbox detected three malwares that had not been detected by any other sandbox, DroidBot sandbox detected two malwares that had not been detected by any other sandbox, and Humanoid detected one malware that had not been detected by any other sandbox.
-Contrasting with the \blls,
-our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid does not improve the general performance of an integrated environment for mining
+Note in the diagram that $53$ malwares have been detected
+by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms),
+out of the 78 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect
+any malware that had not been detected by the other tools. Differently, the Monkey sandbox detected
+three malwares that had not been detected by any other sandbox, the DroidBot sandbox detected two malwares
+that had not been detected by any other sandbox, and the Humanoid sandbox detected one malware that had not
+been detected by any other sandbox. Contrasting with the \blls,
+our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid
+does not improve the general performance of an integrated environment for mining
 Android sandboxes.
@@
 to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
-detected using the sandboxes generated after running the test case tools with the support of DroidFax static analysis algorithms.
-Besides that, in the first execution, none of the resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%).
-According to the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
-In what follows we present some characteristics of two malware that had not been detected by the sandboxes (mobi.infolife.cachepro) and (com.andoop.flyracing), both downloaded from alternative android market, anzhi~\cite{anzhi}.
+detected using the sandboxes generated after running the test case tools with the support of the
+DroidFax static analysis algorithms. Besides that, in the first execution, none of the
+resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
+the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
+PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
 
-The first listing refers to package (mobi.infolife.cachepro), which has a less dangerous malicious strategies, and just translate the app from English language to Chinese language.
-That modification, does not threaten the user's device, however it is a unwanted private app change, and can characterize as misappropriation app.
+The DroidBot and Humanoid sandboxes detected the malicious version of the app
+\texttt{com.andoop.flyracing}. In this particular case,
+the malicious version changed the Android Manifest file,
+adding permissions to receive and send SMS messages
+(Listing~\ref{lst:androidManifest}). Moreover, after decompiling
+this malware, we also observed that the malicious version of the
+\texttt{MainService} class introduced a
+behavior that collects sensitive information (the International Mobile
+Equipment Identity, IMEI) and sends it using an SMS message
+(Listing~\ref{lst:mainService}).
 
-\begin{lstlisting}[caption= smali/mobi/infolife/cachepro/h.smali - (mobi.infolife.cachepro),language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:mobi.infolife.cachepro}]
-
-1:B < const-string v3, "Swith To "
----
-1:M > const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
-\end{lstlisting}
-
-\begin{lstlisting}[caption=AndroidManifest.xml - (com.andoop.flyracing), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65}]
-
-1:B < <meta-data android:name="ADMOB_PUBLISHER_ID"
-                     android:value="a14cf7346295891"/>
----
-1:M > <meta-data android:name="ADMOB_PUBLISHER_ID"
-                     android:value="a14f099bfbf3c61"/>
-\end{lstlisting}
-
-The second listing refers to package (com.andoop.flyracing).
-Your malicious version change the Android Manifest file, modifying the identification of meta-data ADMOB\_PUBLISHER\_ID.
-AdMob \cite{admob} is a mobile app monetization service, provided by Google.
-The Publisher ID \cite{publisherID} is the unique identifier for the AdMob account, and may be used to authenticate communication with Google.
-With that change, the malware is changing the ad revenue destination.
-
-Now we present an malicious app that was detected by 2 sandboxes.
-The package (com.gau.screenguru.finger) belongs to ours dataset, and is a troubling example.
-First it modify the Android Manifest file, adding permissions to receive and send SMS (Listing 3).
-Then, the malicious app use those permissions to performs MainService.java file, that get user's sensitive information, like International Mobile Equipment Identity (IMEI), and sink by SMS message (Listing 4).
-This malicious behaviours was detected by sandboxes builded by Droidbot and Humanoid tools.
-
-\begin{lstlisting}[caption= AndroidManifest.xml - (com.gau.screenguru.finger), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:com.gau.screenguru.finger:androidmanifest}]
+\begin{lstlisting}[caption={Diffs in the \texttt{com.gau.screenguru.finger}
+      AndroidManifest file of the malicious
+      version}, language=Java,
+    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
+    label={lst:androidManifest}]
 
@@
 
-\begin{lstlisting}[caption= com/android/main/MainService.java - (com.gau.screenguru.finger), language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:(com.gau.screenguru.finger):mainservice}]
+\begin{lstlisting}[caption={Diffs in the malicious version
+      of the class \texttt{com.android.main.MainService}
+      (app \texttt{com.gau.screenguru.finger})},
+      language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
+      label={lst:mainService}]
 
@@
 
-%\rb{This is an interesting place to present the details of two or three malwares in this set of 19 malwares that had not been detected by any tool.
-I think Thales could work on this, since he has helped Handrick to dissect the malwares.}
+%% In what follows we present some characteristics of two malwares
+%% that had not been detected by the sandboxes (app \texttt{mobi.infolife.cachepro} and app \texttt{com.andoop.flyracing}).
+
+%% In the first example (\texttt{mobi.infolife.cachepro}), the malicious behavior comprises changes to
+%% the app idiom (Listing~\ref{lst:app65a}) and to the publisher identifier (Listing~\ref{lst:app65b}).
+%% Although such a modification does not threaten the user's device,
+%% it might characterize a scenario of app misappropiation.
+%% Although such a modification does not threaten the user's device,
+%% it might characterize a scenario of app misappropriation. That is, after manually dissecting this particular malware,
+%% we did not identify any change with regard to calls to sensitive APIs or app behavior.
+
+%% \begin{lstlisting}[caption= {Diff in the file \texttt{smali/mobi/infolife/cachepro/h.smali}. \texttt{B} stands for
+%%     the benign version, while \texttt{M} stands for the malign version.},language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65a}]
+
+%% 1:B < const-string v3, "Swith To "
+%% ---
+%% 1:M > const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
+%% \end{lstlisting}
+
+Differently, none of the computed sandboxes detected the malicious version
+of the app \texttt{com.andoop.flyracing}. Indeed,
+the malicious version {\color{red}only} changes the
+Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}.
+However, the AdMob is a monetization service provided by Google, and changing the
+AdMob \emph{publisher identifier} account redirects the advertisement's
+revenue to another destination.
+
+\begin{lstlisting}[caption={Diff in the file \texttt{com.andoop.flyracing}
+      AndroidManifest file of the malicious version.
+      \texttt{B} stands for
+      the benign version, while \texttt{M} stands for the malign version.}, language=XML,
+    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]
+
+1:B < <meta-data android:name="ADMOB_\PUBLISHER_\ID"
+                     android:value="a14cf7346295891"/>
+---
+1:M > <meta-data android:name="ADMOB_\PUBLISHER_\ID"
+                     android:value="a14f099bfbf3c61"/>
+\end{lstlisting}
 

### 2021-03-02 results.tex
revision for jounal - discussion

@@
 
-First we find that static analysis summaries had impact in the Bao et al.
-study.
-It was responsible for improving the results of the tools by 47.78\% than its executions alone, answering our first research question (RQ1).
-Second, Table \ref{tab:malwareWithout} summarizes our findings addressing the second research question (RQ2).
-We realized that disregarding the static analysis algorithms, and discarding Joke tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, and the least affected was DroidBot, proving be the tool with better effective performance, in terms of the number of detected malware.
+First we find that static analysis summaries had impact in the \blls.
+It was responsible for improving the results of the tools, between $16.44\%$ and $51.79\%$, discarding our Joker tool, answering our first research question (RQ1).
+Second, Table \ref{tab:fs} also summarizes our findings addressing the second research question (RQ2).
+We realized that disregarding the static analysis algorithms, and discarding Joker tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, obtaining an effective performance of $28.12\%$, 27 malicious apps, among 96.
+The least affected was DroidBot, proving be the tool with better effective performance, in terms of the number of detected malware, obtaining an effective performance of $63.54\%$, 61 malicious apps, among 96 .
 Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms.
-Our experiment highlight that 69.79\%-81.25\% of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that
+Our experiment highlight that $69.79\%$-$82.29\%$ of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that
 sandboxes can be further boosted when coupled with new static analysis techniques.
-We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, 81.25\% with Monkey, a better performance than all five tools explored at Bao et al., even when they combined all the tools together at theirs work 75.49\%.
+We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, $82.29\%$ with DroidBot, a better performance than all five tools explored at \blls, even when they constructed a sandbox by combining all test generation tools at theirs work $75.49\%$.
 Table \ref{tab:tanted} display the increase of all tools explored at our research.
@@
  Tool & Increase  &  & \\ \midrule
- Monkey & 7 & 78 & 81.25\\
- DroidMate & 10 &  74 & 77.08 \\
- Humanoid & 20 & 69 & 71.87  \\
- Joke & 25 & 67 & 69.79 \\
- DroidBot & 9 & 77 & 80.20  \\\midrule
+ DroidBot & 6 & 79 & 82.29\\
+ Monkey & 7 &  78 & 81.25 \\
+ DroidMate & 7 & 75 & 78.12  \\
+ Humanoid & 16 & 72 & 75.00 \\
+ Joker & 25 & 67 & 69.79  \\\midrule
 

### 2021-03-02 background.tex
Background

@@
 The sandboxing technique comprises of two steps.
-First, rules are miner and will compose the sandbox,
+First, rules are mined and will compose the sandbox,
 %\kn{I thought sandbox was an environment, now it is comprised of rules?}%
-through test generator tools.
+through test generator tools \kn{This sentence seems to miss something "what" happens through test generation tools.} .
 These tools explore program behavior and monitor access to sensitive APIs.
-The second stage ensures that resources not accessed, or accessed differently, at first stage, are denied access.
+The second stage ensures that resources not accessed, or accessed differently than first stage, are denied access.
 So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

### 2021-03-02 setup.tex
Setup

@@
 \blls explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis.
-Since their study also involved a static analysis component, performed by Droidfax as we described at introduction, and whose impact was not measured, we replicated its work to understand the static analysis impact may have had in their results.
+Since their study also involved a static analysis component, performed by Droidfax as we described in Section~\ref{sec:introduction}, and whose impact was not measured, we replicated its work to understand the static analysis impact may have had in their results.
 Thus, this section present the settings of our study, whose goal is to perform this replication, and thus build a general understanding of the implications of static analysis algorithms in the results.
@@
 
- \item What are the benefits of using tainted analysis algorithms to complement the dynamic analysis provided by test generation tools for mining sandboxes?
+ \item What are the benefits of using tainted\kn{Is it tainted analysis or taint analysis?} analysis algorithms to complement the dynamic analysis provided by test generation tools for mining sandboxes?
 \end{enumerate}
@@
 
-Answering the research questions RQ1 and RQ2 allows us to disclose a possible overestimation performance of test generation tools for mining sandboxes,
+Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation\kn{Over estimation of what?} in performance of test generation tools for mining sandboxes,
 as reported in \blls, which might introduce a possible threat to their conclusions. Answering the third research question

### 2021-03-02 results.tex
Reesults -1

@@
 As discussed in the previous section, to this end, we first executed the analysis using the DroidXP benchmark with its default
-configuration. After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm.
+configuration. After that, we executed the analysis again, by disabling the DroidFax static analysis algorithm.
 In this way, we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
@@
 The Impact column shows the impact
-(in percentage) of DroidFax static analysis algorithms in the results.
+(in percentage) of DroidFax static analysis algorithms in the results. \kn{Define impact formally, may be as a ratio}
 
-Note taht, in the \blls, the authors do not present a
+\kn{The following ssentence is kind of stating the obviouss and comes off as an attack already. THis should bee a conclusion box. Also mention why joke has 100\% not just as a result number}
+Note that, in the \blls, the authors do not present a
 discussion about the influence of DroidFax in the results, even

### 2021-03-02 results.tex
Results

@@
 
-\kn{The following ssentence is kind of stating the obviouss and comes off as an attack already. THis should bee a conclusion box. Also mention why joke has 100\% not just as a result number}
+\kn{The following ssentence is kind of stating the obviouss and comes off as an attack already.
+THis should bee a conclusion box.
+Did we introduce joke in study?
+If not please introduce.
+If yes, please use joke by saying "joke, our .....
+improves its performance by"}
 Note that, in the \blls, the authors do not present a
@@
 
-  \item[Humanoid] showed the worse performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
+  \item[Humanoid] showed the worst performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
     the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. WS),
@@
   \item[\joke] is our fake test case generation tool that help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes.
+\kn{joke seems to be defined here but used before}
     We integrated \joke into the DroidXP benchmark as an additional test case generation tool that does not run the Android apps during the benchmark execution.
@@
 that had not been detected by any other sandbox, and the Humanoid sandbox detected one malware that had not
-been detected by any other sandbox. Contrasting with the \blls,
+been detected by any other sandbox.
+\kn{Do our results vary from the results of BLL study or the results claimed by the individual papers themselves.
+We should talk about this.
+} Contrasting with the \blls,
 our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid
@@
 adding permissions to receive and send SMS messages
-(Listing~\ref{lst:androidManifest}). Moreover, after decompiling
+(Listing~\ref{lst:androidManifest}).
+\kn{Is this the only app where the manifest was changed.
+If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} Moreover, after decompiling
 this malware, we also observed that the malicious version of the
@@
 In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset.
-To this end we leverage the FlowDroid tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
+To this end we leverage the FlowDroid\kn{ Have we cited flowdroid before.
+If yes, ignore my comment} tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
 Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
+
+\kn{I see this as a bonus insight.
+We set out to understand whether static analysis can complement and improve dynamic analysis.
+But we seem to also have proven that static analysis alone is superior to dynamic analysis.
+If no other work has touched this topic, we should mention this.
+I cant recollect any work that compared static analysis tools to dynamic analysis tools.
+If they have actually done, we should report them}
 
@@
   is superior than the performance of the
-  mining sandbox approach supported by dynamic analysis only---without
+  mining sandbox approach supported by dynamic analysis only i.e without
   the DroidFax static analysis algorithms.

### 2021-03-02 setup.tex
revision for jounal - setup and conclusions

@@
 the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls.
+At our study, we considered Droidmate-2~\footnote{In this paper, we will use Droidmate to represent Droidmate at version 2} \cite{DBLP:conf/kbse/BorgesHZ18}, because it extend the explore engine of previous version, including a new explorer set, that decide the next events to be performed.
 We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}.
@@
 UI events, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
-For the replication, we also used our benchmark tool, DroidXP ~\cite{DBLP:conf/scam/CostaMCMVBC20},
+For the replication, we also used our benchmark tool, droidXP ~\cite{DBLP:conf/scam/CostaMCMVBC20},
 which helped us to reproduce the original work.
@@
 For both studies, we employed the same dataset $96$ pairs of Android apps (B/M),
-shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail the procedures of each study in what follows.
+shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail our benchmark tool, droidXP, and the procedures of each study in what follows.
+
+\subsection{The Benchmark - DroidXP}
+
+\begin{figure*}[ht]
+  \includegraphics[width=1\textwidth]{images/benchmark4.png}
+  \label{benchArq}
+  \caption{Benchmark architecture}
+  \label{fig:benchArq}
+\end{figure*}
+
+To systematically assess and compare test generation tools for mining android sandboxes, we used our benchmark solution, called DroidXP.
+It relies on a simple \emph{Command Line Interface} (CLI) that favors the execution and configuration of the benchmark.
+It also relies on DroidFax, that instruments Android apps and collects relevant information about their execution, like the set of sensitive APIs a given
+app calls during a test execution. DroidFax also collects inter-component communication (ICC) intent  tracing  using  static  program analysis.
+
+The DroidXP CLI provides two commands: a command that lists all test case
+generation tools (executing the project with the option ``list-tools'') that had been
+integrated into the benchmark; and a command that performs the execution of the benchmark,
+which can be configured using the following parameters:
+
+\begin{itemize}
+    \item \texttt{-tools}: Specifies the test tools used in the experiment
+    \item \texttt{-t}: Specifies the threshold (in seconds) for the execution time in the experiment
+    \item \texttt{-r}: Specifies the number of repetitions used in the experiment
+    \item \texttt{-output-format}: Specifies the output format
+    \item \texttt{--debug}: Specifies to run in DEBUG mode (default: false)
+    \item \texttt{--disable-static}: Disable DroidFax static analysis (default: false)
+
+\end{itemize}
+
+The DroidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
+and includes three main components; where each component is responsible for a specific phase of the
+benchmark (instrumentation, execution, and result analysis).
+
+\subsubsection{Phase 1: Instrumentation}
+
+In the first phase, a researcher must define the corpus of APK files droidXP should consider during a benchmark execution.
+After that, DroidXP starts the DroidFax service that instruments each APK file, so that DroidXP would be able to collect data about each execution.
+To improve the performance of the benchmark, the instrumentation phase runs only once for each APK.
+In this phase, the DroidFax tool also runs some static analysis procedures.
+
+\subsubsection{Phase 2: Execution}
+
+In this phase, DroidXP installs an (already instrumented) APK file into
+an Android emulator, and then executes a test case generation tool
+during a period of time. This process repeats for every test case generation
+tool and APK files. To provide repeatability of the experiment, DroidXP removes all data stored in the emulator before starting
+a new execution. That is, every execution uses a \emph{fresh} emulator,
+without any information that might have been kept during
+previous executions.
+
+The benchmark is relatively easy to add new test
+case generation tools.
+To achieve this goal, it leverage the Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into DroidXP.
+To performance our study replication we integrated successfully all test generation tools previously mentioned into DroidXP.
+
+\subsubsection{Phase 3: Result Analysis}
+
+During the execution, all the data that is required to compute the results are provided by Logcat \cite{Logcat}, one of the Android SDK's native tools and is a command-line tool that dumps a log from the Android emulator.
+Thus, the only part of the log that is analyzed in this phase is the messages sent by the methods inside the Android app that were instrumented on the first phase using the DroidFax tool.
+
+Droidfax computes the coverage each test achieved and which sensitive API was accessed during the execution of that test.
+That last information is required to compute the test generator performance in identifying malicious apps by spotting differences between the sensitive API accessed by each version of an app.
+This information is vital to the measurement of the test generator performance and qualification.
+After this phase, the benchmark outputs the results of the experiment, which is informing the performance of one or more testing generator tools in mining sandboxes.
 

### 2021-03-03 introduction.tex
Label
minor change

@@
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 
@@
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
-Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
+Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably, to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms either to identify privacy leaks or to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
 Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes.

### 2021-03-03 introduction.tex
additinoal pass in the introduction section

@@
 Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably, to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms either to identify privacy leaks or to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
-Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes.
-In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic and static analysis, and then block future calls to sensitive resources unidentified during this exploratory phase, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
 
-The main idea of mining sandboxes is to explore the set of calls to sensitive API methods in a Android app, using different approaches for automatically testing Android apps.
-These analysis explore apps behavior and record all calls to sensitive APIs.
-A sandbox builds upon the calls to sensitive Android APIs, during the execution of the test cases (exploratory phase).
-The sandbox could then block future calls to other sensitive resources which diverge from those found in the exploratory phase.
-Using this approach, based on just test case generation tools, the sandbox accuracy depends on the exploratory capabilities of each testing tool used to mine the sandbox security rules.
+Other approaches rely on the use of dynamic analysis to mine Android sandboxes~\cite{DBLP:conf/icse/JamrozikSZ16}.
+In this case, during an exploratory phase, one leverages an automatic test case generator tool that runs a benign version of an Android app and collects the set of calls made to sensitive APIs.
+This set of calls comprises a sandbox infrastructure.
+The sandbox might then monitor any call to sensitive APIs while the app is running, blocking calls that have not been identified during the exploratory phase---thereby protecting Android users from additional malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
+
+That is, the main idea of mining sandboxes is to explore the set of calls to sensitive API methods of an app, using different approaches
+for automatically testing Android applications. The analysis explores the apps behavior and records all calls to sensitive APIs.
+A sandbox builds upon these calls during the exploratory phase. The sandbox could then block future calls to
+other sensitive resources which diverge from those found in the exploratory phase. Therefore, the sandbox accuracy depends on the exploratory capabilities of each testing tool
+used to mine the sandbox.
 
 Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
-The authors claim that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often assume that additional behaviors are possible than actually would be.
+The authors argue that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
+assume that additional behaviors are possible than actually would be.
 %\kn{Ok.
@@
 The overall flow of definitions needs some thought}
-Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime.
-Thereby, code that is interpreted, decrypted, or downloaded at run time is out of scope for static analysis---even though these more \emph{dynamic} strategies are often used to introduce malicious behavior.
-Nonetheless, the authors do not give any empirical validation about the limitations of static analysis to mine sandboxes.
-As a consequence, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
+Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
+code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
+of programming languages are often used to introduce malicious behavior. Even though these claims
+seem reasonable, Jamrozik et al. do not present an empirical validation about the limitations of static analysis to mine sandboxes.
+Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
 
-The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which present an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
+The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
 Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
-Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
+Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
 
-Our goal is to understand how static analysis
+Our goal in this paper is to understand how static analysis
 algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
-first, we conduct a replication of the work of \blls. Our study differs from the original work in three aspects: (a)
-by isolating the effect of the static analysis component of DroidFax, (b) by considering more recent dynamic analysis tools for testing Android apps,
-and (c) we considering more execution time, and more repetitions, for each apps analysed at our replication.
-In the second study, we explore to what extent we can complement the dynamic analysis approach using tainted analysis algorithms, through Flowdroid \cite{DBLP:conf/pldi/ArztRFBBKTOM14} tool.
+first, we conduct a replication of the \blls. Our research differs from the original work in three aspects: (a)
+we isolate the effect of the static analysis component of DroidFax, (b) we consider in our study more recent dynamic analysis tools for testing Android apps,
+and (c) we extend the execution time and the number of executions of each test case generator tool for all apps
+in our dataset. In the second study, we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to understand how a more advanced static analysis approach
+(based on taint analysis) can complement dynamic analysis in the task of mining sandboxes.
 
-\textit{Extended Version.} This journal paper extends a previous conference publication~\cite{DBLP:conf/scam/CostaMCMVBC20} by expanding the empirical evaluation of sandboxes solutions using DroidXP benchmark tool with:
- \begin{enumerate}[(1)]
-  \item presenting a replication of the accuracy study of test generation tools for mining android sandboxes, using an extension and update of our benchmark solution, that aided us disables the static analysis performed by DroidFax.
-
-  \item discovering which are the contribution installments of types of analysis for malware detection task.
-
-  \item presenting what malware and its characteristics, that was not detected by any tool in our analysis dynamic and static experiment.
-
-  \item presenting data that indicate that static analysis can improve the mining sandboxes process for malware detection.
-  \end{enumerate}
+Here we also use DroidXP to integrate different dynamic analysis tools and then build a
+general understanding about the use of dynamic and static analysis tools for mining
+Android sandboxes. Although we presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
+here we discuss the results of a broader investigation
+that uses DroidXP to explains the performance of static and dynamic analysis
+approaches for mining sandboxes.
 
 %Altogether, this paper brings the following contributions:
-%\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
+\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
+
+\todo[inline]{RB: review the following paragraph later}
 The rest of the paper is organized as follows.

### 2021-03-04 background.tex
revision for jounal - background - setup - result

@@
 
-A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network or other device data.
+A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data.
 It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application.
+This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
+A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software.
+Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not escape the sandbox), and make sure it will never assign the program greater privileges than it should have,
+working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task.
+This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system overall health.
+On Android, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just access user resources, like contacts and location, through specific APIs (Application Programming Interface), and guarded by permissions.
+
+Google Play Store is the main Android app store, and has a flexible policy regarding the process of publishing apps.
+Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
+For security reasons, Google play list each app with the requested permission.
+However, many malicious apps usually request more permissions than their APIs normally would require \cite{DBLP:conf/ccs/FeltCHSW11}.
+Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.
+
+Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
+Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
+Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.
 
@@
 %\kn{I thought sandbox was an environment, now it is comprised of rules?}%
-through test generator tools \kn{This sentence seems to miss something "what" happens through test generation tools.} .
-These tools explore program behavior and monitor access to sensitive APIs.
+through test generator tools, that identifies sensitive Android API, called during their execution. 
+%\kn{This sentence seems to miss something "what" happens through test generation tools.}
+These tools investigate program behavior through resources access realized by theses APIs.
 The second stage ensures that resources not accessed, or accessed differently than first stage, are denied access.

### 2021-03-04 results.tex
revision for jounal - background - setup - result

@@
 
-  \item [Monkey] in the first execution (Exec. WS) produced a sandbox that detected $71$ out of the $96$ pairs of Android apps.
+  \item[Monkey] in the first execution (Exec. WS) produced a sandbox that detected $71$ out of the $96$ pairs of Android apps.
     Contrasting, in the original study, the Monkey's sandbox detected $48$ malwares within the 102 pairs ($47.05$\%). This difference
@@
 
-The DroidBot and Humanoid sandboxes detected the malicious version of the app
-\texttt{com.andoop.flyracing}. In this particular case,
-the malicious version changed the Android Manifest file,
-adding permissions to receive and send SMS messages
+The DroidBot and Humanoid sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}.
+In this particular case, the malicious version changed the Android Manifest file, adding permissions to receive and send SMS messages
 (Listing~\ref{lst:androidManifest}).
+With these permissions, malicious apps may get money fraudulently by sending messages without user confirmation, or may monitor messages or delete them without showing them to user.
 \kn{Is this the only app where the manifest was changed.
-If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} Moreover, after decompiling
-this malware, we also observed that the malicious version of the
+If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} Moreover, after decompiling this malware, we also observed that the malicious version of the
 \texttt{MainService} class introduced a
@@
 
-Differently, none of the computed sandboxes detected the malicious version
-of the app \texttt{com.andoop.flyracing}. Indeed,
-the malicious version {\color{red}only} changes the
-Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}.
-However, the AdMob is a monetization service provided by Google, and changing the
-AdMob \emph{publisher identifier} account redirects the advertisement's
-revenue to another destination.
+Now its an interesting case, because none of the computed sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}.
+Indeed, the malicious version only changes the Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}.
+However, the AdMob is a monetization service provided by Google, and changing the AdMob \emph{publisher identifier} account redirects the advertisement's revenue to another destination.
 
@@
                      android:value="a14f099bfbf3c61"/>
+\end{lstlisting}
+
+Differently, the next malicious version app \texttt{com.happymaau.MathRef} was detected by all computed sandboxes.
+First, the malicious version of package changed the Android Manifest file, adding permissions to access network state and wifi state.
+These changes allow an app to view the status of all networks and make changes to configured wi-fi networks.
+(Listing~\ref{lst:androidManifest2}).
+
+\begin{lstlisting}[caption={Diffs in the \texttt{com.happymaau.MathRef}
+      AndroidManifest file of the malicious
+      version}.
+      , language=XML,
+    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:androidManifest2}]
+
+165:M >    <uses-permission android:name="android.permission.ACCESS_NETWORK_STATE"/>
+166:M >    <uses-permission android:name="android.permission.ACCESS_WIFI_STATE"/>
+\end{lstlisting}
+
+We also observed that the malicious version of the \texttt{d} class, indeed introduced a method \texttt{a}, that collects network and wifi information, like Mac address and network state.
+(Listing~\ref{lst:d})
+
+\begin{lstlisting}[caption={Diffs in the malicious version
+      of the class \texttt{com.mn.vymq.b.d}
+      (app \texttt{com.happymaau.MathRef})},
+      language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
+      label={lst:d}]
+
+105:M > private String a(Context paramContext)
+106:M > {
+107:M >	String str = ((TelephonyManager)paramContext.getSystemService("phone")).getDeviceId();
+108:M > StringBuilder localStringBuilder = new StringBuilder();
+109:M > localStringBuilder.append(str);
+110:M > paramContext = (WifiManager)paramContext.getSystemService("wifi");
+111:M > if (paramContext == null) {}
+112:M >  for (paramContext = null;; paramContext = paramContext.getConnectionInfo())
+113:M >  {
+114:M >   if (paramContext != null)
+115:M >    {
+116:M >      paramContext = paramContext.getMacAddress();
+117:M >      if (paramContext != null) {
+118:M >       localStringBuilder.append(paramContext);
+119:M >      }
+120:M >    }
+121:M >    return a(localStringBuilder.toString());
+122:M >  }
+123:M > }
+\end{lstlisting}
+
+Our last example is from malicious version app \texttt{ru.qixi.android.smartrabbits}.
+It also was detected by all computed sandboxes, and such as the previous malware example, it changed the Android Manifest file, adding this time, permission to access fine location sources.
+This permission allows access location sources, such as the Global Positioning System (GPS) on the phone, where available.
+Malicious applications can use this resource to determine where the phone user are, and may consume additional battery power.
+(Listing~\ref{lst:androidManifest3})
+
+\begin{lstlisting}[caption={Diffs in the \texttt{com.happymaau.MathRef}
+      AndroidManifest file of the malicious
+      version}.
+      , language=XML,
+    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:androidManifest3}]
+
+8:M >    <uses-permission android:name="android.permission.ACCESS_COARSE_LOCATION"/>
+9:M >    <uses-permission android:name="android.permission.ACCESS_FINE_LOCATION"/>
+\end{lstlisting}
+
+This malicious app clandestinely monitors the geographic location user and sink these information.
+The code that follows, show how the method \texttt{c}, from \texttt{q} class, collects these sensitive resource.
+(Listing~\ref{lst:c}).
+
+\begin{lstlisting}[caption={Diffs in the malicious version
+      of the class \texttt{net.crazymedia.iad.d.q}
+      (app \texttt{ru.qixi.android.smartrabbits})},
+      language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
+      label={lst:c}]
+
+65:M > private Location c(Context paramContext)
+66:M > {
+67:M > try
+68:M >  {
+69:M >  if (Arrays.asList(paramContext.getPackageManager().getPackageInfo
+              (paramContext.getPackageName(),4096).requestedPermissions).contains
+              ("android.permission.ACCESS_FINE_LOCATION"))
+
+70:M >   {
+71:M >    paramContext = (LocationManager)paramContext.getSystemService("location");
+72:M >    Criteria localCriteria = new Criteria();
+73:M >    localCriteria.setAccuracy(1);
+74:M >    localCriteria.setAltitudeRequired(false);
+75:M >    localCriteria.setBearingRequired(false);
+76:M >    localCriteria.setCostAllowed(true);
+77:M >    localCriteria.setPowerRequirement(1);
+78:M >    paramContext = paramContext.getLastKnownLocation
+                    (paramContext.getBestProvider(localCriteria, true));
+
+79:M >    return paramContext;
+80:M >   }
+81:M >  }
+82:M >  catch (PackageManager.NameNotFoundException paramContext)
+83:M >  {
+84:M >   paramContext.printStackTrace();
+85:M >   return null;
+86:M >  }
+87:M >  catch (Exception paramContext)
+88:M >  {
+89:M >   paramContext.printStackTrace();
+90:M >  }
+91:M >  return null;
+92:M > }
 \end{lstlisting}

### 2021-03-04 setup.tex
revision for jounal - background - setup - result

@@
 
- \item What are the benefits of using tainted\kn{Is it tainted analysis or taint analysis?} analysis algorithms to complement the dynamic analysis provided by test generation tools for mining sandboxes?
+ \item What are the benefits of using taint
+ %\kn{Is it tainted analysis or taint analysis?} 
+ analysis algorithms to complement the dynamic analysis provided by test generation tools for mining sandboxes?
 \end{enumerate}
@@
 
-Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation\kn{Over estimation of what?} in performance of test generation tools for mining sandboxes,
-as reported in \blls, which might introduce a possible threat to their conclusions. Answering the third research question
+Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation in terms of the number of detected malware by each sandbox, constructed by test generation tools explored in \blls
+%\kn{Over estimation of what?} 
+, which might introduce a possible threat to their conclusions. Answering the third research question
 allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
@@
 \begin{figure}[ht]
-   \includegraphics[width=0.45\textwidth]{images/setup2.png}
+  \centering{
+   \includegraphics[width=0.75\textwidth]{images/setup3.png}}
    \label{Experiment setup}

### 2021-03-04 background.tex
Background

@@
 A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software.
-Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not escape the sandbox), and make sure it will never assign the program greater privileges than it should have,
+Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have,
 working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task.
-This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system overall health.
-On Android, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just access user resources, like contacts and location, through specific APIs (Application Programming Interface), and guarded by permissions.
+This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health.
+Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses non-sensitive user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.
 
-Google Play Store is the main Android app store, and has a flexible policy regarding the process of publishing apps.
+Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps.
 Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
 For security reasons, Google play list each app with the requested permission.
-However, many malicious apps usually request more permissions than their APIs normally would require \cite{DBLP:conf/ccs/FeltCHSW11}.
-Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.
+However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}.
+Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product \kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}.
 
-Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
+Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code \kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
 Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
@@
 
-The Android Mining Sandbox concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security.
+\textbf{The Android Mining Sandbox} concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security.
 The sandboxing technique comprises of two steps.
@@
 %\kn{This sentence seems to miss something "what" happens through test generation tools.}
-These tools investigate program behavior through resources access realized by theses APIs.
-The second stage ensures that resources not accessed, or accessed differently than first stage, are denied access.
+These tools investigate program behavior through resource accesses realized by theses APIs.
+The second stage ensures that resources not accessed, or accessed differently than first stage, are not accessible by the apps.
 So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.
@@
 Automatically mining software resources or components, to infer behavior is not new, and has been discussed before.
-For instance, Whaley et al.
-\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so extract interface from software components.
-Ammons et al \cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
+For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so extract interface from software components.
+Ammons et al~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
 approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
 
-Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work.
+The term test generation comes out out nowhere.} Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
 Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
@@
 L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
-This study indicates that these tools was efficient in identifying at most $70$\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect $75.49$\% of malicious behavior explored ($77$ among $102$).
+This study indicates that these tools were efficient in identifying at most $70$\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect $75.49$\% of malicious behavior explored ($77$ among $102$).
 However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps

### 2021-03-04 background.tex
revision for jounal - background - result

@@
 However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}.
-Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product \kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}.
+Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.~\cite{DBLP:conf/soups/FeltHEHCW12}
+%\kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}
 
-Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code \kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
+Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
+%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
+, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
 Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
@@
 
-\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work.
-The term test generation comes out out nowhere.} Regarding test generating tools used for mining Sandboxes, Jamrozik et al \cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+%\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} 
+The main purpose of test generation tool is to find bugs.
+However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes.
+Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
 Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.

### 2021-03-04 results.tex
revision for jounal - background - result

@@
 from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
-\joke tool for which DroidFax improves its performance by 100\%. This result is
+\joke tool, the fake tool that does not execute apps during a benchmark execution, for which DroidFax improves its performance by 100\%. This result is
 expected, since the \joke tool does not execute any dynamic analysis.
@@
   \item[\joke] is our fake test case generation tool that help us understand the performance of the DroidFax static analysis algorithm for mining sandboxes. 
-\kn{joke seems to be defined here but used before}
-    We integrated \joke into the DroidXP benchmark as an additional test case generation tool that does not run the Android apps during the benchmark execution.
+  %\kn{joke seems to be defined here but used before}
+    We integrated \joke into the DroidXP benchmark as an additional test case generation tool that does not run the Android apps.
     As a result, the analysis using \joke reveals the performance of DroidFax static analysis algorithms alone. For the first execution, with the DroidFax static
@@
 With these permissions, malicious apps may get money fraudulently by sending messages without user confirmation, or may monitor messages or delete them without showing them to user.
-\kn{Is this the only app where the manifest was changed.
-If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} Moreover, after decompiling this malware, we also observed that the malicious version of the
+%\kn{Is this the only app where the manifest was changed. If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} 
+Moreover, after decompiling this malware, we also observed that the malicious version of the
 \texttt{MainService} class introduced a
@@
 
-Now its an interesting case, because none of the computed sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}.
+Now we show an interesting case, because none of the computed sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}.
 Indeed, the malicious version only changes the Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}.
@@
 
-We also observed that the malicious version of the \texttt{d} class, indeed introduced a method \texttt{a}, that collects network and wifi information, like Mac address and network state.
+We also observed that the malicious version of the \texttt{d} class, introduced a method \texttt{a}, that collects network and wifi information, like Mac address and network state.
 (Listing~\ref{lst:d})
@@
 
-Our last example is from malicious version app \texttt{ru.qixi.android.smartrabbits}.
-It also was detected by all computed sandboxes, and such as the previous malware example, it changed the Android Manifest file, adding this time, permission to access fine location sources.
+Our last example is a malicious version app \texttt{ru.qixi.android.smartrabbits}.
+It also was detected by all computed sandboxes, and such as the previous malware example, it changed the Android Manifest file, adding this time, permission to access location sources.
 This permission allows access location sources, such as the Global Positioning System (GPS) on the phone, where available.
@@
 
-This malicious app clandestinely monitors the geographic location user and sink these information.
+This malicious app clandestinely monitors the geographic location user and sink these information to a web server.
 The code that follows, show how the method \texttt{c}, from \texttt{q} class, collects these sensitive resource.
@@
 In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset.
-To this end we leverage the FlowDroid\kn{ Have we cited flowdroid before.
-If yes, ignore my comment} tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
+To this end we leverage the FlowDroid
+%\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
+tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
 Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).

### 2021-03-04 background.tex
second general review

@@
 This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health.
-Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses non-sensitive user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.
+Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.
 

### 2021-03-04 benchmark.tex
second general review

@@
 \begin{figure*}[ht]
-  \includegraphics[width=1\textwidth]{images/benchmark3.png}
+  \includegraphics[width=1\textwidth]{images/benchmark4.png}
   \label{benchArq}
@@
 
-The droidXP CLI provides two commands: a command that lists all test case
+The DroidXP CLI provides two commands: a command that lists all test case
 generation tools (executing the project with the option ``list-tools'') that had been
@@
 
-The droidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
+The DroidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
 and includes three main components; where each component is responsible for a specific phase of the
@@
 
-In the first phase, a researcher must define the corpus of APK files droidXP
+In the first phase, a researcher must define the corpus of APK files DroidXP
 should consider during a benchmark execution.
-After that, droidXP starts the DroidFax service that instruments each APK file, so that droidXP would be able to collect data about each execution.
+After that, DroidXP starts the DroidFax service that instruments each APK file, so that DroidXP would be able to collect data about each execution.
 To improve the performance of the benchmark, the instrumentation phase runs only once for each APK.
@@
 
-In this phase, droidXP installs an (already instrumented) APK file into
+In this phase, DroidXP installs an (already instrumented) APK file into
 an Android emulator, and then executes a test case generation tool
@@
 tool and APK files. To provide repeatability of the experiment,
-droidXP removes all data stored in the emulator before starting
+DroidXP removes all data stored in the emulator before starting
 a new execution. That is, every execution uses a \emph{fresh} emulator,
@@
 case generation tools. To achieve this goal, it leverage the
-Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into droidXP.
+Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into DroidXP.
 Listing \ref{lst:toolspec} shows the contract a developer must override to integrate a new tool.
@@
 test case generation tool. To performance our study replication we integrated successfully 
-the following tools into droidXP.
+the following tools into DroidXP.
 

### 2021-03-04 conclusionfutureworks.tex
second general review

@@
-\section{conclusion and future work}
+\section{Conclusion and future work}
 
@@
 In this paper, we performed two studies.
-In the first we conducted a non-exact replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times.
+In the first we conducted a replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $3$ minute for $3$ times.
 Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis.
 For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
-The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
-Enabling the Droidfax, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid).
-We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated.
-In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.
+The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, $58.33\%$-$76.04\%$ of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
+The impact of Droidfax in the results range from $16.44\%$ (DroidBot) to $51.79\%$ (Humanoid).
+We also found that $18.75\%$ of malicious apps (18 out of 96) could be detected by none of the sandboxes generated.
+In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%).
+With the exception of DroidBot tool, tainted analysis algorithms had a better performance than any sandbox constructed by the execution of another test case tool, without the Droidfax static analysis algorithms.
+Our work show that the number of malicious behaviours detected is increased for all cases with tainted analysis aid, achieving at the best case, $82.29\%$ (79 among 96) of malware detected with DroidBot.
 

### 2021-03-04 results.tex
second general review

@@
 
-\subsection{Result of the first study: A non-exact replication}\label{sec:res-fs}
+\subsection{Result of the first study: A \blls replication}\label{sec:res-fs}
 
@@
 detected using the sandboxes generated after running the test case tools with the support of the
-DroidFax static analysis algorithms. Besides that, in the first execution, none of the
+DroidFax static analysis algorithms. Besides that, in the first execution (WS), none of the
 resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
@@
 tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
-Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).
+Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than three sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms), losing only to sandbox build by Droidbot, that detected $61$ out of the $96$ pairs ($63,54$\%)
 
@@
 Here we present details about one of the malware that Flowdroid had detected.
-At this package (com.yy.fontmaster), from another alternative android market, angeeks~\cite{angeeks}, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours.
+At this package \texttt{com.yy.fontmaster}, from alternative android market, angeeks~\cite{angeeks}, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours.
 The Figure \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.

### 2021-03-04 setup.tex
revision for jounal - background - result
second general review

@@
 for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox modeled by the test generation tool
-under analysis. Figure \ref{fig:setup} shows this experimental setup.
+under analysis.
 
@@
 DroidFax static analysis algorithms.
+Figure \ref{fig:setup} shows all the phases of our experimental, that explore all sensitive resources access by both apps (B/M), and the optional configuration DroidXP, that disables Droidfax static analysis.
 
@@
 data set from the first study. For this second study, we used
-FlowDroid~\cite{10.1145/2666356.2594299}, a static flow analysis tool for Android apps.
+FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, a static flow analysis tool for Android apps.
 The goal is to test accuracy of static analysis, through tainted analysis algorithms, at finding malicious behavior, and compare the results with previous study at the same data set.

### 2021-03-04 introduction.tex
minor review

@@
 Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
-The authors argue that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
+The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
 assume that additional behaviors are possible than actually would be.
@@
 of programming languages are often used to introduce malicious behavior. Even though these claims
-seem reasonable, Jamrozik et al. do not present an empirical validation about the limitations of static analysis to mine sandboxes.
+seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
 Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
@@
 Our goal in this paper is to understand how static analysis
-algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
-first, we conduct a replication of the \blls. Our research differs from the original work in three aspects: (a)
-we isolate the effect of the static analysis component of DroidFax, (b) we consider in our study more recent dynamic analysis tools for testing Android apps,
+algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. Here we
+present the results of two empirical studies that aim to
+address our research goal. In the
+first study, we conduct a replication of the \blls, though our research differs from the original work in three aspects: (a)
+we isolate the effect of the static analysis component of DroidFax, (b) we included a recent dynamic analysis tool for testing Android apps,
 and (c) we extend the execution time and the number of executions of each test case generator tool for all apps
-in our dataset. In the second study, we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to understand how a more advanced static analysis approach
-(based on taint analysis) can complement dynamic analysis in the task of mining sandboxes.
+in our dataset. Differently, in the second study we explore how a more advanced static analysis approach
+(based on taint analysis) can complement dynamic analysis in the task of mining sandboxes---using
+the FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} infrastructure for analysing Android apps.
 
-Here we also use DroidXP to integrate different dynamic analysis tools and then build a
-general understanding about the use of dynamic and static analysis tools for mining
-Android sandboxes. Although we presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
-here we discuss the results of a broader investigation
-that uses DroidXP to explains the performance of static and dynamic analysis
+We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
+and here we discuss the results of a broader investigation
+that also uses DroidXP to explains the performance of static and dynamic analysis
 approaches for mining sandboxes.

### 2021-03-05 setup.tex
text improvements

@@
 
-\blls explored the effectiveness of test generation tools to construct sandboxes, based on sensitive APIs called by apps under analysis.
-Since their study also involved a static analysis component, performed by Droidfax as we described in Section~\ref{sec:introduction}, and whose impact was not measured, we replicated its work to understand the static analysis impact may have had in their results.
-Thus, this section present the settings of our study, whose goal is to perform this replication, and thus build a general understanding of the implications of static analysis algorithms in the results.
-We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.
+The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
+sandboxes, based on the calls to sensitive APIs from 102 pairs (benign / malign) of Android apps. In their work, \emph{performance} is
+measured as the total number of malwares a sandbox is able to identify when comparing the calls to sensitive APIs made by
+the benign and malign versions of the app. A \emph{hit} occurs whenever a sandbox finds that the malicious version of an app calls
+additional sensitive APIs, in comparison to the calls from the corresponding benign version.
+Nonetheless, the \blls uses DroidFax to instrument the Android apps, even though DroidFax also
+collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
+computed the possible impact of DroidFax into the performance of the test generation tools,
+here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results. In addition,
+we investigate whether or not a more advanced static analysis approach is promising for
+mining Android sandboxes.
 
-To achieve these general goals, we intend to answer the following research questions.
+In this section
+we present the settings of our study, whose goal is to build a general understanding of the implications of using static analysis algorithms
+to complement a dynamic analysis approach
+for mining Android sandboxes. % We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.
+To achieve this goal, we answer the following research questions.
 
@@
 
- \item What is the impact of the DroidFax static analysis algorithms in the \blls?
+ \item What is the impact of the DroidFax static analysis algorithms into the results of the \blls?
 
- \item What is the effective performance of each test generation tool, in terms of the number of detected malware, in \blls, disregarding the DroidFax
-  static analysis algorithms?
+ \item What is the effective performance of each test generation tool, in terms of the number of detected malware, when we
+   discard the contributions of the DroidFax static analysis algorithms?
 
  \item What are the benefits of using taint
- %\kn{Is it tainted analysis or taint analysis?} 
- analysis algorithms to complement the dynamic analysis provided by test generation tools for mining sandboxes?
+ analysis algorithms to complement the dynamic analysis approach for mining sandboxes?
 \end{enumerate}
@@
 
-Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation in terms of the number of detected malware by each sandbox, constructed by test generation tools explored in \blls
-%\kn{Over estimation of what?} 
-, which might introduce a possible threat to their conclusions. Answering the third research question
+Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation in terms of the number of detected malware by each sandbox, constructed by the test
+generation tools explored in \blls. Ignoring the implications of DroidFax in the \blls might have introduced a possible threat to their conclusions. Answering the third research question
 allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
@@
 
-We conducted two studies to answer the research questions above.
-First we replicated the \blls.
-However, our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms, in the task to identify malicious apps.
-In addition, we discarded $6$ pairs of
-Android apps we were not able to instrument---out of the $102$ pairs used in the original work.
-We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, and repeated all the execution more 2 times, therefore totaling three executions.
-The original study executed each app at each tool, for just one minute, and just one time.
+We conducted two studies to answer the research questions above. First we replicated the \blls. However, our study differs from the original one in a few decisions. First, here we isolate
+the effect of the DroidFax static analysis algorithms, in the task to identify malicious apps. In addition, altough we use the same dataset of
+$102$ pairs of Android apps used in the \blls, here we discarded $6$ pairs for which
+we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool (Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}), which
+has not been considered in the previous work. Finally, we extended the execution time of each test generation tool, executing each app from the test generation tool for three minutes,
+and built the sandboxes after executing each test generation tool three times. % The original study executed each app at each tool, for just one minute, and just one time.
 
-The others $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
-DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at \blls. We selected Droidbot and DroiMate because they achieved
-the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) in the \blls.
-At our study, we considered Droidmate-2~\footnote{In this paper, we will use Droidmate to represent Droidmate at version 2} \cite{DBLP:conf/kbse/BorgesHZ18}, because it extend the explore engine of previous version, including a new explorer set, that decide the next events to be performed.
-We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}.
-It is part of the Android SDK, and does not require any additional installation effort.
-Since Monkey was developed for stress testing, and can not perform text input, only generating
-UI events, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
-For the replication, we also used our benchmark tool, droidXP ~\cite{DBLP:conf/scam/CostaMCMVBC20},
-which helped us to reproduce the original work.
+Besides Humanoid, our study considers three test generation tools used in the \blls: DroidBot~\cite{DBLP:conf/icse/LiYGC17},
+DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, and Monkey~\cite{Monkey}. We selected DroidBot and DroiMate because they achieved
+the best performance on detecting malicious behavior---when considering the $102$ pairs of Android apps (B/M) in the \blls.
+It is important to note that here we used a new version of DroidMate (DroidMate-2), since it presents several enhancements
+in comparison to the previous version. We also considered the Google's Monkey open source tool, mostly because it is the most
+widely used test generation tool for Android~\cite{DBLP:conf/sigsoft/ZengLZXDLYX16}. Monkey is part of the Android SDK
+and does not require any additional installation effort. We included Humanoid in our study
+because it emulates realistic users, creating human-like test inputs using deep learning techniques.
+We leverage DroidXP~\cite{DBLP:conf/scam/CostaMCMVBC20} (Section~\ref{sec:droidxp}) to integrated all these test generation tools,
+define the study settings, execute the
+experiments, and collect the outputs.
 
 In the second study we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to execute
-tainted analysis algorithms in Android apps, in order to identify pairs of \emph{sources and sinks}. In this case,
-our goal is to investigate the performance on detecting malicious
-behavior using static taint analysis of Android apps. We use two metrics in this second study: the number
-of source-sink flows that FlowDroid identifies when considering the pairs of Android apps (B/M), and the
-execution time of the analysis for each app.
-For both studies, we employed the same dataset $96$ pairs of Android apps (B/M),
-shared by the AndroZoo \cite{DBLP:conf/msr/AllixBKT16} project. We detail our benchmark tool, droidXP, and the procedures of each study in what follows.
+taint analysis algorithms in Android apps, in order to identify \emph{sources-sinks} paths. In this case,
+our goal is to investigate if it is possible to detect malicious
+behavior by comparing the source-sink paths that FlowDroid finds in the
+benign / malign versions of the Android apps. Concerning this second study, a \emph{hit} occurs whenever
+FlowDroid finds an additional source-sink path in the malicious version of an app.
+Our goal is to answer our third research question using this approach. We use two metrics in this second study:
+the total number of malicious apps FlowDroid is able to find and the
+execution time for running the taint analysis algorithm for each app.
+For both studies, we employed the same dataset of $96$ pairs of Android apps (B/M),
+originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
+also used in the \blls.
 
-\subsection{The Benchmark - DroidXP}
+\subsection{The DroidXP benchmark}\label{sec:droidxp}
 
-\begin{figure*}[ht]
-  \includegraphics[width=1\textwidth]{images/benchmark4.png}
-  \label{benchArq}
-  \caption{Benchmark architecture}
-  \label{fig:benchArq}
-\end{figure*}
+We used DroidXP to systematically assess and compare the performance of test generation tools for mining android sandboxes. DroidXP relies on a
+simple \emph{Command Line Interface} (CLI) that simplifies the integration of different test generation tools and favors the setup and execution 
+of the experiments. DroidXP also relies on DroidFax, which instruments Android apps and collects relevant information about
+their execution, including the set of sensitive APIs a given
+app calls during a test execution. DroidFax also collects inter-component communication (ICC) using  static
+program analysis.
 
-To systematically assess and compare test generation tools for mining android sandboxes, we used our benchmark solution, called DroidXP.
-It relies on a simple \emph{Command Line Interface} (CLI) that favors the execution and configuration of the benchmark.
-It also relies on DroidFax, that instruments Android apps and collects relevant information about their execution, like the set of sensitive APIs a given
-app calls during a test execution. DroidFax also collects inter-component communication (ICC) intent  tracing  using  static  program analysis.
-
-The DroidXP CLI provides two commands: a command that lists all test case
+The DroidXP CLI provides commands for listing all test case
 generation tools (executing the project with the option ``list-tools'') that had been
-integrated into the benchmark; and a command that performs the execution of the benchmark,
-which can be configured using the following parameters:
+integrated into the benchmark and commands that execute the experiments. An
+experiment run can be configured according to several parameters, including:
 
@@
     \item \texttt{--debug}: Specifies to run in DEBUG mode (default: false)
-    \item \texttt{--disable-static}: Disable DroidFax static analysis (default: false)
-
+    \item \texttt{--disable-static-analysis}: Disable DroidFax static analysis phase (default: false)
 \end{itemize}
 
-The DroidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
-and includes three main components; where each component is responsible for a specific phase of the
+Figure~\ref{fig:benchArq} shows the DroidXP architecture, based on the pipes-and-filters architectural style \cite{architecture-book}. 
+The architecture includes three main components; where each component is responsible for a specific phase of the
 benchmark (instrumentation, execution, and result analysis).
 
+\begin{figure*}[thb]
+  \includegraphics[width=1\textwidth]{images/benchmark4.png}
+  \label{benchArq}
+  \caption{Benchmark architecture}
+  \label{fig:benchArq}
+\end{figure*}
 \subsubsection{Phase 1: Instrumentation}
 
-In the first phase, a researcher must define the corpus of APK files droidXP should consider during a benchmark execution.
+In the first phase, a researcher must define the corpus of APK files DroidXP should consider during a benchmark execution.
 After that, DroidXP starts the DroidFax service that instruments each APK file, so that DroidXP would be able to collect data about each execution.
 To improve the performance of the benchmark, the instrumentation phase runs only once for each APK.
-In this phase, the DroidFax tool also runs some static analysis procedures.
+In this phase, the DroidFax tool also runs some static analysis procedures---when the option \texttt{--disable-static-analysis} is not set.
 
@@
 
-The benchmark is relatively easy to add new test
-case generation tools.
-To achieve this goal, it leverage the Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into DroidXP.
-To performance our study replication we integrated successfully all test generation tools previously mentioned into DroidXP.
+It is relatively easy to add new test
+case generation tools into DroidXP. To achieve this goal, it leverages the Strategy Design
+pattern~\cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities
+for running each tool we want to integrate into DroidXP.
+To carry out our replication study, we successfully integrated all
+test generation tools previously mentioned into DroidXP: Monkey, DroidBot, DroidMate, and
+Humanoid.
 
@@
 
-During the execution, all the data that is required to compute the results are provided by Logcat \cite{Logcat}, one of the Android SDK's native tools and is a command-line tool that dumps a log from the Android emulator.
-Thus, the only part of the log that is analyzed in this phase is the messages sent by the methods inside the Android app that were instrumented on the first phase using the DroidFax tool.
+During the execution of the instrumented apps, all data that is relevant to our
+research is collected by Logcat~\cite{Logcat}, one of the Android SDK's native tools. Logcat dumps a log from the Android emulator
+while the already instrumented app is in execution. The part of the log we analyze in this phase comprises
+the data sent by the methods within the Android app that were instrumented on the first
+phase using the DroidFax tool.
 
-Droidfax computes the coverage each test achieved and which sensitive API was accessed during the execution of that test.
-That last information is required to compute the test generator performance in identifying malicious apps by spotting differences between the sensitive API accessed by each version of an app.
-This information is vital to the measurement of the test generator performance and qualification.
-After this phase, the benchmark outputs the results of the experiment, which is informing the performance of one or more testing generator tools in mining sandboxes.
+This data includes method coverage from the execution of each test generator tool and the
+set of sensitive APIs the app calls during its execution. This set of calls to
+sensitiva APIs is necessary to estimate the test generator performance in identifying malicious apps---by spotting
+differences between the sensitive API accessed by each version of an app (benign or malign).
+In the end, the benchmark outputs the results of the experiment, which gives the
+performance of one or more testing generator tools in mining sandboxes.
+
+We used the DroidXP infrastructure to conduct the replication of
+the \blls, whose settings we present in the following sections.
 

### 2021-03-05 setup.tex
major change in the structure of the Study Settings section

@@
 Since their study also involved a static analysis component whose impact was not measured, we perform a non-exact replication to understand the impact static analysis may have had in the results...}
-
-The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
-sandboxes, based on the calls to sensitive APIs from 102 pairs (benign / malign) of Android apps. In their work, \emph{performance} is
-measured as the total number of malwares a sandbox is able to identify when comparing the calls to sensitive APIs made by
-the benign and malign versions of the app. A \emph{hit} occurs whenever a sandbox finds that the malicious version of an app calls
-additional sensitive APIs, in comparison to the calls from the corresponding benign version.
-Nonetheless, the \blls uses DroidFax to instrument the Android apps, even though DroidFax also
-collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
-computed the possible impact of DroidFax into the performance of the test generation tools,
-here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results. In addition,
-we investigate whether or not a more advanced static analysis approach is promising for
-mining Android sandboxes.
 
@@
 dynamic analysis through the use of static analysis algorithms.
-
-We conducted two studies to answer the research questions above. First we replicated the \blls. However, our study differs from the original one in a few decisions. First, here we isolate
-the effect of the DroidFax static analysis algorithms, in the task to identify malicious apps. In addition, altough we use the same dataset of
-$102$ pairs of Android apps used in the \blls, here we discarded $6$ pairs for which
-we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool (Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}), which
-has not been considered in the previous work. Finally, we extended the execution time of each test generation tool, executing each app from the test generation tool for three minutes,
-and built the sandboxes after executing each test generation tool three times. % The original study executed each app at each tool, for just one minute, and just one time.
-
-Besides Humanoid, our study considers three test generation tools used in the \blls: DroidBot~\cite{DBLP:conf/icse/LiYGC17},
-DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, and Monkey~\cite{Monkey}. We selected DroidBot and DroiMate because they achieved
-the best performance on detecting malicious behavior---when considering the $102$ pairs of Android apps (B/M) in the \blls.
-It is important to note that here we used a new version of DroidMate (DroidMate-2), since it presents several enhancements
-in comparison to the previous version. We also considered the Google's Monkey open source tool, mostly because it is the most
-widely used test generation tool for Android~\cite{DBLP:conf/sigsoft/ZengLZXDLYX16}. Monkey is part of the Android SDK
-and does not require any additional installation effort. We included Humanoid in our study
-because it emulates realistic users, creating human-like test inputs using deep learning techniques.
-We leverage DroidXP~\cite{DBLP:conf/scam/CostaMCMVBC20} (Section~\ref{sec:droidxp}) to integrated all these test generation tools,
-define the study settings, execute the
-experiments, and collect the outputs.
-
-In the second study we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to execute
-taint analysis algorithms in Android apps, in order to identify \emph{sources-sinks} paths. In this case,
-our goal is to investigate if it is possible to detect malicious
-behavior by comparing the source-sink paths that FlowDroid finds in the
-benign / malign versions of the Android apps. Concerning this second study, a \emph{hit} occurs whenever
-FlowDroid finds an additional source-sink path in the malicious version of an app.
-Our goal is to answer our third research question using this approach. We use two metrics in this second study:
-the total number of malicious apps FlowDroid is able to find and the
-execution time for running the taint analysis algorithm for each app.
-For both studies, we employed the same dataset of $96$ pairs of Android apps (B/M),
-originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
-also used in the \blls.
+We conducted two studies to answer the research questions above. In the
+first study we leverage DroidXP~\cite{DBLP:conf/scam/CostaMCMVBC20} (Section~\ref{sec:droidxp}) to replicate
+the \blls. We present the settings of this first study in Section~\ref{sec:set1}.
+In the second study we use
+FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to investigate the 
+suitability of taint analysis algorithms for mining Android sandboxes.
+We present the settings of the second study in Section~\ref{sec:set2}.
 
@@
 case generation tools into DroidXP. To achieve this goal, it leverages the Strategy Design
-pattern~\cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities
+pattern~\cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the particularities
 for running each tool we want to integrate into DroidXP.
-To carry out our replication study, we successfully integrated all
-test generation tools previously mentioned into DroidXP: Monkey, DroidBot, DroidMate, and
-Humanoid.
+%To carry out our replication study, we successfully integrated all
+%test generation tools previously mentioned into DroidXP: Monkey, DroidBot, DroidMate, and
+%Humanoid.
 
@@
 set of sensitive APIs the app calls during its execution. This set of calls to
-sensitiva APIs is necessary to estimate the test generator performance in identifying malicious apps---by spotting
+sensitive APIs is necessary to estimate the test generator performance in identifying malicious apps---by spotting
 differences between the sensitive API accessed by each version of an app (benign or malign).
@@
 We used the DroidXP infrastructure to conduct the replication of
-the \blls, whose settings we present in the following sections.
+the \blls, whose settings we present in the following section.
 
-\subsection{First Study: A replication \blls}
+\subsection{First Study: A replication of the \blls}\label{sec:set1}
 
-In the first study we executed the DroidXP benchmark with its
-default configuration, that is, enabling the DroidFax
-static analysis algorithms and the test generation tools.
+The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
+sandboxes, based on the calls to sensitive APIs from 102 pairs (benign / malign) of Android apps. In their work, \emph{performance} is
+measured as the total number of malwares a sandbox is able to identify when comparing the calls to sensitive APIs made by
+the benign and malign versions of the app. A \emph{hit} occurs whenever a sandbox finds that the malicious version of an app calls
+additional sensitive APIs, in comparison to the calls from the corresponding benign version.
+Nonetheless, the \blls uses DroidFax to instrument the Android apps, even though DroidFax also
+collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
+computed the possible impact of DroidFax into the performance of the test generation tools,
+here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results.
 
-We investigate the four test case generation tools described earlier and added a fake test
-case generation tool (named Joker) that simulates a test tool that does not execute
+Our replication differs from the original work in a few decisions. First, here we isolate
+the effect of the DroidFax static analysis algorithms, in the task to identify malicious apps. In addition, although we use the same dataset of
+$102$ pairs of Android apps used in the \blls, here we discarded $6$ pairs for which
+we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool (Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}), which
+has not been considered in the previous work. Finally, we extended the execution time of each test generation tool,
+executing each app from the test generation tool for three minutes (instead of one minute in the
+original work),
+and built the sandboxes after executing each test generation tool
+three times---the original work executed each test generation tool
+only once. That is, our goal here is not to conduct an
+exact replication of the \blls, but instead understand
+the role of the DroidFax static analysis algorithms in the
+performance of test case generation tools for mining sandboxes.
+% The original study executed each app at each tool, for just one minute, and just one time.
+
+Besides Humanoid, our study considers three test generation tools used in the \blls: DroidBot~\cite{DBLP:conf/icse/LiYGC17},
+DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, and Monkey~\cite{Monkey}. We selected DroidBot and DroiMate because they achieved
+the best performance on detecting malicious behavior---when considering the $102$ pairs of Android apps (B/M) in the \blls.
+It is important to note that here we used a new version of DroidMate (DroidMate-2), since it presents several enhancements
+in comparison to the previous version. We also considered the Google's Monkey open source tool, mostly because it is the most
+widely used test generation tool for Android~\cite{DBLP:conf/sigsoft/ZengLZXDLYX16}. Monkey is part of the Android SDK
+and does not require any additional installation effort. We included Humanoid in our study
+because it emulates realistic users, creating human-like test inputs using deep learning techniques.
+
+% In the first study we executed the DroidXP benchmark with its
+% default configuration, that is, enabling the DroidFax
+% static analysis algorithms and the test generation tools.
+
+We first run the experiment using the default
+settings of DroidXP, to explore the four test case generation tools described earlier and a fake test
+case generation tool (named \joke). \joke simulates a test tool that does not execute
 the Android apps during a benchmark execution. Using this tool, the results
 of the dynamic analysis are not considered and we can compute the results with
-only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
-Android app (B/M) in each one of the five test generation tools, including Joker,
-for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox modeled by the test generation tool
+only the static analysis component of DroidFax (RQ1). Our study executed each pair of
+Android app (B/M) in each one of the five test generation tools, including \joke,
+for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox
+modeled by the test generation tool
 under analysis.
+
+After that, we replicated the analysis using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
+Using this new configuration, we executed the benchmark again, using the same dataset of Android apps, the same execution time,
+and the same test case generation tools.
+The results of this replication allow us to compute the effective performance
+of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
+DroidFax static analysis algorithms.
+Figure \ref{fig:setup} shows all the phases of our experimental, that explore all sensitive
+resources access by both apps (B/M), and the optional configuration DroidXP, that disables DroidFax static analysis.
 
@@
 
-After that, we replicated the study using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
-With this new configuration, we executed the benchmark again, using the same dataset of Android pairs apps, the same execution time, and the same test case generation tools.
-The results of this replication allow us to compute the effective performance
-of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
-DroidFax static analysis algorithms.
-Figure \ref{fig:setup} shows all the phases of our experimental, that explore all sensitive resources access by both apps (B/M), and the optional configuration DroidXP, that disables Droidfax static analysis.
+\subsection{Second Study: Use of Taint Analysis Algorithms for Mining Sandboxes}\label{sec:set2}
 
-\subsection{Second Study: Tainted analysis algorithms.}
+In the second study 
+we investigate whether or not a more advanced static analysis approach is promising for
+mining Android sandboxes. To this end, we leverage the FlowDroid
+taint analysis algorithms for Android apps, in order to identify paths between
+\emph{sources} and \emph{sinks}. In this case,
+our goal is to investigate if it is possible to detect malicious
+behavior by comparing the source-sink paths that FlowDroid finds in the
+benign / malign versions of the Android apps.
 
-To complement our initial study, we performed the tainted analysis at the same
-data set from the first study. For this second study, we used
-FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, a static flow analysis tool for Android apps.
-The goal is to test accuracy of static analysis, through tainted analysis algorithms, at finding malicious behavior, and compare the results with previous study at the same data set.
-In this second study, a behavior is considered malicious whenever the algorithms
-detected a different set of source-sink pairs, coming from the benign and malign
-versions of an Android app.
+Concerning this second study, a \emph{hit} occurs whenever
+FlowDroid finds an additional source-sink path in the malicious version of an app.
+Our goal is to answer our third research question using this approach. We use two metrics in this second study:
+the total number of malicious apps FlowDroid is able to find and the
+execution time for running the taint analysis algorithm for each app.
+In this second study we use the same dataset of $96$ pairs of Android apps (B/M),
+originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
+also used in the \blls.
 
-Initially, Flowdroid mine all sources and sinks of each benign apps, and enumerates all possible data flows between them. Next, it performs the same process for the malicious version
-of the correspondent app.
-In the final step, we compare the set of source-sink track between the benign app and its corresponding malicious app, in order to discovery some taint tracer different between the apps under analysis.
-
-This study was useful to answer the third research question (RQ3), because it disclosed some pairs of applications with malicious behavior, that could not be detected at first study at none of the scenarios presented, evidencing that there is a benefit of new static analysis techniques, to complement the dynamic analysis provided by test generation tools, at mining sandboxes solutions.
-Details of studies results are at next section.
+We conduct this investigation in three steps. First, we use
+FlowDroid to mine all sources and sinks paths from each benign app, and then enumerate all possible data flows between sources
+and sinks. Next, we repeat the the analysis considering the malicious version
+of the apps. Finally, we compare the sets of source-sink paths between the benign and malicious
+version of an app, in order to reveal the existence of additional paths in the
+malicious version.

### 2021-03-05 results.tex
final revision of the results section

@@
 In this section we detail the findings of our study. We present the results of the first and
-second studies in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}. In Section~\ref{sec:discussion} we summarize the
+second studies in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}, respectively. In Section~\ref{sec:discussion} we summarize the
 implications of our study.
@@
 Our first study is a replication of the \blls.
-As discussed in the previous section, to this end, we first executed the analysis using the DroidXP benchmark with its default
-configuration. After that, we executed the analysis again, by disabling the DroidFax static analysis algorithm.
+As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default
+configuration. After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm.
 In this way, we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
@@
 of DroidFax static analysis algorithms (WOS). 
-The Impact column shows the impact
-(in percentage) of DroidFax static analysis algorithms in the results. \kn{Define impact formally, may be as a ratio}
+The Impact column shows 
+(in percentage) to what extent the DroidFax static analysis algorithms influences
+the performance of the sandboxes created after
+executing the test generation tools. We calculate the impact
+using Eq. (1).
 
-\kn{The following ssentence is kind of stating the obviouss and comes off as an attack already.
-THis should bee a conclusion box.
-Did we introduce joke in study?
-If not please introduce.
-If yes, please use joke by saying "joke, our .....
-improves its performance by"}
-Note that, in the \blls, the authors do not present a
-discussion about the influence of DroidFax in the results, even
-though here we report that the impact of DroidFax in the results is significant, ranging
-from 16.44\% (DroidBot) to 51.79\% (Humanoid)---discarding our
-\joke tool, the fake tool that does not execute apps during a benchmark execution, for which DroidFax improves its performance by 100\%. This result is
-expected, since the \joke tool does not execute any dynamic analysis.
+\begin{eqnarray}
+Impact & = & \frac{(Exec.\ (WS) - \ Exec.\ (WOS)) \times 100}{Exec.\ (WS)} 
+\end{eqnarray}
+
+Table~\ref{tab:fs} shows that the impact of DroidFax in the results is significant, ranging
+from 16.44\% (DroidBot) to 51.79\% (Humanoid). Note that, in the \blls, the authors do not present a
+discussion about the influence of DroidFax in the performance of the
+test generation tools, even though this influence is not negligible. 
+Considering the \joke
+tool, our fake test generation tool that does not execute the apps during
+the benchmark execution, DroidFax improves the performance in 100\%.
+This result is expected, since the \joke tool does not execute any dynamic analysis.
 Next we discuss the result of each individual test generation tool.
@@
   detecting more apps with malicious behavior than any other tool. Similar to the \blls, DroidBot is the test case generation tool
-  whose resulting sandbox detected the largest number of malicious apps. Moreover, in our second execution (Exec WOS), removing the DroidFax
+  whose resulting sandbox detected the largest number of malicious apps. Moreover, in our second execution (Exec. (WOS)), removing the DroidFax
   static analysis support reduced the DroidBot performance in 16.44\%, the smaller impact we observed among the tools.
 
-  \item[Monkey] in the first execution (Exec. WS) produced a sandbox that detected $71$ out of the $96$ pairs of Android apps.
+  \item[Monkey] in the first execution (Exec. (WS)) produced a sandbox that detected $71$ out of the $96$ pairs of Android apps.
     Contrasting, in the original study, the Monkey's sandbox detected $48$ malwares within the 102 pairs ($47.05$\%). This difference
@@
     of three executions---while in the \blls, the authors consider the outcomes of one execution. 
-    Considering our second execution (Exec WOS), there is a reduction of $21.13$\% in the Monkey's performance, leading to
-    a sandobox that was able to detect $56$ malwares.
+    Considering our second execution (Exec. (WOS)), there is a reduction of $21.13$\% in the Monkey's performance, leading to
+    a sandbox that was able to detect $56$ malwares.
 
-  \item[DroidMate] in the first execution (Exec. WS) led to a sandbox that detected 68 apps with malicious behavior ($70.83$\%).
+  \item[DroidMate] in the first execution (Exec. (WS)) led to a sandbox that detected 68 apps with malicious behavior ($70.83$\%).
     In the \blls study, DroidMate also detected $68$ malwares, though considering the $102$ pairs of apps used in the
-    original study. In the second execution(WOS),
+    original study. In the second execution (Exec. (WOS)),
     without the DroidFax static analysis algorithms, the resulting sandbox's performance drops by $23.53$\%, being able to detect
@@
   \item[Humanoid] showed the worst performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
-    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. In the first execution (Exec. WS),
+    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. This might suggest that test generation
+    tools that try to simulate the human behavior, such as Humanoid, are less effective to build Android sand boxes, in comparison
+    with techniques that rely on random testing (such as Monkey). In the first execution (Exec. (WS)),
     the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%). Humanoid was the most affected in the second
-    execution (Exec. WOS), whose resulting sandbox presents a redunction of $51.79$\%  in the number of detected malwares.
+    execution (Exec. (WOS)), whose resulting sandbox presents a reduction of $51.79$\%  in the number of detected malwares.
     Since the \blls did not explore Humanoid,
@@
     algorithms enabled, even though \joke does not execute the Android apps, its resulting sandbox detected 43.75\% of the malwares. For the second execution,
-    that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was not able to detect any malware. This result
-    was expected, since \joke does not analyze the Android apps during the benchmark execution.
+    that is, disabling the DroidFax static analysis algorithm, the resulting \joke sandbox was not able to detect any malware. Therefore,
+    our results show that DroidFax alone is able to detect more than 40\% of the malicious version of the apps.
 
@@
 by all sandboxes generated in the first execution (with the DroidFax static analysis algorithms),
-out of the 78 identified by at least one sandbox. In addition, the DroidBot sandbox did not detect
+out of the 78 malwares identified by at least one sandbox. In addition, the DroidMate sandbox did not detect
 any malware that had not been detected by the other tools. Differently, the Monkey sandbox detected
@@
 been detected by any other sandbox. 
-\kn{Do our results vary from the results of BLL study or the results claimed by the individual papers themselves.
-We should talk about this.
-} Contrasting with the \blls,
-our results suggest that using DroidBot in combination with Monkey, DroidMate, and Humanoid
+Contrasting with the \blls,
+our results suggest that using DroidMate in combination with Monkey, DroidBot, and Humanoid
 does not improve the general performance of an integrated environment for mining
@@
   environment that combines Monkey, DroidMate, and Humanoid to
-  mine Android sandboxes. Introducing the DroidBot 
+  mine Android sandboxes. Introducing the DroidMate 
   tool does not improve the results.
@@
   \centering{
-  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-s1-1.pdf}}
+  \includegraphics[trim=60 20 0 50,scale=0.9]{images/venn-plot-s1-1.pdf}}
   \caption{Venn Diagram highlighting how the sandboxes from the tools can
@@
 the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
-PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
+PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}. In what follows
+we present more details of representative malwares considered
+in our dataset.
 
-The DroidBot and Humanoid sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}.
-In this particular case, the malicious version changed the Android Manifest file, adding permissions to receive and send SMS messages
-(Listing~\ref{lst:androidManifest}).
-With these permissions, malicious apps may get money fraudulently by sending messages without user confirmation, or may monitor messages or delete them without showing them to user.
-%\kn{Is this the only app where the manifest was changed. If yes, I am not sure we can make broad claims about manifest being a serious place of vulnerabilities.} 
+First, consider the malicious version of the app \texttt{com.andoop.flyracing}---which only the DroidBot and
+Humanoid sandboxes were able to detect. 
+In this particular case, the malicious version changed the Android Manifest file,
+adding permissions to receive and send SMS messages
+(Listing~\ref{lst:androidManifest}). With these permissions, malicious apps may get money
+fraudulently by sending messages without user confirmation, or may monitor messages or delete
+them without showing them to user.
+
 Moreover, after decompiling this malware, we also observed that the malicious version of the
@@
 
-%% In what follows we present some characteristics of two malwares
-%% that had not been detected by the sandboxes (app \texttt{mobi.infolife.cachepro} and app \texttt{com.andoop.flyracing}).
-
-%% In the first example (\texttt{mobi.infolife.cachepro}), the malicious behavior comprises changes to
-%% the app idiom (Listing~\ref{lst:app65a}) and to the publisher identifier (Listing~\ref{lst:app65b}).
-%% Although such a modification does not threaten the user's device,
-%% it might characterize a scenario of app misappropiation.
-%% Although such a modification does not threaten the user's device,
-%% it might characterize a scenario of app misappropriation. That is, after manually dissecting this particular malware,
-%% we did not identify any change with regard to calls to sensitive APIs or app behavior.
-
-%% \begin{lstlisting}[caption= {Diff in the file \texttt{smali/mobi/infolife/cachepro/h.smali}. \texttt{B} stands for
-%%     the benign version, while \texttt{M} stands for the malign version.},language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65a}]
-
-%% 1:B < const-string v3, "Swith To "
-%% ---
-%% 1:M > const-string v3, "\u65e0\u6cd5\u542f\u52a8\u5e94\u7528\u201c"
-%% \end{lstlisting}
-
-Now we show an interesting case, because none of the computed sandboxes detected the malicious version of the app \texttt{com.andoop.flyracing}.
-Indeed, the malicious version only changes the Android Manifest file, modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}.
-However, the AdMob is a monetization service provided by Google, and changing the AdMob \emph{publisher identifier} account redirects the advertisement's revenue to another destination.
-
-\begin{lstlisting}[caption={Diff in the file \texttt{com.andoop.flyracing}
-      AndroidManifest file of the malicious version.
-      \texttt{B} stands for
-      the benign version, while \texttt{M} stands for the malign version.}, language=XML,
-    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]
-
-1:B < <meta-data android:name="ADMOB_\PUBLISHER_\ID"
-                     android:value="a14cf7346295891"/>
----
-1:M > <meta-data android:name="ADMOB_\PUBLISHER_\ID"
-                     android:value="a14f099bfbf3c61"/>
-\end{lstlisting}
-
-Differently, the next malicious version app \texttt{com.happymaau.MathRef} was detected by all computed sandboxes.
-First, the malicious version of package changed the Android Manifest file, adding permissions to access network state and wifi state.
-These changes allow an app to view the status of all networks and make changes to configured wi-fi networks.
-(Listing~\ref{lst:androidManifest2}).
+The malicious version of the app \texttt{com.happymaau.MathRef} also changes
+the manifest file to require additional permissions as well as change
+the behavior of the app (with malicious code). All sandboxes were able to
+detect this malware.
+In this case, the malicious version of the app changed the Android Manifest file,
+requiring permissions to access the network and WiFi states (Listing~\ref{lst:androidManifest2}).
+These changes allow an app
+to view the status of all networks and make changes to configured WiFi-fi networks.
 
@@
 
-We also observed that the malicious version of the \texttt{d} class, introduced a method \texttt{a}, that collects network and wifi information, like Mac address and network state.
-(Listing~\ref{lst:d})
+We also observed that the malicious version introduces a method \texttt{a},
+that actually collects network and WiFi information, like Mac address and the network state
+(see Listing~\ref{lst:d}). This information is then shared using an
+HTTP request.
 
@@
 
-Our last example is a malicious version app \texttt{ru.qixi.android.smartrabbits}.
-It also was detected by all computed sandboxes, and such as the previous malware example, it changed the Android Manifest file, adding this time, permission to access location sources.
-This permission allows access location sources, such as the Global Positioning System (GPS) on the phone, where available.
-Malicious applications can use this resource to determine where the phone user are, and may consume additional battery power.
-(Listing~\ref{lst:androidManifest3})
+All computed sandboxes also detected the malicious version of the app \texttt{ru.qixi.android.smartrabbits}.
+This particular malware also changes the Android Manifest file, requesting permission to access location service (Listing~\ref{lst:androidManifest3}).
+This permission allows access location features, such as the Global Positioning System (GPS) on the phone, if it is enabled.
+Malicious applications can use these features to determine where the phone owner is, which is a
+general privacy threat.
 
@@
 
-This malicious app clandestinely monitors the geographic location user and sink these information to a web server.
-The code that follows, show how the method \texttt{c}, from \texttt{q} class, collects these sensitive resource.
-(Listing~\ref{lst:c}).
+In addition, the malicious app clandestinely monitors the geographic location of the user and sink
+these information to a web server. Listing~\ref{lst:c} shows how
+the method \texttt{c}, from \texttt{q} class, collects these sensitive information.
 
@@
 
-\subsection{Result of the second study: Tainted analysis algorithms.}\label{sec:res-ss}
+Finally, the \texttt{com.andoop.flyracing} case is among the apps that none sandbox detected the
+malicious version. Indeed, the malicious version only changes the Android Manifest file,
+modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}. Nonetheless, the AdMob is a monetizing
+service provided by Google, and changing the AdMob \emph{publisher identifier} account redirects
+the advertisement's revenue to another destination. Therefore, it might exist specific
+modifications to the Android manifest file that might complement the mining sandbox
+approach into the task for detecting malwares.
 
-In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset.
-To this end we leverage the FlowDroid
+\begin{lstlisting}[caption={Diff in the file \texttt{com.andoop.flyracing}
+      AndroidManifest file of the malicious version.
+      \texttt{B} stands for
+      the benign version, while \texttt{M} stands for the malign version.}, language=XML,
+    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]
+
+1:B < <meta-data android:name="ADMOB_\PUBLISHER_\ID"
+                     android:value="a14cf7346295891"/>
+---
+1:M > <meta-data android:name="ADMOB_\PUBLISHER_\ID"
+                     android:value="a14f099bfbf3c61"/>
+\end{lstlisting}
+
+\subsection{Results of the second study: Using taint analysis to mine Android malwares}\label{sec:res-ss}
+
+In this second study we used a taint analysis approach to mine differences between the
+benign and malicious versions of the 96 Android apps in our dataset. To this end we leverage the FlowDroid
 %\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
-tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms.
-Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than three sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms), losing only to sandbox build by Droidbot, that detected $61$ out of the $96$ pairs ($63,54$\%)
-
-\kn{I see this as a bonus insight.
-We set out to understand whether static analysis can complement and improve dynamic analysis.
-But we seem to also have proven that static analysis alone is superior to dynamic analysis.
-If no other work has touched this topic, we should mention this.
-I cant recollect any work that compared static analysis tools to dynamic analysis tools.
-If they have actually done, we should report them}
+tool, which tracks how sensitive information flows through the apps using taint analysis algorithms.
+Regarding accuracy, the taint analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%). That is,
+using the taint analysis implementation of FlowDroid alone outperforms the Monkey, DroidMate,
+and Humanoid sandboxes computed in the second execution (without the DroidFax static analysis
+algorithms). This result shows that static analysis algorithms are promising for mining
+sandboxes, demystifying previous claims in the literature.
 
@@
   The performance of FlowDroid to identify malicious behavior
-  is superior than the performance of the
-  mining sandbox approach supported by dynamic analysis only i.e without
+  is equivalent to the performance of the
+  mining sandbox approach supported by dynamic analysis only---i.e., without
   the DroidFax static analysis algorithms.
@@
 
-Additionally, we investigate if we could benefit from combining
-the results from FlowDroid and DroidFax. Figure~\ref{fig:venn-plot2} shows a
+Additionally, we investigate if we could benefit from combining the
+static analysis strategies from FlowDroid and DroidFax. Figure~\ref{fig:venn-plot2} shows a
 Venn-diagram summarizing the results. So, when combining
 the results from FlowDroid and DroidFax, we were able to detect
-$67$ of the malicious apps ($69.79$\%), a performance compatible
-to that we found as response to the first execution of the
+$67$ of the malicious apps ($69.79$\%), a result compatible
+to the performance we found as response to the first execution of the
 test case generation tools---which also considers the DroidFax
@@
 a completely different static analysis approach. Furthermore,
-FlowDroid shows to be more effective than DroidFax, detecting $25$ malicious
+FlowDroid shows to be more effective than DroidFax alone, detecting $25$ malicious
 apps that had not been detected by DroidFax (while DroidFax detected $9$
@@
   (such as FlowDroid and DroidFax) seems promising,
-  leading to a performance similar to that achievend
+  leading to a performance similar to that achieved
   when combining test case generation tools with the
-  DroidFax tool. 
+  DroidFax static analysis algorithms. 
 \end{finding}
@@
 
-Finally, we can highlight that FlowDroid was able to detect $4$ malwares among the $18$ malicious Android apps that had not
+Finally, we highlight that FlowDroid was able to detect $4$ malwares among the $18$ malicious Android apps that had not
 been detected by the sandboxes constructed in the first study. Among these
@@
   to that of using the dynamic analysis approach for mining sandboxes,
-  it was able to detect only four additional malwares (out of the
+  it was able to detect four additional malwares (out of the
   18) that had not been detected in the first study. 
@@
 
-Here we present details about one of the malware that Flowdroid had detected.
-At this package \texttt{com.yy.fontmaster}, from alternative android market, angeeks~\cite{angeeks}, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours.
+%% For instance, FlowDroid reveals an additional source-sink path in
+%% the \texttt{com.yy.fontmaster} app (see Figure~\ref{fig:sourcesink}.
+This  a possible malicious behaviors.
 The Figure \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.
 
-\begin{figure}[ht]%
-    \centering
-    \subfloat[\centering Path source/sink from benign app]{{\includegraphics[width=5cm]{images/pathbenign.png} }}%
-    \qquad
-    \subfloat[\centering Path source/sink from malicious app]{{\includegraphics[width=5cm]{images/pathmalicious.png} }}%
-    \caption{Pairs source/sink different (B/M)}%
-    \label{fig:sourcesink}%
-\end{figure}
+%% \begin{figure}[ht]%
+%%     \centering
+%%     \subfloat[\centering Path source/sink from benign app]{{\includegraphics[width=5cm]{images/pathbenign.png} }}%
+%%     \qquad
+%%     \subfloat[\centering Path source/sink from malicious app]{{\includegraphics[width=5cm]{images/pathmalicious.png} }}%
+%%     \caption{Pairs source/sink different (B/M)}%
+%%     \label{fig:sourcesink}%
+%% \end{figure}
 

### 2021-03-05 introduction.tex
set up the contributions of the paper

@@
 that also uses DroidXP to explains the performance of static and dynamic analysis
-approaches for mining sandboxes.
+approaches for mining sandboxes. Altogether, this paper brings the following contributions:
 
-%Altogether, this paper brings the following contributions:
-\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
+\begin{itemize}
+\item A replication of the \blls study that better clarifies the performance of
+  dynamic analysis tools for mining Android sandboxes.
 
-\todo[inline]{RB: review the following paragraph later}
-The rest of the paper is organized as follows.
+\item A broad comprehension about the role of static analysis tools for mining
+  sandboxes, showing that we can benefit from using both static and dynamic
+  analysis for detecting Android malwares.
+
+\item Evidence that a well known static analysis approach, based on
+  taint analysis, leads to a performance similar to the dynamic analysis
+  approach for mining sandboxes.
+
+\item A replication package of our study that is available on-line, including
+  scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
+  and a benchmark for reproducing and extending our study.\footnote{https://github.com/droidxp/benchmark} 
+\end{itemize}
+
+%% \todo[inline]{RB: review the following paragraph later}
+%% The rest of the paper is organized as follows.
 Section 2 we present a background and some related works.

### 2021-06-03 background.tex
first update - little grammar corrections

@@
 
-A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data.
-It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application.
+A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
+It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}.
 This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
@@
 Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
-For security reasons, Google play list each app with the requested permission.
+For security reasons, Google Play list each app with the requested permission.
 However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}.
@@
 %\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
-, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
+, calling Java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
 Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
@@
 
-\textbf{The Android Mining Sandbox} concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security.
+\textbf{The Android Mining Sandbox} concept is a sandboxing technique that consists of mining rules from an Android app, and use these rules to ensure system security.
 The sandboxing technique comprises of two steps.
@@
 Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}.
-Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system.
+Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the Android operating system.
 Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity.

### 2021-06-03 introduction.tex
first update - little grammar corrections

@@
 The sandbox might then monitor any call to sensitive APIs while the app is running, blocking calls that have not been identified during the exploratory phase---thereby protecting Android users from additional malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
-
-That is, the main idea of mining sandboxes is to explore the set of calls to sensitive API methods of an app, using different approaches
-for automatically testing Android applications. The analysis explores the apps behavior and records all calls to sensitive APIs.
-A sandbox builds upon these calls during the exploratory phase. The sandbox could then block future calls to
-other sensitive resources which diverge from those found in the exploratory phase. Therefore, the sandbox accuracy depends on the exploratory capabilities of each testing tool
-used to mine the sandbox.
 
@@
 and here we discuss the results of a broader investigation
-that also uses DroidXP to explains the performance of static and dynamic analysis
+that also uses DroidXP to explain the performance of static and dynamic analysis
 approaches for mining sandboxes. Altogether, this paper brings the following contributions:
@@
 \begin{itemize}
-\item A replication of the \blls study that better clarifies the performance of
+\item A replication of the \blls that better clarifies the performance of
   dynamic analysis tools for mining Android sandboxes.

### 2021-06-03 setup.tex
first update - little grammar corrections

@@
 collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
-computed the possible impact of DroidFax into the performance of the test generation tools,
+compute the possible impact of DroidFax into the performance of the test generation tools,
 here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results.
@@
 DroidFax static analysis algorithms.
-Figure \ref{fig:setup} shows all the phases of our experimental, that explore all sensitive
+Figure \ref{fig:setup} shows all the phases of our experiments, that explore all sensitive
 resources access by both apps (B/M), and the optional configuration DroidXP, that disables DroidFax static analysis.

### 2021-06-08 responseLetter.tex
add responseLetter - first version

\documentclass{letter}

\usepackage{hyperref}
\usepackage{xcolor}

\signature{Francisco Handrick Tomaz da Costa (on behalf of the authors of the paper)}

\address{Computer Science Department \\ University of Bras\'{i}lia \\ Brazil \\\\ Software Technology Group
 \\ Technical University of Darmstadt \\ Germany}

\begin{document}

\begin{letter}{JSS Editors,}
\opening{The comments of the reviewers have been very useful. They made us aware that some important points we were trying to convey remained obscure. We have corrected infelicities of presentation and all errors that the reviewers brought to our attention. The text in {\color{blue}blue} indicates how we have dealt with each individual comment.}

{\bf Reviewer 1}

\begin{itemize}
\item In the first place, qhat I missed is an overview of the empirical studies conducted and the relation between 
first and second experiment. I would recommend to include, before Sections 3.2 and 3.3, a section 
presenting the overall research methodology and the connections between the studies - in this sense, 
a figure reporting the various steps would be appreciated; Figure 2 only summarizes the design of the first study.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item In the second place, I would recommend to include more details on the experiments conducted. This is especially 
true for the second study, where Section 3.3 is a bit shallow. The three steps of the methodology are indeed shortly 
described without providing enough details, hence possibly precluding verifiability and replicability. In addition, the 
methodology is not linked to the research questions: I would recommend to restructure Section 3 in order to have 
data extraction processes and data analysis producedures for each research question.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item The proposed DroidXP benchmark seems not to be available, which is a pity since it might be very useful for other 
researchers. I believe the paper may have a stronger impact if the tool would be available. The same is true for the 
data and scripts used for the experiments. I would appreciate if the paper may have an online repository making all 
data and tools available.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Another point to improve is connected to the implications of the study. While the paper discusses in nice way the 
results achieved, it does not provide a clear view of how those results can be potentially useful for researchers 
working on Android sandboxes as well as what are the next steps that the research community should pursue to 
improve the detection of malwares.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Last but not least, the threats to validity section should be improved, by commenting on conclusion and construct validity.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\end{itemize}

{\bf Reviewer 2}

\begin{itemize}

\item The abstract is not clear. First, the context if not well addressed. For example, why ``mining Android sandboxes'' is 
important? I had to read several related reference at the beginning to understand it. Second, it is not common practice to 
include reference in abstract. However, I reserve my opinion since I know it may be preferred by some researchers.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item In Figure 2, you used ``Malicious'', but in most other places, you used ``Malign''. Please unify your choice of terminology.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item In 3.3, you mentioned ``we investigate whether or not a more advanced static analysis approach is promising for mining 
Android sandboxes. To this end, we leverage the FlowDroid taint analysis algorithms...''. True, FlowDroid has its edge 
in privacy leakage detection, but what's your justification for saying FlowDroid is more advanced in terms of static analysis?

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item By definition, mining sandboxes means a technique to confine an application to resources accessed during automatic 
testing [1]. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
not "Mining Sandboxes". Also, FlowDroid requires as input the sources and sinks APIs. But you mine "all sources and sinks 
paths". Do you mean all APIs? FlowDroid will never finish running. Assume a set of sensitive sources and sinks are selected, 
FlowDroid is already good in suggesting which one is malign by revealing info flows. What's the point of applying [1]'s setting?

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item The significance of this work is questionable. The first study is a mere replication of the existing work [2], except, disabling 
part of the framework. The finding is that DroidFaX is important part for DroidXP. Well, your proved literature's correctness. 
It would be more impressive the other way round.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item I find what's written in Finding 2 is not exciting. It is intuitive based on the results of [1] to know that a comprehensive 
comparison combining multiple dynamic tools would improve the performance.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Listings 1-7 illustrate more details of representative malware in the dataset. But what is the take-away message? What 
conclusions and/or inspirations can be drawn from such listings?

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item The title itself is inaccurate. You removed DroidFax from the replicated work[1]. But it is not the only static analysis part. 
Actually, many dynamic testing tools use static analysis to better guide their testing strategy.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Typos:
1. Page 3: to explains -- to explain.
2. Page 3: BLL-Study study -- BLL-Study.
3. Page 8, does not computed -- does not compute.
4. Page 9, of our experimental -- of our experiments.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\end{itemize}

{\bf Reviewer 3}

\begin{itemize}

\item It is not clear how this paper can be considered an extension of the DroidXP paper presented in SCAM 2020.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Introduction, para 3 is repeating para 2

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
analysis must often assume that additional behaviors are possible than actually would be.''
Please explain

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item "We presented and evaluated DroidXP in a conference paper [11]"
What is DroidXP? It should be introduced to a reader who is not familiar.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Google play - Google Play
* java - Java / android - Android
* ``Another approach to rooting''
What is rooting?

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Please rephrase:
``Those are kind of attack that usually tackled with the Android Mining Sandbox''
``For instance, Whaley et al. [18] combine dynamic and static analysis for API mining and so extract interface from software components.''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item What are sensitive behaviors? ``showed that Droidbot is able to trigger an amount of sensitive behaviors''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Please rephrase:
``From the same authors, another test generator tool for Android, described as Humanoid [23], is a Droidbot evolution and
presents a proposal that can generate humans like tests inputs, using deep learning.''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Briefly explain the taint analysis
``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Please explain:
``FastDroid [28] mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Section 3.1, the help text is not adding much value

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item Section 4.1 can be written more concisely.
* It is not clear what is the value of the malware discussion between pages 13 and 15. It may be removed.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\vspace{0.2cm}

\item There are several other typos and grammatical errors.

\vspace{0.2cm}

{\color{blue}{\bf Answer:} answer}

\end{itemize}

{\bf Meta review}

We want to thank all comments we received. Based on this feedback, we conducted additional research activities and improved the paper in several directions.

\closing{Yours Faithfully,}

\end{letter}
\end{document}

### 2021-06-08 responseLetter.tex
add responseLetter - first version

@@
 testing [1]. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
-not "Mining Sandboxes". Also, FlowDroid requires as input the sources and sinks APIs. But you mine "all sources and sinks 
-paths". Do you mean all APIs? FlowDroid will never finish running. Assume a set of sensitive sources and sinks are selected, 
+not ``Mining Sandboxes''. Also, FlowDroid requires as input the sources and sinks APIs. But you mine ``all sources and sinks 
+paths''. Do you mean all APIs? FlowDroid will never finish running. Assume a set of sensitive sources and sinks are selected, 
 FlowDroid is already good in suggesting which one is malign by revealing info flows. What's the point of applying [1]'s setting?
@@
 
-\item "We presented and evaluated DroidXP in a conference paper [11]"
+\item ``We presented and evaluated DroidXP in a conference paper [11]''
 What is DroidXP? It should be introduced to a reader who is not familiar.

### 2021-06-09 setup.tex
R2-C4

@@
 
-\subsection{Second Study: Use of Taint Analysis Algorithms for Mining Sandboxes}\label{sec:set2}
+\subsection{Second Study: Use of Taint Analysis for Malware Identification}\label{sec:set2}
 
@@
 we investigate whether or not a more advanced static analysis approach is promising for
-mining Android sandboxes. To this end, we leverage the FlowDroid
+identifying malwares, given a version of an app that is proved to be secure.
+To this end, we leverage the FlowDroid
 taint analysis algorithms for Android apps, in order to identify paths between
@@
 our goal is to investigate if it is possible to detect malicious
-behavior by comparing the source-sink paths that FlowDroid finds in the
+behavior by identifying the divergent source-sink paths that FlowDroid finds in the
 benign / malign versions of the Android apps.
@@
 
-We conduct this investigation in three steps. First, we use
-FlowDroid to mine all sources and sinks paths from each benign app, and then enumerate all possible data flows between sources
-and sinks. Next, we repeat the the analysis considering the malicious version
-of the apps. Finally, we compare the sets of source-sink paths between the benign and malicious
+We conduct this investigation in three steps. First, we define
+the set of API calls considered as \emph{source of sensitive information} (e.g.,
+a method that access the address book) or
+that \emph{might share information} (e.g., a method that sends messages
+to external peers). We rely on a the source-sink definitions of a previous
+study~\cite{}. After defining the sources and sinks of interest,
+we run FlowDroid to mine the source-sink paths from each benign app, and then enumerate the
+possible data flows between sources and sinks. These paths are considered valid in
+our analysis. Next, we repeat the the FlowDroid execution considering the malicious version
+of the apps. In the final step, we compare the sets of source-sink paths between the benign and malicious
 version of an app, in order to reveal the existence of additional paths in the
 malicious version.
+
+\begin{figure}
+\includegraphics[scale=0.3]{images/second-study-settings.pdf}
+\end{figure}

### 2021-06-09 setup.tex
R2-C4

@@
 To this end, we leverage the FlowDroid
-taint analysis algorithms for Android apps, in order to identify paths between
-\emph{sources} and \emph{sinks}. In this case,
-our goal is to investigate if it is possible to detect malicious
-behavior by identifying the divergent source-sink paths that FlowDroid finds in the
-benign / malign versions of the Android apps.
+taint analysis algorithms for Android apps, in order to identify dataflows
+that might lead to the leakage of sensitive information. Our
+goal here is to investigate if it is possible to detect malicious
+behavior by identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
+analysing a benign and a malign versions of an Android app.
+define.
 
-Concerning this second study, a \emph{hit} occurs whenever
-FlowDroid finds an additional source-sink path in the malicious version of an app.
-Our goal is to answer our third research question using this approach. We use two metrics in this second study:
+FlowDroid takes as input an Android Application Package (APK file) and
+a set of API methods marked either as {\bf source}
+or {\bf sink}. Source methods are those that access \emph{sensitive information} (e.g.,
+a method that access the address book), while sink methods are those 
+that \emph{might share information with external peers} (e.g., a method that
+sends messages to a recipient). We rely on the source-sink definitions of a previous
+study~\cite{}, which involves ABC source methods and XYZ sink methods.
+FlowDroid then uses a \emph{context, flow, and field
+sensitive analysis} to identify all dataflow paths from sources to sinks~\cite{}.
+However, it is important to note that not all source-sink paths are malicious, and then we
+follow a specific methodology to identify malwares in our work: we raise a
+warning (a \emph{hit}) whenever
+FlowDroid finds an additional source-sink path in the malicious version of an app, which
+has not been identified when analysing the benign version.
+
+Our research settings involve three steps (see Figure~\ref{fig:settings2}).
+In the first, we execute FlowDroid to mine the source-sink paths from a
+benign version of an app, and then enumerate a set (S1) with the 
+possible dataflows between sources and sinks. All paths in S1 are considered safe in
+our analysis. In the second step we repeat the FlowDroid execution, though
+considering the malicious APK version of the app. This leads to a second set (S2) of source-sink paths. In the final step, we compute the difference (S3) between
+the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$), in order to reveal
+the existence of additional paths in the
+malicious version. If the set S3 is not empty, we conclude that FlowDroid
+identified the malware.
+
+We use two metrics in this second study:
 the total number of malicious apps FlowDroid is able to find and the
 execution time for running the taint analysis algorithm for each app.
-In this second study we use the same dataset of $96$ pairs of Android apps (B/M),
+Moreover, in this second study we use the same dataset of $96$ pairs of Android apps (B/M),
 originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
@@
 
-We conduct this investigation in three steps. First, we define
-the set of API calls considered as \emph{source of sensitive information} (e.g.,
-a method that access the address book) or
-that \emph{might share information} (e.g., a method that sends messages
-to external peers). We rely on a the source-sink definitions of a previous
-study~\cite{}. After defining the sources and sinks of interest,
-we run FlowDroid to mine the source-sink paths from each benign app, and then enumerate the
-possible data flows between sources and sinks. These paths are considered valid in
-our analysis. Next, we repeat the the FlowDroid execution considering the malicious version
-of the apps. In the final step, we compare the sets of source-sink paths between the benign and malicious
-version of an app, in order to reveal the existence of additional paths in the
-malicious version.
-
 \begin{figure}
-\includegraphics[scale=0.3]{images/second-study-settings.pdf}
+  \centering{\includegraphics[scale=0.4]{images/second-study-settings.pdf}}
+  \caption{Overview of our approach in the second study.}
+  \label{fig:settings2}
 \end{figure}

### 2021-06-09 letter/responseLetter.tex
updates on the response letter to address R2C3

--- 2021-06-08 responseLetter.tex
@@
 \begin{itemize}
-\item In the first place, qhat I missed is an overview of the empirical studies conducted and the relation between 
+\item In the first place, what I missed is an overview of the empirical studies conducted and the relation between 
 first and second experiment. I would recommend to include, before Sections 3.2 and 3.3, a section 
@@
 
-{\color{blue}{\bf Answer:} answer}
+{\color{blue}{\bf Answer.} answer}
 
@@
 methodology is not linked to the research questions: I would recommend to restructure Section 3 in order to have 
-data extraction processes and data analysis producedures for each research question.
+data extraction processes and data analysis procedures for each research question.
 
@@
 
-{\color{blue}{\bf Answer:} answer}
+{\color{blue}{\bf Answer.} Thanks for raising this question.
+Here we were intended to say that FlowDroid implements a more advanced static analysis approach than DroidFax.
+We agree that the sentence is ambiguous, and we fixed that in the new version of the paper (first paragraph
+  of section 3.3).}
 
@@
 testing [1]. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
-not ``Mining Sandboxes''. Also, FlowDroid requires as input the sources and sinks APIs. But you mine ``all sources and sinks 
-paths''. Do you mean all APIs? FlowDroid will never finish running. Assume a set of sensitive sources and sinks are selected, 
+not ``Mining Sandboxes''.
+
+\vspace{0.2cm}
+
+{\color{blue}{\bf Answer.} We totally agree.
+We changed the title of Section 3.3 and fixed this wrong misconception related to our taint analysis usage, which is used not for mining sandboxes but rather as an alternative approach for identifying malware.
+Fixing this issue required modifications not only in Section 3.3 but also in many other parts of the paper (including Abstract, Introduction, and Results).
+Many thanks for raising this issue.}
+
+\vspace{0.2cm}
+
+\item Also, FlowDroid requires as input the sources and sinks APIs. But you mine ``all sources and sinks 
+paths''. Do you mean all APIs? FlowDroid will never finish running. 
+\vspace{0.2cm}
+
+{\color{blue}{\bf Answer.} You are right: we actually use a set of sensitive sources and sinks.
+We changed the second paragraph of Section 3.3 to clarify this point.
+Thanks.
+We hope that the current version of our paper fixes this misunderstanding.}
+
+\vspace{0.2cm}
+
+\item Assume a set of sensitive sources and sinks are selected, 
 FlowDroid is already good in suggesting which one is malign by revealing info flows. What's the point of applying [1]'s setting?
@@
 
-{\color{blue}{\bf Answer:} answer}
+{\color{blue}{\bf Answer.} Our idea in the second study is to find divergences in the info flows when considering two executions of FlowDroid: one execution using the benign version and one execution using the malicious version.
+The source-sink paths collected in the first execution of FlowDroid (benign version)
+ {\bf are not considered suspicious}.
+Only the paths in the second execution, which do not appear in the first execution, are considered suspect and are used to point out the malware.
+We changed Section 3.3 to detail our approach better.}
+
+\vspace{0.2cm}
+
+{\color{blue}{\bf Answer.} answer}
 

### 2021-06-09 setup.tex
updates on the response letter to address R2C3

@@
 In the second study 
-we investigate whether or not a more advanced static analysis approach is promising for
+we investigate whether or not taint-based static analysis approach is also promising for
 identifying malwares, given a version of an app that is proved to be secure.

### 2021-06-09 letter/responseLetter.tex
update on the response letter to address some observation from R3

@@
 \begin{itemize}
-\item In the first place, what I missed is an overview of the empirical studies conducted and the relation between 
+\item In the first place, qhat I missed is an overview of the empirical studies conducted and the relation between 
 first and second experiment. I would recommend to include, before Sections 3.2 and 3.3, a section 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} answer}
 
@@
 methodology is not linked to the research questions: I would recommend to restructure Section 3 in order to have 
-data extraction processes and data analysis procedures for each research question.
+data extraction processes and data analysis producedures for each research question.
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} We changed Section 3.3 to detail our approach better. We also created a picture that can help understand the methodology of our second study.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Thanks for this comment. Our tool actually is available at gitHub repository at:
+
+https://github.com/droidxp/benchmark.
+ \vspace{0.2cm}
+
+We also provide data and scripts of our experiments on-line at:
+
+https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html. 
+\vspace{0.2cm}\newline
+At Section 1 (Introduction) we highlight the existence of these 2 repositories that can be useful for other researchers interested in our study.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Thanks for this observation. We change the picture and unify our terminology.}
 
@@
 
-{\color{blue}{\bf Answer.} Thanks for raising this question.
+{\color{blue}{\bf Answer:} Thanks for raising this question.
 Here we were intended to say that FlowDroid implements a more advanced static analysis approach than DroidFax.
@@
 
-{\color{blue}{\bf Answer.} answer}
-
-\vspace{0.2cm}
-
 \item The significance of this work is questionable. The first study is a mere replication of the existing work [2], except, disabling 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Sorry about these typos and grammar. We corrected all of them. Thanks.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Paragraphs 2 and 3 have indeed similar content. We removed paragraphs 3.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime.
+In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} We agree with that.
+To mitigate this issue, we introduced better DroidXP, contextualizing why its development was important for our study.
+Text improvement is present in the paragraph 6 of introduction}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Sorry about these typos.
+We corrected all of them.
+Thank one more time.
+With respect to ``rooting'': It's a process performed on Android devices like smartphones or tablets, which allows users of the Android mobile operating system, to execute privileged commands that are typically unavailable at its default configuration.
+The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux.\newline
+From: https://en.wikipedia.org/wiki/Rooting(Android)
+}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} With respect to the first sentence, we decided to remove it, since we realized that it was misleading.
+The second sentence we rephrase like : ``For instance Whaley et al.
+[18] combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.''}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Sensitive behaviors at Android context occurs when  an Android application functionality can result in accessing or leaking of Android users sensitive data.
+Example of sensitive behaviors: File accesses and network access.
+We improve the text with this definition at Background and related works Section, paragraph 6.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} We rephrase the text at Background and related works Section, paragraph 6, to better explain Humanoid test generation tool.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} We agree that taint analysis explanation was very briefly.
+We reviewed our Background and related works Section, to better explain taint analysis from paragraph 7.
+We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”.
+To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows within source code Java.
+}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Background and related works Section}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} Thanks for raising this point.
+The section 3.1 presented our Benchmark tool DroidXP.
+We understand that the tool description was important for the paper since it was helpful for our first study conduction.
+DroidXP helped us to easily integrate the different test generation tools, and understand the effect of the static analysis component at each integrated tool.
+It was useful for us and can be very useful for other researchers.
+We
+reviewed the first paragraph of section 3.1 to clarify the importance of DroidXP for our study conduction.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer:} We agree that the sentence was messy.
+We rephrased the sentence to clarify the first paragraph of Section 4.1.
+``Then we repeated the process, however this time we isolate the effect of the static analysis component of DroidFax.''}
 

### 2021-06-09 letter/responseLetter.tex
update on the response letter to address some observation from R3

@@
 
-{\color{blue}{\bf Answer:} Thanks for this comment. Our tool actually is available at gitHub repository at:
+{\color{blue}{\bf Answer.} Thanks for this comment. Our tool actually is available at gitHub repository at:
 
@@
 
-{\color{blue}{\bf Answer:} Thanks for this observation. We change the picture and unify our terminology.}
+{\color{blue}{\bf Answer.} Thanks for this observation. We change the picture and unify our terminology.}
 
@@
 
-{\color{blue}{\bf Answer:} Thanks for raising this question.
+{\color{blue}{\bf Answer.} Thanks for raising this question.
 Here we were intended to say that FlowDroid implements a more advanced static analysis approach than DroidFax.
@@
 
-{\color{blue}{\bf Answer:} Sorry about these typos and grammar. We corrected all of them. Thanks.}
+{\color{blue}{\bf Answer.} Sorry about these typos and grammar. We corrected all of them. Thanks.}
 
@@
 
-{\color{blue}{\bf Answer:} Paragraphs 2 and 3 have indeed similar content. We removed paragraphs 3.}
+{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We removed paragraphs 3.}
 
@@
 
-{\color{blue}{\bf Answer:} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime.
+{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime.
 In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
@@
 
-{\color{blue}{\bf Answer:} We agree with that.
+{\color{blue}{\bf Answer.} We agree with that.
 To mitigate this issue, we introduced better DroidXP, contextualizing why its development was important for our study.
@@
 
-{\color{blue}{\bf Answer:} Sorry about these typos.
+{\color{blue}{\bf Answer.} Sorry about these typos.
 We corrected all of them.
@@
 
-{\color{blue}{\bf Answer:} With respect to the first sentence, we decided to remove it, since we realized that it was misleading.
+{\color{blue}{\bf Answer.} With respect to the first sentence, we decided to remove it, since we realized that it was misleading.
 The second sentence we rephrase like : ``For instance Whaley et al.
@@
 
-{\color{blue}{\bf Answer:} Sensitive behaviors at Android context occurs when  an Android application functionality can result in accessing or leaking of Android users sensitive data.
+{\color{blue}{\bf Answer.} Sensitive behaviors at Android context occurs when  an Android application functionality can result in accessing or leaking of Android users sensitive data.
 Example of sensitive behaviors: File accesses and network access.
@@
 
-{\color{blue}{\bf Answer:} We rephrase the text at Background and related works Section, paragraph 6, to better explain Humanoid test generation tool.}
+{\color{blue}{\bf Answer.} We rephrase the text at Background and related works Section, paragraph 6, to better explain Humanoid test generation tool.}
 
@@
 
-{\color{blue}{\bf Answer:} We agree that taint analysis explanation was very briefly.
+{\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly.
 We reviewed our Background and related works Section, to better explain taint analysis from paragraph 7.
@@
 
-{\color{blue}{\bf Answer:} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Background and related works Section}
+{\color{blue}{\bf Answer.} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Background and related works Section}
 
@@
 
-{\color{blue}{\bf Answer:} Thanks for raising this point.
+{\color{blue}{\bf Answer.} Thanks for raising this point.
 The section 3.1 presented our Benchmark tool DroidXP.
@@
 
-{\color{blue}{\bf Answer:} We agree that the sentence was messy.
+{\color{blue}{\bf Answer.} We agree that the sentence was messy.
 We rephrased the sentence to clarify the first paragraph of Section 4.1.

### 2021-06-09 background.tex
update on the response letter to address some observation from R3

@@
 Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
-Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.
 
@@
 Automatically mining software resources or components, to infer behavior is not new, and has been discussed before.
-For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so extract interface from software components.
+For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.
 Ammons et al~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
@@
 However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes.
-Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random GUI exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
 Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
-In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors, like data leaks and file accesses, higher than Monkey.
-From the same authors, another test generator tool for Android, described as Humanoid \cite{DBLP:conf/kbse/LiY0C19}, is a Droidbot evolution and presents a proposal that can generate humans like tests inputs, using deep learning.
+In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors higher than Monkey.
+Sensitive behaviors at Android context occurs when an Android app functionality can result in accessing or leaking of Android users sensitive data.
+Example of sensitive behaviors are file accesses and network access.
+Another test generator tool for Android is called Humanoid \cite{DBLP:conf/kbse/LiY0C19}, which is a Droidbot evolution.
+It's also a GUI test generation that learning how humans interact with Android apps.
+In contrary to random input generators, Humanoid use the learned model to generate human-like test inputs, and prioritize the possible interactions on a GUI, according their importance.
 
@@
 
-Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet.
-Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}.
-Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the Android operating system.
+\textbf{Taint analysis} is a special type of static or dynamic analysis that purpose is to track data flows within programs~\cite{DBLP:conf/sigsoft/PauckBW18}.
+It can identify sensitive information leakage detecting taint flow between ``source'' and ``sink''.
+In Android apps context, a data leak occurs when sensitive data, such as contact, or device ID, flows from a private source to public sinks, like the internet.
+Taint analysis can present possible malicious data flow to malware detection tools or even for a human check, that can decide if the ``source-sink" relationship is or is not an unwanted behavior.
+Thereby, taint analysis monitors sensitive source ``tainted" through the app by starting at a pre-defined point.
+
+In Android context, sources are the APIs in which apps access sensitive information, called sensitive APIs.
+The analysis follows the data flow until it reaches a sink, like a method that sends SMS.
+Finally, it brings exact information about which data will be leaked and where~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}.
+The Android SDK provides APIs that allow apps to send private data to other apps on the same device, or remote devices.
+As these APIs may lead to sensitive data leakage, they are security-critical and require special attention and control~\cite{DBLP:conf/osdi/EnckGCCJMS10}.
+(Listing~\ref{lst:sourceSink}) presents a simple data leakage example.
+In this example, the device information is captured at line 4 (source) and then leaked at line 9 (sink), by SMS transmission.
+
+\begin{lstlisting}[caption={Simple Data Leakage},
+      language=Java, basicstyle=\fontsize{8}{6}\selectfont\ttfamily,
+      label={lst:sourceSink}]
+
+1 > localObject2 = (TelephonyManager)getSystemService("phone");
+2 > if (localObject2 != null)
+3 > {
+4 >  this.imei = ((TelephonyManager)localObject2).getDeviceId();//source
+5 > }
+6 > if ("".equals(this.destMobile)) {
+7 >  getDestMobile();
+8 > }
+9 > sendSMS(this.destMobile, "imei:" + this.imei)//sink
+\end{lstlisting}
+
+Wei et al.~\cite{DBLP:conf/issta/HuangDMD15} propose a scalable taint analysis for Android apps that applies traditional taint analysis techniques with targeted optimizations specific to Android OS.
 Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity.
 A significant issue with taint analysis is the cost of the tool itself hampering the performance.
-FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.
-
-%Although our study does not incorporate any taint analysis, one can imagine that applying taint analysis as an extra static analysis can drastically improve the precision of the dynamic analysis tools.
+FastDroid~\cite{DBLP:journals/compsec/ZhangTD21} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis, called taint value graph (TVG).
+To improve the efficiency and precision, FastDroid focuses on exploring the propagation of taint values, rather than the traditional data flow analysis.
+FastDroid constructs taint value graphs (TVGs) exploring taint values, then it extracts a subset of potential taint flows (PTFs) from it.
+FastDroid improves the analysis process by performing analysis only on (PTFs).

### 2021-06-09 introduction.tex
update on the response letter to address some observation from R3

@@
 assume that additional behaviors are possible than actually would be.
-%\kn{Ok.
-In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes.
-The overall flow of definitions needs some thought}
-Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
-code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
-of programming languages are often used to introduce malicious behavior. Even though these claims
-seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
+Many times, codes are interpreted, decrypted, or even downloaded at runtime.
+In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.
+In addition, code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features} of programming languages are often used to introduce malicious behavior.
+Even though these claims seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
 Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
@@
 
-We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
-and here we discuss the results of a broader investigation
-that also uses DroidXP to explain the performance of static and dynamic analysis
+Along with the research advancements in the area of test case generation, new solutions are constantly emerging, and researchers and practitioners (including ourselves) have come up against technical difficulties in to reproduce the previous studies that compare test case generation tools to mine sandboxes.
+At our first study, to replicate \blls, we benefit from our benchmark tool, called DroidXP, developed to help researchers and practitioners to integrate test case generation tools and compare
+their performance on mining sandboxes at Android platform.
+The repository for DroidXP is available at GitHub\footnote{https://github.com/droidxp/benchmark} and offers direct access to all source code, installation process, how to run and dependencies.
+We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, and here we discuss the results of a broader investigation that also uses DroidXP to explain the performance of static and dynamic analysis
 approaches for mining sandboxes. Altogether, this paper brings the following contributions:
@@
   scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
-  and a benchmark for reproducing and extending our study.\footnote{https://github.com/droidxp/benchmark} 
+  and a benchmark for reproducing and extending our study.
 \end{itemize}

### 2021-06-09 results.tex
update on the response letter to address some observation from R3

@@
 As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default
-configuration. After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm.
+configuration.
+Then we repeated the process, however this time we isolate the effect of the static analysis component of DroidFax.
 In this way, we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes.
@@
 
-First we find that static analysis summaries had impact in the \blls.
-It was responsible for improving the results of the tools, between $16.44\%$ and $51.79\%$, discarding our Joker tool, answering our first research question (RQ1).
-Second, Table \ref{tab:fs} also summarizes our findings addressing the second research question (RQ2).
-We realized that disregarding the static analysis algorithms, and discarding Joker tool, among the tools analyzed in your study, Humanoid had the biggest performance drop, obtaining an effective performance of $28.12\%$, 27 malicious apps, among 96.
-The least affected was DroidBot, proving be the tool with better effective performance, in terms of the number of detected malware, obtaining an effective performance of $63.54\%$, 61 malicious apps, among 96 .
-Finally, we answered our last research question (RQ3) when we leverage sandboxes, complementing the dynamic analysis provided by test generation tool with tainted analysis algorithms.
-Our experiment highlight that $69.79\%$-$82.29\%$ of malware in dataset can be now uncovered by the complement of tainted analysis algorithms, evidencing that
-sandboxes can be further boosted when coupled with new static analysis techniques.
-We found that the number of identified malicious apps detected is increased for all cases, achieving at the best case, $82.29\%$ with DroidBot, a better performance than all five tools explored at \blls, even when they constructed a sandbox by combining all test generation tools at theirs work $75.49\%$.
-Table \ref{tab:tanted} display the increase of all tools explored at our research.
+Our research reinforces the importance of exploring, the contributions of each component used in surveys.
+The \blls suggested a precision of almost $70\%$ of dynamic analysis tools to differentiate between  the benign and malicious app.
+However, when our work went into the details of the methodology adopted by \blls, it discovered that in their research, the authors ignore the fact that DroidFax tool statically analyzes the Android apps.
+Thereby, our research isolates the contribution of each analysis component (static and dynamic), and reveals that in the best case, dynamic analysis tools obtained a performance of $63.54\%$, showing an overestimation of the performance of the dynamic analysis tools for mining sandboxes at \blls.
+
+Besides that, we also found that static analysis, performed by taint analysis algorithms, detected $60,42\%$ malware analyzed.
+That fact made evident that it is possible to leverage sandboxes, complementing dynamic analysis tools with taint analysis algorithms.
+Researchers and apps developers could investigate the use of new static analysis techniques, or a combination of different approaches, to help developers on the task of developing safer apps.
+
+Our results show that static analysis in short had an impact on the \blls and were responsible for improving the results of the tools, between $16.44\%$ and $51.79\%$, which answers our first research question (RQ1).
+Table \ref{tab:fs} also summarizes our findings addressing the second research question (RQ2).
+We realized that disregarding the static analysis algorithms, Humanoid had the biggest performance drop, obtaining an effective performance of $28.12\%$.
+The least affected tool was DroidBot, proving to be the tool with better effective performance in terms of the number of detected malware, obtaining an effective performance of $63.54\%$.
+Finally, we answered our last research question (RQ3) when we leverage the sandbox, complementing the dynamic analysis with taint analysis algorithms, showing that $69.79\%$-$82.29\%$ of malware can be now uncovered by the static analysis  complement.
+As a result, the number of malicious apps detected increased in all cases, achieving in the best case, $82.29\%$ with DroidBot , evidencing that a sandbox can be further boosted when coupled with new static analysis techniques.
+Dynamic analysis coupled with taint analysis algorithms showed a better performance than all five tools explored at \blls, even when they constructed a sandbox by combining all test generation tools when they achieved $75.49\%$ of malware detection.
+Table \ref{tab:tanted} displays an increase of malware detection on all tools explored in our research.
 
@@
 \end{tabular} 
-\caption{Malwares detected in 96 pair (B/M) increased by Tainted analysis Algorithms}
+\caption{Malwares detected in 96 pair (B/M) increased by Taint analysis Algorithms}
 \label{tab:tanted}

### 2021-06-10 results.tex
update on the response letter to address some observation from R3
presenting a better motivation for the pieces of code

@@
   environment that combines Monkey, DroidMate, and Humanoid to
-  mine Android sandboxes. Introducing the DroidMate 
-  tool does not improve the results.
+  mine Android sandboxes. Contrasting with the \blls, introducing the DroidMate 
+  tool does not improve the overall performance for detecting malwares using
+  a mining sandbox approach.
 \end{finding}
@@
 the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
-PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}. In what follows
-we present more details of representative malwares considered
-in our dataset.
+PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
+At this point, an additional question arises: what are the characteristics
+of the malwares that have (not) been identified using the mining sandbox approach?
+To explore this question, we take advantage of the
+\texttt{dex2jar} tool to reverse-engineer all 96 malwares considered in our analysis and
+computed the \emph{diffs} of the benign/malicious versions of the APPs.
+The results of this activity are available in our replication
+package.\footnote{https://github.com/droidxp/paper-replication-package/blob/master/diff/} 
+In what follows we dissect a few examples of malwares
+that at least one dynamic analysis tool was able to
+identify using the mining sandbox approach. After that,
+we present the characteristics of a malware that none of the tools
+was able to detect. Our goal here is to provide
+a lower-level intuition about the classes of malware the
+mining sandbox approach is able to detect. A reader that
+is not interested in these details could skip to
+Section~\ref{sec:res-ss}.
 
-First, consider the malicious version of the app \texttt{com.andoop.flyracing}---which only the DroidBot and
-Humanoid sandboxes were able to detect. 
-In this particular case, the malicious version changed the Android Manifest file,
+To start with, consider the malicious version of the app \texttt{com.andoop.flyracing}---which both DroidBot and
+Humanoid sandboxes could detect in our analysis. 
+In this particular case, the malicious version changes the Android Manifest file,
 adding permissions to receive and send SMS messages
 (Listing~\ref{lst:androidManifest}). With these permissions, malicious apps may get money
-fraudulently by sending messages without user confirmation, or may monitor messages or delete
-them without showing them to user.
+fraudulently by sending messages without user confirmation, for instance.
 
-Moreover, after decompiling this malware, we also observed that the malicious version of the
-\texttt{MainService} class introduced a
+After decompiling this malware, we also observed that the malicious version of the
+\texttt{MainService} class introduces a
 behavior that collects sensitive information (the International Mobile
@@
 detect this malware.
-In this case, the malicious version of the app changed the Android Manifest file,
+In this case, the malicious version of the app changes the Android Manifest file,
 requiring permissions to access the network and WiFi states (Listing~\ref{lst:androidManifest2}).
 These changes allow an app
-to view the status of all networks and make changes to configured WiFi-fi networks.
+to view the status of all networks and make changes to configured WiFi networks.
 
@@
 
-We also observed that the malicious version introduces a method \texttt{a},
+The malicious version also introduces a method \texttt{a},
 that actually collects network and WiFi information, like Mac address and the network state
@@
 
-All computed sandboxes also detected the malicious version of the app \texttt{ru.qixi.android.smartrabbits}.
-This particular malware also changes the Android Manifest file, requesting permission to access location service (Listing~\ref{lst:androidManifest3}).
-This permission allows access location features, such as the Global Positioning System (GPS) on the phone, if it is enabled.
+All resulting sandboxes also detected the malicious version of the app \texttt{ru.qixi.android.smartrabbits}.
+This particular malware also changes the Android Manifest file,
+requesting permission to access the location service (Listing~\ref{lst:androidManifest3}).
+This permission allows access to location features, such as the Global Positioning System (GPS) on the phone, if it is enabled.
 Malicious applications can use these features to determine where the phone owner is, which is a
-general privacy threat.
+classic and well-documented privacy threat.
 
@@
 In addition, the malicious app clandestinely monitors the geographic location of the user and sink
-these information to a web server. Listing~\ref{lst:c} shows how
-the method \texttt{c}, from \texttt{q} class, collects these sensitive information.
+this information to a web server. Listing~\ref{lst:c} shows how
+the method \texttt{c}, from the class named \texttt{q}, collects this sensitive information.
 
@@
 
-Finally, the \texttt{com.andoop.flyracing} case is among the apps that none sandbox detected the
-malicious version. Indeed, the malicious version only changes the Android Manifest file,
-modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}. Nonetheless, the AdMob is a monetizing
+This pattern of changing the Android Manifest file and including
+new method calls characterizes the classes of malwares for which
+the mining sandbox approach excels. 
+In a different vein, the malicious version of the app
+\texttt{com.andoop.flyracing} is among the apps that none of the sandboxes could
+detect. Indeed, the malicious version only changes the Android Manifest file,
+modifying the meta-data \texttt{ADMOB\_PUBLISHER\_ID}. The AdMob is a monetizing
 service provided by Google, and changing the AdMob \emph{publisher identifier} account redirects
-the advertisement's revenue to another destination. Therefore, it might exist specific
-modifications to the Android manifest file that might complement the mining sandbox
-approach into the task for detecting malwares.
+the advertisement's revenue to another destination. Based on
+this observation, we envision integrating a different approach that reasons
+about modifications to the Android manifest file and that might complement the mining sandbox
+approach into the task for detecting malwares; since the mining
+sandbox approach is not able to detect malicious packages that
+do not introduce new method calls for sensitive APIs.
 
@@
 
-\subsection{Results of the second study: Using taint analysis to mine Android malwares}\label{sec:res-ss}
+\subsection{Results of the second study: Use of Taint Analysis for Malware Identification}\label{sec:res-ss}
 

### 2021-06-13 letter/responseLetter.tex
update on the response letter to address some observation from R3
update paper with R3 commits. Letter response also updated

--- 2021-06-09 letter/responseLetter.tex
@@
 
-{\color{blue}{\bf Answer:} answer}
+{\color{blue}{\bf Answer:} In the introduction, we rephrase paragraphs 5 and 6 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
 
@@
 
-{\color{blue}{\bf Answer:} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime.
-In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
+{\color{blue}{\bf Answer:} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``That is because many times codes can be interpreted, decrypted, or even downloaded at runtime.
+In these cases, the static analysis could be ineffective for mining sandboxes, since that if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
 
@@
 To mitigate this issue, we introduced better DroidXP, contextualizing why its development was important for our study.
-Text improvement is present in the paragraph 6 of introduction}
+Text improvement is present in the paragraph 5 of introduction}
 
@@
 With respect to ``rooting'': It's a process performed on Android devices like smartphones or tablets, which allows users of the Android mobile operating system, to execute privileged commands that are typically unavailable at its default configuration.
-The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux.\newline
-From: https://en.wikipedia.org/wiki/Rooting(Android)
+The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux.
+We insert a footnote with a link that better explain this term at page 4.\newline
+(https://en.wikipedia.org/wiki/Rooting(Android))
 }
@@
 {\color{blue}{\bf Answer:} We agree that taint analysis explanation was very briefly.
-We reviewed our Background and related works Section, to better explain taint analysis from paragraph 7.
+We reviewed our Background and related works Section, to better explain taint analysis from paragraph 8.
 We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”.
@@
 
+what  are  thecharacteristics  of  the  malwares  that  have  (not)  been  identified  using  the  mining  sandbox  approach
+
+Our goal here is to provide a lower-level intuition about the classes of malware the mining sandbox approach is able to detect.
+
 \vspace{0.2cm}
 
-{\color{blue}{\bf Answer:} answer}
+{\color{blue}{\bf Answer:} Thanks for raising this issue.
+Actually our purpose was to present the characteristics of malware that have or have not been identified using the mining sandox approach.
+Our goal is to provide a lower-level intuition about the classes of malware, the mining sandbox approach is good enough, and which ones it fails.
+We rephrased the section 4.1 at this point, to clarify this issue about malware discussion.}
 
@@
 
-{\color{blue}{\bf Answer:} answer}
+{\color{blue}{\bf Answer:} Sorry about these typos and grammar.
+We revised all the text, and corrected this problem like at page 9 (does not computed – does not compute), and page 10 (of our experimental – of our experiments), and some other mistakes that went unnoticed.}
 

### 2021-06-13 letter/responseLetter.tex
update paper with R3 commits. Letter response also updated

--- 2021-06-09 letter/responseLetter.tex
@@
 
-{\color{blue}{\bf Answer:} We changed Section 3.3 to detail our approach better. We also created a picture that can help understand the methodology of our second study.}
+{\color{blue}{\bf Answer.} We changed Section 3.3 to detail our approach better. We also created a picture that can help understand the methodology of our second study.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} In the introduction, we rephrase paragraphs 5 and 6 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
 
@@
 
-{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``Many times, codes are interpreted, decrypted, or even downloaded at runtime.
-In these cases, the static analysis could be ineffective for mining sandboxes, since if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
+{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``That is because many times codes can be interpreted, decrypted, or even downloaded at runtime.
+In these cases, the static analysis could be ineffective for mining sandboxes, since that if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
 
@@
 {\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly.
-We reviewed our Background and related works Section, to better explain taint analysis from paragraph 7.
+We reviewed our Background and related works Section, to better explain taint analysis from paragraph 8.
 We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”.
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} Thanks for raising this issue.
+Actually our purpose was to present the characteristics of malware that have or have not been identified using the mining sandox approach.
+Our goal is to provide a lower-level intuition about the classes of malware, the mining sandbox approach is good enough, and which ones it fails.
+We rephrased the section 4.1 at this point, to clarify this issue about malware discussion.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} Sorry about these typos and grammar.
+We revised all the text, and corrected this problem like at page 9 (does not computed – does not compute), and page 10 (of our experimental – of our experiments), and some other mistakes that went unnoticed.}
 

### 2021-06-14 letter/responseLetter.tex
addressing the criticism on replication

--- 2021-06-09 letter/responseLetter.tex
@@
-\documentclass{letter}
+\documentclass[12pt,english]{scrlttr2}
 
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[]{babel}
+
+\newkomavar{fromplace}
+\setkomavar{fromname}{Francisco Handrick da Costa}
+\setkomavar{fromaddress}{Fairytail-Lane 1}
+\setkomavar{fromplace}{12345 Cologne}
+
+\firsthead{%
+\begin{tabular}{p{0.7\textwidth}p{0.3\textwidth}}
+& \usekomavar{fromname} \newline \usekomavar{fromaddress}  \newline \usekomavar{fromplace} 
+\end{tabular}
+}
+
+% \documentclass{letter}
+
+% \usepackage{natbib}
 \usepackage{hyperref}
 \usepackage{xcolor}
+\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
 
-\signature{Francisco Handrick Tomaz da Costa (on behalf of the authors of the paper)}
+% \signature{Francisco Handrick Tomaz da Costa (on behalf of the authors of the paper)}
 
-\address{Computer Science Department \\ University of Bras\'{i}lia \\ Brazil \\\\ Software Technology Group
- \\ Technical University of Darmstadt \\ Germany}
+%\address{Computer Science Department \\ University of Bras\'{i}lia \\ Brazil \\\\ Software Technology Group
+% \\ Technical University of Darmstadt \\ Germany}
 
@@
 
-\begin{letter}{JSS Editors,}
+\begin{letter}{Dear JSS Editors,}
+
 \opening{The comments of the reviewers have been very useful.
@@
 
-{\color{blue}{\bf Answer.} Thanks for this comment. Our tool actually is available at gitHub repository at:
+{\color{blue}{\bf Answer.} Thanks for this comment. We make avaiable our tool, datasets and
+  scripts in the following links:
 
-https://github.com/droidxp/benchmark.
- \vspace{0.2cm}
+  \begin{itemize}
+    \item \href{https://github.com/droidxp/benchmark}{GitHub repository}.
+    \item \href{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}{datasets and scripts}
+  \end{itemize}
 
-We also provide data and scripts of our experiments on-line at:
-
-https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html. 
 \vspace{0.2cm}\newline
@@
 paths''. Do you mean all APIs? FlowDroid will never finish running.
+
 \vspace{0.2cm}
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} We respectfully disagree with this opinion.
+The relevance of replication in software enginer has gained much more attention in recent years (including recommendations for that~\cite{role-of-replication,standards}),
+  not only to validate past results~\cite{msr-replication} but also to generate new insights
+  from previous research results~\cite{} or even refute past conclusions~\cite{topas-replication}.
+  Indeed, we carried out a non-exact replication of~\cite{}, and the results of our study
+  sheds light that the performance of the dynamic analysis tools explored in~\cite{} is
+  actually different from the previous report. We also agree with the perspective of Shullet al.~\cite{},
+  who argue that an exact replication that achieves the same conclusions of an original work
+  is still valuable to generalize the results of a research. Nonetheless, here we go beyond that,
+  because we give evidence that the performance of the dynamic analysis tools in the previous research
+  work had been overestimated. To make this point clear, we changed \ldots}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.}The \emph{Finding 2 box} summarizes that we achieve the best performance on mining sandboxes when combining Humanoid, Monkey and DroidBot.
+Adding DroidMate to this configuration does not improve the overall performance.
+This result is novel and different from the previous research.
+We have made a slight change in this particular box to stress this point.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} We agree.
+Nonetheless, DroidFax is not part of the dynamic analysis tools.
+According to Bao et al., their goal on using DroidFax was to instrument the APKs with the intent of collecting calls to sensitive APIs.
+However, the use of DroidFax in their study actually lead to an increase in the peformance of dynamic analysis tools for mining sandboxes.
+We did not change any internal component of the dynamic analysis tools, which indeed might include static analysis components.
+We review the title to mitigate this problem.}
 
@@
 
-{\color{blue}{\bf Answer.} Sorry about these typos and grammar. We corrected all of them. Thanks.}
+{\color{blue}{\bf Answer.} Sorry about these typos and grammar issues. We corrected all of them. Thanks.}
 
@@
 
+% \bibliographystyle{unsrtnat}
+% \bibliography{references}
+
 \end{letter}

### 2021-06-14 background.tex

@@
 , calling Java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
-Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
+Another approach to rooting\footnote{https://en.wikipedia.org/wiki/Rooting(Android)} is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
 

### 2021-06-14 introduction.tex

--- 2021-06-03 introduction.tex
@@
 assume that additional behaviors are possible than actually would be.
-%\kn{Ok.
-In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes.
-The overall flow of definitions needs some thought}
-Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
-code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
-of programming languages are often used to introduce malicious behavior. Even though these claims
-seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
+That is because many times codes can be interpreted, decrypted, or even downloaded at runtime.
+In these cases, the static analysis could be ineffective for mining sandboxes, since that if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.
+In addition, code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features} of programming languages are often used to introduce malicious behavior.
+Even though these claims seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
 Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
@@
 
-Our goal in this paper is to understand how static analysis
-algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. Here we
-present the results of two empirical studies that aim to
+Here we replicated \blls, benefiting from our benchmark tool called DroidXP.
+We developed DroidXP to help researchers and practitioners (including ourselves) to integrate test case generation tools and compare their performance on mining sandboxes at Android platform.
+The repository for DroidXP is available at GitHub\footnote{https://github.com/droidxp/benchmark} where offers direct access to all source code, installation process, dependencies, and how to run.
+We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, and here we discuss the results of a broader investigation that also uses DroidXP to explain the performance of static and dynamic analysis approaches for mining sandboxes.
+Our goal is to understand how static analysis algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes.
+This work is an extension of SCAM 2020 paper, since that for our actual study, we had to adapt DroiXP to allow it to isolate the effects of static analysis component of DroidFax, and take into account this effect at our analysis.
+
+Our research work presents the results of two empirical studies that aim to
 address our research goal. In the
-first study, we conduct a replication of the \blls, though our research differs from the original work in three aspects: (a)
-we isolate the effect of the static analysis component of DroidFax, (b) we included a recent dynamic analysis tool for testing Android apps,
-and (c) we extend the execution time and the number of executions of each test case generator tool for all apps
-in our dataset. Differently, in the second study we explore how a more advanced static analysis approach
+first study, we conduct a replication of the \blls, as presented at SCAN 2020 conference~\cite{DBLP:conf/scam/CostaMCMVBC20}, though our research differs from the original work in three aspects:
+
+\begin{enumerate}[(a)]
+  \item We isolate the effect of the static analysis component of DroidFax.
+   \item We included a fake test
+case generation tool (named \joke).
+\joke simulates a test tool that does not execute Android apps during DroidXP execution, disregarding the effects of dynamic analysis, and computing the results with only static analysis DroidFax component.
+\item We extend the execution time and the number of executions of each test case generator tool for all apps
+in our dataset.
+
+\end{enumerate}
+
+Differently, in the second study we explore how a more advanced static analysis approach
 (based on taint analysis) can complement dynamic analysis in the task of mining sandboxes---using
@@
 
-We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
-and here we discuss the results of a broader investigation
-that also uses DroidXP to explain the performance of static and dynamic analysis
-approaches for mining sandboxes. Altogether, this paper brings the following contributions:
+Altogether, this paper brings the following contributions:
 
@@
   sandboxes, showing that we can benefit from using both static and dynamic
-  analysis for detecting Android malwares.
+  analysis for detecting Android malware.
 
@@
 
-\item A replication package of our study that is available on-line, including
+\item A replication package of our study that is available online, including
   scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
-  and a benchmark for reproducing and extending our study.\footnote{https://github.com/droidxp/benchmark} 
+  and a benchmark for reproducing and extending our study.
 \end{itemize}

### 2021-06-14 letter/responseLetter.tex
positioning this paper with respect to the SCAM paper

--- 2021-06-13 letter/responseLetter.tex
@@
-\documentclass{letter}
+\documentclass[12pt,english]{scrartcl}
 
+\usepackage{scrletter}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[]{babel}
+\usepackage[numbers]{natbib}
+
+% \usepackage{natbib}
+% \bibliographystyle{unsrtnat}
+
+%% \newkomavar{fromplace}
+%% \setkomavar{fromname}{Francisco Handrick da Costa (on behalf of the authors of the paper}
+%% \setkomavar{fromaddress}{Computer Science Department \\ University of Bras\'{i}lia}
+%% \setkomavar{fromplace}{Brazil}
+
+%% \firsthead{%
+%% \begin{tabular}{p{0.7\textwidth}p{0.3\textwidth}}
+%% & \usekomavar{fromname} \newline \usekomavar{fromaddress}  \newline \usekomavar{fromplace} 
+%% \end{tabular}
+%% }
+
+% \documentclass{letter}
+
+% \usepackage{natbib}
 \usepackage{hyperref}
@@
 
-\signature{Francisco Handrick Tomaz da Costa (on behalf of the authors of the paper)}
+\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
 
-\address{Computer Science Department \\ University of Bras\'{i}lia \\ Brazil \\\\ Software Technology Group
- \\ Technical University of Darmstadt \\ Germany}
+% \signature{Francisco Handrick Tomaz da Costa (on behalf of the authors of the paper)}
+
+%\address{Computer Science Department \\ University of Bras\'{i}lia \\ Brazil \\\\ Software Technology Group
+% \\ Technical University of Darmstadt \\ Germany}
 
 \begin{document}
+\setkomavar{fromname}{Francisco Handrick da Costa}
+\setkomavar{fromaddress}{Computer Science Department \\ University of Bras\'{i}lia \\ Brazil}
 
-\begin{letter}{JSS Editors,}
+\begin{letter}{Dear JSS Editors,}
+
 \opening{The comments of the reviewers have been very useful.
@@
 
-{\color{blue}{\bf Answer.} Thanks for this comment. Our tool actually is available at gitHub repository at:
+{\color{blue}{\bf Answer.} Thanks for this comment. We make available our tool, datasets and
+  scripts in the following links:
 
-https://github.com/droidxp/benchmark.
+  \begin{itemize}
+    \item \href{https://github.com/droidxp/benchmark}{GitHub repository}.
+    \item \href{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}{datasets and scripts}
+  \end{itemize}
+
   \vspace{0.2cm}
 
-We also provide data and scripts of our experiments on-line at:
-
-https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html. 
-\vspace{0.2cm}\newline
 At Section 1 (Introduction) we highlight the existence of these 2 repositories that can be useful for other researchers interested in our study.}
@@
 
-{\color{blue}{\bf Answer.} Thanks for this observation. We change the picture and unify our terminology.}
+{\color{blue}{\bf Answer.} Thanks for this observation. We unified our terminology throughout the current
+  version of the paper.}
 
@@
 Here we were intended to say that FlowDroid implements a more advanced static analysis approach than DroidFax.
-We agree that the sentence is ambiguous, and we fixed that in the new version of the paper (first paragraph
-  of section 3.3).}
+We agree that the sentence is ambiguous, and we fixed that in the new version of the paper (both in Introduction and in the first paragraph
+  of Section 3.3).}
 
@@
 \item By definition, mining sandboxes means a technique to confine an application to resources accessed during automatic 
-testing [1]. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
+testing~\cite{jamrozikZ16}. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
 not ``Mining Sandboxes''.
@@
 {\color{blue}{\bf Answer.} We totally agree.
-We changed the title of Section 3.3 and fixed this wrong misconception related to our taint analysis usage, which is used not for mining sandboxes but rather as an alternative approach for identifying malware.
+We changed the title of Section 3.3 and fixed this wrong mischaracterization related to our taint analysis usage, which is used not for mining sandboxes but rather as an alternative approach for identifying malware.
 Fixing this issue required modifications not only in Section 3.3 but also in many other parts of the paper (including Abstract, Introduction, and Results).
@@
 paths''. Do you mean all APIs? FlowDroid will never finish running.
+
 \vspace{0.2cm}
 
-{\color{blue}{\bf Answer.} You are right: we actually use a set of sensitive sources and sinks.
-We changed the second paragraph of Section 3.3 to clarify this point.
-Thanks.
-We hope that the current version of our paper fixes this misunderstanding.}
+{\color{blue}{\bf Answer.} You are right: we actually use a curate set of sensitive sources and sinks
+  that is available in the FlowDroid repository.
+  We changed the second paragraph of Section 3.3 to clarify this point. Thanks.
+  We hope that the current version of our paper fixes this problem.}
 
@@
 \item Assume a set of sensitive sources and sinks are selected, 
-FlowDroid is already good in suggesting which one is malign by revealing info flows. What's the point of applying [1]'s setting?
+  FlowDroid is already good in suggesting which one is malign by revealing info flows. What's the point of
+  applying~\cite{jamrozikZ16}'s setting?
 
@@
 
-{\color{blue}{\bf Answer.} Our idea in the second study is to find divergences in the info flows when considering two executions of FlowDroid: one execution using the benign version and one execution using the malicious version.
-The source-sink paths collected in the first execution of FlowDroid (benign version)
+{\color{blue}{\bf Answer.} Our approach in the second study aims to find divergences in the source-sink
+  flows when considering two executions of FlowDroid: one execution using the benign version and
+  one execution using the malicious version. The source-sink paths collected
+  in the first execution of FlowDroid (benign version)
   {\bf are not considered suspicious}.
 Only the paths in the second execution, which do not appear in the first execution, are considered suspect and are used to point out the malware.
-We changed Section 3.3 to detail our approach better.}
+We changed Section 3.3 to
+  detail our approach better.}
 
@@
 
-\item The significance of this work is questionable. The first study is a mere replication of the existing work [2], except, disabling 
-part of the framework. The finding is that DroidFaX is important part for DroidXP. Well, your proved literature's correctness. 
+\item The significance of this work is questionable. The first study is a mere replication of the existing
+  work~\cite{DBLP:conf/wcre/BaoLL18}, except, disabling 
+part of the framework. The finding is that DroidFax is important part for DroidXP. Well, your proved literature's correctness. 
 It would be more impressive the other way round.
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} We respectfully disagree with the ``mere replication''
+  opinion. Indeed, the relevance of replication in software engineer
+  has gained much more attention in recent years~\cite{role-of-replication,shepperd-role-replication},
+  not only to validate past results~\cite{msr-replication} but also to generate new insights
+  from previous research results~\cite{kohl:icse-2020} or even refute past conclusions~\cite{toplas-replication}.
+  Indeed, we carried out an external, non-exact replication
+  of~\cite{DBLP:conf/wcre/BaoLL18}, and the results of our study
+  shed light that the efficacy of the dynamic analysis tools is
+  actually different from the previous report~\cite{DBLP:conf/wcre/BaoLL18}. That is,
+  although we agree with the perspective of
+  Shullet et al.~\cite{role-of-replication},
+  who argue that an exact replication that achieves the same conclusions of an original work
+  is still valuable to generalize the results of a research, here we go beyond that,
+  and give evidence that the efficacy of the dynamic analysis tools in the previous research
+  work had been overestimated. We review the introduction section to clarify this point.}
 
@@
 
-\item I find what's written in Finding 2 is not exciting. It is intuitive based on the results of [1] to know that a comprehensive 
+\item I find what's written in Finding 2 is not exciting. It is intuitive based on the results
+  of~\cite{jamrozikZ16} to know that a comprehensive 
 comparison combining multiple dynamic tools would improve the performance.
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.}\emph{Finding 2} summarizes that we achieve the best performance on mining sandboxes when combining Humanoid, Monkey, and DroidBot.
+Adding DroidMate to this configuration does not improve the overall performance.
+This result is novel and different from the previous research.
+We have made a slight change in this particular box to stress this point.}
 
@@
 
-\item Listings 1-7 illustrate more details of representative malware in the dataset. But what is the take-away message? What 
+\item Listings 1---7 illustrate more details of representative malware in the dataset. But what is the take-away message? What 
 conclusions and/or inspirations can be drawn from such listings?
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.}The goal of the listings is twofold.
+First, to explain the characteristics of the malwares for which the mining sandbox approach could correctly identify the malicious behavior.
+Second, to highlight a particular kind of malwares for which the mining sandbox approach is not practical (last malware example).
+For the first class of malware, the malicious version of the apps frequently includes changes in the Android manifest file and also modifies the bytecode to include additional method calls that might share sensitive information.
+The listings show concrete examples of the code after a re-engineering effort, which might help readers understand why the mining sandbox approach works for those cases.
+Similarly, the last instance of malware only changes the manifest file.
+Since it does not include any additional method call, the mining sandbox approach could not point out the malicious version of the app as malware.
+We changed the last paragraphs of Section 4.1 to justify these listings better.
+}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} We agree.
+Nonetheless, DroidFax is not part of the dynamic analysis tools.
+According to Bao et al.~\cite{jamrozikZ16}, their goal on using DroidFax was to instrument the APKs with the intent of collecting calls to sensitive APIs, while executing the dynamic analysis tools.
+However, the use of DroidFax in their study actually lead to an increase in the performance of dynamic analysis tools for mining sandboxes.
+We did not change any internal component of the dynamic analysis tools, which indeed might include static analysis components.
+We reviewed the title to mitigate this problem.}
 
@@
 
-\item What are sensitive behaviors? ``showed that Droidbot is able to trigger an amount of sensitive behaviors''
+\item What are sensitive behaviors? ``showed that DroidBot is able to trigger an amount of sensitive behaviors''
 
@@
 \item Please rephrase:
-``From the same authors, another test generator tool for Android, described as Humanoid [23], is a Droidbot evolution and
+``From the same authors, another test generator tool for Android, described as Humanoid [23], is a DroidBot evolution and
 presents a proposal that can generate humans like tests inputs, using deep learning.''
@@
 {\color{blue}{\bf Answer.} Thanks for raising this issue.
-Actually our purpose was to present the characteristics of malware that have or have not been identified using the mining sandox approach.
+Actually our purpose was to present the characteristics of malware that have or have not been identified using the mining sandbox approach.
 Our goal is to provide a lower-level intuition about the classes of malware, the mining sandbox approach is good enough, and which ones it fails.
@@
 
+\bibliographystyle{abbrvnat}
+\bibliography{references}
+
 \end{letter}

### 2021-06-14 introduction.tex
positioning this paper with respect to the SCAM paper

--- 2021-06-03 introduction.tex
@@
 The sandbox might then monitor any call to sensitive APIs while the app is running, blocking calls that have not been identified during the exploratory phase---thereby protecting Android users from additional malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
-
-Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
-The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
-assume that additional behaviors are possible than actually would be.
-%\kn{Ok.
-In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes.
-The overall flow of definitions needs some thought}
-Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
-code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
-of programming languages are often used to introduce malicious behavior. Even though these claims
-seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
+Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis---mostly because of the overapproximation problem: ``static analysis often assume that more behaviors are possible than actually would be''~\cite{DBLP:conf/icse/JamrozikSZ16}.
+In addition, code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features} of programming languages are often used to introduce malicious behavior.
+Even though these claims are reasonable, previous research results do not present empirical assessments about the limitations of static analysis to mine sandboxes.
 Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.
@@
 The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
-Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) (B/M) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
-Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which might lead to an over estimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
+Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
+Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which might lead to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
 
-Our goal in this paper is to understand how static analysis
-algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. Here we
-present the results of two empirical studies that aim to
-address our research goal. In the
-first study, we conduct a replication of the \blls, though our research differs from the original work in three aspects: (a)
-we isolate the effect of the static analysis component of DroidFax, (b) we included a recent dynamic analysis tool for testing Android apps,
-and (c) we extend the execution time and the number of executions of each test case generator tool for all apps
-in our dataset. Differently, in the second study we explore how a more advanced static analysis approach
-(based on taint analysis) can complement dynamic analysis in the task of mining sandboxes---using
-the FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} infrastructure for analysing Android apps.
+The goal of this paper is two fold. First we present the results of an
+external, non-exact replication~\cite{role-of-replication} of the \blls. To this end,
+we take advantage of DroidXP, a tool suite that helps researchers (including ourselves) to
+integrate test case generation tools and compare their performance on
+mining Android sandboxes. We discussed the design and implementation of DroidXP in a conference
+paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, which also
+includes an initial evaluation of DroidXP.
+As a matter of fact, the results of the first DroidXP evaluation revealed a possible
+overestimation in the performance of dynamic analysis tools as
+reported in the \blls---which in the end motivated us to
+conduct the non-exact replication of that study. Here we extend
+our previous work with a slight customization of DroidXP, which allowed us
+to reproduce the \blls by means of a serie of experiments
+that reveal the actual performance of the
+dynamic analysis tools. Section~\ref{sec:droidxp} revisit the
+DroidXP design, while Section~\ref{sec:set1} discuss
+the setup of our replication study.
 
-We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
-and here we discuss the results of a broader investigation
-that also uses DroidXP to explain the performance of static and dynamic analysis
-approaches for mining sandboxes. Altogether, this paper brings the following contributions:
+%% In summary, our current study differs fromthe original work in three aspects:
+
+%% \begin{enumerate}[(a)]
+%%   \item We isolate the effect of the static analysis component of DroidFax.
+%%    \item We included a fake test
+%% case generation tool (named \joke).
+\joke simulates a test tool that does not execute Android apps during DroidXP execution, disregarding the effects of dynamic analysis, and computing the results with only static analysis DroidFax component.
+%% \item We extend the execution time and the number of executions of each test case generator tool for all apps
+%% in our dataset.
+
+%% \end{enumerate}
+%% where offers direct access to all source code, installation process, dependencies, and how to run.
+We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, and here we discuss the results of a broader investigation that also uses DroidXP to explain the performance of static and dynamic analysis approaches for mining sandboxes.
+Our goal is to understand how static analysis algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes.
+This work is an extension of SCAM 2020 paper, since that for our actual study, we had to adapt DroiXP to allow it to isolate the effects of static analysis component of DroidFax, and take into account this effect at our analysis.
+
+%% Our research work presents the results of two empirical studies that aim to
+%% address our research goal. In the
+%% first study, we conduct a replication of the \blls, as presented at {\color{red}SCAN 2020} conference~\cite{DBLP:conf/scam/CostaMCMVBC20}, though
+
+Second, in this paper we also explore how a static analysis approach
+(based on taint analysis) compares and complements the mining sandbox technique
+for identifying malicious behavior that infects benign applications.
+The idea here is to compare the dataflows from \emph{source} to
+\emph{sink} statements computed using two executions of the
+FlowDroid infrastructure: one execution that analyses
+a benign version of an Android app and one execution that
+analyses a malicious version. We consider that
+the taint analysis approach is able to identify a malware whenever
+we find a dataflow from a source to a sink in the second execution
+that does not appear in the first one. We detail the
+settings of this taint analysis study in Section~\ref{sec:set2}
+
+Altogether, this paper brings the following contributions:
 
@@
 \item A replication of the \blls that better clarifies the performance of
-  dynamic analysis tools for mining Android sandboxes.
+  dynamic analysis tools for mining Android sandboxes. The results of
+  our replication (Section~\ref{sec:res-fs})
+  give evidence that the previous work overestimated
+  the performance of the dynamic analysis tools---that is, without
+  DroidFax (an independent component used for running the
+  \blls experiment), the performance of the tools drop by {\color{red}xyz\%}.
 
@@
   sandboxes, showing that we can benefit from using both static and dynamic
-  analysis for detecting Android malwares.
+  analysis for detecting malicious Android apps. In addition,
+  we give evidence that a well known static analysis approach, based on
+  taint analysis, leads to a performance similar to the dynamic analysis
+  approach for diferenciating benign and malign versions of the same
+  app (Section~\ref{sec:res-ss}).
 
-\item Evidence that a well known static analysis approach, based on
-  taint analysis, leads to a performance similar to the dynamic analysis
-  approach for mining sandboxes.
+\item A reproduction package of our study that is available online, including
+  scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
+  and a benchmark for reproducing and extending our study. The repository for DroidXP is available
+at GitHub\footnote{https://github.com/droidxp/benchmark}.
 
-\item A replication package of our study that is available on-line, including
-  scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
-  and a benchmark for reproducing and extending our study.\footnote{https://github.com/droidxp/benchmark} 
 \end{itemize}
-
-%% \todo[inline]{RB: review the following paragraph later}
-%% The rest of the paper is organized as follows.
-Section 2 we present a background and some related works.
-Section 3 introduces the study setting of our research and Section 4 complements presenting some results and discussion, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples.
-Finally, Sections 5 and 6, summarizes the paper, presenting some threats, presenting the final conclusions, and discussing our ideas for future works.
-
-%% \begin{enumerate}[(1)]
-%%  \item presenting a non-exact replication of the study of the efficiency of test generation tools for mining android sandboxes, using a benchmark solution developed for this specific purpose.
-
-%%  \item discovering which are the contribution installments of types of analysis for malware detection task.
-
-%%  \item presenting which are malware characteristics, that was not detected by any tool in our analysis dynamic and static experiment.
-
-%%  \item presenting data that indicate that static analysis can improve the mining sandboxes process for malware detection.
-%%  \end{enumerate}
-
-%% We organize the remainder of this paper as follows.
-Section 2 we present a background and some related works.
-Section 3 describes all the apps malware used in our experiment, presenting their characterization.
-Section 4 introduces the study setting of our research.
-Section 5 presented some results, highlighting some motivation malware example.
-Section 6 we present the use of a promising static analysis tool, in our motivation example.
-Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-06-14 setup.tex
positioning this paper with respect to the SCAM paper

--- 2021-06-09 setup.tex
@@
 and does not require any additional installation effort. We included Humanoid in our study
-because it emulates realistic users, creating human-like test inputs using deep learning techniques.
+because it is a recent tool that emulates realistic users, creating human-like test inputs using deep learning techniques.
 
@@
 Android app (B/M) in each one of the five test generation tools, including \joke,
-for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox
+for three minutes, and for three times. We then investigated the performance of each tool to detect malicious behaviors in the sandbox
 modeled by the test generation tool
@@
 In the second study 
-we investigate whether or not a more advanced static analysis approach is promising for
-identifying malwares, given a version of an app that is proved to be secure.
+we investigate whether or not a taint-based static analysis approach is also promising for
+identifying malwares, given a version of an app that we can assume to be secure.
 To this end, we leverage the FlowDroid
@@
 goal here is to investigate if it is possible to detect malicious
-behavior by identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
+behavior by means of identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
 analysing a benign and a malign versions of an Android app.
@@
 a set of API methods marked either as {\bf source}
-or {\bf sink}. Source methods are those that access \emph{sensitive information} (e.g.,
+or {\bf sink} (or both). Source methods are those that access \emph{sensitive information} (e.g.,
 a method that access the address book), while sink methods are those 
 that \emph{might share information with external peers} (e.g., a method that
-sends messages to a recipient). We rely on the source-sink definitions of a previous
-study~\cite{}, which involves ABC source methods and XYZ sink methods.
+sends messages to a recipient). We rely on the source-sink definitions
+of the FlowDroid implementation~\cite{arzt:pldi-2014,rasthofer-source-sink},
+which involves a curate list of source and sink methods (including callbacks and
+other Android API methods of interest).
 FlowDroid then uses a \emph{context, flow, and field
-sensitive analysis} to identify all dataflow paths from sources to sinks~\cite{}.
+sensitive analysis} to identify all dataflow paths from sources to sinks~\cite{arzt:pldi-2014}.
 However, it is important to note that not all source-sink paths are malicious, and then we
@@
 benign version of an app, and then enumerate a set (S1) with the 
-possible dataflows between sources and sinks. All paths in S1 are considered safe in
+possible dataflows between sources and sinks. All paths in S1 are considered secure in
 our analysis. In the second step we repeat the FlowDroid execution, though
-considering the malicious APK version of the app. This leads to a second set (S2) of source-sink paths. In the final step, we compute the difference (S3) between
+considering the malicious APK version of the app.
+This leads to a second set (S2) of source-sink paths. In the final step, we compute the difference (S3) between
 the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$), in order to reveal

### 2021-06-14 abstract.tex
update abstract - we did not use Taint Analysis for mining sandboxes

@@
 This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the efficacy of tainted analysis algorithms for mining Android sandboxes.
+In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement mining Android sandboxes.
 To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al.
@@
 work, leading to an overestimation of the performance of the dynamic analysis tools.
-The results of the second study show that (static) tainted analysis is also practical for mining Android sandboxes, with a performance similar to that reached by dynamic analysis tools.
+The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}

### 2021-06-14 abstract-jss.tex
update abstract - we did not use Taint Analysis for mining sandboxes

@@
 This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the efficacy of tainted analysis algorithms for mining Android sandboxes.
+In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement mining Android sandboxes.
 To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al.
-study.
-%\emph{Results.}
+study.%\emph{Results.}
 Our study brings several findings.
@@
 work, leading to an overestimation of the performance of the dynamic analysis tools.
-The results of the second study show that (static) tainted analysis is also practical for mining Android sandboxes, with a performance similar to that reached by dynamic analysis tools.
+The results of the second study show that (static) tainted analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}

### 2021-06-15 abstract-jss.tex
abstract improvements

--- 2021-02-25 abstract-jss.tex
@@
 \begin{abstract}
-  The use of sandboxes is an effective technique for malware analysis.
-However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for mining Android sandboxes.
-Accordingly, in this paper we present the results of two studies that investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
+%  \emph{Context.}
+The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}.
+The mining sandbox approach consists in running fuzzing test tools into a benign version of the app.
+This exploratory phase records all calls to sensitive APIs.
+Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the fuzzing tools again in a different version of the app.
+During this second execution of the fuzzing tools, a warning of possible malicious behavior is raised whenever the new version of the app calls a sensitive API not recorded in the exploratory phase.
+%  \emph{Problem.}
+
+The use of a mining sandbox approach is an effective technique for Android malware analysis, as previous research works revealed.
+Particularly, existing reports present an accuracy of almost 70\% in the identification of malicious behavior using dynamic analysis tools to mine android sandboxes.
+However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static with a mining sandbox approach for identifying malicious behavior.
+Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools tailored for mining Android sandboxes, in the task of identifying malicious behavior.
 %\emph{Method.}
-In the first study we conduct a non-exact replication of the Bao et al.
-work, a previous study that compares the performance of test case generation tools for mining Android sandboxes.
-Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) they used to instrument the Android apps in their experiments.
+
+In the first study we conduct a non-exact replication of a previous study (hereafter \blls) that compares the performance of test case generation tools for mining Android sandboxes.
+Differently from the original work, here we isolate the effect of an independent  static analysis component (DroidFax) they used to instrument the Android apps in their experiments.
 This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the efficacy of tainted analysis algorithms for mining Android sandboxes.
-To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al.
-study.
+In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining Android sandbox approach previously used to identify malicious behavior.
+To this end, we executed the FlowDroid tool to mine the source-sink flows from benign/malign pairs of Android apps used in a previous research work.
 %\emph{Results.}
+
 Our study brings several findings.
-For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
-work, leading to an overestimation of the performance of the dynamic analysis tools.
-The results of the second study show that (static) tainted analysis is also practical for mining Android sandboxes, with a performance similar to that reached by dynamic analysis tools.
+For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the \blls dataset, leading to an overestimation of the performance of the dynamic analysis tools.
+The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}

### 2021-06-15 abstract.tex
abstract improvements

@@
 For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}.
+The mining sandbox approach consists in running fuzzing test tools into a benign version of the app.
+This exploratory phase records all calls to senstive appis.
+Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the fuzzing tools again in a different version of the app.
+During this second execution of the fuzzing tools, a warning of possible malicious behavior is raised whenever the new version of the app calls a sensitive API not recorded in the exploratory phase.
 %  \emph{Problem.}
-The use of sandboxes is an effective technique for malware analysis.
-However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for mining Android sandboxes.
-Accordingly, in this paper we present the results of two studies that investigate whether or not static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes.
+The use of a mining sandbox approach is an effective technique for Android malware analysis, as previous research works revealed.
+Particularly, existing reports present an accuracy of almost 70\% in the identification of malicious behavior using dynamic analysis tools to mine android sandboxes.
+However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for identifying malicious behavior.
+Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools in the task of identifying malicious behavior.
 %\emph{Method.} 
-In the first study we conduct a non-exact replication of the Bao et al.
-work, a previous study that compares the performance of test case generation tools for mining Android sandboxes.
-Differently from the original work, here we isolate the effect of the static analysis tool (DroidFax) they used to instrument the Android apps in their experiments.
+In the first study we conduct a non-exact replication a previous study that compares the performance of test case generation tools for mining Android sandboxes.
+Differently from the original work, here we isolate the effect of an independent  static analysis component (DroidFax) they used to instrument the Android apps in their experiments.
 This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement mining Android sandboxes.
-To this end, we executed the FlowDroid tool to mine the source-sink flows from the benign/malign pairs of Android apps used in the Bao et al.
-study.
+In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining Android sandbox approach previously used to identify malicious behavior.
+To this end, we executed the FlowDroid tool to mine the source-sink flows from benign/malign pairs of Android apps used in a previous research work.
 %\emph{Results.}
 Our study brings several findings.
-For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the Bao et al.
-work, leading to an overestimation of the performance of the dynamic analysis tools.
+For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the work we replicated in this study, leading to an overestimation of the performance of the dynamic analysis tools.
 The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.

### 2021-06-16 letter/responseLetter.tex
update all paper and response letter

@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} answer  }
 
@@
 
-{\color{blue}{\bf Answer.} We changed Section 3.3 to detail our approach better. We also created a picture that can help understand the methodology of our second study.}
+{\color{blue}{\bf Answer.} We restructured Section 3.3 to detail our approach better.
+We created sub Section 3.2.1 to present data extraction process of our First study, and 3.2.2 to present data analysis procedure.
+In some way, we created sub Section 3.3.1 and 3.3.2, to address the same issues, referring to our second study.
+With this restructuring we better clarify our study setting Section, presenting more details about our first (Section 3.2) and second study (Section 3.3).
+We also created a picture that can help to understand the methodology of our second study (Figure 3).
+}
 
@@
 working on Android sandboxes as well as what are the next steps that the research community should pursue to 
-improve the detection of malwares.
+improve the detection of malware.
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} We agree.
+To mitigate this issue, we include at Section 6 (Conclusion and future work Section) one last paragraph that points how our results can be useful for researches at Android sandboxes.
+In the same paragraph, we also highlight which next steps can contribute to research evolution.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} We improved the abstract, making it clearer. We better contextualized ``mining sandbox approach'', presenting its definition e importance for Android malware analysis.}
 
@@
   that is available in the FlowDroid repository.
-  We changed the second paragraph of Section 3.3 to clarify this point. Thanks.
+  We changed the first paragraph of Section 3.3.1 to clarify this point. Thanks.
   We hope that the current version of our paper fixes this problem.}
@@
 Only the paths in the second execution, which do not appear in the first execution, are considered suspect and are used to point out the malware.
-We changed Section 3.3 to
+We changed Section 3.3.2 to
   detail our approach better.}
@@
 
-{\color{blue}{\bf Answer.} In the introduction, we rephrase paragraphs 5 and 6 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
+{\color{blue}{\bf Answer.} In the introduction, we rephrase paragraphs 4 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
 
@@
 
-{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 3, where we add the follow text: ``That is because many times codes can be interpreted, decrypted, or even downloaded at runtime.
-In these cases, the static analysis could be ineffective for mining sandboxes, since that if static analysis determines that some behavior will not occur, it no longer will be checked at runtime.''}
+{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 2.}
 
@@
 
-{\color{blue}{\bf Answer.} We agree with that.
-To mitigate this issue, we introduced better DroidXP, contextualizing why its development was important for our study.
-Text improvement is present in the paragraph 5 of introduction}
+{\color{blue}{\bf Answer.} We agree with that. To mitigate this issue, we introduced better DroidXP at introduction, paragraph 4.}
 
@@
 
-{\color{blue}{\bf Answer.} Sensitive behaviors at Android context occurs when  an Android application functionality can result in accessing or leaking of Android users sensitive data.
+{\color{blue}{\bf Answer.} Sensitive behaviors at Android context occurs when an Android app functionality can result in accessing or leaking of users sensitive data.
 Example of sensitive behaviors: File accesses and network access.
-We improve the text with this definition at Background and related works Section, paragraph 6.}
+We improve the text with this definition at Section 2 (Background and related works), paragraph 6.}
 
@@
 
-{\color{blue}{\bf Answer.} We rephrase the text at Background and related works Section, paragraph 6, to better explain Humanoid test generation tool.}
+{\color{blue}{\bf Answer.} We rephrase the text at Section 2 (Background and related works) paragraph 6, to better explain Humanoid test generation tool.}
 
@@
 {\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly.
-We reviewed our Background and related works Section, to better explain taint analysis from paragraph 8.
+We reviewed our Section 2 (Background and related works), to better explain taint analysis from paragraph 8.
 We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”.
@@
 
-{\color{blue}{\bf Answer.} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Background and related works Section}
+{\color{blue}{\bf Answer.} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Section 2 (Background and related works)}
 
@@
 We understand that the tool description was important for the paper since it was helpful for our first study conduction.
-DroidXP helped us to easily integrate the different test generation tools, and understand the effect of the static analysis component at each integrated tool.
+DroidXP helped us to easily integrate the different test generation tools, and understand the effect of the static analysis component at each tool.
 It was useful for us and can be very useful for other researchers.

### 2021-06-16 conclusionfutureworks.tex
update all paper and response letter

@@
 Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis.
-For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
+For the second experiment, we complement the dynamic analysis using taint analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
 The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, $58.33\%$-$76.04\%$ of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
@@
 We also found that $18.75\%$ of malicious apps (18 out of 96) could be detected by none of the sandboxes generated.
-In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%).
-With the exception of DroidBot tool, tainted analysis algorithms had a better performance than any sandbox constructed by the execution of another test case tool, without the Droidfax static analysis algorithms.
-Our work show that the number of malicious behaviours detected is increased for all cases with tainted analysis aid, achieving at the best case, $82.29\%$ (79 among 96) of malware detected with DroidBot.
+In the second experiment, the taint analysis detected 58 among 96 pairs investigated (60.42\%).
+With the exception of DroidBot tool, taint analysis algorithms had a better performance than any sandbox constructed by the execution of another test case tool, without the Droidfax static analysis algorithms.
+Our work show that the number of malicious behaviours detected is increased for all cases with taint analysis aid, achieving at the best case, $82.29\%$ (79 among 96) of malware detected with DroidBot.
 
@@
 And, we will compare these results with this experiment's results.
-This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.
+This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark DroidXP has on its results.
+
+Our research topic is very critical around the world, and contributions to this domain are necessary and should be considered strategic from the privacy perspective.
+The present work offered relevant insights into the role of dynamic and static Analysis for Android malware detection, and can be potentially useful for security researchers at Android platform.
+Our empirical findings demonstrate that static analysis techniques when combined with dynamic analysis at mining sandbox approach is a promising line of work
+to improve the task of identifying malicious behavior at Android apps.
+As a next step, the research community should pursue explore possible static analysis techniques aimed at information flow analysis \cite{DBLP:conf/kbse/ShenVTADLKZ14} in general, and taint analysis \cite{arzt:pldi-2014} specifically, that we believe are possible to be integrated with dynamic analysis techniques, to compose a new mining proposal in sandbox.
+Another research line should also concentrate on the study of improvement in automatic test generation to modeling sandbox.
+Some studies point that code coverage of automatic test generation is not high \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}\cite{DBLP:conf/kbse/ChoudharyGO15}, and needs improvement.
+When we are talking about ``improvement'', we refer not only to the ability to detect bugs but rather coverage of ``typical'' behavior, answering as accurately as possible the question: ``What an Android app actually proposes to do ?''

### 2021-06-16 setup.tex
update all paper and response letter

@@
 Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation in terms of the number of detected malware by each sandbox, constructed by the test
-generation tools explored in \blls. Ignoring the implications of DroidFax in the \blls might have introduced a possible threat to their conclusions. Answering the third research question
-allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
+generation tools explored in \blls. Ignoring the implications of DroidFax in the \blls might have introduced a possible threat to their conclusions. Answering research question RQ3
+allows us to open up the possibility of finding new strategies for malware detection, complementing the performance of
 dynamic analysis through the use of static analysis algorithms.
@@
 FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to investigate the 
-suitability of taint analysis algorithms for mining Android sandboxes.
+suitability of taint analysis algorithms to complement mining Android sandboxes.
+The main idea of this second study is explore the possibility of detected extra malware, do not detected at our first study, through another static analysis strategy based on taint analysis.
 We present the settings of the second study in Section~\ref{sec:set2}.
@@
 The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
-sandboxes, based on the calls to sensitive APIs from 102 pairs (benign / malign) of Android apps. In their work, \emph{performance} is
-measured as the total number of malwares a sandbox is able to identify when comparing the calls to sensitive APIs made by
-the benign and malign versions of the app. A \emph{hit} occurs whenever a sandbox finds that the malicious version of an app calls
-additional sensitive APIs, in comparison to the calls from the corresponding benign version.
-Nonetheless, the \blls uses DroidFax to instrument the Android apps, even though DroidFax also
-collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
+sandboxes. Since the \blls does not
 compute the possible impact of DroidFax into the performance of the test generation tools,
@@
 $102$ pairs of Android apps used in the \blls, here we discarded $6$ pairs for which
-we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool (Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}), which
+we were not able to instrument---out of the $102$ pairs used in the original work, originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16}.
+We also introduced a recent test generator tool (Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}), which
 has not been considered in the previous work. Finally, we extended the execution time of each test generation tool,
@@
 
-% In the first study we executed the DroidXP benchmark with its
-% default configuration, that is, enabling the DroidFax
-% static analysis algorithms and the test generation tools.
+\subsubsection{Sensitive APIs extraction process}
 
-We first run the experiment using the default
-settings of DroidXP, to explore the four test case generation tools described earlier and a fake test
-case generation tool (named \joke). \joke simulates a test tool that does not execute
-the Android apps during a benchmark execution. Using this tool, the results
-of the dynamic analysis are not considered and we can compute the results with
-only the static analysis component of DroidFax (RQ1). Our study executed each pair of
-Android app (B/M) in each one of the five test generation tools, including \joke,
-for three minutes, and for three times. We then investigated the performance of each tool to detect malicious behaviors in the sandbox
-modeled by the test generation tool
-under analysis.
+In our first study, sensitive APIs extraction process starts with monitoring of invocations of sensitive APIs during the apps (already instrumented) execution by test generation tools under analysis.
+This task is essential for the process since sensitive APIs are used to access resource sensitives and it call could be a clue of private data leakage.
+Our study based at a list of 97 sensitive APIs, defined by the AppGuard privacy-control framework~\cite{DBLP:conf/esorics/BackesGHMS13}.
+Initially, we performances the extraction process using the default settings of DroidXP, (e.g., using DroidFax static analysis component).
+We explored the four test case generation tools described earlier and a fake test case generation tool (named \joke).
 
-After that, we replicated the analysis using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
-Using this new configuration, we executed the benchmark again, using the same dataset of Android apps, the same execution time,
+\joke simulates a test tool that does not execute the Android apps during the exploratory phase.
+Using this tool the results of the dynamic analysis are not considered, and we can compute the results with only the static analysis component of DroidFax (RQ1).
+Our study executed each 96 pair of
+Android app (B/M) in each test generation tool, including \joke, for three minutes, and for three times.
+
+Then we repeated this process, however this time we used a DroidXP configuration that disables the DroidFax static analysis algorithm.
+With this new configuration, we monitored sensitive APIs invocations again, using the same 96 pair of Android app (B/M), the same execution time,
 and the same test case generation tools.
-The results of this replication allow us to compute the effective performance
-of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
-DroidFax static analysis algorithms.
-Figure \ref{fig:setup} shows all the phases of our experiments, that explore all sensitive
-resources access by both apps (B/M), and the optional configuration DroidXP, that disables DroidFax static analysis.
+With this new configuration, became possible computer the effective performance of each test generation tool, in terms of malware detected, discarding the contributions of DroidFax static analysis algorithm (RQ2).
+
+\subsubsection{Sensitive APIs analysis procedures}
+
+After exploring all sensitive APIs by all test tools, we analyzed the \emph{performance} of these tools to detect malicious behaviors.
+The procedure starts with the analysis of each sandbox modeled by their respective test generation tools, based on the calls to sensitive APIs.
+
+The test generation tool \emph{performance} is measured as the total number of malware, your respective sandbox is able to identify when comparing the calls to sensitive APIs made by the benign and malign versions of the app.
+We raise a warning (a \emph{hit}) whenever a sandbox finds that the malicious version of an app calls additional sensitive APIs, in comparison to the calls from the corresponding benign version.
+Figure \ref{fig:setup} shows all the phases of our experiments, that explore all sensitive resources access by both apps (B/M), and the optional configuration DroidXP, which disables DroidFax static analysis.
+
+Assuming that our fake test case generation tool does not run the Android apps, its \emph{performance} analysis will reveal the DroidFax static algorithms impact at \blls, answering our first research question (RQ1).
+The analysis of the calls to sensitive APIs made by the 96 pair (B/M), when we disable the DroidFax static analysis component, will reveal the effective \emph{performance} of each test generation test tool under analysis, answering our second research question (RQ2).
 
@@
 To this end, we leverage the FlowDroid
-taint analysis algorithms for Android apps, in order to identify dataflows
+taint analysis algorithms for Android apps, at version 2.8, in order to identify dataflows
 that might lead to the leakage of sensitive information. Our
@@
 analysing a benign and a malign versions of an Android app.
-define.
+
+\subsubsection{Source-sink paths extraction}
 
@@
 sensitive analysis} to identify all dataflow paths from sources to sinks~\cite{arzt:pldi-2014}.
-However, it is important to note that not all source-sink paths are malicious, and then we
-follow a specific methodology to identify malwares in our work: we raise a
-warning (a \emph{hit}) whenever
+
+Source-sink paths extraction involve two steps (see Figure~\ref{fig:settings2}).
+In the first, we execute FlowDroid to mine the source-sink paths from a benign version of an app, and then enumerate a set (S1) with the
+possible dataflows between sources and sinks. All paths in S1 are considered secure for
+our future analysis. In the second step we repeat the FlowDroid execution, though
+considering the malicious APK version of the app.
+This leads to a second set (S2) of source-sink paths.
+
+\subsubsection{Source-sink paths analysis}
+
+For our analysis it is important to note that not all source-sink paths are malicious, and then we
+follow a specific methodology to identify malware in our work: we raise a warning (a \emph{hit}) whenever
 FlowDroid finds an additional source-sink path in the malicious version of an app, which
 has not been identified when analysing the benign version.
-
-Our research settings involve three steps (see Figure~\ref{fig:settings2}).
-In the first, we execute FlowDroid to mine the source-sink paths from a
-benign version of an app, and then enumerate a set (S1) with the 
-possible dataflows between sources and sinks. All paths in S1 are considered secure in
-our analysis. In the second step we repeat the FlowDroid execution, though
-considering the malicious APK version of the app.
-This leads to a second set (S2) of source-sink paths. In the final step, we compute the difference (S3) between
-the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$), in order to reveal
-the existence of additional paths in the
-malicious version. If the set S3 is not empty, we conclude that FlowDroid
+For this end, we compute the difference (S3) between the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$), in order to reveal the existence of additional paths in the malicious version (third step).
+If the set S3 is not empty, we conclude that FlowDroid
 identified the malware.
@@
 We use two metrics in this second study:
-the total number of malicious apps FlowDroid is able to find and the
-execution time for running the taint analysis algorithm for each app.
-Moreover, in this second study we use the same dataset of $96$ pairs of Android apps (B/M),
-originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
-also used in the \blls.
+the total number of malicious apps FlowDroid is able to find and the execution time for running the taint analysis algorithm for each app.
+Moreover, in this second study we use the same dataset of $96$ pairs of Android apps (B/M) used in the First study.
+Our second study will lead to discover what is the capacity of malware detection of taint analysis algorithms compared to mining sandbox approach, and its potential to complement dynamic analysis for mining sandboxes, thus answering our last research question (RQ3).
 

### 2021-06-17 setup.tex
review of the setup section

--- 2021-06-14 setup.tex
@@
 
-In this section
-we present the settings of our study, whose goal is to build a general understanding of the implications of using static analysis algorithms
-to complement a dynamic analysis approach
-for mining Android sandboxes. % We also investigate how static analysis can improve the performance of mining sandboxes, in the task of identifying malicious behavior.
-To achieve this goal, we answer the following research questions.
+Our research work aims to better understand
+the use of static analysis to mine Android sandboxes
+and explore the benefits of combining taint analysis
+with the mine sandbox approach for identifying malicious
+behavior. 
+On the one hand, Jamrozik et al. suggest that a 
+static analysis approach for mining sandboxes
+might be ineffective---due to \emph{overapproximation
+problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
+However, to the best of our knowledge,
+there is no empirical study comparing
+static and dynamic analysis for mining sandboxes.
+On the other hand, the \blls explored the mining sandbox approach by comparing
+the performance of {\bf dynamic analysis tools} for identifying
+malicious behavior. Nonetheless, their
+research also involved an external static analysis component (DroidFax)
+whose impact on the results was not measured.
+This lack of understanding about the implications of
+static analysis for mining sandboxes motivates
+our research, which investigates the following research questions.
 
@@
 
-Answering the research questions RQ1 and RQ2 allows us to expose a possible overestimation in terms of the number of detected malware by each sandbox, constructed by the test
-generation tools explored in \blls. Ignoring the implications of DroidFax in the \blls might have introduced a possible threat to their conclusions. Answering the third research question
-allows us to open up the possibility of finding new strategies for designing mining sandbox techniques, complementing the performance of
+Answering the research questions RQ1 and RQ2 allows us to better
+understand the relevance of combining static
+and dynamic analysis for mining Android sandboxes. Moreover,
+exploring RQ1 and RQ2 can reveal 
+a possible overestimation of the performance of the
+dynamic analysis tools in the \blls. Answering research question RQ3
+allows us to open up the possibility of finding new strategies for malware detection, complementing the performance of
 dynamic analysis through the use of static analysis algorithms.
-We conducted two studies to answer the research questions above. In the
-first study we leverage DroidXP~\cite{DBLP:conf/scam/CostaMCMVBC20} (Section~\ref{sec:droidxp}) to replicate
-the \blls. We present the settings of this first study in Section~\ref{sec:set1}.
-In the second study we use
+We conducted two empirical studies to answer the research questions above. We address
+the research questions RQ1 and RQ2 in the
+first empirical study, whose goal is to conduct a non-exact replication of
+the \blls. We conduct the first empirical study using
+DroidXP~\cite{DBLP:conf/scam/CostaMCMVBC20} (Section~\ref{sec:droidxp}), a
+tool that simplifies the execution of experiments
+that compare the performance of dynamic analysis tools
+in the task of identifying malwares, using a mining sandbox
+approach. We present the study settings of the first
+empirical study in Section~\ref{sec:set1}.
+In the second empirical study we use
 FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to investigate the 
-suitability of taint analysis algorithms for mining Android sandboxes.
-We present the settings of the second study in Section~\ref{sec:set2}.
+suitability of taint analysis algorithms to complement the mining sandbox
+approach for identifying malwares, and thus it targets our third
+research question (RQ3). We present the settings of the second
+empirical study in Section~\ref{sec:set2}.
 
@@
 
-We used DroidXP to systematically assess and compare the performance of test generation tools for mining android sandboxes. DroidXP relies on a
-simple \emph{Command Line Interface} (CLI) that simplifies the integration of different test generation tools and favors the setup and execution 
-of the experiments. DroidXP also relies on DroidFax, which instruments Android apps and collects relevant information about
+We used DroidXP to systematically assess and compare the
+performance of test generation tools for mining android sandboxes. DroidXP relies on a
+simple \emph{Command Line Interface} (CLI) that simplifies the integration
+of different test generation tools and favors the setup and execution 
+of the experiments. DroidXP also relies on DroidFax, which instruments
+Android apps and collects relevant information about
 their execution, including the set of sensitive APIs a given
-app calls during a test execution. DroidFax also collects inter-component communication (ICC) using  static
+app calls during a test execution. DroidFax also collects
+inter-component communication (ICC) using  static
 program analysis.
@@
 generation tools (executing the project with the option ``list-tools'') that had been
-integrated into the benchmark and commands that execute the experiments. An
-experiment run can be configured according to several parameters, including:
+integrated into the tool and commands for executing the experiments. An
+\emph{experiment run} can be configured according to several parameters, including:
 
@@
 
-Figure~\ref{fig:benchArq} shows the DroidXP architecture, based on the pipes-and-filters architectural style \cite{architecture-book}. 
+Figure~\ref{fig:benchArq} shows the DroidXP architecture, based on the pipes-and-filters
+architectural style \cite{architecture-book}. 
 The architecture includes three main components; where each component is responsible for a specific phase of the
-benchmark (instrumentation, execution, and result analysis).
+experiments execution (instrumentation, execution, and result analysis).
 
@@
   \label{benchArq}
-  \caption{Benchmark architecture}
+  \caption{DroidXP architecture}
   \label{fig:benchArq}
 \end{figure*}
+
 \subsubsection{Phase 1: Instrumentation}
 
-In the first phase, a researcher must define the corpus of APK files DroidXP should consider during a benchmark execution.
-After that, DroidXP starts the DroidFax service that instruments each APK file, so that DroidXP would be able to collect data about each execution.
-To improve the performance of the benchmark, the instrumentation phase runs only once for each APK.
-In this phase, the DroidFax tool also runs some static analysis procedures---when the option \texttt{--disable-static-analysis} is not set.
+In the first phase, a researcher must define the corpus of APK files DroidXP should consider during an
+experiment execution. After that, DroidXP starts the DroidFax service that instruments each APK file,
+so that DroidXP would be able to collect data (e.g., calls to sensitive APIs) about each execution.
+To improve the performance of DroidXP, the instrumentation phase runs only once for each APK.
+In this phase, the DroidFax tool also runs some static analysis procedures---when the
+option \texttt{--disable-static-analysis} is not set.
 
@@
 during a period of time. This process repeats for every test case generation
-tool and APK files. To provide repeatability of the experiment, DroidXP removes all data stored in the emulator before starting
+tool and APK files. To provide repeatability of the experiment, DroidXP
+removes all data stored in the emulator before starting
 a new execution. That is, every execution uses a \emph{fresh} emulator,
@@
 previous executions. 
-
 It is relatively easy to add new test
-case generation tools into DroidXP. To achieve this goal, it leverages the Strategy Design
-pattern~\cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the particularities
-for running each tool we want to integrate into DroidXP.
+case generation tools into DroidXP. Indeed,
+every new tool must override two methods
+of a \texttt{Tool} abstract class (according to
+the Strategy Design pattern~\cite{patterns-book}.
 %To carry out our replication study, we successfully integrated all
@@
 differences between the sensitive API accessed by each version of an app (benign or malign).
-In the end, the benchmark outputs the results of the experiment, which gives the
+In the end, DroidXP outputs the results of the experiment, which gives the
 performance of one or more testing generator tools in mining sandboxes.
 
-We used the DroidXP infrastructure to conduct the replication of
-the \blls, whose settings we present in the following section.
+We used the DroidXP infrastructure to conduct our
+first empirical study, whose settings we present in the following section.
 
@@
 three times---the original work executed each test generation tool
-only once. That is, our goal here is not to conduct an
+only once. It is important to note that our goal here is not to conduct an
 exact replication of the \blls, but instead understand
@@
 
-% In the first study we executed the DroidXP benchmark with its
-% default configuration, that is, enabling the DroidFax
-% static analysis algorithms and the test generation tools.
+\subsubsection{Data Collection}
 
-We first run the experiment using the default
-settings of DroidXP, to explore the four test case generation tools described earlier and a fake test
-case generation tool (named \joke). \joke simulates a test tool that does not execute
-the Android apps during a benchmark execution. Using this tool, the results
-of the dynamic analysis are not considered and we can compute the results with
-only the static analysis component of DroidFax (RQ1). Our study executed each pair of
-Android app (B/M) in each one of the five test generation tools, including \joke,
-for three minutes, and for three times. We then investigated the performance of each tool to detect malicious behaviors in the sandbox
-modeled by the test generation tool
-under analysis.
+Similarly to the \blls, besides
+method coverage information, our experiments record every call
+to \emph{sensitive methods} of the Android
+platforms, while a given test case generation tool
+is running. We consider the
+same set of 97 sensitive methods 
+the AppGuard privacy-control framework
+uses~\cite{DBLP:conf/esorics/BackesGHMS13}.
 
-After that, we replicated the analysis using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
-Using this new configuration, we executed the benchmark again, using the same dataset of Android apps, the same execution time,
-and the same test case generation tools.
-The results of this replication allow us to compute the effective performance
-of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
-DroidFax static analysis algorithms.
-Figure \ref{fig:setup} shows all the phases of our experiments, that explore all sensitive
-resources access by both apps (B/M), and the optional configuration DroidXP, that disables DroidFax static analysis.
+Here we take advantage of
+DroidXP to execute the different test case generation
+tools () in
 
-\begin{figure}[ht]
-  \centering{
-   \includegraphics[width=0.75\textwidth]{images/setup3.png}}
-   \label{Experiment setup}
-   \caption{Experiment setup}
-   \label{fig:setup}
- \end{figure}
+To answer the first two research questions
+(RQ1 and RQ2), we also included in our experiments
+a fake test case generation tool named
+Joker.
+
+We executed DroidXP using two
+configurations. In the first (WOS), we executed DroidXP
+using the dataset of 96 pairs of Android apps---each pair
+including a benign and a malign version,
+the four test case generation tools (DroidBot, DroidMate, Monkey, and Humanoid),
+and the \texttt{--disable-static-analysis} option of
+DroidFax, which disables the
+execution of the DroidFax static analysis
+component from the experiment. The WOS configuration
+runs the test case generation tools for three times, using
+a time limit of three minutes. 
+In the second configuration (WS), we executed DroidXP
+using the same dataset of 96 pairs of Android apps, though 
+executing only a fake test case generator tool (named Joker)
+{\bf without} the \texttt{--disable-static-analysis} option.
+Joker simulates a test tool that does not
+run the Android apps during an experiment execution.
+
+Using the WS configuration, the Execution Phase of
+DroidXP does not collect any call to 
+sensitive APIs, and thus we can estimate the performance of the
+static analysis component of DroidFax (and thus answer
+RQ1).
+Differently, the WOS configuration
+disables the static analysis component of DroidFax and
+we could better estimate the true performance of the test
+case generation tools for mining android sandboxes 
+(answering RQ2).
+
+\subsubsection{Data Analysis}
+
+DroidXP produces a
+dataset with the sensitive
+APIs that the benign / malign
+versions of an app call, during
+the execution of each test case
+generation tool. We estimate the
+performance of a test case generation
+tool by considering the percentage of
+malwares its \emph{sandbox} is able to
+identify.
+
+Recall that we build a sandbox 
+during the exploratory of the mining
+sandbox approach. This exploratory
+phase records the set of 
+sensitive APIs a benign version of an
+app calls---during the execution of a test
+case generation tool. Similarly to the \blls,
+we consider that a sandbox of an
+app identifies a malware whenever the
+malicious version makes a call to a sensitive API  
+that has not been recorded during the exploratory
+phase.
+
+To sum up, in order to analyse the
+performance of the test case generation tools (including Joker),
+we just have to compare the calls to sensitive APIs made by
+the benign and malign versions of the apps, during
+the execution of the tools. We then use descriptive statistics
+and plots to compare the performance of the tools and
+answer RQ1 and RQ2.
 
@@
 
-In the second study 
+In the second empirical study 
 we investigate whether or not a taint-based static analysis approach is also promising for
-identifying malwares, given a version of an app that we can assume to be secure.
+identifying malwares, given a version of an app that we can assume to be secure (goal of research
+question RQ3).
 To this end, we leverage the FlowDroid
-taint analysis algorithms for Android apps, in order to identify dataflows
+taint analysis algorithms for Android apps (version 2.8), in order to identify dataflows
 that might lead to the leakage of sensitive information. Our
 goal here is to investigate if it is possible to detect malicious
-behavior by means of identifying the \emph{divergent} source-sink paths that FlowDroid reveals after
+behavior by means of the \emph{divergent} source-sink paths that FlowDroid reveals after
 analysing a benign and a malign versions of an Android app.
-define.
+
+\subsubsection{Data Collection}
 
@@
 FlowDroid then uses a \emph{context, flow, and field
-sensitive analysis} to identify all dataflow paths from sources to sinks~\cite{arzt:pldi-2014}.
-However, it is important to note that not all source-sink paths are malicious, and then we
-follow a specific methodology to identify malwares in our work: we raise a
-warning (a \emph{hit}) whenever
+sensitive analysis} to identify dataflow paths from sources to sinks~\cite{arzt:pldi-2014}.
+
+Our data collection approach involves three steps (see Figure~\ref{fig:settings2}).
+In the first, we execute FlowDroid to mine the source-sink paths from a benign version of an app, and then enumerate a set (S1) with the
+possible dataflows between sources and sinks. All paths in S1 are considered secure
+in our analysis. In the second step we repeat the FlowDroid execution, though
+considering the malicious APK version of the app.
+This leads to a second set (S2) of source-sink paths.
+
+It is important to note that not all source-sink paths are malign, and then we
+follow a specific methodology to identify malwares using taint analysis. That is,
+we only report a malware when
 FlowDroid finds an additional source-sink path in the malicious version of an app, which
 has not been identified when analysing the benign version.
+To this end, in the third step we compute the difference (S3) between the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$).
+If the set S3 is not empty, we assume that FlowDroid
+has identified the malware.
 
-Our research settings involve three steps (see Figure~\ref{fig:settings2}).
-In the first, we execute FlowDroid to mine the source-sink paths from a
-benign version of an app, and then enumerate a set (S1) with the 
-possible dataflows between sources and sinks. All paths in S1 are considered secure in
-our analysis. In the second step we repeat the FlowDroid execution, though
-considering the malicious APK version of the app.
-This leads to a second set (S2) of source-sink paths. In the final step, we compute the difference (S3) between
-the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$), in order to reveal
-the existence of additional paths in the
-malicious version. If the set S3 is not empty, we conclude that FlowDroid
-identified the malware.
-
-We use two metrics in this second study:
-the total number of malicious apps FlowDroid is able to find and the
-execution time for running the taint analysis algorithm for each app.
-Moreover, in this second study we use the same dataset of $96$ pairs of Android apps (B/M),
-originally shared in the AndroZoo repository~\cite{DBLP:conf/msr/AllixBKT16} and
-also used in the \blls.
+In this second study we use the same dataset of $96$ pairs of Android apps (B/M) used in the first empirical
+study.
 
@@
 \end{figure}
+
+\subsubsection{Data analysis}
+
+We use two metrics in this second study:
+the total number of malicious apps FlowDroid is able to
+find and the execution time for running the taint analysis algorithm
+for each app. Similarly to the first empirical study,
+we use descriptive statistics
+and plots to compare the performance of the taint analysis and
+mining sandbox approaches.

### 2021-06-18 introduction.tex
update all paper and response letter
Introduction comments

@@
 
-Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}.
-Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
+Almost two-thirds of the world use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}.
+Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}\kn{Can we here say by how much?}.
 Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably, to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms either to identify privacy leaks or to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
 
-Other approaches rely on the use of dynamic analysis to mine Android sandboxes~\cite{DBLP:conf/icse/JamrozikSZ16}.
-In this case, during an exploratory phase, one leverages an automatic test case generator tool that runs a benign version of an Android app and collects the set of calls made to sensitive APIs.
+Another perspective to the solving the same problem are approaches that rely on the use of dynamic analysis to mine Android sandboxes~\cite{DBLP:conf/icse/JamrozikSZ16}.
+With dynamic approaches, during an exploratory phase, one leverages an automatic test case generator tool that runs a benign version of an Android app and collects the set of calls made to sensitive APIs\kn{Is this the case for just Jamrozik's work or all of dynamic approaches.
+It is not clear}.
 This set of calls comprises a sandbox infrastructure.
@@
 
-The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes.
+The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes\kn{The use of word same here makes me wonder if readers could be confused.
+IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right?
+Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}.
 Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
@@
   DroidFax (an independent component used for running the
-  \blls experiment), the performance of the tools drop by {\color{red}xyz\%}.
+  \blls experiment), the performance of the tools drop between $16.44$\% to $58$\%.
 

### 2021-06-18 background.tex
Background.tex

@@
 
+\kn{This section starts abrupt.
+We should have a line that says what concepts we introduce on a high level.
+Also, I feel "sandbox" itself should be one of the backgrounds and have a textbf after the introductory line.}
 A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}.

### 2021-06-18 results.tex
update all paper and response letter
Results and setup

@@
 
-Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
+Altogether, ignoring  \joke, our study reveals that from $58.33$\% (Humanoid)
 to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
@@
 and Humanoid sandboxes computed in the second execution (without the DroidFax static analysis
-algorithms). This result shows that static analysis algorithms are promising for mining
+algorithms). This result shows that static analysis algorithms are promising to complement mining
 sandboxes, demystifying previous claims in the literature.

### 2021-06-18 setup.tex
Results and setup

@@
 
+\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis.
+a.k.a effect of taint analysis on sandboxes.
+But in the introduction we kind of use the general S-D interaction and this problem interchangeably.
+I have left a comment at the introduction.}
 Our research work aims to better understand
@@
 
- \item What is the effective performance of each test generation tool, in terms of the number of detected malware, when we
+ \item What is the effective performance of each test generation tool\kn{Should we use the term sandboxes instead of test generation tools?
+Test generation is just part of sandboxes right?}, in terms of the number of detected malware, when we
    discard the contributions of the DroidFax static analysis algorithms?
@@
 
+\kn{Isnt DroidXP a contribution of our approach? If yes, we should start more confidently than saying we "used" it. We should introduce it as a contribution as such.}
 We used DroidXP to systematically assess and compare the

### 2021-06-18 setup.tex
additional review on Section 3

@@
 
-\kn{Isnt DroidXP a contribution of our approach? If yes, we should start more confidently than saying we "used" it. We should introduce it as a contribution as such.}
-We used DroidXP to systematically assess and compare the
-performance of test generation tools for mining android sandboxes. DroidXP relies on a
+We designed and implemented DroidXP to systematically assess and compare the
+performance of test generation tools for mining android sandboxes. It allows
+the integration and comparison of test case generation tools for mining sandboxes, and simplifies
+the reproduction of the studies. DroidXP relies on a
 simple \emph{Command Line Interface} (CLI) that simplifies the integration
@@
 The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
-sandboxes. Since the \blls does not
+sandboxes~\cite{DBLP:conf/wcre/BaoLL18}. Since the \blls does not
 compute the possible impact of DroidFax into the performance of the test generation tools,
@@
 same set of 97 sensitive methods 
-the AppGuard privacy-control framework
+from the AppGuard privacy-control framework
 uses~\cite{DBLP:conf/esorics/BackesGHMS13}.
 
-Here we take advantage of
-DroidXP to execute the different test case generation
-tools () in
-
-To answer the first two research questions
-(RQ1 and RQ2), we also included in our experiments
-a fake test case generation tool named
-Joker.
-
 We executed DroidXP using two
-configurations. In the first (WOS), we executed DroidXP
+configurations. In the first (named WOS), we executed DroidXP
 using the dataset of 96 pairs of Android apps---each pair
@@
 a time limit of three minutes. 
-In the second configuration (WS), we executed DroidXP
+In the second configuration (named WS), we executed DroidXP
 using the same dataset of 96 pairs of Android apps, though 
@@
 sensitive APIs, and thus we can estimate the performance of the
-static analysis component of DroidFax (and thus answer
+static analysis component of DroidFax (answering
 RQ1).
@@
 case generation tools for mining android sandboxes 
-(answering RQ2).
+(answering RQ2). For comparison purpose, we also
+executed the four test case generation tools using the
+DroidFax static analysis component.
 
@@
 tool by considering the percentage of
-malwares its \emph{sandbox} is able to
-identify.
+malwares in our dataset
+its resulting sandbox is able to identify .
 
 Recall that we build a sandbox 
-during the exploratory of the mining
+during the exploratory phase of the mining
 sandbox approach. This exploratory
@@
 that has not been recorded during the exploratory
-phase.
+phase (see Figure~\ref{fig:settings1}).
+
+\begin{figure}
+  \centering{\includegraphics[scale=0.4]{images/first-study-settings.pdf}}
+  \caption{Overview of our approach for malware identification in the first study.}
+  \label{fig:settings1}
+\end{figure}
 
@@
 or {\bf sink} (or both). Source methods are those that access \emph{sensitive information} (e.g.,
-a method that access the address book), while sink methods are those 
+a method that access the user location), while sink methods are those 
 that \emph{might share information with external peers} (e.g., a method that
@@
 has not been identified when analysing the benign version.
-To this end, in the third step we compute the difference (S3) between the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$).
+Therefore, in the third step we compute the difference (S3) between the sets S2 and S1 (i.e., $S3 = S2 \setminus S1$).
 If the set S3 is not empty, we assume that FlowDroid

### 2021-06-18 letter/responseLetter.tex
review a few answers to R1 an R2

@@
 
-{\color{blue}{\bf Answer.} answer  }
-
-\vspace{0.2cm}
-
 \item In the second place, I would recommend to include more details on the experiments conducted. This is especially 
@@
 
-{\color{blue}{\bf Answer.} We restructured Section 3.3 to detail our approach better.
-We created sub Section 3.2.1 to present data extraction process of our First study, and 3.2.2 to present data analysis procedure.
-In some way, we created sub Section 3.3.1 and 3.3.2, to address the same issues, referring to our second study.
-With this restructuring we better clarify our study setting Section, presenting more details about our first (Section 3.2) and second study (Section 3.3).
-We also created a picture that can help to understand the methodology of our second study (Figure 3).
-}
+{\color{blue}{\bf Answer.} Thanks for raising these issues. We reviewed Section 3 in full,
+to detail our approach better. In particular, we expanded the methodology of our
+second study (Section 3.3) and highlighted our data collection and analysis procedures.
+Regarding verifiability and replicability, we improved the documentation of our
+packages and tools (see the next comment).}
 
@@
 
-{\color{blue}{\bf Answer.} Thanks for this comment. We make available our tool, datasets and
-  scripts in the following links:
+{\color{blue}{\bf Answer.} Thanks for this comment.
+All tools, datasets, and scripts we used in our research are available on-line.
+The following repositories present detailed instructions about these assets:
 
   \begin{itemize}
-    \item \href{https://github.com/droidxp/benchmark}{GitHub repository}.
-    \item \href{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}{datasets and scripts}
+    \item \href{https://github.com/droidxp/benchmark}{DroidXP GitHub repository}.
+    \item \href{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}{Datasets and scripts}
   \end{itemize}
@@
 
-At Section 1 (Introduction) we highlight the existence of these 2 repositories that can be useful for other researchers interested in our study.}
+  We also included references to these repositories in the first section (Introduction) of the current version of
+  our paper.}
 
@@
 
-{\color{blue}{\bf Answer.} We agree.
-To mitigate this issue, we include at Section 6 (Conclusion and future work Section) one last paragraph that points how our results can be useful for researches at Android sandboxes.
-In the same paragraph, we also highlight which next steps can contribute to research evolution.}
+{\color{blue}{\bf Answer.} Still pending.}
 
@@
 
-\item The abstract is not clear. First, the context if not well addressed. For example, why ``mining Android sandboxes'' is 
-important? I had to read several related reference at the beginning to understand it. Second, it is not common practice to 
+\item The abstract is not clear. First, the context if not well addressed.
+  For example, why ``mining Android sandboxes'' is important? I had to read
+  several related reference at the beginning to understand it. Second, it is not common practice to 
 include reference in abstract. However, I reserve my opinion since I know it may be preferred by some researchers.
@@
 
-{\color{blue}{\bf Answer.} We improved the abstract, making it clearer. We better contextualized ``mining sandbox approach'', presenting its definition e importance for Android malware analysis.}
+{\color{blue}{\bf Answer.} Thanks for raising these questions. We reviewed the abstract
+  to better explain the relevance of the mining sandbox approach. Literature reports
+  show that the mining sandbox approach is effective  not only to prevent malicious
+  calls to sensitive APIs but also to classify a version of an app as a malware.}
 
@@
 
-\item In Figure 2, you used ``Malicious'', but in most other places, you used ``Malign''. Please unify your choice of terminology.
+\item In Figure 2, you used ``Malicious'', but in most other places, you used ``Malign''.
+  Please unify your choice of terminology.
 
@@
 \item By definition, mining sandboxes means a technique to confine an application to resources accessed during automatic 
-testing~\cite{jamrozikZ16}. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already 
-not ``Mining Sandboxes''.
+testing~\cite{jamrozikZ16}. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already not ``Mining Sandboxes''.
 
@@
 We changed the title of Section 3.3 and fixed this wrong mischaracterization related to our taint analysis usage, which is used not for mining sandboxes but rather as an alternative approach for identifying malware.
-Fixing this issue required modifications not only in Section 3.3 but also in many other parts of the paper (including Abstract, Introduction, and Results).
+Fixing this issue required modifications not only in Section 3.3 but also in many other parts of the paper (including the paper Title, Abstract, Introduction, and Results).
 Many thanks for raising this issue.}
@@
   that is available in the FlowDroid repository.
-  We changed the first paragraph of Section 3.3.1 to clarify this point. Thanks.
+  We changed Section 3.3 to clarify this point. Thanks once again.
   We hope that the current version of our paper fixes this problem.}
@@
 Only the paths in the second execution, which do not appear in the first execution, are considered suspect and are used to point out the malware.
-We changed Section 3.3.2 to
+We changed Section 3.3 to
   detail our approach better.}
@@
 
-{\color{blue}{\bf Answer.} We respectfully disagree with the ``mere replication''
-  opinion. Indeed, the relevance of replication in software engineer
+{\color{blue}{\bf Answer.} The relevance of replication in software engineer
   has gained much more attention in recent years~\cite{role-of-replication,shepperd-role-replication},
@@
 
-\item The title itself is inaccurate. You removed DroidFax from the replicated work[1]. But it is not the only static analysis part. 
-Actually, many dynamic testing tools use static analysis to better guide their testing strategy.
+\item The title itself is inaccurate. You removed DroidFax from the replicated work~\cite{DBLP:conf/wcre/BaoLL18}.
+  But it is not the only static analysis part. Actually, many dynamic testing tools use
+  static analysis to better guide their testing strategy.
 
@@
 We reviewed the title to mitigate this problem.}
-
-\vspace{0.2cm}
-
-\item Typos:
-1. Page 3: to explains -- to explain.
-2. Page 3: BLL-Study study -- BLL-Study.
-3. Page 8, does not computed -- does not compute.
-4. Page 9, of our experimental -- of our experiments.
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} Sorry about these typos and grammar issues. We corrected all of them. Thanks.}
 
@@
 
-{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We removed paragraphs 3.}
+{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We removed paragraph 3.}
 
@@
 
-{\color{blue}{\bf Answer.} We explained better the sentence at Introduction, paragraph 2.}
+{\color{blue}{\bf Answer.} We explained better this sentence in the second paragraph of our
+  first section (Introduction). Thanks for raising this issue.}
 

### 2021-06-21 introduction.tex
changes in the RQs

@@
 Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
-Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which might lead to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.
+Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which, as we discuss in this paper, leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work.
+Moreover, since DroidFax is an independent component (it is not part of the dynamic analysis tools explored in the \blls), a practitioner might run a dynamic analysis tool alone that is likely to present a smaller capacity to identify malware.
 

### 2021-06-21 setup.tex
changes in the RQs

@@
 On the other hand, the \blls explored the mining sandbox approach by comparing
-the performance of {\bf dynamic analysis tools} for identifying
+the performance of five {\bf dynamic analysis tools} (DroidMate, DroidBot, PUMA,
+GUIRipper, and Monkey) for identifying
 malicious behavior. Nonetheless, their
 research also involved an external static analysis component (DroidFax)
-whose impact on the results was not measured.
+whose impact on the results was not measured---in terms of malware
+identification. 
 This lack of understanding about the implications of
@@
 
- \item What is the impact of the DroidFax static analysis algorithms into the results of the \blls?
+\item What is the impact of the DroidFax static analysis algorithms on the results of the BLL-Study?
+  We estimate the impact in terms of the number of detected malwares.
 
- \item What is the effective performance of each test generation tool\kn{Should we use the term sandboxes instead of test generation tools?
-Test generation is just part of sandboxes right?}, in terms of the number of detected malware, when we
+ \item What is the effective performance of each sandbox, in terms of the number of detected malware, when we
    discard the contributions of the DroidFax static analysis algorithms?
@@
  \item What are the benefits of using taint
- analysis algorithms to complement the dynamic analysis approach for mining sandboxes?
+   analysis algorithms to complement the dynamic analysis approach for mining sandboxes,
+   in terms of additional malwares identified?
 \end{enumerate}

### 2021-06-22 results.tex
review the implications section

@@
 %% \end{figure}
-
-\subsection{Discussion}\label{sec:discussion}
-
-Our research reinforces the importance of exploring, the contributions of each component used in surveys.
-The \blls suggested a precision of almost $70\%$ of dynamic analysis tools to differentiate between  the benign and malicious app.
-However, when our work went into the details of the methodology adopted by \blls, it discovered that in their research, the authors ignore the fact that DroidFax tool statically analyzes the Android apps.
-Thereby, our research isolates the contribution of each analysis component (static and dynamic), and reveals that in the best case, dynamic analysis tools obtained a performance of $63.54\%$, showing an overestimation of the performance of the dynamic analysis tools for mining sandboxes at \blls.
-
-Besides that, we also found that static analysis, performed by taint analysis algorithms, detected $60,42\%$ malware analyzed.
-That fact made evident that it is possible to leverage sandboxes, complementing dynamic analysis tools with taint analysis algorithms.
-Researchers and apps developers could investigate the use of new static analysis techniques, or a combination of different approaches, to help developers on the task of developing safer apps.
-
-Our results show that static analysis in short had an impact on the \blls and were responsible for improving the results of the tools, between $16.44\%$ and $51.79\%$, which answers our first research question (RQ1).
-Table \ref{tab:fs} also summarizes our findings addressing the second research question (RQ2).
-We realized that disregarding the static analysis algorithms, Humanoid had the biggest performance drop, obtaining an effective performance of $28.12\%$.
-The least affected tool was DroidBot, proving to be the tool with better effective performance in terms of the number of detected malware, obtaining an effective performance of $63.54\%$.
-Finally, we answered our last research question (RQ3) when we leverage the sandbox, complementing the dynamic analysis with taint analysis algorithms, showing that $69.79\%$-$82.29\%$ of malware can be now uncovered by the static analysis  complement.
-As a result, the number of malicious apps detected increased in all cases, achieving in the best case, $82.29\%$ with DroidBot , evidencing that a sandbox can be further boosted when coupled with new static analysis techniques.
-Dynamic analysis coupled with taint analysis algorithms showed a better performance than all five tools explored at \blls, even when they constructed a sandbox by combining all test generation tools when they achieved $75.49\%$ of malware detection.
-Table \ref{tab:tanted} displays an increase of malware detection on all tools explored in our research.
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{lccc}\toprule
- Test Generation & FlowDroid & Total & \%\\
- Tool & Increase  &  & \\ \midrule
- DroidBot & 6 & 79 & 82.29\\
- Monkey & 7 &  78 & 81.25 \\
- DroidMate & 7 & 75 & 78.12  \\
- Humanoid & 16 & 72 & 75.00 \\
- Joker & 25 & 67 & 69.79  \\\midrule
-
-\end{tabular} 
-\caption{Malwares detected in 96 pair (B/M) increased by Taint analysis Algorithms}
-\label{tab:tanted}
-\end{table}
-
-%%here we also have to write about the intersection between droidfax and tainted analysis now, and about what 1 reveled and other dont, and otherwise.
-
-%Here we can write about MOTIVATION EXAMPLES.

### 2021-06-22 conclusionfutureworks.tex
implications + spell checker
additional pass on the conclusions sections

--- 2021-02-17 conclusionfutureworks.tex
@@
-\section{conclusion and future work}
+\section{Conclusions}
 
-Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities.
-Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including \blls.
-But the impact of static analysis on these mining approaches is unexplored currently.
-The use of static analysis techniques, like taint analysis algorithms, to detect malicious behaviours, seems promising and can leverage sandboxes accuracy.
-However, many authors argue in favor of dynamic analysis for  mining sandboxes, highlight limitations at static analysis at this task, neglecting the complement that could be obtained with it.
-To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.
+In this paper we reported the
+results of two empirical studies that explore
+techniques for Android malware identification.
+The first study is a non-exact replication of a
+previous research work~\cite{DBLP:conf/wcre/BaoLL18},
+which investigates the Android mining sandbox
+approach for malware identification. There,
+Bao et al. report that more than 70\% of
+the malwares in their dataset can be
+detected by the sandboxes built from the
+execution of five test case generation
+tools (such as Monkey and DroidMate). Our replication
+study revealed that this performance is only
+achieved if we enable a static
+analysis component from DroidFax that was supposed to only
+instrument the Android \texttt{apk} files,
+though that independently contributes to
+building the sandboxes statically. As such,
+the use of DroidFax leads to an
+overestimation of the performance of the
+mining sandbox approach supported by dynamic analysis.
+Indeed, the execution of DroidFax alone enabled
+us to generate a sandbox that can
+identify 43.75\% of the malwares from 
+their dataset.
 
-In this paper, we performed two studies.
-In the first we conducted a non-exact replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times.
-Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis.
-For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment.
-The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms.
-Enabling the Droidfax, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid).
-We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated.
-In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.
-
-As future work, we plan to investigate other promising tools to enhance our data from previous executions.
-We will use the benchmark to test tools like Sapienz (a search-based test generation tool)~\cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}.
-And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
-Also, we will execute each of the tools used in this experiment without the benchmark.
-And, we will compare these results with this experiment's results.
-This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.
+In the second study we investigated
+a new approach based on taint analysis
+for malware identification, which
+leads to promising results. First,
+the taint based static analysis approach
+detected 60.42\% of the
+malwares in the dataset. When combining
+taint analysis with the
+mining sandbox approach, we were
+able to identify 82.29\% of the
+malwares in the dataset. These results
+have implications for both researchers and
+practitioners. First, we review the literature
+showing, for the first time, empirical evidence
+that the mining sandbox approach benefits
+from using both dynamic and static analysis. Second,
+practitioners can improve malware identification using
+a combination of 
+the mining sandbox approach with taint analysis.
+Nonetheless, both the mining sandbox approach and
+taint analysis present limitations. In particular,
+we are not able to identify a malware that
+uses the same set of calls to sensitive APIs of the
+benign version of an app, using
+the mining sandbox approach. Similarly, we are not
+able to identify a malware that presents the same
+paths from sources to sinks of the corresponding benign version of
+an app, using the taint analysis approach. 
+To mitigate these limitations, we envision the use of other approaches---such as machine learning
+algorithms to classify changes in non-code assets (e.g., Android
+manifest files) and symbolic execution to differentiate
+malicious calls or source-sink paths.

### 2021-06-22 implications.tex
minor fix

\section{Implications}\label{sec:implications}

The results discussed so far bring evidence
that the \blls study overestimated the
performance of the dynamic analysis tools in
malware identification using the mining sandboxes.
This finding has implications for both
researchers and practitioners. First,
we revisit the literature showing that
DroidFax alone is also effective for mining
sandboxes, being able to identify 43.75\%
of the malwares in our dataset. Moreover,
DroidFax identifies malwares that
none of the generated sandboxes
were able to find, increasing the
performance of the sandbox in at most $51.79\%$ (in the
case of Humanoid).

Table~\ref{tab:fs} in the previous section summarizes this finding: when
executing the mining sandbox approach without the
support of DroidFax static analysis, Humanoid's sandbox
could identify only 27 malwares ($28.12\%$ of the
malwares in our dataset).
Conversely, the DroidBot sandbox achieved the best performance in
terms of the number of detected malware without the DroidFax support for static analysis,
being able to identify $63.54\%$ of the malwares.
The message
here is that researchers and practitioners should
explore the use of DroidFax (or a similar tool) in conjunction 
with dynamic analysis techniques for mining sandboxes---
reviewing the findings of the \blls~\cite{DBLP:conf/wcre/BaoLL18}
and enriching the discussion about
the limitations of static analysis for
mining sandboxes~\cite{DBLP:conf/icse/JamrozikSZ16}.

In the second study we used FlowDroid
to explore a novel approach for malware identification,
which aims to compare the source-sink paths of two
versions of an app (one known to
be secure and another that might
have been repackage or that might have
an injected malicious behavior).
Contrasting with the static
analysis limitations discussed in~\cite{DBLP:conf/icse/JamrozikSZ16},
our findings indicate that
this approach is also effective for malware
identification. Indeed, our taint
analysis approach using FlowDroid
detects several malwares
that none of the sandboxes generated
with the dynamic analysis tools (plus
the DroidFax static analysis component)
could identify (see Table~\ref{tab:taint}). These
result has also implications
for both academia and industry. First,
this it reinforces the benefits
of integrating both static and
dynamic analysis for malware identification.
Second, this finding suggests that
practitioners can benefit from using
an integrated approach that
combines the mining sandbox approach
with taint analysis for malware
identification.

\begin{table}[ht]
\centering
\begin{tabular}{lccc}\toprule
 Test Generation & FlowDroid & Total & \%\\
 Tool & Increase  &  & \\ \midrule
 DroidBot & 6 & 79 & 82.29\\
 Monkey & 7 &  78 & 81.25 \\
 DroidMate & 7 & 75 & 78.12  \\
 Humanoid & 16 & 72 & 75.00 \\
 Joker & 25 & 67 & 69.79  \\\midrule

\end{tabular} 
\caption{Malwares detected in 96 pair (B/M) increased by the taint analysis approach}
\label{tab:taint}
\end{table}

% research community

% practitioners

%%here we also have to write about the intersection between droidfax and tainted analysis now, and about what 1 reveled and other dont, and otherwise.

%Here we can write about MOTIVATION EXAMPLES.

### 2021-06-22 results.tex
logistic regression for the first study

@@
 detected using the sandboxes generated after running the test case tools with the support of the
-DroidFax static analysis algorithms. Besides that, in the first execution (WS), none of the
+DroidFax static analysis algorithms. We also investigate if the use
+of the DroidFax static analysis component is statistically significant to identify
+malwares in our experiment. To this end, we build a logistic regression model
+in the form $Malware \sim Tool + StaticAnalysis + Repetition$. Table~\ref{tab:log-reg1}
+shows the results of the logistic regression analysis, highlighting the
+Humanoid has a negative and significant impact on malware identification and
+the use of DroidFax static analysis has a positive and significant
+impact on malware identification.
+
+\begin{table}[ht]
+  \centering
+     \caption{Results of the Logistic Regression} 
+       \begin{small}
+     \begin{tabular}{lrlc}
+   \toprule
+  & \emph{Estimate} & \emph{p-value} & \emph{C.I.} \\ 
+   \midrule
+   Tool [DroidBot] & 0.1034 & 0.4718 & (-0.133$, $0.340) \\ 
+   Tool [DroidMate] & -0.0561 & 0.6955 & (-0.292$, $0.180) \\ 
+   Tool [Humanoid] & -0.8910  & 0.0000 $^{***}$ & (-1.131$, $-0.651) \\ 
+   Tool [Monkey] & -0.0110 & 0.9390 &  (-0.247$, $0.225)\\ 
+   DroidFax static analysis & 0.8867 & 0.0000 $^{***}$ & (0.743$, $1.031)\\ 
+   Repetition & -0.0171 & 0.7487 & (-0.105$, $0.071) \\ \midrule
+   AIC            & 3001.07     \\
+   Num. obs.      & 2304        \\
+   \bottomrule
+   \multicolumn{4}{l}{\scriptsize{$^{***}$ \emph{p-value} $<0.001$}}
+     \end{tabular}
+        \end{small}
+
+    \label{tab:log-reg1} 
+\end{table}
+
+Besides that, in the first execution (WS), none of the
 resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to

### 2021-06-22 setup.tex
logistic regression for the first study

@@
 the benign and malign versions of the apps, during
-the execution of the tools. We then use descriptive statistics
+the execution of the tools. In the end, we generate
+a set of observations, where each observation
+contains the tool name, the number of the repetition (in the
+range [1..3]), a boolean value reporting the use of the
+DroidFax static analysis component, and a boolean value indicating
+whether or not the malware has been identified. We use descriptive statistics
 and plots to compare the performance of the tools and
-answer RQ1 and RQ2.
+answer RQ1 and RQ2. We also use \emph{Logistic Regression} to understand
+the relevance of the features (tool, repetition, DroidFax static analysis
+component) to predict the malware identification.
 

### 2021-06-23 results.tex
logistic regressions

@@
 In this section we detail the findings of our study. We present the results of the first and
-second studies in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}, respectively. In Section~\ref{sec:discussion} we summarize the
+second studies in Section~\ref{sec:res-fs} and Section~\ref{sec:res-ss}, respectively. In Section~\ref{sec:implications} we summarize the
 implications of our study.
@@
 detected using the sandboxes generated after running the test case tools with the support of the
-DroidFax static analysis algorithms. We also investigate if the use
-of the DroidFax static analysis component is statistically significant to identify
-malwares in our experiment. To this end, we build a logistic regression model
+DroidFax static analysis algorithms. {\color{red}We also investigate if the use
+  of the DroidFax static analysis component leads to statistically significant benefit
+  on malware identification. To this end, we build a logistic regression model
 in the form $Malware \sim Tool + StaticAnalysis + Repetition$. Table~\ref{tab:log-reg1}
-shows the results of the logistic regression analysis, highlighting the
-Humanoid has a negative and significant impact on malware identification and
-the use of DroidFax static analysis has a positive and significant
-impact on malware identification.
+shows the results of the logistic regression analysis, highlighting that
+(a) Humanoid has a negative, though significant impact on malware identification; and
+(b) the use of DroidFax static analysis has a positive and significant
+impact on malware identification.}
 
@@
   \centering
-     \caption{Results of the Logistic Regression} 
+     \caption{Results of the Logistic Regression (first study)} 
        \begin{small}
@@
         \end{small}
-
     \label{tab:log-reg1} 
@@
 In what follows we dissect a few examples of malwares
-that at least one dynamic analysis tool was able to
-identify using the mining sandbox approach. After that,
-we present the characteristics of a malware that none of the tools
+that at least one of the resulting  was able to
+identify. After that,
+we present the characteristics of a malware that none of the sandboxes
 was able to detect. Our goal here is to provide
@@
 adding permissions to receive and send SMS messages
-(Listing~\ref{lst:androidManifest}). With these permissions, malicious apps may get money
+(Listing~\ref{lst:androidManifest}). Adding these permissions, a malicious app may get money
 fraudulently by sending messages without user confirmation, for instance.
+The pair \texttt{L:M} indicates
+a code segment that appears in line \texttt{L} of the malign (\texttt{M})
+version of an app.
 
@@
 The malicious version of the app \texttt{com.happymaau.MathRef} also changes
-the manifest file to require additional permissions as well as change
+the Manifest file to require additional permissions as well as change
 the behavior of the app (with malicious code). All sandboxes were able to
@@
 this observation, we envision integrating a different approach that reasons
-about modifications to the Android manifest file and that might complement the mining sandbox
+about modifications to the Android Manifest file and that might complement the mining sandbox
 approach into the task for detecting malwares; since the mining
@@
 and Humanoid sandboxes computed in the second execution (without the DroidFax static analysis
-algorithms). This result shows that static analysis algorithms are promising to complement mining
-sandboxes, demystifying previous claims in the literature.
+algorithms). This result shows that static analysis algorithms are promising to complement
+the mining sandbox approach.
 
@@
 static analysis algorithms. More interesting, from those $67$
-malicious apps identified, $33$ pairs had been found by
-both tools (FlowDroid and DroidFax), even though they follow
+malicious apps identified, $33$ malwares had been found by
+both FlowDroid and DroidFax, even though they follow
 a completely different static analysis approach. Furthermore,
@@
 apps that had not been detected by DroidFax (while DroidFax detected $9$
-malicious apps that had not been detected by FlowDroid).
+malicious apps that had not been detected by FlowDroid). {\color{red}The results
+of a logistic regression analysis, considering the
+model $Malware \sim Tool$, where Malware is a response
+variable indicating if the malware has been detected or not and
+Tool is either FlowDroid or the sandbox DroidFax
+static analysis component generates, reveals the existence
+of a significant difference between
+the performance of both tools (see Table~\ref{tab:log-reg2}).}
+
+\begin{table}[ht]
+  \centering
+     \caption{Results of the Logistic Regression (second study)} 
+       \begin{small}
+     \begin{tabular}{lrlc}
+   \toprule
+  & \emph{Estimate} & \emph{p-value} & \emph{C.I.} \\ 
+   \midrule
+   Tool [FlowDroid] & 0.4229 & 0.0428 $^{**}$ & (0.080$, $0.766) \\
+   Tool [DroidFax static analysis component] & -1.2730 & 0.0000 $^{***}$ & (-1.560$, $-0.986) \\ \midrule
+   AIC            & 334.61     \\
+   Num. obs.      & 288        \\
+   \bottomrule
+   \multicolumn{4}{l}{\scriptsize{$^{***}$ \emph{p-value} $<0.001$; $^{***}$ \emph{p-value} $<0.05$}}
+     \end{tabular}
+        \end{small}
+
+    \label{tab:log-reg2} 
+\end{table}
 

### 2021-06-23 setup.tex
logistic regressions

@@
 and plots to compare the performance of the tools and
-answer RQ1 and RQ2. We also use \emph{Logistic Regression} to understand
-the relevance of the features (tool, repetition, DroidFax static analysis
-component) to predict the malware identification.
+answer RQ1 and RQ2. We also use \emph{Logistic Regression}~\cite[Chapter~4]{statistical-learning}
+to understand the statistical relevance and
+the contribution of each feature (tool, repetition, DroidFax static analysis
+component) to malware identification.
 
@@
 and plots to compare the performance of the taint analysis and
-mining sandbox approaches.
+mining sandbox approaches. We also use \emph{Logistic Regression}~\cite[Chapter~4]{statistical-learning}
+to better understand the statistical
+significance of the benefits of using FlowDroid
+(in comparison to the DroidFax static analysis
+component only).

### 2021-06-24 background.tex
update introduction and background

--- 2021-06-14 background.tex
@@
 
-A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
+%\kn{This section starts abrupt.
+We should have a line that says what concepts we introduce on a high level.
+Also, I feel "sandbox" itself should be one of the backgrounds and have a textbf after the introductory line.}
+
+In this background session, we present information that is important to understand the remainder of this paper. As a first step, we introduce
+Sandbox, its concept, and some sandbox security issues.
+After, we introduce Android Sandbox Mining technique, and how this approach can deal with malware detection at Android apps.
+Lastly, we present some concepts about Taint analysis.
+
+\textbf{A Sandbox} is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
 It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}.

### 2021-06-24 setup.tex
another pass in the threats to validity section

@@
 
-\item What is the impact of the DroidFax static analysis algorithms on the results of the BLL-Study?
+\item What is the impact of the DroidFax static analysis algorithms on the results of the \blls?
   We estimate the impact in terms of the number of detected malwares.
@@
 the contribution of each feature (tool, repetition, DroidFax static analysis
-component) to malware identification.
+component) to malware identification. Our hypothesis here is that
+the DroidFax static analysis component has a positive
+effect on the performance of the sandboxes to identify malwares.
 
@@
 (in comparison to the DroidFax static analysis
-component only).
+component only). Our hypothesis here is that
+FlowDroid outperforms, in terms of the number of
+detected malware, the sandbox generated
+by the DroidFax static analysis component.

### 2021-06-24 threats.tex
another pass in the threats to validity section

--- 2021-02-16 threats.tex
@@
 
-Due to the randomization behavior presented by each chosen tool, we should not validate the results of this experiment without considering the presence of random events in the execution.
-To mitigate this, we have used a configuration of the benchmark DroidXP tool that runs multiple times each test and computes the average result from those executions.
-So, the comparison between the results of this experiment and the experiment presented by Bao et al.
-could be more precise.
-Beyond that, we tested only 96 of the original 102 pairs of apps in this experiment because the benchmark could not execute those six pairs of apps due to crashes in the Android emulator.
-This difference threatens the validity of the comparison between the Bao et al.'s experiment and ours.
+As any empirical work, this work also has
+limitations and threats to its validity. We
+organize this section using the taxonomy
+of Wohlin et al.~\cite[Chapter 8]{10.5555/2349018}.
+
+\textbf{Conclusion Validity} is concerned with
+the issues that might compromise the
+correct conclusion about the causal relation
+between the treatment and the outputs of an
+experiment. The use of inadequate statistical
+methods and low statistical significance
+are examples of threats to the conclusion validity.
+Besides using descriptive statistics and
+plots, we also leverage
+binomial logistic regression to support our conclusions
+in our two empirical studies. Indeed, the results of our logistic
+regression analysis give evidence about the existence
+of a true pattern in the data, indicating that the DroidFax
+static analysis component increases the performance of the sandboxes
+we built from the execution of the dynamic
+analysis tools (first study) and that FlowDroid outperforms
+the DroidFax static analysis component in the
+task of identifying malwares (second study).
+
+\textbf{Internal Validity} relates to external factors that might
+impact the independent variables without the researchers' 
+knowledge. Our two empirical studies are \emph{technology-oriented}~\cite{10.5555/2349018,expruna},
+which are not subject to learning effect threats. Nonetheless,
+due to the random behavior of the test case generation tools,
+we should not validate the results of this experiment without considering the presence of
+random events in the execution. To mitigate this threat, we have used a configuration of
+DroidXP that runs multiple times each tool and computes the average result
+from those executions. So, we could adequately compare the results of our experiment with
+the results of the \blls. Beyond that,
+we tested only 96 of the original 102 pairs of apps in this experiment because the we
+could not execute those six pairs of apps due to crashes in the Android emulator.
+However, our goal here is not to conduct an exact replication of the previous work,
+but actually to better understand how static analysis supports and complements
+the mining sandbox approach for malware identification.
+
+\textbf{Construct Validity} concerns possible issues that might
+prevent a researcher to draw a conclusion from the experimental
+results. The design of our first study involves one treatment
+(a two-level factor indicating the use or not of the
+DroidFax static analysis component) and three independent
+variables: {\bf app id} (96 level factor), the test
+case generation tool (4-level factor, including DroidBot,
+DroidMate, Monkey, and Humanoid), and the 3-level factor repetition
+(we executed every tool three times for all apps, with and without
+the DroidFax static analysis component). The dependent variable
+indicates if a malware has been identified by the sandbox
+of a given test case generation tool built with (or without) the
+DroidFax static analysis component (in a particular repetition). This
+design leads to a total of 2304 observations, which is in conformance with the recommendations
+of Arcuri and Briand~\cite{arcuri:icse11} for this kind of experiment.
+Our second study presents a more straightforward design, comprising a two
+factor treatment (FlowDroid x the DroidFax static analysis) and   
+the same set of 96 apps of the first study. The dependent variable
+indicates if a malware has been identified by FlowDroid
+or by the sandbox the DroidFax static analysis component generates. This
+design leads to a smaller number of runs,
+but we still believe that it is sufficient to draw our conclusions
+(as the results of the logistic regression indicate).
+
+\textbf{External Validity} concerns whether or not the
+researchers can generalize the results for different scenarios.
+Our study shares some of the threats the
+\blls had presented. In particular, here we used the same set of pairs of apps from a \emph{piggy-backed} dataset
+released by Li et al.~\cite{li2017understanding}. That is, using this dataset, we could not
+cover all categories of Android malware. Besides that, we only used a small number of four test
+case generation tools in this study. To mitigate these threats and enrich
+the generalization of our research, we make available DroidXP, which does allow future
+experiments to evaluate other test case generation tools in different malware
+datasets.

### 2021-06-24 introduction.tex

@@
 Almost two-thirds of the world use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}.
-Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}\kn{Can we here say by how much?}.
+Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased.
+Malware samples grow from just three families and 100 samples in 2010 to more than hundred families with thousands of samples in 2013~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}%\kn{Can we here say by how much?}
+.
 Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably, to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms either to identify privacy leaks or to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
 
-Another perspective to the solving the same problem are approaches that rely on the use of dynamic analysis to mine Android sandboxes~\cite{DBLP:conf/icse/JamrozikSZ16}.
-With dynamic approaches, during an exploratory phase, one leverages an automatic test case generator tool that runs a benign version of an Android app and collects the set of calls made to sensitive APIs\kn{Is this the case for just Jamrozik's work or all of dynamic approaches.
-It is not clear}.
+Another perspective to the solving the same problem are approaches that rely on the use of dynamic analysis to mine Android sandboxes.
+Jamrozik et al.
+proposed BOXMATE tool~\cite{DBLP:conf/icse/JamrozikSZ16}, which with dynamic approaches, during an exploratory phase, one leverages an automatic test case generator tool that runs a benign version of an Android app and collects the set of calls made to sensitive APIs
+%\kn{Is this the case for just Jamrozik's work or all of dynamic approaches. It is not clear}
+.
 This set of calls comprises a sandbox infrastructure.
 The sandbox might then monitor any call to sensitive APIs while the app is running, blocking calls that have not been identified during the exploratory phase---thereby protecting Android users from additional malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
-Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis---mostly because of the overapproximation problem: ``static analysis often assume that more behaviors are possible than actually would be''~\cite{DBLP:conf/icse/JamrozikSZ16}.
+Jamrozik et al.
+argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis---mostly because of the overapproximation problem: ``static analysis often assume that more behaviors are possible than actually would be''~\cite{DBLP:conf/icse/JamrozikSZ16}.
 In addition, code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features} of programming languages are often used to introduce malicious behavior.
@@
 
-The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes\kn{The use of word same here makes me wonder if readers could be confused.
+The same lack of understanding about static and dynamic analysis complementing each other also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes%\kn{The use of word same here makes me wonder if readers could be confused.
 IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right?
-Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}.
-Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
+Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}
+.
+Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malicious version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
 Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which, as we discuss in this paper, leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work.
@@
   taint analysis, leads to a performance similar to the dynamic analysis
-  approach for diferenciating benign and malign versions of the same
+  approach for diferenciating benign and malicious versions of the same
   app (Section~\ref{sec:res-ss}).

### 2021-06-25 letter/responseLetter.tex
update responseLetter and TODO

@@
 
-{\color{blue}{\bf Answer.} Still pending.}
+{\color{blue}{\bf Answer.} You are right. To mitigate this issue, we created a new Section 5 (Implications), that present how our results can be useful for both researchers and practitioner.}
 
@@
 
-{\color{blue}{\bf Answer.} answer}
+{\color{blue}{\bf Answer.} Thanks for this observation.
+We reviewed the Section 6 (Threats) to detail better internal and external validity.
+Concerning construct validity, we also add it at this Section.}
 
@@
 
-{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We removed paragraph 3.}
+{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We reviewed Section 1 (Introduction) and removed paragraph 3.}
 
@@
 
-{\color{blue}{\bf Answer.} We explained better this sentence in the second paragraph of our
-  first section (Introduction). Thanks for raising this issue.}
+{\color{blue}{\bf Answer.} We explained better this sentence at introduction, paragraph 2. Thanks for raising this issue.}
 
@@
 
-{\color{blue}{\bf Answer.} We agree with that. To mitigate this issue, we introduced better DroidXP at introduction, paragraph 4.}
+{\color{blue}{\bf Answer.} We agree. To mitigate this issue, we introduced better DroidXP at introduction, paragraph 4.}
 
@@
 The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux.
-We insert a footnote with a link that better explain this term at page 4.\newline
+We insert a footnote with a link that better explain this term at page 5.\newline
 (https://en.wikipedia.org/wiki/Rooting(Android))
@@
 Example of sensitive behaviors: File accesses and network access.
-We improve the text with this definition at Section 2 (Background and related works), paragraph 6.}
+We improve the text with this definition at Section 2 (Background and related works), paragraph 7.}
 
@@
 
-{\color{blue}{\bf Answer.} We rephrase the text at Section 2 (Background and related works) paragraph 6, to better explain Humanoid test generation tool.}
+{\color{blue}{\bf Answer.} We rephrase the text at Section 2 (Background and related works) paragraph 7, to better explain Humanoid test generation tool.}
 
@@
 {\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly.
-We reviewed our Section 2 (Background and related works), to better explain taint analysis from paragraph 8.
+We reviewed our Section 2 (Background and related works), to better explain taint analysis from paragraph 9.
 We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”.
-To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows within source code Java.
+To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows.
 }
@@
 The section 3.1 presented our Benchmark tool DroidXP.
-We understand that the tool description was important for the paper since it was helpful for our first study conduction.
-DroidXP helped us to easily integrate the different test generation tools, and understand the effect of the static analysis component at each tool.
+The tool description was important for the paper since it was helpful for our first study conduction.
+DroidXP helped us to easily integrate different test generation tools, and understand the effect of the static analysis component at each tool.
 It was useful for us and can be very useful for other researchers.
@@
 
-{\color{blue}{\bf Answer.} We agree that the sentence was messy.
-We rephrased the sentence to clarify the first paragraph of Section 4.1.
-``Then we repeated the process, however this time we isolate the effect of the static analysis component of DroidFax.''}
+{\color{blue}{\bf Answer.} We reviewed the Section 3 (Study Settings) in full and so, we better explain the methodology. With this update, we removed this sentence.}
 
@@
 
-{\color{blue}{\bf Answer.} Sorry about these typos and grammar.
-We revised all the text, and corrected this problem like at page 9 (does not computed – does not compute), and page 10 (of our experimental – of our experiments), and some other mistakes that went unnoticed.}
+{\color{blue}{\bf Answer.} Sorry about these typos and grammar. We revised all the text, and corrected several mistakes that went unnoticed.}
 

### 2021-06-25 results.tex
update result and setup session

@@
   \item[Humanoid] showed the worst performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
-    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. This might suggest that test generation
-    tools that try to simulate the human behavior, such as Humanoid, are less effective to build Android sand boxes, in comparison
-    with techniques that rely on random testing (such as Monkey). In the first execution (Exec. (WS)),
+    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate.
+This might suggest that, since Humanoid learn how humans interact with apps, and use the learned model to guide test generation, at simulate environment, this method to generate test inputs are less effective to build Android sandbox, in comparison with techniques that rely on random testing (such as Monkey).
+In the first execution (Exec.
+(WS)),
     the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%). Humanoid was the most affected in the second
@@
     we do not have a baseline for comparison with the previous work.
+
+    an automated GUI test
+generator that is able to learn how humans interact with
+mobile apps and then use the learned model to guide test
+generation as a human tester.
 
@@
 The pair \texttt{L:M} indicates
-a code segment that appears in line \texttt{L} of the malign (\texttt{M})
+a code segment that appears in line \texttt{L} of the malicious (\texttt{M})
 version of an app.
@@
       \texttt{B} stands for
-      the benign version, while \texttt{M} stands for the malign version.}, language=XML,
+      the benign version, while \texttt{M} stands for the malicious version.}, language=XML,
     basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]
@@
 
+\pgfplotsset{compat=1.9}% supress warning
+\begin{filecontents*}{result.csv}
+   App,Detected,Benign Source-Sinks,Malicious Source-Sinks,Execution Time (s)
+
+\end{filecontents*}
+
+%\begin{table}[ht]
+%    \centering
+%    \begin{tiny}
+%        \begin{tabular}{c|c|c|c|c}%
+%            \bfseries Pair App & \bfseries Detected & %\bfseries Source-sink (Benign) & \bfseries Source-sink %(Malicious) & \bfseries Execution Time (s)% specify %table head
+%            \csvreader[head to column %names]{result.csv}{}% use head of csv as column names
+%            {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvc%oliv&\csvcolv}% specify your coloumns here
+%        \end{tabular}
+%     \end{tiny}
+%        \caption{Malwares detected in 96 pair (B/M) by %the taint analysis approach}
+%        \label{tab:taintDetec}
+%\end{table}
+
 Finally, we highlight that FlowDroid was able to detect $4$ malwares among the $18$ malicious Android apps that had not

### 2021-06-25 setup.tex
update result and setup session

@@
 might be ineffective---due to \emph{overapproximation
-problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
+problem}~\cite{DBLP:conf/icse/JamrozikSZ16}.
 However, to the best of our knowledge,
@@
 Joker simulates a test tool that does not
-run the Android apps during an experiment execution.
+run the Android apps during an experiment execution, and your use revealed the performance of static analysis component of DroidFax.
 

### 2021-06-25 abstract-jss.tex
additional review on the abstract

@@
 %  \emph{Context.}
-The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+The popularization of the Android platform and the growing number of Android applications (apps) that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
 For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}.
-The mining sandbox approach consists in running fuzzing test tools into a benign version of the app.
+The mining sandbox approach consists in running dynamic analysis tools on a benign version of an Android app.
 This exploratory phase records all calls to sensitive APIs.
-Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the fuzzing tools again in a different version of the app.
+Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the dynamic analysis tools again in a different version of the app.
 During this second execution of the fuzzing tools, a warning of possible malicious behavior is raised whenever the new version of the app calls a sensitive API not recorded in the exploratory phase.
@@
 Particularly, existing reports present an accuracy of almost 70\% in the identification of malicious behavior using dynamic analysis tools to mine android sandboxes.
-However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static with a mining sandbox approach for identifying malicious behavior.
+However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static
+analysis with a mining sandbox approach for identifying malicious behavior.
 Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools tailored for mining Android sandboxes, in the task of identifying malicious behavior.
@@
 Differently from the original work, here we isolate the effect of an independent  static analysis component (DroidFax) they used to instrument the Android apps in their experiments.
-This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining Android sandbox approach previously used to identify malicious behavior.
+This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses tools positively---through the execution of specific static analysis algorithms DroidFax also implements.
+In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining sandbox approach previously used to identify malicious behavior.
 To this end, we executed the FlowDroid tool to mine the source-sink flows from benign/malign pairs of Android apps used in a previous research work.
@@
 Our study brings several findings.
-For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the \blls dataset, leading to an overestimation of the performance of the dynamic analysis tools.
-The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
+For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the \blls dataset, contributing substantially in the the performance of the dynamic analysis tools in the \blls.
+The results of the second study show that taint analysis is also practical to complement the mining sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}

### 2021-06-26 introduction.tex
additional pass into the introduction section

@@
 Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased.
-Malware samples grow from just three families and 100 samples in 2010 to more than hundred families with thousands of samples in 2013~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}%\kn{Can we here say by how much?}
-.
+In only three years, researchers reported a substantial increase in the population of Android malwares: from just three families and a hundred samples in 2010 to more than a hundred families with thousands of samples in 2013~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}.
 Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably, to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms either to identify privacy leaks or to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance.
 
-Another perspective to the solving the same problem are approaches that rely on the use of dynamic analysis to mine Android sandboxes.
-Jamrozik et al.
-proposed BOXMATE tool~\cite{DBLP:conf/icse/JamrozikSZ16}, which with dynamic approaches, during an exploratory phase, one leverages an automatic test case generator tool that runs a benign version of an Android app and collects the set of calls made to sensitive APIs
-%\kn{Is this the case for just Jamrozik's work or all of dynamic approaches. It is not clear}
+Another alternative for protecting users from Android malicious behavior consists in the use of dynamic analysis to mine Android sandboxes~\cite{DBLP:conf/icse/JamrozikSZ16}.
+The mine sandbox approach starts with an
+exploratory phase, in which a practitioner takes advantage of automatic test case generator tools that explores an Android application while recording the set of sensitive APIs the app calls. 
 .
-This set of calls comprises a sandbox infrastructure.
-The sandbox might then monitor any call to sensitive APIs while the app is running, blocking calls that have not been identified during the exploratory phase---thereby protecting Android users from additional malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
+This set of senstivie calls comprises a sandbox infrastructure.
+After the exploratory phase, the sandbox might then monitor any call to sensitive APIs while a user is running the app, blocking the calls that have not been identified during the exploratory phase---thereby protecting Android users from additional malicious behavior~\cite{DBLP:conf/icse/JamrozikSZ16}.
 Jamrozik et al.
@@
 
-The same lack of understanding about static and dynamic analysis complementing each other also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes%\kn{The use of word same here makes me wonder if readers could be confused.
+The lack of understanding about static and dynamic analysis complementing each other also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that explores the performance of dynamic analysis for identifying malicious behavior using the mining sandbox approach.
+%\kn{The use of word same here makes me wonder if readers could be confused.
 IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right?
 Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}
-.
 Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malicious version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
-Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which, as we discuss in this paper, leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work.
-Moreover, since DroidFax is an independent component (it is not part of the dynamic analysis tools explored in the \blls), a practitioner might run a dynamic analysis tool alone that is likely to present a smaller capacity to identify malware.
+Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps).
+As we discuss in this paper, this DroidFax static analysis component leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work.
+{\color{red}In the security domain, overestimating the performance of a technique for malware identification brings serious risks, and we show here that DroidFax improves significantly the performance of the dynamic analysis tools for mining sandboxes.}
 
@@
 conduct the non-exact replication of that study. Here we extend
-our previous work with a slight customization of DroidXP, which allowed us
-to reproduce the \blls by means of a serie of experiments
+our previous work with a couple of customizations of DroidXP, which allowed us
+to reproduce the \blls by means of a serie of new experiments
 that reveal the actual performance of the
@@
 \emph{sink} statements computed using two executions of the
-FlowDroid infrastructure: one execution that analyses
+FlowDroid infrastructure~\cite{arzt:pldi-2014}: one execution that analyses
 a benign version of an Android app and one execution that
@@
   scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
-  and a benchmark for reproducing and extending our study. The repository for DroidXP is available
+  and tooling for reproducing and extending our study. The repository for DroidXP is available
 at GitHub\footnote{https://github.com/droidxp/benchmark}.

### 2021-06-26 results.tex
update result and setup session
additional pass into the introduction section

@@
     we do not have a baseline for comparison with the previous work.
-
-    an automated GUI test
-generator that is able to learn how humans interact with
-mobile apps and then use the learned model to guide test
-generation as a human tester.
 
@@
 Even though the time to execute the FlowDroid analysis depends on the size
-of the app, the longest run took only 437 seconds.
+of the app, the longest run took only 437 seconds. Figure~\ref{fig:histogram}
+summarizes the FlowDroid execution time---which most often
+concludes the execution in less than 50 seconds (32.11 seconds
+on average, with a standard deviation of 70.04).
 
-\pgfplotsset{compat=1.9}% supress warning
-\begin{filecontents*}{result.csv}
-   App,Detected,Benign Source-Sinks,Malicious Source-Sinks,Execution Time (s)
-
-\end{filecontents*}
+\begin{figure}
+  \centering{
+  \includegraphics[scale=0.5]{images/histogram.pdf}}
+  \caption{Histogram summarizing the time to execute FlowDroid}
+  \label{fig:histogram}
+\end{figure}
 

### 2021-06-28 background.tex
first review on the background section

@@
 
-In this background session, we present information that is important to understand the remainder of this paper. As a first step, we introduce
-Sandbox, its concept, and some sandbox security issues.
-After, we introduce Android Sandbox Mining technique, and how this approach can deal with malware detection at Android apps.
-Lastly, we present some concepts about Taint analysis.
+In this section we present information that is necessary to understand the remainder of this paper.
+First, we introduce some background information about the use of \emph{sandbox} to protect access
+to sensitive resources. After, we review the mining sandbox approach for detecting malicious
+behavior in Android apps. Finally, we present some background information about
+taint analysis.
 
@@
 It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}.
-This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
+This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
 A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software.
-Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have,
+Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have,
 working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task.
@@
 Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps.
-Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
-For security reasons, Google Play list each app with the requested permission.
+Therefore, every month many Android apps are removed from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
+For security reasons, Google Play lists each app with the requested permission.
 However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}.
-Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.~\cite{DBLP:conf/soups/FeltHEHCW12}
-%\kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}
+Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product~\cite{DBLP:conf/soups/FeltHEHCW12}.
 
-Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
-%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
-, calling Java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls.
-Another approach to rooting\footnote{https://en.wikipedia.org/wiki/Rooting(Android)} is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access.
+Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, for instance by obfuscating calls to native code that is allowed to make system calls~\cite{DBLP:journals/corr/abs-2002-04540} or conducting side attacks to make system calls from a benign app.
 
-%It also guarantees an unbiased testing environment, ensuring the same pre-configured beginning status of the environment \kn{I dont understand what a pre-configured beginning status is}.
-
-\textbf{The Android Mining Sandbox} concept is a sandboxing technique that consists of mining rules from an Android app, and use these rules to ensure system security.
-The sandboxing technique comprises of two steps.
+\textbf{The Android Mining Sandbox} approach is a sandboxing technique that consists of mining rules from an Android app, and use these rules to ensure system security.
+The mining sandbox approach comprises of two steps.
 First, rules are mined and will compose the sandbox,

### 2021-06-28 setup.tex
first review on the background section

@@
 using the same dataset of 96 pairs of Android apps, though 
-executing only a fake test case generator tool (named Joker)
+also executing a fake test case generator tool (named Joker)
 {\bf without} the \texttt{--disable-static-analysis} option.
 Joker simulates a test tool that does not
-run the Android apps during an experiment execution, and your use revealed the performance of static analysis component of DroidFax.
+run the Android apps during an experiment execution, and its usage
+allow us to estimate the actual performance of the DroidFax static analysis component.
 

### 2021-06-29 background.tex
Review partially the background section

@@
 
-In this section we present information that is necessary to understand the remainder of this paper.
-First, we introduce some background information about the use of \emph{sandbox} to protect access
-to sensitive resources. After, we review the mining sandbox approach for detecting malicious
-behavior in Android apps. Finally, we present some background information about
-taint analysis.
+In this section, we present information that is necessary to understand the remainder of this paper.
+First, we introduce some background information about the use of \emph{sandboxes} to protect access to sensitive resources.
+After, we review the mining sandbox approach for detecting malicious behavior in Android apps.
+Finally, we present some background information about taint analysis.
 
@@
 This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
-A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software.
-Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have,
-working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task.
+A sandbox environment should be able to shield the host machine or operating system from any damages caused by third-party software.
+Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task.
 This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health.
@@
 
-Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps.
-Therefore, every month many Android apps are removed from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
-For security reasons, Google Play lists each app with the requested permission.
-However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}.
-Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product~\cite{DBLP:conf/soups/FeltHEHCW12}.
+Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the apps' publishment process.
+Therefore, every month administrators remove several Android apps from the Play Store because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}.
+For security reasons, Google Play lists each app with its requested permissions.
+However, many malicious apps usually ask for more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}.
+Those permissions are presented to the user during a new app's installation, since Android version 6, but most users are careless since they are only interested in the end product~\cite{DBLP:conf/soups/FeltHEHCW12}.
 
@@
 
-\textbf{The Android Mining Sandbox} approach is a sandboxing technique that consists of mining rules from an Android app, and use these rules to ensure system security.
-The mining sandbox approach comprises of two steps.
-First, rules are mined and will compose the sandbox,
-%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
-through test generator tools, that identifies sensitive Android API, called during their execution. 
-%\kn{This sentence seems to miss something "what" happens through test generation tools.}
-These tools investigate program behavior through resource accesses realized by theses APIs.
-The second stage ensures that resources not accessed, or accessed differently than first stage, are not accessible by the apps.
-So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.
+\textbf{The Android Mining Sandbox} approach is a sandboxing technique that uses test generator tools to explore an Android app's dynamic behavior to define what sensitive resources are necessary to build the sandbox.
+And, we use this sandbox to ensure the app execution's security by restricting the resources that are allowed to use.
+In a first, exploratory phase, a practitioner uses test generator tools to execute a benign version of an app and record the set of sensitive APIs the app calls.
+Secondly, we define the sandbox based on the sensitive APIs mined in the first phase.
+This sandbox will ensure that malicious apps require only sensitive APIs, and if not, it will prohibit the malicious app's access.
 
@@
 For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.
-Ammons et al~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning
-approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
+Ammons et al.~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
 

### 2021-06-29 background.tex
Review background section

@@
 %\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} 
-The main purpose of test generation tool is to find bugs.
+The main purpose of a test generation tool is to find bugs.
 However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes.
 Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
-Li e tal.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
-In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis, and showed that Droidbot is able to trigger an amount of sensitive behaviors higher than Monkey.
-Sensitive behaviors at Android context occurs when an Android app functionality can result in accessing or leaking of Android users sensitive data.
-Example of sensitive behaviors are file accesses and network access.
+Li et al.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
+In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis and showed that Droidbot can trigger several sensitive behaviors more than Monkey.
+Sensitive behaviors in the Android context occurs when an Android app functionality can result in accessing or leaking of Android users' sensitive data.
+Examples of sensitive behaviors are file access and network access.
 Another test generator tool for Android is called Humanoid \cite{DBLP:conf/kbse/LiY0C19}, which is a Droidbot evolution.
 It's also a GUI test generation that learning how humans interact with Android apps.
-In contrary to random input generators, Humanoid use the learned model to generate human-like test inputs, and prioritize the possible interactions on a GUI, according their importance.
+In contrary to random input generators, Humanoid uses the learned model to generate human-like test inputs, and prioritize the possible interactions on a GUI, according to their importance.
 
@@
 
-L Bao et al~.\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
+L Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
 This study indicates that these tools were efficient in identifying at most $70$\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect $75.49$\% of malicious behavior explored ($77$ among $102$).
-However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used an instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps
 
 \textbf{Taint analysis} is a special type of static or dynamic analysis that purpose is to track data flows within programs~\cite{DBLP:conf/sigsoft/PauckBW18}.
-It can identify sensitive information leakage detecting taint flow between ``source'' and ``sink''.
-In Android apps context, a data leak occurs when sensitive data, such as contact, or device ID, flows from a private source to public sinks, like the internet.
-Taint analysis can present possible malicious data flow to malware detection tools or even for a human check, that can decide if the ``source-sink" relationship is or is not an unwanted behavior.
-Thereby, taint analysis monitors sensitive source ``tainted" through the app by starting at a pre-defined point.
+It can identify sensitive information leakage by detecting taint flow between ``source'' and ``sink''.
+In the context of Android apps, a data leak occurs when sensitive data, such as contact, or device ID, flows from a private source to public sinks, like the internet.
+Taint analysis can present possible malicious data flow to malware detection tools or even for a human check, which can decide if the ``source-sink" relationship is or is not an unwanted behavior.
+Thereby, taint analysis monitors sensitive sources ``tainted" through the app by starting at a pre-defined point.
 
-In Android context, sources are the APIs in which apps access sensitive information, called sensitive APIs.
+In the Android context, sources are the APIs in which apps access sensitive information, called sensitive APIs.
 The analysis follows the data flow until it reaches a sink, like a method that sends SMS.
-Finally, it brings exact information about which data will be leaked and where~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}.
+Finally, it brings exact information about which data will be leaked~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}.
 The Android SDK provides APIs that allow apps to send private data to other apps on the same device, or remote devices.
@@
 Wei et al.~\cite{DBLP:conf/issta/HuangDMD15} propose a scalable taint analysis for Android apps that applies traditional taint analysis techniques with targeted optimizations specific to Android OS.
-Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity.
+Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves the precision of traditional approaches by including context and flow sensitivity.
 A significant issue with taint analysis is the cost of the tool itself hampering the performance.
 FastDroid~\cite{DBLP:journals/compsec/ZhangTD21} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis, called taint value graph (TVG).
-To improve the efficiency and precision, FastDroid focuses on exploring the propagation of taint values, rather than the traditional data flow analysis.
+To improve efficiency and precision, FastDroid focuses on exploring the propagation of taint values, rather than the traditional data flow analysis.
 FastDroid constructs taint value graphs (TVGs) exploring taint values, then it extracts a subset of potential taint flows (PTFs) from it.

### 2021-06-29 background.tex
final review of the background section

@@
 
-In this section, we present information that is necessary to understand the remainder of this paper.
-First, we introduce some background information about the use of \emph{sandboxes} to protect access to sensitive resources.
-After, we review the mining sandbox approach for detecting malicious behavior in Android apps.
-Finally, we present some background information about taint analysis.
+In this section, we introduce the concepts and terminology that are necessary to understand the remainder of this paper.
+First, Section~\ref{sec:sandbox} introduces some background information about the use of \emph{sandboxes} to protect invalid access to sensitive resources.
+After that, in Section~\ref{sec:android-sandbox} we review the mining sandbox approach for detecting malicious behavior in Android apps.
+Finally, Section~\ref{sec:taint} presents some background information about taint analysis.
 
-\textbf{A Sandbox} is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
-It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}.
-This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
-A sandbox environment should be able to shield the host machine or operating system from any damages caused by third-party software.
-Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task.
-This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health.
+\subsection{The Sandbox Approach for Protecting Resources}\label{sec:sandbox}
+
+A \emph{sandbox} is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
+Sandboxes enable testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}.
+This need might arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised~\cite{DBLP:journals/peerj-cs/MaassSCS16}.
+A sandbox environment must be able to shield the host machine or operating system from any damages caused by third-party software.
+Thus, a sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, working with the principle of \emph{least privilege}, giving permissions to users according to their needs, i.e., giving them no more power than needed to successfully perform their task.
+This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall reliability.
+
 Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.
-
 Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the apps' publishment process.
@@
 
-\textbf{The Android Mining Sandbox} approach is a sandboxing technique that uses test generator tools to explore an Android app's dynamic behavior to define what sensitive resources are necessary to build the sandbox.
-And, we use this sandbox to ensure the app execution's security by restricting the resources that are allowed to use.
-In a first, exploratory phase, a practitioner uses test generator tools to execute a benign version of an app and record the set of sensitive APIs the app calls.
-Secondly, we define the sandbox based on the sensitive APIs mined in the first phase.
-This sandbox will ensure that malicious apps require only sensitive APIs, and if not, it will prohibit the malicious app's access.
+\subsection{Mining Android Sandbox}
 
-Automatically mining software resources or components, to infer behavior is not new, and has been discussed before.
-For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.
-Ammons et al.~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data type.
+The mining Android sandbox approach~\cite{DBLP:conf/icse/JamrozikSZ16} relies on test generator tools to explore an Android app's dynamic behavior, and thus mine a set of sensitive resources the app needs.
+The sandbox uses this set of sensitive APIs to ensure the app execution's security by restricting the resources that are allowed to use.
+The mining sandbox approach works in two phases.
+In the first, named exploratory phase, a practitioner uses test generator tools to execute a benign version of an app and record the set of sensitive APIs the app calls.
+In the second phase, named execution, the sandbox constraints the app to access only the sensitive APIs mined in the first phase.
+Accordingly, the sandbox ensures that a malicious app could not call any sensitive API, besides those calls to APIs recorded in the first phase.
 
-%\kn{Please write one sentence here saying why test generation tools could solve the problem, and then list the related work. The term test generation comes out out nowhere.} 
-The main purpose of a test generation tool is to find bugs.
-However, it also can be used to explore program behavior, and thus assist in the task of building Sandboxes.
-Regarding test generating tools used for mining Sandboxes, Jamrozik et al ~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
-Li et al.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access by apps, following a model-based exploration strategy.
-In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis and showed that Droidbot can trigger several sensitive behaviors more than Monkey.
-Sensitive behaviors in the Android context occurs when an Android app functionality can result in accessing or leaking of Android users' sensitive data.
-Examples of sensitive behaviors are file access and network access.
-Another test generator tool for Android is called Humanoid \cite{DBLP:conf/kbse/LiY0C19}, which is a Droidbot evolution.
-It's also a GUI test generation that learning how humans interact with Android apps.
-In contrary to random input generators, Humanoid uses the learned model to generate human-like test inputs, and prioritize the possible interactions on a GUI, according to their importance.
+The idea of automatically mining software resources or components to infer behavior is not new, and has been discussed before.
+For instance, Whaley et al.~\cite{DBLP:conf/issta/WhaleyML02} combine dynamic and static analysis for API mining and so infer program behavior based on an usage example of Java classes.
+Ammons et al.~\cite{DBLP:conf/popl/AmmonsBL02} propose a machine learning approach, called specification mining, to discover temporal and data-dependence relationships that a program follows when interacting with an API or abstract data types.
 
-%~\kn{What is being compared with what.
-Is droidbot compared with monkey.
-If yes, then what is the proof  of concept example of using Droidbot?
-Something we have built.
-Or is the comparison between Droidbot and Monkey as an example of using droidbot?}.
+The main purpose of a test generator tool is to program crashes or bugs in general.
+Nonetheless, it is also possible to use test generator tools to explore program behavior (dynamic analysis), and thus assist in the task of building sandboxes.
+Regarding test generator tools used for mining Android sandboxes, Jamrozik et al~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+Li et al.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access from Android apps, following a model-based exploration strategy.
+In their work, the authors present a comparison between DroidBot and Monkey~\cite{Monkey} regarding malware analysis and show that DroidBot can trigger several sensitive calls more often than Monkey.
+Sensitive calls in the Android context occurs when an Android app functionality can result in accessing or leaking of Android users' sensitive data.
+Examples of sensitive calls access user location or network information.
+Humanoid is another test generator tool for Android~\cite{DBLP:conf/kbse/LiY0C19}---actually a DroidBot evolution.
+It is also a GUI test generator that learning how humans interact with Android apps.
+In contrary to random input generators, Humanoid uses a learned model to generate human-like test inputs, and prioritize the possible interactions on a GUI, according to their importance.
 
-L Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} had provided an important comparative study between five test generation tools that find malware by mining sandboxes techniques: DroidMate, Monkey, GUIRipper \cite{DBLP:conf/kbse/AmalfitanoFTCM12}, Puma \cite{DBLP:conf/mobisys/Hao0NHG14}, and Droidbot.
-This study indicates that these tools were efficient in identifying at most $70$\% of the malware in a specific dataset and also reports that after combining all test generator tools, it was possible to detect $75.49$\% of malicious behavior explored ($77$ among $102$).
-However, this study did not focus on the possible interference of static analysis in the final result, since this study used an instrumentation tool \cite{DBLP:conf/icsm/CaiR17a}, that also performs a static analysis of the apps
+Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} present a comparative study test generator tools to identify malicious behavior using the mining sandboxes approach.
+Their study indicates that the tools were efficient in identifying at most $70$\% of the malware in a specific dataset and also reports that after, combining all test generator tools, it was possible to detect $75.49$\% of malicious behavior explored ($77$ among $102$).
+However, this study did not focus on the possible interference of static analysis in the final result, since this study used DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument the apps, though, as we discuss in this paper, DroidFax also performs a static analysis of the apps whose results complement the dynamic analysis approach for mining sandboxes.
 
-\textbf{Taint analysis} is a special type of static or dynamic analysis that purpose is to track data flows within programs~\cite{DBLP:conf/sigsoft/PauckBW18}.
-It can identify sensitive information leakage by detecting taint flow between ``source'' and ``sink''.
-In the context of Android apps, a data leak occurs when sensitive data, such as contact, or device ID, flows from a private source to public sinks, like the internet.
+\subsection{Taint Analysis}\label{sec:taint}
+
+Taint analysis is a special type of static or dynamic analysis that aims to track data flows within programs~\cite{DBLP:conf/sigsoft/PauckBW18}.
+Typically, taint analysis is used to identify sensitive information leakage by detecting taint flow between ``sources'' and ``sinks''.
+In the context of Android apps, a data leak occurs when sensitive data, such as contact, or device ID, flows from a sensitive resource to a method that might \emph{sink} information to other peers, like sending a message.
 Taint analysis can present possible malicious data flow to malware detection tools or even for a human check, which can decide if the ``source-sink" relationship is or is not an unwanted behavior.
@@
 The analysis follows the data flow until it reaches a sink, like a method that sends SMS.
-Finally, it brings exact information about which data will be leaked~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}.
+It brings precise information about which data will be leaked~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}.
 The Android SDK provides APIs that allow apps to send private data to other apps on the same device, or remote devices.
@@
 Wei et al.~\cite{DBLP:conf/issta/HuangDMD15} propose a scalable taint analysis for Android apps that applies traditional taint analysis techniques with targeted optimizations specific to Android OS.
-Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves the precision of traditional approaches by including context and flow sensitivity.
+FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves the precision of traditional approaches by including context and flow sensitivity.
 A significant issue with taint analysis is the cost of the tool itself hampering the performance.
@@
 FastDroid improves the analysis process by performing analysis only on (PTFs).
+In this paper we investigate the use of taint analysis to identify malicious behavior, by mining the source an sink pairs from distinct versions of an app.

### 2021-06-29 introduction.tex
final revision

@@
 As we discuss in this paper, this DroidFax static analysis component leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work.
-{\color{red}In the security domain, overestimating the performance of a technique for malware identification brings serious risks, and we show here that DroidFax improves significantly the performance of the dynamic analysis tools for mining sandboxes.}
+In the security domain, overestimating the performance of a technique for malware identification brings serious risks, and we show here that DroidFax inflated significantly the performance of the dynamic analysis tools for mining sandboxes, as reported in the \blls.
 

### 2021-06-29 results.tex
final revision

@@
 detected using the sandboxes generated after running the test case tools with the support of the
-DroidFax static analysis algorithms. {\color{red}We also investigate if the use
-  of the DroidFax static analysis component leads to statistically significant benefit
+DroidFax static analysis algorithms. We also investigate if the use
+  of the DroidFax static analysis component leads to a statistically significant benefit
   on malware identification. To this end, we build a logistic regression model
@@
 (b) the use of DroidFax static analysis has a positive and significant
-impact on malware identification.}
+impact on malware identification.
 
@@
 apps that had not been detected by DroidFax (while DroidFax detected $9$
-malicious apps that had not been detected by FlowDroid). {\color{red}The results
+malicious apps that had not been detected by FlowDroid). The results
 of a logistic regression analysis, considering the
@@
 of a significant difference between
-the performance of both tools (see Table~\ref{tab:log-reg2}).}
+the performance of both tools (see Table~\ref{tab:log-reg2}).
 

### 2021-06-29 setup.tex
final revision

@@
 
-%\kn{This paragraph requires a motivation.
-The details of Boa's study must be described upfront.
-Something like "Boa et al.'s study performs .....
-Since their study also involved a static analysis component whose impact was not measured, we perform a non-exact replication to understand the impact static analysis may have had in the results...}
-
-\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis.
-a.k.a effect of taint analysis on sandboxes.
-But in the introduction we kind of use the general S-D interaction and this problem interchangeably.
-I have left a comment at the introduction.}
 Our research work aims to better understand

### 2021-06-29 letter/responseLetter.tex
review paper's title and part of the response letter

@@
 
-{\color{blue}{\bf Answer.} You are right. To mitigate this issue, we created a new Section 5 (Implications), that present how our results can be useful for both researchers and practitioner.}
+{\color{blue}{\bf Answer.} To mitigate this issue, we reviewed our Section 4 (Results) and created a new Section 5 (Implications), which present how our results can be useful for both researchers and practitioner.
+Thanks for this observation.}
 
@@
 
-{\color{blue}{\bf Answer.} Thanks for this observation.
-We reviewed the Section 6 (Threats) to detail better internal and external validity.
-Concerning construct validity, we also add it at this Section.}
+{\color{blue}{\bf Answer.} Thanks for this observation. We reviewed our Threats to Validity section according to
+  a \emph{threats to validity} taxonomy for this kind of study~\cite{10.5555/2349018}. The current version
+  of the paper includes specific sections addressing Conclusion Validity, Internal Validity, External
+Validity, and Construct Validity.}
 
@@
 {\color{blue}{\bf Answer.} Thanks for raising these questions. We reviewed the abstract
-  to better explain the relevance of the mining sandbox approach. Literature reports
-  show that the mining sandbox approach is effective  not only to prevent malicious
-  calls to sensitive APIs but also to classify a version of an app as a malware.}
+  to better explain the relevance of the mining sandbox approach. As a short answer,
+  literature reports show that the mining sandbox approach is effective  not only to prevent malicious
+  calls to sensitive APIs but also to classify a version of an Android application as a malware.}
 

### 2021-06-30 introduction.tex
Update introduction.tex
Remove Krishina comments.

@@
 The lack of understanding about static and dynamic analysis complementing each other also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that explores the performance of dynamic analysis for identifying malicious behavior using the mining sandbox approach.
-%\kn{The use of word same here makes me wonder if readers could be confused.
-IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right?
-Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}
 Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malicious version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
@@
 the setup of our replication study.
-
-%% In summary, our current study differs fromthe original work in three aspects:
-
-%% \begin{enumerate}[(a)]
-%%   \item We isolate the effect of the static analysis component of DroidFax.
-%%    \item We included a fake test
-%% case generation tool (named \joke).
-\joke simulates a test tool that does not execute Android apps during DroidXP execution, disregarding the effects of dynamic analysis, and computing the results with only static analysis DroidFax component.
-%% \item We extend the execution time and the number of executions of each test case generator tool for all apps
-%% in our dataset.
-
-%% \end{enumerate}
-%% where offers direct access to all source code, installation process, dependencies, and how to run.
-We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, and here we discuss the results of a broader investigation that also uses DroidXP to explain the performance of static and dynamic analysis approaches for mining sandboxes.
-Our goal is to understand how static analysis algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes.
-This work is an extension of SCAM 2020 paper, since that for our actual study, we had to adapt DroiXP to allow it to isolate the effects of static analysis component of DroidFax, and take into account this effect at our analysis.
-
-%% Our research work presents the results of two empirical studies that aim to
-%% address our research goal. In the
-%% first study, we conduct a replication of the \blls, as presented at {\color{red}SCAN 2020} conference~\cite{DBLP:conf/scam/CostaMCMVBC20}, though
 

### 2021-06-30 letter/responseLetter.tex
Update responseLetter.tex
Update Reviewer 3

@@
 
+\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
+analysis must often assume that additional behaviors are possible than actually would be.''
+Please explain
+
+\vspace{0.2cm}
+
+\item Please rephrase:
+``Those are kind of attack that usually tackled with the Android Mining Sandbox''
+``For instance, Whaley et al. [18] combine dynamic and static analysis for API mining and so extract interface from software components.''
+
+\vspace{0.2cm}
+
+\item Please rephrase:
+``From the same authors, another test generator tool for Android, described as Humanoid [23], is a DroidBot evolution and
+presents a proposal that can generate humans like tests inputs, using deep learning.''
+
+\vspace{0.2cm}
+
+\item Briefly explain the taint analysis
+``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''
+
+\vspace{0.2cm}
+
+\item Please explain:
+``FastDroid [28] mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.''
+
+\vspace{0.2cm}
+
+\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''
+
+\vspace{0.2cm}
+
+\item There are several other typos and grammatical errors.
+
+\vspace{0.2cm}
+
+{\color{blue}{\bf Answer.} Reviewer 3 suggested several improvements to the article.
+To mitigate the improvements pointed, we reviewed the current version of the paper to better clarify Section 1 (Introduction) and Section 3 (Study Settings).
+We also present more details on FastDroid and Taint Analysis in Section 2 (Background and related work), and we have revised the entire text, correcting several errors that have gone unnoticed.}
+
+\vspace{0.2cm}
+
 \item It is not clear how this paper can be considered an extension of the DroidXP paper presented in SCAM 2020.
@@
 
-{\color{blue}{\bf Answer.} In the introduction, we rephrase paragraphs 4 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
+{\color{blue}{\bf Answer.} In the Section 1 (Introduction) we rephrase paragraphs 4 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
 
@@
 
-\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
-analysis must often assume that additional behaviors are possible than actually would be.''
-Please explain
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} We explained better this sentence at introduction, paragraph 2. Thanks for raising this issue.}
-
-\vspace{0.2cm}
-
 \item ``We presented and evaluated DroidXP in a conference paper [11]''
@@
 
-{\color{blue}{\bf Answer.} We agree. To mitigate this issue, we introduced better DroidXP at introduction, paragraph 4.}
+{\color{blue}{\bf Answer.} We agree. To mitigate this issue, we introduced better DroidXP at Section 1 (Introduction), paragraph 4.}
 
@@
 
-\item Please rephrase:
-``Those are kind of attack that usually tackled with the Android Mining Sandbox''
-``For instance, Whaley et al. [18] combine dynamic and static analysis for API mining and so extract interface from software components.''
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} With respect to the first sentence, we decided to remove it, since we realized that it was misleading.
-The second sentence we rephrase like : ``For instance Whaley et al.
-[18] combine dynamic and static analysis for API mining and so infer program behavior based on an example use of a Java class.''}
-
-\vspace{0.2cm}
-
 \item What are sensitive behaviors? ``showed that DroidBot is able to trigger an amount of sensitive behaviors''
@@
 
-\item Please rephrase:
-``From the same authors, another test generator tool for Android, described as Humanoid [23], is a DroidBot evolution and
-presents a proposal that can generate humans like tests inputs, using deep learning.''
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} We rephrase the text at Section 2 (Background and related works) paragraph 7, to better explain Humanoid test generation tool.}
-
-\vspace{0.2cm}
-
-\item Briefly explain the taint analysis
-``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly.
-We reviewed our Section 2 (Background and related works), to better explain taint analysis from paragraph 9.
-We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”.
-To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows.
-}
-
-\vspace{0.2cm}
-
-\item Please explain:
-``FastDroid [28] mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.''
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} To address this issue, we explained better how FastDroid improves the taint analysis efficiency at the last paragraph of Section 2 (Background and related works)}
-
-\vspace{0.2cm}
-
 \item Section 3.1, the help text is not adding much value
@@
 
-{\color{blue}{\bf Answer.} Thanks for raising this point.
-The section 3.1 presented our Benchmark tool DroidXP.
+{\color{blue}{\bf Answer.} The section 3.1 presented our Benchmark tool DroidXP.
 The tool description was important for the paper since it was helpful for our first study conduction.
@@
 It was useful for us and can be very useful for other researchers.
-We
-reviewed the first paragraph of section 3.1 to clarify the importance of DroidXP for our study conduction.}
-
-\vspace{0.2cm}
-
-\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} We reviewed the Section 3 (Study Settings) in full and so, we better explain the methodology. With this update, we removed this sentence.}
+We reviewed the first paragraph of section 3.1 to clarify the importance of DroidXP for our study conduction.
+We included references to DroidXP GitHub repository in the Section 1 (Introduction), since it might be very useful for both researchers and practitioner.}
 
@@
 Actually our purpose was to present the characteristics of malware that have or have not been identified using the mining sandbox approach.
-Our goal is to provide a lower-level intuition about the classes of malware, the mining sandbox approach is good enough, and which ones it fails.
+Our goal is to provide a lower-level intuition about the classes of malware, the mining sandbox approach is effective, and which ones it fails.
 We rephrased the section 4.1 at this point, to clarify this issue about malware discussion.}
-
-\vspace{0.2cm}
-
-\item There are several other typos and grammatical errors.
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} Sorry about these typos and grammar. We revised all the text, and corrected several mistakes that went unnoticed.}
 

### 2021-06-30 letter/responseLetter.tex
last review on the response letter

@@
 
+ {\color{blue}{\bf Answer.} Reviewer 3 suggested several improvements to the article and clarifications.
+Thanks for that.
+We reviewed the current version of the paper to better clarify Section 1 (Introduction) and Section 3 (Study Settings).
+We also present more details about DroidXP, FastDroid and Taint Analysis in Section 2 (Background and Related Work), and we have revised the entire text, correcting several errors that have gone unnoticed.}
+
 \begin{itemize}
-
-\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
-analysis must often assume that additional behaviors are possible than actually would be.''
-Please explain
-
-\vspace{0.2cm}
-
-\item Please rephrase:
-``Those are kind of attack that usually tackled with the Android Mining Sandbox''
-``For instance, Whaley et al. [18] combine dynamic and static analysis for API mining and so extract interface from software components.''
-
-\vspace{0.2cm}
-
-\item Please rephrase:
-``From the same authors, another test generator tool for Android, described as Humanoid [23], is a DroidBot evolution and
-presents a proposal that can generate humans like tests inputs, using deep learning.''
-
-\vspace{0.2cm}
-
-\item Briefly explain the taint analysis
-``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''
-
-\vspace{0.2cm}
-
-\item Please explain:
-``FastDroid [28] mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.''
-
-\vspace{0.2cm}
-
-\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''
-
-\vspace{0.2cm}
-
-\item There are several other typos and grammatical errors.
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} Reviewer 3 suggested several improvements to the article.
-To mitigate the improvements pointed, we reviewed the current version of the paper to better clarify Section 1 (Introduction) and Section 3 (Study Settings).
-We also present more details on FastDroid and Taint Analysis in Section 2 (Background and related work), and we have revised the entire text, correcting several errors that have gone unnoticed.}
-
-\vspace{0.2cm}
 
@@
 
-{\color{blue}{\bf Answer.} In the Section 1 (Introduction) we rephrase paragraphs 4 to better clarify how our paper is an extension of DroidXP paper from SCAM 2020.}
+{\color{blue}{\bf Answer.} Thanks for raising this question. In our previous paper,
+  the DroidXP's evaluation revealed a possible
+overestimation in the performance of the dynamic analysis tools as
+reported in the Bao et al. work~\cite{DBLP:conf/wcre/BaoLL18}---which in the end motivated us to
+conduct the non-exact replication of that study. In this current paper, 
+we extended DroidXP with a new feature to enable / disable the
+static analysis component of DroidFax and integrated an additional
+tool (Joker), which allowed us
+to reproduce the Bao et al. research by means of a set of new experiments
+that reveal the actual performance of the dynamic analysis tools.
+In addition, we investigate in this paper the effect of using
+taint analysis to complement the mining sandbox approach for
+malware identification. In the current version of this paper
+we better explain the paper's extension.}
 
@@
 
-\item Introduction, para 3 is repeating para 2
+\item ``Another approach to rooting'' What is rooting?
 
@@
 
-{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We reviewed Section 1 (Introduction) and removed paragraph 3.}
-
-\vspace{0.2cm}
-
-\item ``We presented and evaluated DroidXP in a conference paper [11]''
-What is DroidXP? It should be introduced to a reader who is not familiar.
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} We agree. To mitigate this issue, we introduced better DroidXP at Section 1 (Introduction), paragraph 4.}
-
-\vspace{0.2cm}
-
-\item Google play - Google Play
-* java - Java / android - Android
-* ``Another approach to rooting''
-What is rooting?
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} Sorry about these typos.
-We corrected all of them.
-Thank one more time.
-With respect to ``rooting'': It's a process performed on Android devices like smartphones or tablets, which allows users of the Android mobile operating system, to execute privileged commands that are typically unavailable at its default configuration.
-The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux.
-We insert a footnote with a link that better explain this term at page 5.\newline
-(https://en.wikipedia.org/wiki/Rooting(Android))
+{\color{blue}{\bf Answer.} Rooting is a process performed on Android devices that allows
+  users of the Android mobile operating system, to execute privileged commands that are typically unavailable.
+  The term comes from the fact that Android system is based on Linux, whose superuser (root) has access to administrative permissions on Linux.
+Since the ``rooting'' term is not well known, we reviewed the text to avoid its use.
+Thanks for your comment.
 }
@@
 
-{\color{blue}{\bf Answer.} Sensitive behaviors at Android context occurs when an Android app functionality can result in accessing or leaking of users sensitive data.
-Example of sensitive behaviors: File accesses and network access.
-We improve the text with this definition at Section 2 (Background and related works), paragraph 7.}
+{\color{blue}{\bf Answer.} We used the term ``sensitive behaviors'' to represent calls to APIs that access private information of an Android user.
+Access to a sensitive API (such as location or address book) might lead to privacy issues and the leakage of confidential data.
+We agree that this terminology is not so precise, so we prefer to use the term ``access to sensitive'' APIs through the paper, instead of sensitive behavior.}
 
@@
 
-\item Section 3.1, the help text is not adding much value
+\item Section 4.1 can be written more concisely. It is not clear what is the value of the malware
+  discussion between pages 13 and 15. It may be removed.
 
@@
 
-{\color{blue}{\bf Answer.} The section 3.1 presented our Benchmark tool DroidXP.
-The tool description was important for the paper since it was helpful for our first study conduction.
-DroidXP helped us to easily integrate different test generation tools, and understand the effect of the static analysis component at each tool.
-It was useful for us and can be very useful for other researchers.
-We reviewed the first paragraph of section 3.1 to clarify the importance of DroidXP for our study conduction.
-We included references to DroidXP GitHub repository in the Section 1 (Introduction), since it might be very useful for both researchers and practitioner.}
-
-\vspace{0.2cm}
-
-\item Section 4.1 can be written more concisely.
-* It is not clear what is the value of the malware discussion between pages 13 and 15. It may be removed.
-
-\vspace{0.2cm}
-
-{\color{blue}{\bf Answer.} Thanks for raising this issue.
-Actually our purpose was to present the characteristics of malware that have or have not been identified using the mining sandbox approach.
-Our goal is to provide a lower-level intuition about the classes of malware, the mining sandbox approach is effective, and which ones it fails.
-We rephrased the section 4.1 at this point, to clarify this issue about malware discussion.}
+{\color{blue}{\bf Answer.}Thanks for raising this issue.
+Actually, our goal in this part of the paper is to characterize the malwares that have or have not been identified using the mining sandbox approach.
+We then provide a lower-level intuition about the classes of malware the mining sandbox approach is effective to identify and which ones it fails.
+We reviewed Section 4.1 to motivate this discussion better.
+Nonetheless, we can remove this part of the paper if the reviewers agree that we should remove it.}
 

### 2021-09-13 background.tex
final revision
last review on the response letter
Remove Krishna comments
change Works to Work
Final review before publication

@@
-\section{Background and related works}
-
-%\kn{This section starts abrupt.
-We should have a line that says what concepts we introduce on a high level.
-Also, I feel "sandbox" itself should be one of the backgrounds and have a textbf after the introductory line.}
+\section{Background and Related Work}
 
@@
 
-\subsection{Mining Android Sandbox}
+\subsection{Mining Android Sandbox}\label{sec:android-sandbox}
 
@@
 Nonetheless, it is also possible to use test generator tools to explore program behavior (dynamic analysis), and thus assist in the task of building sandboxes.
-Regarding test generator tools used for mining Android sandboxes, Jamrozik et al~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
+Regarding test generator tools used for mining Android sandboxes, Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikZ16} proposed DroidMate, a test generation tool that implements a pseudo-random graphical user interface (GUI) exploration strategy, and was the first approach to leverage test generation to extract sandbox rules from apps.
 Li et al.~\cite{DBLP:conf/icse/LiYGC17} proposed DroidBot, a test generator tool that explores sensitive resources access from Android apps, following a model-based exploration strategy.

### 2021-09-13 abstract.tex

@@
 %  \emph{Context.}
-The popularization of the Android platform and the growing number of Android apps that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
+The popularization of the Android platform and the growing number of Android applications (apps) that manage sensitive data turned the Android ecosystem into an attractive target for malicious software.
 For this reason, researchers and practitioners have investigated new approaches to address Android's security issues, including techniques that leverage dynamic analysis to \textit{mine Android sandboxes}.
-The mining sandbox approach consists in running fuzzing test tools into a benign version of the app.
-This exploratory phase records all calls to senstive appis.
-Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the fuzzing tools again in a different version of the app.
+The mining sandbox approach consists in running dynamic analysis tools on a benign version of an Android app.
+This exploratory phase records all calls to sensitive APIs.
+Later, we can use this information to (a) prevent calls to other sensitive APIs (those not recorded in the exploratory phase) or (b) run the dynamic analysis tools again in a different version of the app.
 During this second execution of the fuzzing tools, a warning of possible malicious behavior is raised whenever the new version of the app calls a sensitive API not recorded in the exploratory phase.
 %  \emph{Problem.}
+
 The use of a mining sandbox approach is an effective technique for Android malware analysis, as previous research works revealed.
 Particularly, existing reports present an accuracy of almost 70\% in the identification of malicious behavior using dynamic analysis tools to mine android sandboxes.
-However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static and dynamic analysis for identifying malicious behavior.
-Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools in the task of identifying malicious behavior.
+However, although the use of dynamic analysis for mining Android sandboxes has been investigated before, little is known about the potential benefits of combining static
+analysis with a mining sandbox approach for identifying malicious behavior.
+Accordingly, in this paper we present the results of two studies that investigate the impact of using static analysis to complement the performance of existing dynamic analysis tools tailored for mining Android sandboxes, in the task of identifying malicious behavior.
 %\emph{Method.}
-In the first study we conduct a non-exact replication a previous study that compares the performance of test case generation tools for mining Android sandboxes.
+
+In the first study we conduct a non-exact replication of a previous study (hereafter \blls) that compares the performance of test case generation tools for mining Android sandboxes.
 Differently from the original work, here we isolate the effect of an independent  static analysis component (DroidFax) they used to instrument the Android apps in their experiments.
-This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses positively---through the execution of specific static analysis algorithms.
-In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining Android sandbox approach previously used to identify malicious behavior.
-To this end, we executed the FlowDroid tool to mine the source-sink flows from benign/malign pairs of Android apps used in a previous research work.
+This decision was motivated by the fact that DroidFax could have influenced the efficacy of the dynamic analyses tools positively---through the execution of specific static analysis algorithms DroidFax also implements.
+In our second study, we carried out a new experiment to investigate the efficacy of taint analysis algorithms to complement the mining sandbox approach previously used to identify malicious behavior.
+To this end, we executed the FlowDroid tool to identifying source-sink paths from benign/malign pairs of Android apps used in a previous research work.
 %\emph{Results.}
+
 Our study brings several findings.
-For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the dataset of the work we replicated in this study, leading to an overestimation of the performance of the dynamic analysis tools.
-The results of the second study show that (static) taint analysis is also practical to complement mining Android sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
+For instance, the first study reveals that DroidFax alone (static analysis) can detect 43.75\% of the malwares in the \blls dataset, contributing substantially in the the performance of the dynamic analysis tools in the \blls.
+The results of the second study show that taint analysis is also practical to complement the mining sandboxes approach, with a performance similar to that reached by dynamic analysis tools.
 \end{abstract}
 
-\begin{IEEEkeywords}
-Malware Detection,
-Mining Sandboxes,
-Software Security,
-Android Platform,
-Empirical Studies,
-Static Analysis and Dynamic Analysis
-\end{IEEEkeywords}
+\begin{keyword}
+Malware Detection \sep Mining Sandboxes \sep Android Platform \sep Static Analysis and Dynamic Analysis 
+\end{keyword}
